### 2016-09-22 draft.tex
rename second.tex to draft.tex

%\documentclass[12pt, letterpaper]{article}
%\usepackage{graphicx}
%\usepackage{moreverb}
%\usepackage{mdwlist}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage[hmargin=1in,vmargin=1in]{geometry}
%\usepackage[left=0.9in,top=0.9in,right=0.9in,nohead]{geometry}

%\newcommand{\be}{\begin{equation}}
%\newcommand{\ee}{\end{equation}}
%\newcommand{\bi}{\begin{itemize*}}
%\newcommand{\ei}{\end{itemize*}}
%\newcommand{\bgd}{\begin{gathered}}
%\newcommand{\egd}{\end{gathered}}
%\newcommand{\bgr}{\begin{gather}}
%\newcommand{\edgr}{\end{gather}}
%\newcommand{\mb}{\mathbf}
%\newcommand{\ve}{\varepsilon}
%\newcommand{\real}{\mathbb{R}}
%\newcommand{\de}{\delta}
%  \usepackage{setspace}
%  \doublespacing

%\thispagestyle{empty}

%\begin{document}\title{Inefficient Concessions and Mediation} 
%\author{ Ben Horne}
%To Do : define what is ineffieicncy
%\maketitle

%\section{Abstract}
%We explore a model of bilateral conflict, examining the role of concessions as signals, in addition to being ends in themselves. In doing so, we open up a rationale for mediation: to remove the inefficiencies of signaling in the pre-play round of negotiations. Two parties are engaged in conflict, manifested as the stage game Nash equilibrium of a repeated Prisoner's Dilemma. Each party distrusts the other's willingness to pursue peace, and can indicate its own willingness through costly signaling, i.e. concessions. In resolving this trust issue and attempting to end the conflict, efficient concessions are generally preferred, but optimal signaling can include inefficiency if concessions can later be used against the giving party.  Under such scenarios, a third party mediator can sometimes reduce inefficiency and improve welfare, and we give an explanation for the mechanism that makes mediation effective.
%Two parties are engaged in conflict, and each distrusts the other's willingness to pursue peace. Each can indicate its own interest in peace through costly signaling, or concessions. In certain environments, however, a lack of trust means that optimal concessions are not made, creating inefficiencies in the negotiation that can reduce the possibility of peace. Through a formal model, we explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace. In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
 %   Results show that in bilateral negotiation, parties may prefer to give inefficient concessions due to the other party’s potential power to hurt. Additionally, conditions are shown under which a party be willing to, or even prefer to, give the first concession rather than waiting or giving simultaneously.    ...gain insight into the usefulness of concessions in making peace between warring factions. 
%\newpage

\section{Introduction and motivation} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power. But this is not understood as a problem of private information, as you treat it here, but as one of credible commitment. Its not clear how your types map onto the commitment problem. HOW: THAT TYPES COULD CHANGE OVER TIME?

In negotiations with its neighbors, Israel is hesitant to give certain concessions. The Golan Heights, captured from Syria during the 1967 War, is a particular point of contention in Israeli-Syrian relations. While the Golan Heights does not have the West Bank's historic or religious importance, Israel values it for its highly strategic location. The Golan Heights could be a useful concession, but Israel senses that were she to give over the land, Syria may ultimately use the concession against them. This same hesitancy exists with the West Bank settlements. Many are located on hilltops that could offer strategic military outposts for forces hostile to Israel. When it occasionally abandons settlements, Israel generally dismantles all infrastructure, including water and electricity, and bulldozes the buildings. Although inefficient, this reduces the possibility of those settlements being used against Israeli interests. Without trust, the most efficient concessions cannot be made.

This holds for concessions other than land. Russia is loathe to cede further autonomy to Chechnya, even though independence could hypothetically relieve tensions and reduce violence. If Chechen independence could in fact lead to lowered violence, it is possible that this move would be in Russia's best interest. But the Russians perceive, perhaps correctly, that any move towards autonomy might only give Chechens further leverage against the Kremlin. They also realize that were Chechnya to realize its hopes, other ethnic areas like Tatarstan might be emboldened to demand more. From the Russian perspective, granting the concession of increased autonomy would likely have future costs.

In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions. Mediation has long been understood as a mechanism for reducing mistrust, but in most of the published literature on international conflict mediation lacks a rigorous theoretical framework.

This paper has three parts. First, it explores the role of costly concessions in a game theoretic framework, evoking a two-sided version of Spence signaling (1973). Second, after considering existing explanations for inefficient concessions, it proposes a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace. Finally, this paper uses a mechanism design framework to model a third party's role in bringing about more efficient concessions. Many scholars contend that mediators with enforcement capabilities can help to resolve conflict; this formal analysis provides an explanation for why enforcement is effective.

\section{Literature review and model introduction}

While an integral part of conflict literature, concessions have not been adequately addressed by theoretical research. The broader literature that attempts to model war has included concessions as part of bargaining, but has not explicitly considered the role of concessions in achieving peace. Schelling's \emph{Arms and Influence} (1966) modeled war with a game theoretic framework, and Powell (1999) has also defended the use of modeling in understanding war. Fearon (1995), Powell (1996a and 1996b, 2006) and others consider war to be a bargaining failure, caused by commitment problems and asymmetric information. In these models war can be averted by splitting the pie (i.e. the disputed territory) in a way acceptable to both parties. Concessions are modeled as offering part of the pie to the other party. %LAKE: You need to situation what you’re doing in the bargaining literature and relate your model to its principal results. WAR IS WELL ESTABLISHED AS BARGAINING!!!

The literature often views conflicts as bargaining over assets that confer future power. In these cases, a lack of credible commitment can create a holdup problem. A lack of trust prevents the high level of interaction that would otherwise be optimal.

We will approach the commitment problem  through this same general understanding, but modeling a party's willingness to cooperate as private information. A high type is willing to cooperate; a low type has incentives to not cooperate. These types map onto the commitment problem, with a high type one who is able to commit in certain scenarios. A low type, though perhaps willing, is unable to do so. A low type may posture like the high type, but lacks the political muscle or will to make the necessary concessions for peace. Democratic leaders may more often be high types because they are less likely to face coups or other hostilities in reaction to short term decisions. This is not always the case, however. Mahmous Abbas may be a low type, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population. %MORE commitment literature needs to be cited here.

Third party involvement is ubiquitious in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.  Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others insist that a correct analysis finds mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al. 2006).  But the term mediation encompasses a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation suspect. The type of mediation affects the negotiation outcome (Bercovitch 2000; Beardsley et al. 2006) and timing is important (Greig 2005a). It is essential to focus more precisely on the specific actions and environments that make use of a certain type of mediation, which is how we approach the question. This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has certain manipulative abilities---as defined below.

Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006). In this paper, parties are in conflict and can benefit from seeking mediation in order to overcome mistrust. Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008). Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010). These empirical results, while interesting, have generally lacked strong theoretical foundations. Mediation is used, but why actors use it is not well understood. This paper helps to fill this gap by explaining at least one of meditation's roles. %NEED TO EDIT THIS PARAGRAPH- WHICH EMPIRICAL RESULT!!!!!(S)

Concessions form the centerpiece of the GRIT (graduated and reciprocated initiatives in tension reduction) theory in the psychological literature (Osgood 1962) and have shown ample success in lab settings. Komorita (1973) conducts lab experiments using a repeated Prisoner's Dilemma similar to the setup in our paper and finds costly conciliatory acts (concessions) to be useful in promoting cooperation. De Dreu (1995) likewise uses a lab setting to experiment with concessions and conflict.  %de dreu bases experiments on shelling 60 and bacharach and lawler 81/ lawler 92 about deterrance, the shelling conflict spiral was not fully rejected, but the alternative of deterrance was supported
In addition to concessions, De Dreu also reports laboratory results on mediation; he concludes that a weaker mediator should work with promises while a more powerful one can be effective with threats.  Larson (1988) and others have applied this framework to political science questions. On the theoretical side, Filson and Werner (2007) use a bargaining setup to explore the sensitivities of costs compared to the sensitivity of giving concessions. 
%LAKE: The psychological literature as applied in political science spent a lot of time in the 1970s and 1980s focusing on Graduated Reductions in Tensions (GRIT) as a form of confidence building. See Debbie Larson’s work (she’s at Poli Sci, UCLA, I don’t have the cites handy). This is clearly relevant to your discussion of the laboratory experiments on p.3. BH WATSON'S STARTING SMALL COULD BE RELEVANT HERE

This paper will explore the role of concessions as signals, and not only as ends in themselves. Concessions may play either role -- or both -- in conflict resolution. If concessions are used solely for signaling, this can be considered inefficient as value can be lost. We will examine cases where concessions have material value, signaling value, and both.

In analyzing both the signaling and material value of concessions, an extensive literature on gift giving is particularly helpful. Like concessions, costly gifts have been shown to have a valuable role in relationship building. And the gift giving literature, more so than the concessions literature, focuses specifically on the issue of efficiency. Inefficiency is defined for the purposes of this paper as some sort of money burning: giving a gift or concession that is more costly to the giver than it is valuable to the recipient, that is, using a concession as a signal and not taking advantage of its full inherent value. It is not problematic for giving to also have a signaling component, but it is ideal if the full value of the gift can be transferred. %The theoretical basis for this has its roots in the economics literature on gift giving.  %this needs lots of work and maybe a cite- use def of "inefficiency" in the camerer paper or others

Gift giving as a whole is inefficient (Waldfogel 2009); it has been estimated that Christmas gift-giving is only 75 percent efficient, meaning that the average gift is valued at 75 cents of the dollar that is spent on it (Waldfogel 1993). But merely looking at aggregate numbers blurs together many possible reasons for gift giving. It has even been theorized that buying something that the receiver would not buy himself is an inherent component of gift giving (Thaler 1985). Often, inefficient gifts occur in the formative stages of relationships or in immature relationships (Camerer 1988). Gifts given in established relationships, such as wedding presents or spousal gifts, are more likely to be cash gifts or efficient gifts that are specifically requested or selected from a registry. Since inefficient gift giving is more likely involved in nascent relationships and partnerships, it is natural to suppose that inefficient gifts play a signaling role in addition to the material value of transferring the gift's inherent worth. %Several situations have been proposed where inefficient gifts can help keep types separated in partnership models. However the current literature on inefficiency in gift giving relies on unrealistic special cases that do not apply in more general partnership formation environments.

In efforts to explain the existence of gift giving,  Camerer (1988) and Van de Ven (2000) give several anthropological explanations for inefficiency. Amongst these explanations are altruism, social mores, and egoism. But the most relevant explanation for the field of international relations is that gift giving is strategic. Camerer also creates a theoretical model using mechanism design that models gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types. This strategic giving of gifts in societies looks very much like the strategic giving of concessions to remedy conflict situations. When modeled game theoretically, these different environments look even more similar.

Camerer's model includes players that have one period to signal before they decide whether to partner. There are two types, high types and low types, and a separating equilibrium is characterized by a threshold gift that is necessary for high types to reveal themselves while low types do not send a gift (or send a gift of  zero cost). Two high types who have just received each other's gifts will then choose to create a partnership with a positive payoff; other combinations will not find it economical to form a partnership.

Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts. In order to explain inefficiency, Camerer adds in an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts. If types separate in the pre-play period with low types not being willing to pay, high types are saved the cost of sending a signal to low types in the main game.  High types would, in some parameterizations, be given incentives to give inefficient equilibrium gifts in the main game in order to lower the low types' expected payoff of playing to below the pay-to-play fee. Such an action can keep out the low types and this can raise the expected payoff for a high type by saving on the gifts given. %While pre-play communication can lead to inefficient gift-giving, it is not realistic to think that partnership formation generally has this structure, therefore while Camerer's explanation is theoretically sound, it lacks the ability to be a general explanation for inefficient gifts.

Several other papers essentially use Camerer's theoretical explanation for inefficient gifts.  Iannaccone (1992), Rabin (1993),  Kranton (1996) and Carmichael and MacLeod (1997) all use a similar explanation with various modifications to the model. Carmichael and MacLeod (1997) extend the argument to long time frames, arguing that inefficient gifts might arise evolutionarily by keeping ``parasite'' numbers low.  In an environment with repeated opportunities for concessions Watson (1996, 1999) is able to show that a strong relationship can be reached by starting with small gifts and increasing their size as the relationship becomes more committed. Kranton (1996) applies a similar concept to a model resembling Camerer (1988). See Van de Ven (2000) for an analysis of how these papers relate to each other.

The second major way to explain inefficient gifts is expressed in Prendergast and Stole (2001). The authors have a result that explains inefficient gift giving by modeling utility of matching--if players are of a like mindset they get an extra benefit; they are willing to take the risk of giving the wrong gift. This explanation has less applications to questions of conflict.

% However, there are some inadequacies in the model. In their model, agents derive utility from giving and receiving the ``correct" gift because it signals that a friendship is true. There are two types of receivers, A and B. Givers have a prior belief along the A-B continuum that must remain unknown to receivers for the model to work. Givers can choose to give gift A, gift B, or cash. The technological constraint of only two types/ gifts is crucial to the inefficiency result as well in the sense that the gift is in fact an imprecise signal of the giver's belief. Givers' utility includes altruism and a match payoff. This match payoff means players might be willing to risk giving the wrong gift- hence inefficiency. Altruism (wanting recipients to be happy) keeps a giver from giving a gift if his prior is ambiguous enough. Receivers' utility derives from a match payoff as well as the inherent utility of the gift. One limitation of the model is that if (realistic) cheap talk were allowed in addition to the gift, cash could be sent with a note telling which gift the sender believes is correct to ensure efficiency. Receivers do not tell their type because that would sacrifice the match payoff. The authors ``solve" this issue for givers by claiming bought gifts yield a higher payoff than cash with a note. This last explanation works mathematically but is not a general theory- essentially they just argue ``people like gifts."

While these several explanations for inefficiency are interesting, we propose another theoretical contribution to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle. The basic formulation of our model is most similar to Camerer (1988) who also uses mechanism design; our model is an expansion of Camerer's analysis. The model can achieve the Camerer result and another similar to that of Prendergast and Stole (2001) but adds a very different explanation for inefficiency. %An extension at the end of our paper compares simultaneous versus sequential concessions in a bilateral negotiation environment. The theory yields results about the effectiveness of different types of enforcement in various circumstances. 
%Since neither the models exemplified by Camerer nor Prendergast and Stole uses a truly general formulation to yield inefficient gift giving % in a one-shot setting,
This paper expands upon the existing literature by generalizing the analysis using mechanism design theory more extensively than has been done thus far. %The analysis for this paper is more extensive than any of the published papers mentioned and shows where mechanisms can and cannot improve upon the benchmark bilateral results. 
The basic model is a costly signaling model, at its root similar to ideas in Spence (1973) and subsequent papers. See Connelly et al. (2011) for a review of the costly signaling literature. In essence, the model shows that if concessions can be later used against the party that gives, then giving inefficient concessions can be in their best interest. While our model is tailored to an international relations setting, the mathematical explanation for inefficient giving of concessions may be more broadly applicable.

\section{Formal model description} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING. EMPHASIZE SCENARION (EGYPT USRAEL ETC) THAT ARE BETTER TO MODEL WITH Our MODEL. IT CAN ALSO BE THOUGHT OF AS REDUCED FORM OF A BARGAINING MOEL, BUT IT DOES NOT NEED TO BE! NEED TO GIVE EXAMPLES WHERE Our MODEL IS BETTER THAN BARGAINING- EXAMPLES. WHEN TRUST IS AN ISSUE (PUT THIS IN THE TRUST SECTION)
%Need to add risk aversion in MAIN TEXT

Countries\footnote{Players will be referred to as countries, though it could also be appropriate to think of players as intra-state actors, as in a civil war. } are of two possible types, high and low. A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$. $\delta_h >\delta_l$ and both $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2. The type distinction, as explained later in the model, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict with the other specific country. It should not be thought of as an inherent quality of a country, but rather an interactive parameter. Thus it is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}

 The probability of nature selecting high type for a given player is $p$. The probability of nature selecting low type is $1-p$.\footnote{Note that parameters are symmetric across countries, as is consistent with the literature. Qualititative results do not depend on this being the case, and equilibria and equilibrium concessions can easily be calculated with asymmetric parameters between players.}  Countries are aware of their own type, but not the type of the other country.  Similar scenarios have been modeled as credible commitment problems in the bargaining literature. Our model can be thought of as a reduced form bargaining model, but it can also be considered somewhat differently -- when trust is the issue to be solved, there are several solutions to conflict. Concessions are one way in which countries can signal their commitment.  By modeling the conflict in such a way we can also gain insight from how a third party can affect trust issues inherent to the conflict. %might want to cite fearon and bargaining lit here
%might want to eventually add the stochastic type switch- or at least talk about how that changes analysis

In period 0, countries 1 and 2 simultaneously give costly concessions $g_1$ and $g_2$ $\in \mathbb{R} \geq 0$. Concessions are given at cost $C(g_i)$ and benefit the recipient $g_i$, where $i\in\left\{l,h\right\}$. For simplicity, let us initially assume $C(g_i)= g_i$. We will relax this assumption later.

Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs represented below. While not a good representation of all-out war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict, not a zero-sum short term war. In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so. The critical results of this paper do not depend on a prisoner's dilemma structure; they require only that a better result can be achieved through trust or credible commitment. Thus, a stag hunt or other game structures are also possible. The Prisoner's Dilemma is used because of its wide exposure in the literature.\footnote{This payoff matrix does not distinguish between civil and interstate conflict, though in practice the effects on the payoffs might indeed have a different structure in the different cases.} %cite difference from fearon here?
%LAKE More generally, the problem of war, on which you implicitly focus, is now understood as a pure bargaining game (i.e., zero sum). This is not well represented by the PD. You need to make the link – or differentiate – what you’re doing here from the Fearon-Powell models to which you appeal.

The choice of ``Trust'' or ``Fight'' will be referred to as the county's stage game action.

\captionof{table}{Stage Game Payoffs}
\begin{center}
\begin{tabular}{|l|c|c|}
  \hline      & Trust & Fight \\ \hline
	 Trust& T, T& -D, T+W \\ \hline
	Fight & T+W,-D& W-D, W-D \\ \hline
\end{tabular}
\end{center}

$T\geq0$: Benefit from the other country playing Trust

$W\geq0$: Additional benefit from playing Fight

$D\geq0$: Damages due to the other country playing Fight

Assume $T>W-D$. 
 Payoffs for a country are the sum the stage game payoffs, discounted by $\delta.$ For example, if both parties play ``Trust'' in every period, the payoff for a player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$ Parameters are common knowledge with the exception of $\delta_i$, which is country i's private information. %Countries' utility is calculated as ex interim utility (Holmstrom and Myerson 1983),  i.e. when countries know their own type but not that of the other country. Depending on parameters, multiple equilibria are often possible. 
The measure of social welfare, and thus the determinant of the optimal equilibrium, will be the sum of participating high types' expected utilities.

 If $\delta$ is high enough for both countries, the cooperative outcome of ``Peace'' (Trust, Trust) can be sustained with a grim trigger punishment threat. The assumption $T>W-D$ ensures that payoffs from Peace (even if it cannot be held as an equilibrium) are higher than for ``War'' (Fight, Fight).\footnote{A country whose payoffs violate this assumption is of a special ``very low'' type that will be considered later in the analysis.}
For a Peace equilibrium to exist, $\delta$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
The threshold $\delta^*$ needed is \be
 \delta^* = \frac{W}{T+D}
 \ee
Assume $\delta_h> \delta^*$ and $\delta_l < \delta^*$.

\section{Analysis of benchmark cases }
%examples!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

When countries are faced with doubts about each other's motives, they have several options of how to proceed. There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor for the high type ($\delta_h$) exceeds the cutoff found in expression (1), there are many types of equilibria; consider for instance oscillating every other period between Peace and War with a grim trigger War threat. In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios. These are also always payoff dominated by at least one of the other equilibria discussed, so are not attractive.} A thorough analysis of the different types of equilibria, as well as all proofs for this section, can be found in the appendix. 
\\
\\
{\bf \emph{Pooling equilibrium}\\}
\vskip-.2in
In the \emph{pooling equilibrium}, both countries do not give concessions in period 0, then always play Fight in every period beginning with period 1. 
Countries continue to doubt, doing nothing to bridge the credibility gap, and thus not cooperating. This is a \emph{pooling equilibrium}, and is likely to happen when countries are in long-set patterns of distrust. Active fighting is not necessary; remaining outside of a state of peace is all that is required.  See Lemma 1 and Lemma 2 in the appendix for a formal characterization of this type of equilibrium.

Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward. While both sides posture that they want peace, and while there has been some lessening of tensions, very few concrete actions have been taken that move the sides toward settlement. This conflict is a stalemate.

Sri Lanka is another example. While the government has finally won the war of secession, it still refuses to address grievances of the minorities and leaves the conflict still unresolved. Other prominent examples of this pooling equilibrium include Israel and its neighbors, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts. The mistrust of the other party is perhaps justified- indeed if one party did take the first step and give a concession first, they may indeed be taken advantage of.

In any case, these long lasting stalemates are the types of conflict which are most appropriate for mediator involvement. Without a third party, there is little hope of overcoming mistrust. In some sense then, these are the cases that are most interesting because the international community might play a positive role. A mediator will be added to the model later to illustrate exactly how this role can be played. 
\\
\\
{\bf \emph{Separating without concessions}\\}
\vskip-.2in
The other two equilibria are separating equilibria in which low types and high types have different strategies. In a \emph{no-concessions separating equilibrium}, no concessions are given by either type in period 0. In period 1, high types play Trust while low types play Fight. So long as there are two high types, as revealed by their period 1 play, both countries continue to play Trust in all following periods. Otherwise, both countries play Fight in all following periods. 
\\
\\
{\bf Theorem 1:} The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.\\
\emph{Proof}: See appendix.
\\
\\
In this equilibrium two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.  This is representative of a case where countries have suspicions about each other, but proceed anyway.

Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way. Certain relationships between the USA and countries that its wikileaks alienated- such as Italy- would be an example. Italy essentially laughed off the criticisms and reassured the USA of its commitment to their relationship. Warsaw pact countries generally allowed the USSR similar leeway; it was better to have occasionally imperfect cooperation than conflict. Certain things can disrupt trust without completely derailing actions.

Of course, it is possible that in a \emph{no-concessions separating equilibrium} one country can take advantage of the other.  It can be argued that indeed that did happen in the Warsaw pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.

Though it will not be modeled here, a stochastic component -- when countries occasionally unilaterally defect -- can explain why powerful countries like the USSR more often ``get away'' with cheating: the payoffs to the relationship are not symmetric. Losing the USA or USSR as an ally is much more devastating for a satellite country than vise versa, therefore big countries can have their alliances and take advantage of them too.
\\
\\
{\bf \emph{Separating through concessions}\\}
\vskip-.2in
The third option is for distrustful countries to use concessions as a way of building trust. In the model this is the \emph{concessions separating equilibrium}. This equilibrium is costly, but can be worth the investment if the other country also cooperates. It is also not as risky as cooperating without concessions, as in the previous equilibrium. The concessions are given before more substantive actions, thus concessions are a costly signal that the other country is serious about cooperating. Most agreements come with concessions, and in many cases, though not all, they are used as signals. The goal is to use this option to avoid continual distrust; a mediator is one way of enabling this solution.

In the \emph{concessions separating equilibrium}, low types do not give concessions while high types give a concession of a certain size in period 0. If both countries receive concessions, they know the other is a high type and both play Trust in subsequent periods. Otherwise, if both players do not receive concessions, there is at least one low type so both countries play Fight in subsequent periods.

The analysis is conducted with standard Incentive Compatibility and Individual Rationality constraints. Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever played forever if Fight is played by any party in any round. This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace. Because we look at grim trigger punishments, there are essentially only 4 equilibrium combinations of strategies after concessions are given:
1) Both countries play Trust always, 
2) Both play Fight always, 
3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.

Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior. Let $X_{ij}$ represent the sum of discounted payoffs for country i where subscripts represent first round strategies of that country. If both countries play T in round 1, the corresponding payoff to country i is represented as $ X_{TT}=\frac {T}{1- \delta_i}$. Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$. Note that because types have different discount rates, these quantities are different by type, and when ambiguous will be superscripted to indicate the type (e.g. $X_{FT}^h$ represents the high type). Note that because of the signaling value of the concessions given in period 0, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium (both play Trust if there were two high signals; otherwise both play Fight). $X_{FT}$ and $X_{TF}$ are still necessary for calculating the equilibrium concession $g_h$.%might make the first one TF for clarity
\\
\\
{\bf \emph{Lemma 3:}} In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium. \\
\emph{Proof:} See appendix.\\
\\
{\bf Theorem 2:} In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.\\
\emph{Proof:} See appendix.

This smallest concession is denoted $g_h^*$ and is calculated in equation (11) in the appendix to be $p(T+D).$

In general, a high probability of a high type will make this no-concessions separating equilibrium very attractive. Under low $p$, high types are better off choosing the pooling equilibrium.

Concessions separating equilibria are a way for countries to solve their disputes. By giving costly concessions, they signal their intentions in a way that a partner unwilling to make peace would not be willing to signal.  A mediator can sometimes make this a possibility, as will be shown in section 7, but this equilibrium is also achievable bilaterally in some cases.

One example of such an equilibrium includes Israel and Egypt at the Camp David Accords. Both parties gave concessions (Israel a material land concession and Egypt diplomatic recognition of Israel) that signaled their willingness to end the stalemate that had characterized the previous five years. Of course this result depended on Carter's use of mediation techniques, including use of manipulative mediation -- a concept we will explore in section 7 below.

%another example

\section{Inefficiency and concessions} % Lake says combine this from the start and allow inefficiency
We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give. For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country. The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.

In the model, countries choose a scalar $e$ to multiply by their given concession $g$. $0 \leq e \leq 1$. As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$. The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value. These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1. The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix. \\
\\
{\bf Theorem 3:} It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium. \\
\emph{Proof:}
The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types. However, the expected separation utilities under this game are now
\be
U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
\ee
and
\be
U_l=X_{FF}+peg_h 
\ee
 $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function. It also holds for any monotone cost function.}$\blacksquare$

We now model concessions to potentially have real material help or harm to the giver. The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society. The former hurts the giver of the concessions in war; the latter helps the giver in peace. The Golan heights is such an example: if Syria is an ally of Israel, the Golan Heights is a reasonable concession to make, but if Syria later turns out to betray a trust, surrender of the strategic land would be disastrous for Israel. %Another example is ADD more examples

Allow $T,W$ and $D$ to be functions $T(\cdot),W(\cdot)$ and $D(\cdot)$. Payoffs depend on arguments $s_i$, the size of country i's civil society and $m_i$, the size of country i's military. $s_i$ and $m_i$ are exogenous.

In period 0, after receiving his concession, a country makes the decision to allocate it between military and civil society. $\alpha_i$ is the portion of his received concession that country i chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country i dedicates to military buildup. This decision is a simple optimization problem for each country. Parameters are common knowledge so the result of this decision is well known should the country's type be known. Concessions are immediately converted into civil society or military gifts and incorporated into payoff functions. 
 $C_h(\cdot)=C_l(\cdot)=1$ as earlier in the model description. Periods 1 to $\infty$ are as before but with the following stage game payoffs:
\newpage
\captionof{table}{Modified Stage Game Payoffs}
\begin{center}

\begin{tabular}{|l|c|c|}
  \hline      & Trust & Fight \\ \hline
	 Trust& \small$T(s_2+\alpha_2g_1)$, & \small$-D(m_2+(1-\alpha_2)g_1),$ \\
  & \small$T(s_1+\alpha_1g_2)$ & \small$T(s_1+\alpha_1g_2)  +W(m_2+(1-\alpha_2)g_1) $\\ \hline
	Fight & \small$T(s_2+\alpha_2g_1)+W(m_1+(1-\alpha_1)g_2),$& \small$W(m_1+(1-\alpha_1)g_2)-D(m_2+(1-\alpha_2)g_1),$ \\
	 & \small$-D(m_1+(1-\alpha_1)g_2) $ & \small$W(m_2+(1-\alpha_2)g_1)-D(m_1+(1-\alpha_1)g_2)$ \\ \hline
\end{tabular}
\end{center}
\vskip.1in
{\bf Theorem 4:} Under some parameters, the optimal equilibrium uses inefficient concessions. \\
 \emph{Proof}:   Because it is relatively complicated to calculate equilibrium concessions in the general case, a slight simplification of the general model will be made for proof of inefficient concessions. Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments. Also assume that $s_1=s_2=m_1=m_2=1.$ Because of linearity, equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$. Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results. 
The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(T+D)}{1-pT}$.
Under an equilibrium with purely inefficient concessions $(e=0)$, the minimum separating concession would be $g'=p(T+D)$.

Assuming gifts must be non-negative, $g^*$ will always be greater than $g'$. This is not enough to show that inefficient concessions are sometimes optimal. To show this, consider high type equilibrium utility and assume that the high types are perfectly patient (that is, $\de_h=1$):  
\be
U_h=pT(1+eg)+peg+(1-p)(W-D(1+eg))\footnote{Note the gift payment does not enter here: the current period is weighted $1-\de$, which is 0, while the future is weighted $\de=1$.}
\ee

Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession needs to be determined by comparing the utility under each. For low $p$, the term $(1-p)(W-D(1+eg))$ dominates, showing that clearly, as low an $e$ as possible is best, so $e=0$, that is, complete inefficiency is the best possible equilibrium efficiency level. It is thus rational under such parameters for inefficient gifts to be given as concessions. $\blacksquare$ 
%need to also write constraints for high type IC to be satisfied, or appeal to forward induction
%? And, a mechanism improves upon inefficiency because it allows a high types to only give a gift to other high types, thus decreasing their costs and still giving the same equilibrium matches.  . Does this rely on varied costs of giving- i.e with same costs can a mechanism still improve? 
%note damages due to alpha can be understood as political losses/ embarrassment of failure to make peace as much as they can be seen as military damages.
%{\bf Theorem 12:}\\  
%When concessions are inefficient, $M$ can still improve over bilateral negotiation. \\
% \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong.

This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, the desired inefficiency of  pre-play communication can also be found in our model. With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly. In Prendergast and Stole the two types are equal except in labeling; in our model, high types and low types are used so there is an incentive for low types to try to pose as high types. Aside from this difference, essentially the same result is found: if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a ay to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.

\section{Mediation}
All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator which will be modeled as a mechanism.  Mediation has been studied to some degree in the formal literature and has most recently been modeled using mechanism design. Applying mechanism design to mediation has been used, to date, by Fey and Ramsay (2008, 2010 and 2011), Bester and Warneryd (2006) and Horner et. al. (2010).

Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz, 2002), much of the literature has focused on self-enforcing mechanisms. If however a credible third party does exist, then results beyond self enforcing agreements can be relevant.  A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997). We will now introduce a mediator who does both.

The model setup is as before, but instead of parties being free to give whatever concession they want, the mediator solicits type reports and then enforces incentive compatible concessions. This mediator wil be modeled as a mechanism $M$.

$M$ inputs the reports of types $t_1$ and $t_2$ and outputs the required concessions $g_1$ and $g_2$. Formally, $ M:(t_1,t_2)\rightarrow( g_1(\cdot), g_2(\cdot))$.  The countries are bound to send the mandated concessions. The benchmark case requires the countries to send the same concession to both types, since types are private information.  $M$ can differentiate based on recipient's type. Otherwise, the setup is identical to the benchmark case.

Welfare is again considered as the sum of the high type utilities. Qualitatively, similar results would hold if we also included low types in the analysis with weighting based on $p$. In the analysis, incentive compatibility and individual rationality constraints must be satisfied. The revelation principle is used to attain truthful self-identification (Myerson 1979). For mediation to be useful, $C_l(\cdot)$ needs to be pointwise greater than $C_h(\cdot)$, and we will assume this. This means that a low type is not identical to a high type, and indeed bears greater costs for peaceful actions. This can be thought of as a leader who must explain peace to his people. If the people want to make peace with the rival, posturing for peace is not costly for the leader. But if the people do not want to make peace with the rival, the leader loses credibility by outwardly touting peace. Therefore taking a peaceful action is more costly, and perhaps even impossible. This low type leader can bluff in the bilateral setting but not, as we will see, when a mediator is present. 
\\
\\
{\bf Theorem 5:} A mediator can be used to eliminate inefficient concessions. \\
\emph{Proof:}  $C_l(\cdot)> C_h(\cdot)$ as per the assumption above.  The low type IC ($pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$). Under $M$, the low type IC can bind without having high types give a concession to low types. The equilibrium separating gift $g^{*M}$ will be larger than $g^*$ in this case, specifically 
\be
g^{*M}= \frac{p(X_{FT}^l-X_{FF}^l)}{1-p}
\ee
High type utility under $M$ is 
\be
U_h^M= pX_{TT}+(1-p)X_{FF}
\ee
because high types exchange concessions of the same value. $U_h^M>U_h^*$. Note that no additional wealth is created by $M$, but less is transferred to low types, and welfare is defined as high-type utility.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$}  $\blacksquare$

Since the low type IC constraint binds, the only way which a mechanism can improve upon the benchmark case is by having asymmetric costs of giving for the types. As per Theorem 4, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types. If costs are disparate, under certain parameters the mediator can mandate concessions only between declared high types. This means there is no longer a need for inefficient concessions since concessions will never be used against the giver. Thus, a mediator is able to remove inefficiency in concession giving and bring willing parties to the table to give the gifts necessary to achieve peace.

The improvements by the mediator here do not rely on the mediator's private information as in the models of Kydd (2003), Rauchhaus (2006) and Smith and Stam (2003). Therefore the mediator's preferences need not be a huge factor in her participation. So long as the costs are small enough to be worth her participation the mediator can effectively enter and assist in solving the conflict.

The value of truth telling by the mediator has been brought up in the literature. Kydd (2003) studies bias in mediation and how a mediator can credibly communicate information to the parties. Conversely Horner et al. (2010) rely on the mediator to ``hoard'' information in order to be able to improve on unmediated interaction. In our model, a successful mediator relies on the parties trusting her. However, here the mediator had no incentive to lie: lying can only potentially hurt the high types, the only type who the mediatorcan possibly help.

\section{Conclusion}
In states of perpetual conflict, concessions have been shown in the literature to ease distrust. Our paper shows a mechanism by which this might work. In our model's setup, there are three potential types of equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which is essentially a state of war for all types. Second, if prior trust is sufficiently high, a no-concessions pooling equilibrium exists where high types trust in the first period and can maintain that trust if both are high types. Third, the most intuitive or realistic type of equilibrium, a concessions giving separating equilibrium exists where high types offer concessions to eliminate the distrust.

While parties generally are better off when concessions are efficient, we have shown that inefficiency may be useful. In particular, if concessions may be used for further material harm against the giver, it may be better to give inefficient concessions. This explanation captures the hesitancy of nations to fully engage in moving forward with a peace process when there is mutual distrust. %As previously shown in the literature, if parties are trying to enter a club or alliance, it may be necessary to give inefficient concessions. %Our model can achieve that result, first shown in Camerer (1988), that inefficiency plays a role in pre-play communication and can be used to separate out unwanted partners. Our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred. To achieve this countries must have preferences over the types of the recipients of their concessions. If there is a regret of giving a concession to a country who does not pan out to be an ally, then inefficiency can be preferred. While this is a relatively behavioral or emotional explanation for interpersonal gift giving, it might hold some weight in an international political arena. This flavor, of matching types, is similar in nature to Prendergast and Stole, who use two different, though equal types, while our explanation uses a high and a low type.
%I have further shown that

However, there must be a caveat about modeling concessions. The initial thought would be that it is somewhat abstract to model a concession as a number. However it is not necessarily insufficient as often times concessions really do come in sizes, for example the number of prisoners released, an amount of land ceded, or an amount of time given to carry out actions. So the magnitude of concessions can indeed vary. But while magnitudes vary, the real caveat is that the nature of the concessions is sometimes non-negotiable. For instance if one country demands release of hostages, it is not possible-or at least not realistic- for the other country to give the equivalent value in land, cash or weapons.

In practice, in ``sons of the soil'' conflicts, concessions are indivisible (Walter 2002), therefore if inefficient concessions need to be given, no concessions will be in fact given as an inefficient concession is an impossibility. The full value is the only concession worth making because it is the only one that will be accepted. Inefficient concessions can have the same signaling value, but unless signaling is the only facet of a concession that is valued, this is not enough. Therefore when we think about concessions, we should think about their nature as being fixed. With this in mind, we can then accurately consider whether concessions are of sufficient size. These observations do not undermine the model.  Countries may prefer to give inefficient concessions; they do not necessarily prefer to receive them.

The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy this inefficiency if she is trusted. One result of this formal exposition is to show the mechanisms through which a mediator can help. Since the mediator eliminates inefficient concessions, the observation that inefficient concession may not do the trick only further indicates the value of a mediator even more.
%our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred.

While this model uses manipulative mediation, which is indeed used in resolving conflicts, the usefulness of mediation relies on perfect trust of the mediator. Such an all-powerful mediator is a strong assumption, and while useful as a benchmark, it is unlikely to exist in most scenarios. It would be useful as a further exercise to examine the effectiveness of mediators with different strengths of enforcement capabilities.

While it is an important theoretical result to show how a mediator can help conflict situations, it should also be noted that mediation is not free, at least to the providing (third) party. Therefore, the inefficiencies borne by the inefficient concessions and/ or by the ongoing conflict must not be outweighed by the cost of providing the mediation. If the model accurately captures the costs, the expected savings of mediation can be calculated and therefore the usefulness of mediation in a specific scenario can be determined. This will allow the mediator to analyze whether her involvement is worthwhile.

This paper succeeds in showing a role for inefficient concessions, and shows how a mediator can remedy this situation. Opportunities for further research clearly include looking at the roles of different types of mediation. Because of the many humanitarian, security and diplomatic implications of this work, both deeper and broader analysis is required.
%This said, if the paper is really about mediation, then the mediator needs more scrutiny. What are the mediator’s incentives? Why should he reveal truthfully what the parties tell him? It would seem simple enough to make the mediator part of the game, with an payment function that is a fraction of the surplus from eliminating the inefficiency. This leads to interesting implications. Given some cost to the mediator, they will be more likely to volunteer when e* is large, etc. But treating the mediator as a deus ex machina leaves the current model incomplete.

\section{Appendix}

\noindent {\bf \emph{Pooling equilibrium}\\}
\emph{Lemma 1:} From period 1 on, playing fight in all periods regardless of beliefs constitutes an equilibrium strategy of the continuation game for both types. \\
\emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight. Thus the stage game equilibrium is (Fight, Fight) and in any repeated game, playing the stage game equilibrium in each period is an equilibrium of the entire game. $\blacksquare$\\
\\
\emph{Lemma 2:} From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.\\
\emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight. Playing Trust is only possible in equilibrium where there is punishment for playing Fight. The minimax payoff is $W-D$, and punishing a country by playing it every period is the worst possible punishment, hence it gives the greatest potential for a country to be given incentives to play Trust. Low types, with $\delta_l < \delta^*$ achieve a higher payoff deviation from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.  $\blacksquare$\\

One high type equilibrium strategy is to pool with the low types and always play Fight. If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, Lemma 2 shows that the low-type of player $i$ best responds by always playing Fight. The high-type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior by Lemma 1. Given that the stage-game equilibrium will be (Fight,Fight), there is no incentive to give a concession in period 0 because concessions are costly and signaling one's type can give no benefit in this equilibrium. Types pool by never giving concessions and always playing Fight. 
 %add intro about the 3 types of equilibria. 
 \\
 \\
 {\bf \emph{Separating without concessions}}

 Let us examine the conditions for a separating equilibrium held in place by a grim trigger.\\
 \\
{\bf Theorem 1:} The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}$.\\
 \emph{Proof}:
Countries with the equilibrium strategy to play Trust in the first round reveal themselves as a high type as per Lemma 2. This will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from deviating against someone playing the pooling (always Fight) strategy. If both countries play Trust in a period, a Peace equilibrium takes place and both countries continue to play peace in every period with the grim trigger threat of the War equilibrium. Low types play Fight in the first period, so a high type that observed Fight being played would respond by playing Fight in period 2 and in all future periods.  If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, a high type will be given incentives to play Trust in the first round rather than Fight. Formally, to play Trust, the following must be satisfied:%Make clearer language!!!!!!!
%FUTURE WORK ON DELY OF PEACE- IF PEACE WILL E THERE, YOU MIGHT BE VERY RISK AVERSE TO GETTING SCREWED BY THE LOW TYPE SO KEEP PUTTING OFF THE RISKY FIRST TRUST ROUND
\be
p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )\geq p (T + W + \frac{\de_h}{1-\de_h}(W-D)) +(1-p)\frac{W-D}{1- \delta_h}
\ee

This simplifies to the condition of high types choosing Trust in period 1 if and only if: 
\be
\delta_h \geq \frac{W}{(1-p)W + p(T+D)}
\ee
Since under some parameter sets this condition will hold, this type of separating equilibrium can exist. Let us refer to such an equilibrium as a  \emph{no-concessions separating equilibrium}, since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0. $\blacksquare$
\\
%This section could use some cleanup and streamlining
\\
{\bf \emph{Separating through concessions}}

If the condition in equation (8) is not met, in the absence of period 0 concessions\footnote{Countries need to deliver concessions in period 0, not just promise them. A concession that is promised but not delivered will count as cheap talk.} two high types would play Fight in every period because both would not have the incentive to play Trust. If instead high types are provided sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1. Two high types would avoid the trap of War that would occur under pooling.

This type of equilibrium will be called a \emph{concessions separating equilibrium}. We refer to the optimal equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type. These equilibrium gifts will mean that when period 1 is reached, countries know which type the other country is and choose to play accordingly.  The concessions phase acts as a coordination device to match countries' actions.  To play different actions from each other is an off equilibrium contingency. These off equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession. 
\\
\\
\emph{Lemma 3:}
In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium. \\
\emph{Proof:}
According to the revelation principle, we can assume that in a concessions separating equilibrium countries reveal their types truthfully, allowing period 1 actions where High types only play Trust with other high types, and play Fight with low types. Low types play Fight (Lemma 2) and their payoff is $U_l=X_{FF}+ pg_h-g_l$. Though low types might be willing to give a non-zero gift in a separating equilibrium, it must distinguish them from the high types. Thus it cannot help them to achieve a higher payoff, and because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is 0. High types have the incentive to play Trust only in the Peace equilibrium, which can only be sustained by a pair of high types. Both types benefit from the other country playing Trust because of the payoff structure so all countries have incentive to signal that they are high types if concessions are costless (cheap talk). Thus costless announcements cannot lead to truthful revelation. If concessions lead to a separating equilibrium, they must be costly. $\blacksquare$
\\
\\
{\bf Theorem 2:} In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.\\
\emph{Proof:} Under certain conditions, the high types will be given incentives to send costly concessions in order to reveal their type and separate (Lemma 3). In a separating equilibrium constructed here, any-off equilibrium behavior (a concession not equal to the equilibrium concession) will be considered low type gifts.  In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$  is:\\  
\be
pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h 
\ee
This equation represents the low types' incentives by truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift. Rearranging and simplifying this inequality, in order to separate the high types need give a gift 
\be
g_h \geq p(X_{FT}^l-X_{FF}^l). 
\ee 
High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$. Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation, which is when equation (10) holds with equality. Substituting in the definitions of the $X$ variables yields the minimum separating gift to be:\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made. Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils. Thus, a more powerful country would be more able to plunder, and hence has to make a greater concession to convincingly convey its type as being high. }
\be
g_h^*=p(T+D) 
\ee 
 In order to incentivize high types to send nonzero concessions, the high type IC must not be violated. The payoff from separating must be higher than the payoff from pooling with the low types. 
\be
pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h
\ee

Combining equations (11) and (12), we have the condition for a concessions separating equilibrium to exist:
\be
pX_{TT}^h-pX_{FF}^h - p(X_{FT}^l-X_{FF}^l) \geq 0
\ee
In terms of original variables, the condition for a concessions separating equilibrium to exist is:
\be
%p_1(\frac{T+D-W}{1-\delta_h}-p_2(T+D)\geq 0. point is the p's arent the same; i might have gotten them backwards. simplified this is:
\frac{T+D-W}{1-\delta_h}-(T+D)\geq 0
\ee
$\blacksquare$\\

The no-concessions separating equilibrium also will exist if equation (8) holds. In the case that both exist, the preferable equilibrium will be the one with a higher  payoff. The high types will prefer the concessions separating equilibrium if and only if
\be
pX_{TT}^h+(1-p)X_{FF}^h - g_h \geq p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )
\ee
This is simplified to preferring the concessions separating equilibrium if and only if
\be
 (1-p)W-p(T+D)\geq0.
\ee
%note this can be simplified by using primals of X's, DO THIS!!!!!!!!!!!!!!!!

\newpage
\section{Bibliography} %can add search(kaplan), expoeriments (2) and workplace gift exchange papers (the "gift giving as a medium" explanation
\ssp
\begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.05in}}

\item Allee, Todd L. and Paul K. Huth. (2006). ``Legitimizing Dispute Settlement: International Legal Rulings as Domestic Political Cover." \emph{American Political Science Review} 100:2, 219-34.

\item Beardsley, Kyle. (2010). ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. Forthcoming.

\item Beardsley, Kyle, David M. Quinn, Bidisha Biswas, and Jonathan Wilkenfeld. (2006). ``Mediation Style and Crisis Outcomes." \emph{The Journal of Conflict Resolution} 50:1,  58-86.

\item Bercovitch, Jacob, ed. (1996). \emph{Resolving International Conflicts: The Theory and Practice of Mediation.} Boulder, CO: Lynne Rienner.

\item Bercovitch, Jacob. (1997). ``Mediation in International Conflict," in I.W. Zartman and J.L. Rasmussen (eds.), \emph{Peacemaking in International Conflict}, Washington DC: US Institute of Peace.

\item Bercovitch, Jacob. (2000). ``Why do they do it like this? An analysis of factors influencing mediation in international conflicts." \emph{Journal of Conflict Resolution} 44:2, 170-202.

\item Bercovitch, Jacob and Richard Jackson. (2001). ``Negotiation or Mediation? An Exploration of Factors Affecting the Choice of Conflict Management in International Conflict.'' \emph{Negotiation Journal} 17:1, 59-77.

\item Bercovitch, Jacob, and Jeff Langley. (1993). ``The Nature of Dispute and the Effectiveness of International Mediation.'' \emph{Journal of Conflict Resolution} 37, 670-691.

\item Bester, Helmut and Karl Warneryd. (2006). ``Conflict and the Social Contract." \emph{ Scandinavian Journal of Economics} 108(2), 231-49.

\item Camerer, Colin. (1988). ``Gifts as Economic Signals and Social Symbols.'' \emph {The American Journal of Sociology,} Vol. 94, Supplement: Organizations and Institutions: Sociological and Economic Approaches to the Analysis of Social Structure: S180-S214.

\item Carmichael, H. Lorne and W. Bentley MacLeod. (1997). ``Gift Giving and the Evolution of Cooperation.'' \emph {International Economic Review} 38:3, 485-509.

\item Connelly, Brian L., S. Trevis Certo, R. Duane Ireland and Christopher R. Reutzel. (2011). ``Signaling Theory: A Review and Assessment.'' \emph {Journal of Management}. 37:1, 39-67.

\item De Dreu, Carsten K. W. (1995). ``Coercive Power And Concession Making in Bilateral Negotiation.'' \emph{Journal of Conflict Resolution} 39, 646.

\item Dixon, William. (1996). ``Third-Party Techniques for Preventing Conflict Escalation and Promoting Peaceful Settlement.'' \emph{International Organization} 50, 653-681.

\item Fey, Mark and Kristopher W. Ramsay. (2009). ``Mechanism Design Goes to War: Peaceful Outcomes with Interdependent and Correlated Types." \emph{Review of Economic Design} 13:3, 233-250.

\item Fey, Mark and Kristopher W. Ramsay. (2010). ``When Is Shuttle Diplomacy Worth the Commute?" \emph{World Politics} 62:4, 529-60.

\item Fey, Mark and Kristopher W. Ramsay. (2011). ``Uncertainty and Incentives in Crisis Bargaining: Game-Free Analysis of International Conflict." \emph{American Journal of Political Science} 55, 149-169.

\item Filson, Darren and Suzanne Werner. (2007). ``Implications for War Onset, Duration, and Outcomes Sensitivity to Costs of Fighting versus Sensitivity to Losing the Conflict.'' \emph{Journal of Conflict Resolution} 51: 691.

\item Fortna, Virginia Page. (2003). \emph{ Peace Time: Cease-Fire Agreements and the Durability of Peace.} Princeton: Princeton University Press.

\item Greig, J. Michael. (2005a). ``Moments of Opportunity: Recognizing Conditions of Ripeness for International Mediation Between Enduring Rivals,'' \emph{Journal of Conflict Resolution} 45, 691-718.

\item Greig, J. Michael, (2005b). ``Stepping into the Fray: When Do Mediators Mediate?'' \emph{American Journal of Political Science} 49:2, 249-66.

\item Greig, J. Michael and Paul F. Diehl. (2006). ``Softening Up: Making Conflicts More Amenable to Diplomacy,'' \emph{International Interactions} 32, 355-84.

\item Horner, Johannes, Massimo Morelli and Francesco Squintani. (2010). ``Mediation and Peace.'' Cowles foundation. Unpublished manuscript.

\item Iannaccone, Laurence. (1992). ``Sacrifice and Stigma: reducing free-riding in cults, communes, and other collectives.'' \emph{Journal of Political Economy} 100:2, 271-291.

\item Komorita, Stuart S. (1973).  ``Concession-Making and Conflict Resolution.  \emph{Journal of Conflict Resolution} 17:4, 745-762.

\item Kranton, Rachel (1996). ``The formation of cooperative relationships.'' \emph{Journal of Law, Economics, and Organization}, 12:1, 214-233.

\item Kydd, Andrew. (2003). ``Which Side Are You On? Bias, Credibility, and Mediation." \emph{American Journal of Political Science} 47:4, 597-611.

\item Larson, Deborah Welch. (1987). ``The psychology of reciprocity in international relations.'' \emph{Negotiation Journal.} 4:3, 281-301.

\item Myerson, Roger B. (1979). ``Incentive Compatibility and the Bargaining Problem." \emph {Econometrica} 47, 61-73.

\item Osgood, Charles E. (1962). \emph {An alternative to war or surrender.}  Oxford, England: University of  Illinois Press.

\item Prendergast, Canice and Lars Stole. (2001). ``The Non-Monetary Nature of Gifts.'' \emph {European Economic Review} 45:10, 1793-810.

\item Rabin, Matthew. (1993). ``Incorporating fairness into game theory and economics.'' \emph{American Economic Review} 83:5, 1281-1301.

\item Rauchhaus, Robert. (2006). ``Asymmetric Information, Mediation, and Conflict Management." \emph{World Politics} 58:2, 207-401.

\item Smith, Alastair, and Alan Stam. (2003). ``Mediation and Peacekeeping in a Random Walk Model of Civil and Interstate War." \emph{International Studies Review} 5:4, 115-35.

\item Spence, Michael. (1973). ``Job Market Signaling." \emph {The Quarterly Journal of Economics}, 87:3, 355-74.

\item Svensson, Isak. (2008). ``Do Mediators Go Where they Are Needed Most? Mediation Selection in Civil Wars,'' Unpublished manuscript.

\item Terris, Lesley G. and Zeev Maoz. (2005). ``Rational Mediation: A Theory and a Test.'' \emph{Journal of Peace Research} 44:5, 563-583.

\item Thaler, Richard. (1985). ``Mental Accounting and Consumer Choice.'' \emph{Marketing Science} 4:3, 199-214.

\item Van Damme, E. (1989). ``Stable equilibria and forward induction. \emph{Journal of Economic Theory} 48:2, 476-496.

\item Van de Ven, Jeroen. (2000).``The economics of the gift.'' Unpublished manuscript.

\item Waldfogel, Joel (2009). \emph{Scroogenomics: Why You Shouldn't Buy Presents for the Holidays}. Princeton: Princeton University Press.

\item Waldfogel, Joel (1993). ``The deadweight loss of Christmas,'' \emph{The American Economic Review} 83:5, 1328-1336.

\item Walter, Barbara F. (2002). \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton: Princeton University Press.

\item Waltz, Kenneth (2001).  \emph {Man, the State and War: A Theoretical Analysis.} New York : Columbia University Press. %ref cites page 159

\item Watson, Joel (1996). ``Building a Relationship,'' Unpublished manuscript.

\item Watson, Joel. (1999). ``Starting Small and Renegotiation,'' {Journal of Economic Theory} 85:1, 52-90.

\end{list}

%\end{document}

### 2016-09-27 draft.tex
format draft to compile independently and revise abstract

@@
-%\documentclass[12pt, letterpaper]{article}
-%\usepackage{graphicx}
-%\usepackage{moreverb}
-%\usepackage{mdwlist}
-%\usepackage{amsmath}
-%\usepackage{amssymb}
-%\usepackage[hmargin=1in,vmargin=1in]{geometry}
+\documentclass[12pt, letterpaper]{article}
+\usepackage{graphicx}
+\usepackage{moreverb}
+\usepackage{mdwlist}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{caption}
+\usepackage{verbatim}
+\usepackage[hmargin=1in,vmargin=1in]{geometry}
 %\usepackage[left=0.9in,top=0.9in,right=0.9in,nohead]{geometry}
 
-%\newcommand{\be}{\begin{equation}}
-%\newcommand{\ee}{\end{equation}}
-%\newcommand{\bi}{\begin{itemize*}}
-%\newcommand{\ei}{\end{itemize*}}
-%\newcommand{\bgd}{\begin{gathered}}
-%\newcommand{\egd}{\end{gathered}}
-%\newcommand{\bgr}{\begin{gather}}
-%\newcommand{\edgr}{\end{gather}}
-%\newcommand{\mb}{\mathbf}
-%\newcommand{\ve}{\varepsilon}
-%\newcommand{\real}{\mathbb{R}}
-%\newcommand{\de}{\delta}
-%  \usepackage{setspace}
-%  \doublespacing
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\bi}{\begin{itemize*}}
+\newcommand{\ei}{\end{itemize*}}
+\newcommand{\bgd}{\begin{gathered}}
+\newcommand{\egd}{\end{gathered}}
+\newcommand{\bgr}{\begin{gather}}
+\newcommand{\edgr}{\end{gather}}
+\newcommand{\mb}{\mathbf}
+\newcommand{\ve}{\varepsilon}
+\newcommand{\real}{\mathbb{R}}
+\newcommand{\de}{\delta}
+  \usepackage{setspace}
+  \doublespacing
 
-%\thispagestyle{empty}
+\thispagestyle{empty}
 
-%\begin{document}\title{Inefficient Concessions and Mediation} 
-%\author{ Ben Horne}
+\title{Inefficient Concessions and Mediation} 
+\author{Kristy Buzard\\
+Syracuse University \\
+kbuzard@syr.edu\\
+Ben Horne\\ 
+University of California, San Diego}
 %To Do : define what is ineffieicncy
-%\maketitle
 
-%\section{Abstract}
-%We explore a model of bilateral conflict, examining the role of concessions as signals, in addition to being ends in themselves.
-In doing so, we open up a rationale for mediation: to remove the inefficiencies of signaling in the pre-play round of negotiations.
-Two parties are engaged in conflict, manifested as the stage game Nash equilibrium of a repeated Prisoner's Dilemma.
-Each party distrusts the other's willingness to pursue peace, and can indicate its own willingness through costly signaling, i.e.
-concessions.
-In resolving this trust issue and attempting to end the conflict, efficient concessions are generally preferred, but optimal signaling can include inefficiency if concessions can later be used against the giving party.
-Under such scenarios, a third party mediator can sometimes reduce inefficiency and improve welfare, and we give an explanation for the mechanism that makes mediation effective.
-%Two parties are engaged in conflict, and each distrusts the other's willingness to pursue peace.
-Each can indicate its own interest in peace through costly signaling, or concessions.
-In certain environments, however, a lack of trust means that optimal concessions are not made, creating inefficiencies in the negotiation that can reduce the possibility of peace.
-Through a formal model, we explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
+\begin{document}
+\maketitle
+
+\begin{abstract}
+When two parties are engaged in conflict and each distrusts the other's willingness to pursue peace, concessions can be used to indicate an interest in making peace.
+We demonstrate that a lack of trust can prevent optimal concessions from being made, creating inefficiencies in negotiation that can reduce the possibility of peace.
+We use a game-theoretic model to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
 In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
- %   Results show that in bilateral negotiation, parties may prefer to give inefficient concessions due to the other party’s potential power to hurt.
-Additionally, conditions are shown under which a party be willing to, or even prefer to, give the first concession rather than waiting or giving simultaneously.
-...gain insight into the usefulness of concessions in making peace between warring factions.
-%\newpage
+\end{abstract}
 
-\section{Introduction and motivation} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power.
+\section{Introduction} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power.
 But this is not understood as a problem of private information, as you treat it here, but as one of credible commitment.
@@
 
-\captionof{table}{Stage Game Payoffs}
+%\captionof{table}{Stage Game Payoffs}
 \begin{center}
@@
 \newpage
-\captionof{table}{Modified Stage Game Payoffs}
+%\captionof{table}{Modified Stage Game Payoffs}
 \begin{center}
@@
 \section{Bibliography} %can add search(kaplan), expoeriments (2) and workplace gift exchange papers (the "gift giving as a medium" explanation
-\ssp
+
 \begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.05in}}
@@
 
-%\end{document}
+\end{document}

### 2016-09-27 draft.tex
remove references to 'formal'

@@
 kbuzard@syr.edu\\
+\\
 Ben Horne\\ 
-University of California, San Diego}
+University of California, San Diego\\
+\\}
 %To Do : define what is ineffieicncy
@@
 Finally, this paper uses a mechanism design framework to model a third party's role in bringing about more efficient concessions.
-Many scholars contend that mediators with enforcement capabilities can help to resolve conflict; this formal analysis provides an explanation for why enforcement is effective.
+Many scholars contend that mediators with enforcement capabilities can help to resolve conflict; this analysis provides an explanation for why enforcement is effective.
 
@@
 
-\section{Formal model description} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING.
+\section{Model} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING.
 EMPHASIZE SCENARION (EGYPT USRAEL ETC) THAT ARE BETTER TO MODEL WITH Our MODEL.
@@
 
-%\captionof{table}{Stage Game Payoffs}
 \begin{center}
+\captionof{table}{Stage Game Payoffs}
 \begin{tabular}{|l|c|c|}
@@
 \section{Analysis of benchmark cases }
-%examples!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 When countries are faced with doubts about each other's motives, they have several options of how to proceed.
@@
  $C_h(\cdot)=C_l(\cdot)=1$ as earlier in the model description. Periods 1 to $\infty$ are as before but with the following stage game payoffs:
-\newpage
-%\captionof{table}{Modified Stage Game Payoffs}
+
 \begin{center}
-
+\captionof{table}{Modified Stage Game Payoffs}
 \begin{tabular}{|l|c|c|}
@@
 We will now consider the involvement of a mediator which will be modeled as a mechanism.
-Mediation has been studied to some degree in the formal literature and has most recently been modeled using mechanism design.
-Applying mechanism design to mediation has been used, to date, by Fey and Ramsay (2008, 2010 and 2011), Bester and Warneryd (2006) and Horner et.
+In the theoretical literature, mediation has most recently been modeled using mechanism design (Fey and Ramsay 2008, 2010 and 2011; Bester and Warneryd 2006; and Horner et.
 al.
-(2010).
+2010).
 
@@
 
-$M$ inputs the reports of types $t_1$ and $t_2$ and outputs the required concessions $g_1$ and $g_2$.
-Formally, $ M:(t_1,t_2)\rightarrow( g_1(\cdot), g_2(\cdot))$.
+$M$ inputs the reports of types $t_1$ and $t_2$ and outputs the required concessions $g_1$ and $g_2$ so that $ M:(t_1,t_2)\rightarrow( g_1(\cdot), g_2(\cdot))$.
 The countries are bound to send the mandated concessions.
@@
 The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy this inefficiency if she is trusted.
-One result of this formal exposition is to show the mechanisms through which a mediator can help.
+One contribution of this paper is to show the mechanisms through which a mediator can help.
 Since the mediator eliminates inefficient concessions, the observation that inefficient concession may not do the trick only further indicates the value of a mediator even more.
@@
 If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, a high type will be given incentives to play Trust in the first round rather than Fight.
-Formally, to play Trust, the following must be satisfied:%Make clearer language!!!!!!!
+To play Trust, the following must be satisfied:%Make clearer language!!!!!!!
 %FUTURE WORK ON DELY OF PEACE- IF PEACE WILL E THERE, YOU MIGHT BE VERY RISK AVERSE TO GETTING SCREWED BY THE LOW TYPE SO KEEP PUTTING OFF THE RISKY FIRST TRUST ROUND

### 2016-10-01 draft.tex
update horner, morelli and squintani reference
finish updating reference list for previous citations
revise old intro, remove break for old lit review/model intro secion

@@
 This holds for concessions other than land.
-Russia is loathe to cede further autonomy to Chechnya, even though independence could hypothetically relieve tensions and reduce violence.
-If Chechen independence could in fact lead to lowered violence, it is possible that this move would be in Russia's best interest.
+Russia is loathe to cede further autonomy to Chechnya, even though it could hypothetically relieve tensions and reduce violence.
+If Chechen autonomy could in fact lead to lowered violence, it is possible that this move would be in Russia's best interest.
 But the Russians perceive, perhaps correctly, that any move towards autonomy might only give Chechens further leverage against the Kremlin.
-They also realize that were Chechnya to realize its hopes, other ethnic areas like Tatarstan might be emboldened to demand more.
 From the Russian perspective, granting the concession of increased autonomy would likely have future costs.
 
-In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions.
-Mediation has long been understood as a mechanism for reducing mistrust, but in most of the published literature on international conflict mediation lacks a rigorous theoretical framework.
+%In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions.
+Mediation has long been understood as a mechanism for reducing mistrust, but in much of the published literature on international conflict mediation lacks a rigorous theoretical framework.
 
-This paper has three parts.
-First, it explores the role of costly concessions in a game theoretic framework, evoking a two-sided version of Spence signaling (1973).
-Second, after considering existing explanations for inefficient concessions, it proposes a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
-Finally, this paper uses a mechanism design framework to model a third party's role in bringing about more efficient concessions.
-Many scholars contend that mediators with enforcement capabilities can help to resolve conflict; this analysis provides an explanation for why enforcement is effective.
-
-\section{Literature review and model introduction}
+This paper uses a two-sided Spence signaling (1973) model to propose a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
+We then suggest a new explanation for the effectiveness of third-party mediation by demonstrating in a mechanism design framework that a mediator can facilitate more efficient concessions.
 
@@
 
-\item Beardsley, Kyle. (2010). ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. Forthcoming.
+\item Beardsley, Kyle. (2010). ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. 47:2, 395-406.
 
@@
 
-\item Horner, Johannes, Massimo Morelli and Francesco Squintani. (2010). ``Mediation and Peace.'' Cowles foundation. Unpublished manuscript.
+\item Horner, Johannes, Massimo Morelli and Francesco Squintani. (2010). ``Mediation and Peace.'' \emph{The Review of Economic Studies} 84, 1483-1501.
 

### 2016-10-01 draft.tex
move mediation to end of intro; add hyperref
compact intro discussion of concessions

@@
   \doublespacing
+
+\usepackage[pdftex,
+bookmarks=true,
+bookmarksnumbered=false,
+pdfview=fitH,
+bookmarksopen=true,hyperfootnotes=false]{hyperref}
 
@@
 But the Russians perceive, perhaps correctly, that any move towards autonomy might only give Chechens further leverage against the Kremlin.
-From the Russian perspective, granting the concession of increased autonomy would likely have future costs.
-
-%In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions.
-Mediation has long been understood as a mechanism for reducing mistrust, but in much of the published literature on international conflict mediation lacks a rigorous theoretical framework.
+From the Russian perspective, granting the concession of increased autonomy might have large future costs.
 
 This paper uses a two-sided Spence signaling (1973) model to propose a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
-We then suggest a new explanation for the effectiveness of third-party mediation by demonstrating in a mechanism design framework that a mediator can facilitate more efficient concessions.
+We then suggest a new explanation for the effectiveness of third-party mediation.
+Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to peace.
 
-While an integral part of conflict literature, concessions have not been adequately addressed by theoretical research.
+While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research.
 The broader literature that attempts to model war has included concessions as part of bargaining, but has not explicitly considered the role of concessions in achieving peace.
@@
 Fearon (1995), Powell (1996a and 1996b, 2006) and others consider war to be a bargaining failure, caused by commitment problems and asymmetric information.
+When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation.
+
 In these models war can be averted by splitting the pie (i.e.
 the disputed territory) in a way acceptable to both parties.
-Concessions are modeled as offering part of the pie to the other party.
-%LAKE: You need to situation what you’re doing in the bargaining literature and relate your model to its principal results.
-WAR IS WELL ESTABLISHED AS BARGAINING!!!
+Concessions are modeled as offering part of the pie to the other party, and asymmetric information is about each party's \textit{resolve} to fight and/or military capabilities (Arena 2013).
+In this context, an example of costly signaling would be military preparations for war (Slantchev 2011).
 
-The literature often views conflicts as bargaining over assets that confer future power.
-In these cases, a lack of credible commitment can create a holdup problem.
-A lack of trust prevents the high level of interaction that would otherwise be optimal.
-
-We will approach the commitment problem  through this same general understanding, but modeling a party's willingness to cooperate as private information.
-A high type is willing to cooperate; a low type has incentives to not cooperate.
+We will approach the commitment problem through this same general understanding, but we model a party's ability to cooperate as private information.
+A high type is able to cooperate; a low type has incentives not to cooperate.
 These types map onto the commitment problem, with a high type one who is able to commit in certain scenarios.
@@
 
-Third party involvement is ubiquitious in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
-Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others insist that a correct analysis finds mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al.
-2006).
-But the term mediation encompasses a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation suspect.
-The type of mediation affects the negotiation outcome (Bercovitch 2000; Beardsley et al.
-2006) and timing is important (Greig 2005a).
-It is essential to focus more precisely on the specific actions and environments that make use of a certain type of mediation, which is how we approach the question.
-This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has certain manipulative abilities---as defined below.
-
-Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006).
-In this paper, parties are in conflict and can benefit from seeking mediation in order to overcome mistrust.
-Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
-Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010).
-These empirical results, while interesting, have generally lacked strong theoretical foundations.
-Mediation is used, but why actors use it is not well understood.
-This paper helps to fill this gap by explaining at least one of meditation's roles.
-%NEED TO EDIT THIS PARAGRAPH- WHICH EMPIRICAL RESULT!!!!!(S)
-
-Concessions form the centerpiece of the GRIT (graduated and reciprocated initiatives in tension reduction) theory in the psychological literature (Osgood 1962) and have shown ample success in lab settings.
+%Concessions form the centerpiece of the GRIT (graduated and reciprocated initiatives in tension reduction) theory in the psychological literature (Osgood 1962) and have shown ample success in lab settings.
 Komorita (1973) conducts lab experiments using a repeated Prisoner's Dilemma similar to the setup in our paper and finds costly conciliatory acts (concessions) to be useful in promoting cooperation.
@@
 %de dreu bases experiments on shelling 60 and bacharach and lawler 81/ lawler 92 about deterrance, the shelling conflict spiral was not fully rejected, but the alternative of deterrance was supported
-In addition to concessions, De Dreu also reports laboratory results on mediation; he concludes that a weaker mediator should work with promises while a more powerful one can be effective with threats.
+%In addition to concessions, De Dreu also reports laboratory results on mediation; he concludes that a weaker mediator should work with promises while a more powerful one can be effective with threats.
 Larson (1988) and others have applied this framework to political science questions.
@@
 While our model is tailored to an international relations setting, the mathematical explanation for inefficient giving of concessions may be more broadly applicable.
+
+%In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions.
+Mediation has long been understood as a mechanism for reducing mistrust, but in much of the published literature on international conflict mediation lacks a rigorous theoretical framework.
+
+Third party involvement is ubiquitious in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
+Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others insist that a correct analysis finds mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al.
+2006).
+But the term mediation encompasses a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation suspect.
+The type of mediation affects the negotiation outcome (Bercovitch 2000; Beardsley et al.
+2006) and timing is important (Greig 2005a).
+It is essential to focus more precisely on the specific actions and environments that make use of a certain type of mediation, which is how we approach the question.
+This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has certain manipulative abilities---as defined below.
+
+Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006).
+In this paper, parties are in conflict and can benefit from seeking mediation in order to overcome mistrust.
+Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
+Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010).
+These empirical results, while interesting, have generally lacked strong theoretical foundations.
+Mediation is used, but why actors use it is not well understood.
+This paper helps to fill this gap by explaining at least one of meditation's roles.
+%NEED TO EDIT THIS PARAGRAPH- WHICH EMPIRICAL RESULT!!!!!(S)
+
+In the theoretical literature, mediation has most recently been modeled using mechanism design (Fey and Ramsay 2008, 2010 and 2011; Bester and Warneryd 2006; and Horner et. al. 2010).
 
@@
 \section{Mediation}
-All results in this paper thus far have relied on bilateral engagement.
-We will now consider the involvement of a mediator which will be modeled as a mechanism.
-In the theoretical literature, mediation has most recently been modeled using mechanism design (Fey and Ramsay 2008, 2010 and 2011; Bester and Warneryd 2006; and Horner et.
-al.
-2010).
+All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator which will be modeled as a mechanism.
 
@@
 
+\item Arena, Philip. (2013). ``Costly Signaling, Resolve, and Martial Effectiveness." Unpublished manuscript.
+
 \item Beardsley, Kyle. (2010). ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. 47:2, 395-406.
@@
 
-\item De Dreu, Carsten K. W. (1995). ``Coercive Power And Concession Making in Bilateral Negotiation.'' \emph{Journal of Conflict Resolution} 39, 646.
+%\item De Dreu, Carsten K. W. (1995). ``Coercive Power And Concession Making in Bilateral Negotiation.'' \emph{Journal of Conflict Resolution} 39, 646.
 
@@
 
-\item Filson, Darren and Suzanne Werner.
+%\item Filson, Darren and Suzanne Werner.
 (2007).
@@
 
-\item Komorita, Stuart S. (1973).  ``Concession-Making and Conflict Resolution.  \emph{Journal of Conflict Resolution} 17:4, 745-762.
+%\item Komorita, Stuart S. (1973).  ``Concession-Making and Conflict Resolution.  \emph{Journal of Conflict Resolution} 17:4, 745-762.
 
@@
 
-\item Osgood, Charles E. (1962). \emph {An alternative to war or surrender.}  Oxford, England: University of  Illinois Press.
+%\item Osgood, Charles E. (1962). \emph {An alternative to war or surrender.}  Oxford, England: University of  Illinois Press.
 
@@
 
-\item Rauchhaus, Robert. (2006). ``Asymmetric Information, Mediation, and Conflict Management." \emph{World Politics} 58:2, 207-401.
+\item Rauchhaus, Robert. (2006). ``Asymmetric Information, Mediation, and Conflict Management.'' \emph{World Politics} 58:2, 207-401.
+
+\item Slantchev, Branislav. (2011). ``Military Threats: The Costs of Coercion and the Price of Peace.'' Cambridge: Cambridge University Press.
 

### 2016-10-01 draft.tex
finish revising intro, expanding lit review, including ref list

@@
 \\}
+\date{September 30, 2016}
 %To Do : define what is ineffieicncy
@@
 
-This paper will explore the role of concessions as signals, and not only as ends in themselves.
-Concessions may play either role -- or both -- in conflict resolution.
-If concessions are used solely for signaling, this can be considered inefficient as value can be lost.
-We will examine cases where concessions have material value, signaling value, and both.
+In conflict resolution, concessions may act as signals or as an end in themselves -- or as both simultaneously.
+One contribution of this paper is that it allows concessions to have material value, signaling value, and both.
+We will show that when concessions are used solely for signaling, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.
 
@@
 
-Gift giving as a whole is inefficient (Waldfogel 2009); it has been estimated that Christmas gift-giving is only 75 percent efficient, meaning that the average gift is valued at 75 cents of the dollar that is spent on it (Waldfogel 1993).
+%Gift giving as a whole is inefficient (Waldfogel 2009); it has been estimated that Christmas gift-giving is only 75 percent efficient, meaning that the average gift is valued at 75 cents of the dollar that is spent on it (Waldfogel 1993).
 But merely looking at aggregate numbers blurs together many possible reasons for gift giving.
 It has even been theorized that buying something that the receiver would not buy himself is an inherent component of gift giving (Thaler 1985).
+
 Often, inefficient gifts occur in the formative stages of relationships or in immature relationships (Camerer 1988).
@@
 But the most relevant explanation for the field of international relations is that gift giving is strategic.
-Camerer also creates a theoretical model using mechanism design that models gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
+Camerer also uses mechanism design to model gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
 This strategic giving of gifts in societies looks very much like the strategic giving of concessions to remedy conflict situations.
-When modeled game theoretically, these different environments look even more similar.
+When modeled game-theoretically, these different environments look even more similar.
 
@@
 
-Several other papers essentially use Camerer's theoretical explanation for inefficient gifts.
-Iannaccone (1992), Rabin (1993),  Kranton (1996) and Carmichael and MacLeod (1997) all use a similar explanation with various modifications to the model.
-Carmichael and MacLeod (1997) extend the argument to long time frames, arguing that inefficient gifts might arise evolutionarily by keeping ``parasite'' numbers low.
-In an environment with repeated opportunities for concessions Watson (1996, 1999) is able to show that a strong relationship can be reached by starting with small gifts and increasing their size as the relationship becomes more committed.
-Kranton (1996) applies a similar concept to a model resembling Camerer (1988).
-See Van de Ven (2000) for an analysis of how these papers relate to each other.
+%Iannaccone (1992), Rabin (1993),  Kranton (1996) and Carmichael and MacLeod (1997) all use a similar explanation for inefficient gifts with various modifications to the model.
+In an environment with repeated opportunities for concessions Watson (1996, 1999) is able to show that a strong relationship can be reached by starting with small gifts and increasing their size as the relationship becomes more committed.\footnote{See Van de Ven (2000) for an overview of this literature.}
 
-The second major way to explain inefficient gifts is expressed in Prendergast and Stole (2001).
-The authors have a result that explains inefficient gift giving by modeling utility of matching--if players are of a like mindset they get an extra benefit; they are willing to take the risk of giving the wrong gift.
-This explanation has less applications to questions of conflict.
+The second major explanation for inefficient gifts is expressed in Prendergast and Stole (2001).
+The authors explain inefficient gift giving by modeling the utility of matching.
+That is, if players are of a like mindset they get an extra benefit so they are willing to take the risk of giving the wrong gift.
 
@@
 
-While these several explanations for inefficiency are interesting, we propose another theoretical contribution to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle.
-The basic formulation of our model is most similar to Camerer (1988) who also uses mechanism design; our model is an expansion of Camerer's analysis.
-The model can achieve the Camerer result and another similar to that of Prendergast and Stole (2001) but adds a very different explanation for inefficiency.
+We propose another theoretical contribution to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle.
+The basic formulation of our mechanism-design approach is an expansion of Camerer's (1988) analysis.
+The model can achieve the basic `inefficient gifts' results of Camerer (1988) and Prendergast and Stole (2001) but does so using a very different explanation for inefficiency.
 %An extension at the end of our paper compares simultaneous versus sequential concessions in a bilateral negotiation environment.
@@
 %Since neither the models exemplified by Camerer nor Prendergast and Stole uses a truly general formulation to yield inefficient gift giving % in a one-shot setting,
-This paper expands upon the existing literature by generalizing the analysis using mechanism design theory more extensively than has been done thus far.
+%This paper expands upon the existing literature by generalizing the analysis using mechanism design theory more extensively than has been done thus far.
 %The analysis for this paper is more extensive than any of the published papers mentioned and shows where mechanisms can and cannot improve upon the benchmark bilateral results.
-The basic model is a costly signaling model, at its root similar to ideas in Spence (1973) and subsequent papers.
-See Connelly et al.
-(2011) for a review of the costly signaling literature.
-In essence, the model shows that if concessions can be later used against the party that gives, then giving inefficient concessions can be in their best interest.
-While our model is tailored to an international relations setting, the mathematical explanation for inefficient giving of concessions may be more broadly applicable.
+The basic model is a costly signaling model, at its root similar to ideas in Spence (1973) and subsequent papers.\footnote{See Connelly et al.
+(2011) for a review of the costly signaling literature.} In essence, the model shows that if concessions can be later used against the party that gives, then it can be in a negotiating party's best interest to give inefficient concessions.
+While our model is tailored to an international relations setting, the explanation for inefficient giving of concessions may be more broadly applicable.
 
@@
 
+This demonstration of the incentives for inefficient concessions leads to a new explanation for the role of mediators in conflict resolution.
 Third party involvement is ubiquitious in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
@@
 2006) and timing is important (Greig 2005a).
-It is essential to focus more precisely on the specific actions and environments that make use of a certain type of mediation, which is how we approach the question.
-This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has certain manipulative abilities---as defined below.
 
+It is essential to focus more precisely on the specific actions and environments that make use of particular types of mediation, which is how we approach the question.
+This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has manipulative abilities.
 Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006).
@@
 Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010).
-These empirical results, while interesting, have generally lacked strong theoretical foundations.
-Mediation is used, but why actors use it is not well understood.
-This paper helps to fill this gap by explaining at least one of meditation's roles.
-%NEED TO EDIT THIS PARAGRAPH- WHICH EMPIRICAL RESULT!!!!!(S)
 
-In the theoretical literature, mediation has most recently been modeled using mechanism design (Fey and Ramsay 2008, 2010 and 2011; Bester and Warneryd 2006; and Horner et. al. 2010).
+These empirical results have until recently lacked strong theoretical foundations.
+Mediation is used, but we are only beginning to understand why actors use it.
+Recently, mediation has begun to be modeled using mechanism design for settings where militarization or the resolve to fight are private information (Bester and Warneryd 2006; Fey and Ramsay 2008, 2010 and 2011; Horner et.
+al.
+2010; Meirowitz et al.
+2012, 2013).
+This paper expands the theoretical literature by modeling the role of mediation when information is asymmetric about parties' abilities to commit to peace.
+Here, a mediator can remove the incentive to make concessions that are inefficient.
 
@@
 In our model, a successful mediator relies on the parties trusting her.
-However, here the mediator had no incentive to lie: lying can only potentially hurt the high types, the only type who the mediatorcan possibly help.
+However, here the mediator had no incentive to lie: lying can only potentially hurt the high types, the only type who the mediator can possibly help.
 
@@
 
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2013). ``Mediation and Strategic Militarization.'' Unpublished manuscript.
+
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2013). ``Dispute Resolution Institutions
+and Strategic Militarization.'' Unpublished manuscript.
+
 \item Myerson, Roger B. (1979). ``Incentive Compatibility and the Bargaining Problem." \emph {Econometrica} 47, 61-73.
@@
 
-\item Thaler, Richard. (1985). ``Mental Accounting and Consumer Choice.'' \emph{Marketing Science} 4:3, 199-214.
+%\item Thaler, Richard. (1985). ``Mental Accounting and Consumer Choice.'' \emph{Marketing Science} 4:3, 199-214.
 
@@
 
-\item Waldfogel, Joel (2009). \emph{Scroogenomics: Why You Shouldn't Buy Presents for the Holidays}. Princeton: Princeton University Press.
+%\item Waldfogel, Joel (2009). \emph{Scroogenomics: Why You Shouldn't Buy Presents for the Holidays}. Princeton: Princeton University Press.
 
-\item Waldfogel, Joel (1993). ``The deadweight loss of Christmas,'' \emph{The American Economic Review} 83:5, 1328-1336.
+%\item Waldfogel, Joel (1993). ``The deadweight loss of Christmas,'' \emph{The American Economic Review} 83:5, 1328-1336.
 

### 2016-10-01 draft.tex
update abstract for submission to Midwest Theory (Purdue)

@@
 \begin{abstract}
-When two parties are engaged in conflict and each distrusts the other's willingness to pursue peace, concessions can be used to indicate an interest in making peace.
+When two parties are engaged in conflict and each distrusts the other's ability to pursue peace, concessions can be used to indicate an interest in making peace.
 We demonstrate that a lack of trust can prevent optimal concessions from being made, creating inefficiencies in negotiation that can reduce the possibility of peace.
-We use a game-theoretic model to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
+We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
 In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.

### 2016-11-29 draft.tex
fix one typo

@@
 In Prendergast and Stole the two types are equal except in labeling; in our model, high types and low types are used so there is an incentive for low types to try to pose as high types.
-Aside from this difference, essentially the same result is found: if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a ay to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.
+Aside from this difference, essentially the same result is found: if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.
 

### 2016-11-29 presentation.tex
add presentation from unrecognizedstates

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

\usecolortheme{beaver}
\useinnertheme{default}
\setbeamertemplate{itemize item}[triangle]
\setbeamertemplate{itemize subitem}[triangle]
\setbeamertemplate{itemize subsubitem}[circle]
\setbeamertemplate{enumerate items}[default]
\setbeamertemplate{blocks}[upper=block head,rounded]
\setbeamercolor{item}{fg=black}
\usefonttheme{serif} %should allow ccfonts to take effect

\usepackage{cite}
\usepackage{times, verbatim,xcolor,bm}
\usepackage{amsbsy,amssymb, amsmath, amsthm}
\usepackage{booktabs}
%David miller's fonts
	\usepackage[T1]{fontenc}
	\usepackage[boldsans]{ccfonts}
	\usepackage[euler-hat-accent]{eulervm}

\newcommand{\al}{\alpha}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^{tw}}}
\newcommand{\ga}{\gamma}
\newcommand{\ve}{\varepsilon}
\newcommand{\ta}{\theta}
\newcommand{\de}{\delta}
\newcommand{\ov}{\overline}

\newenvironment{changemargin}[2]{% 
  \begin{list}{}{% 
    \setlength{\topsep}{0pt}% 
    \setlength{\leftmargin}{#1}% 
    \setlength{\rightmargin}{#2}% 
    \setlength{\listparindent}{\parindent}% 
    \setlength{\itemindent}{\parindent}% 
    \setlength{\parsep}{\parskip}% 
  }% 
  \item[]}{\end{list}}

\begin{document}
\title[Unrecognized States: A Theory of Self-Determination and Foreign Influence\hspace{1.25in}\insertframenumber/\inserttotalframenumber]{Unrecognized States: A Theory of Self-Determination and Foreign Influence}
\author[Kristy Buzard, Benjamin Graham and Ben Horne]{Kristy Buzard, Benjamin Graham and Ben Horne\\ kbuzard@syr.edu}
\date{September 23, 2016}
\maketitle
%\insertpresentationendpage removed b/c of appendix

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{Unrecognized States}
Unrecognized states (URS): control and govern territory, seek recognition
\pause
\begin{itemize}[<+->]
  \item Six current URS more than 20 yrs old (+ Eastern Ukraine)
	\item No explanation in the literature for how this can be a stable outcome
\end{itemize}
\end{frame}

\begin{frame}{What we do}

\pause
We demonstrate unrecognized statehood can be a ``status quo'' outcome
\pause
\begin{itemize}[<+->]
	\item (SPN) Equilibrium in a repeated game
	\item Four players
		\begin{itemize}[<+->]
			\item Home government
			\item Secessionist elite
			\item Patron state
			\item International community
		\end{itemize}
	\item State variable: Status Quo (SQ) payoffs for secessionists
\end{itemize}

\end{frame}

\begin{frame}{The General Idea}

\pause
In each period: secessionists and gov't each choose (simultaneously) among $\left\{\text{Fight, Status Quo, Cede}\right\}$
\pause
		\begin{itemize}
			\item We need Status Quo to be a stage game best response for both secessionists and gov't
		\end{itemize}

\pause
\vskip.2in
We add some more realistic elements:
\pause
		\begin{enumerate}[<+->]
			\item Unrecognized status reduces Status Quo payoffs of secessionists each period
			\item Patron and int'l community can make investments in both actors' payoffs
		\end{enumerate}

\end{frame}

\begin{frame}{Outline of Talk}
\pause
\begin{enumerate}[<+->]
	\item Model
	\item Status quo equilibrium
	\item What we can say about sanctions
\end{enumerate}
\end{frame}

\section{Model}
\subsection{Economic and Political Structure}
\begin{frame}{Timeline}
\pause
\begin{figure}
\includegraphics[width=\linewidth,height=\textheight,keepaspectratio]{Timeline2.pdf}
%\caption{Timeline}
\end{figure}
\end{frame}

\subsection{The Players}

\begin{frame}{Outside Actors}
	\pause
International community ($c$): desires reunification \\
\pause
Patron ($p$): desires recognized independence
\pause
\begin{itemize}	
	\item Each has preferences that are aligned with one of the home state actors
	\pause
	\item Patron may most prefer SQ; our assumption stacks the deck against us
\end{itemize}

\pause
\vskip.2in
$p$'s per period payoffs: $U_{pt} = -\alpha X + \lambda Y - R_{pt}$ \\
$c$'s per period payoffs: $U_{ct} = \beta X - \nu Y - R_{ct}$
\begin{itemize}
	\item $X=1$ if the secessionists rejoin the home state \\
	\item $Y=1$ if the home state recognizes the secessionists 
\end{itemize}
\end{frame}

\begin{frame}{Home State Actors}
	\pause
Central Government of Home State ($g$): desires reunification \\
\pause
Secessionists ($s$): desire recognized independence
\pause
\begin{itemize}	
	\item Central issue of contention: recognized independence vs. reunification.
\end{itemize}

\pause
\vskip.2in
Assumptions:
\begin{itemize}[<+->]
	\item Issue of status is indivisible, highly valued by both sides
	\item Insufficient credible side payments for easy settlement
\end{itemize}
\end{frame}

\begin{frame}{Stage Game between Home Gov't $\&$ Secessionists}
\pause
	\begin{center}
\begin{tabular}{|  c| c | c | c |} 
\hline
  $g\downarrow$,     $ s\rightarrow$  & Fight & Status Quo &Cede \\ \hline
	Fight & $\omega_{gt}, \omega_{st}$ &$\omega_{gt}, \omega_{st}$&$W_{gt}, L_{st}$ \\ \hline
	Status Quo& $\omega_{gt}, \omega_{st}$& $Q_{gt}, Q_{st}$ &$W_{gt}, L_{st}$ \\ \hline
	Cede&$L_{gt}, W_{st}$& $L_{gt}, W_{st}$ &$Q_{gt}, Q_{st}$ \\ \hline
 %\multicolumn{4}{c} {Stage Game Payoffs}\\ 
\end{tabular}
\end{center}
\vskip.05in
where $\omega_{it} \equiv p_1 \left(W_{it}-\zeta_i\right) + \left(1-p_1\right)\left( L_{it}-\zeta_i\right)$
\begin{itemize}
	\item fixed cost of war $\zeta_i$
	\item probabilities $p_1$ of victory, $1 - p_1$ of loss 
		\begin{itemize}
			\item can also handle non-decisive war
		\end{itemize}
\end{itemize}
\vskip.05in
and e.g. $Q_{st} \equiv Q_{s,t-1} -\mu + R_{pt} - R_{ct}$
\end{frame}

\section{Status Quo Equilibrium}
\subsection{}

\begin{frame}{Unrecognized Statehood as Stable Equilibrium}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 1}
  There exists an equilibrium in which the outcome is perpetual unrecognized statehood. The actions in this equilibrium are 
	\begin{enumerate}
		\item in the first period, the patron invests to create a buffer of $\frac{\beta}{1-\delta}$ between the secessionists' payoffs from ceding and the status quo;
		\item the patron invests up to $\mu$ each period thereafter to maintain the buffer;
		\item the int'l community invests nothing;
		\item both inside players choose $Status$ $Quo$ each period.
	\end{enumerate}

\end{beamerboxesrounded}
\end{frame}

\begin{frame}{Unrecognized Statehood as Stable Equilibrium (Con't)}
\pause
  The following are sufficient conditions for the equilibrium:
	\begin{enumerate}[<+->]
		\item \textit{For each inside actor, choosing status quo provides the highest expected payoff at the beginning of the game.}

\item  \textit{The patron can afford to deter the int'l community from inducing reunification at the beginning of the game.}

\item \textit{The patron can afford to pay to maintain the status quo.}

\item \textit{Reunification is more important for the patron to avoid than for the int'l community to achieve.}

\item  \textit{Recognition is more important for the int'l community to avoid than for the patron to achieve.}

	\end{enumerate}
\end{frame}

\section{Sanctions}
\begin{frame}{Sanctions (I)}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 2}
  Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect only the secessionists' Status Quo payoffs. In order for sanctions to lead to ceding by the secessionists, the following are required:
	\pause
	\begin{enumerate}[<+->]
\item The patron must be unable or find it not worthwhile to invest the additional amount now required to maintain the status quo.

\item The patron must be unable or find it not worthwhile to invest to instigate fighting by the secessionists.

\item The continuation value from Status Quo must fall below that from Cede before it falls below that from Fight.
\end{enumerate}

\end{beamerboxesrounded}

\end{frame}

\begin{frame}{Sanctions (II)}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 3}
  Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect both the secessionists' status quo payoffs and its military capabilities. \\
	\pause
	\vskip.05in
	The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.
\end{beamerboxesrounded}

\end{frame}

\section{Conclusion}
\subsection{}
\begin{frame}{Conclusion}
\begin{itemize}[<+->]
	\item We present a unified four-player framework for analyzing unrecognized statehood and its alternatives
	\item We show unrecognized statehood can emerge in equilibrium even when it is a terrible outcome for all involved
		\begin{itemize}
			\item Unfortunately, it is not difficult to imagine Eastern Ukraine on our list of URS in 20 years
		\end{itemize}
	\item The model demonstrates why sanctions may be counterproductive and suggests that positive inducements may be more productive
\end{itemize}

\end{frame}

\end{document}

### 2016-11-29 presentation.tex
date/title/author modifications to presention

@@
 \begin{document}
-\title[Unrecognized States: A Theory of Self-Determination and Foreign Influence\hspace{1.25in}\insertframenumber/\inserttotalframenumber]{Unrecognized States: A Theory of Self-Determination and Foreign Influence}
-\author[Kristy Buzard, Benjamin Graham and Ben Horne]{Kristy Buzard, Benjamin Graham and Ben Horne\\ kbuzard@syr.edu}
-\date{September 23, 2016}
+\title[Inefficient Concessions and Mediation\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Inefficient Concessions and Mediation}
+\author[Kristy Buzard and Ben Horne]{Kristy Buzard and Ben Horne\\ kbuzard@syr.edu}
+\date{December 3, 2016}
 \maketitle
@@
 \pause
-\begin{figure}
-\includegraphics[width=\linewidth,height=\textheight,keepaspectratio]{Timeline2.pdf}
-%\caption{Timeline}
-\end{figure}
 \end{frame}

### 2016-12-01 presentation.tex
add first few results to presentation

@@
 \begin{enumerate}[<+->]
-	\item Model
-	\item Status quo equilibrium
-	\item What we can say about sanctions
+	\item M
+	\item S
+	\item W
 \end{enumerate}
@@
 \subsection{The Players}
-
-\begin{frame}{Outside Actors}
-	\pause
-International community ($c$): desires reunification \\
-\pause
-Patron ($p$): desires recognized independence
-\pause
-\begin{itemize}	
-	\item Each has preferences that are aligned with one of the home state actors
-	\pause
-	\item Patron may most prefer SQ; our assumption stacks the deck against us
-\end{itemize}
-
-\pause
-\vskip.2in
-$p$'s per period payoffs: $U_{pt} = -\alpha X + \lambda Y - R_{pt}$ \\
-$c$'s per period payoffs: $U_{ct} = \beta X - \nu Y - R_{ct}$
-\begin{itemize}
-	\item $X=1$ if the secessionists rejoin the home state \\
-	\item $Y=1$ if the home state recognizes the secessionists 
-\end{itemize}
-\end{frame}
 
@@
 \pause
+
 \begin{center}
-\begin{tabular}{|  c| c | c | c |} 
-\hline
-  $g\downarrow$,     $ s\rightarrow$  & Fight & Status Quo &Cede \\ \hline
-	Fight & $\omega_{gt}, \omega_{st}$ &$\omega_{gt}, \omega_{st}$&$W_{gt}, L_{st}$ \\ \hline
-	Status Quo& $\omega_{gt}, \omega_{st}$& $Q_{gt}, Q_{st}$ &$W_{gt}, L_{st}$ \\ \hline
-	Cede&$L_{gt}, W_{st}$& $L_{gt}, W_{st}$ &$Q_{gt}, Q_{st}$ \\ \hline
- %\multicolumn{4}{c} {Stage Game Payoffs}\\ 
+\begin{tabular}{|l|c|c|}
+  \hline      & Trust & Fight \\ \hline
+	 Trust& T, T& -D, T+W \\ \hline
+	Fight & T+W,-D& W-D, W-D \\ \hline
 \end{tabular}
 \end{center}
+
 \vskip.05in
-where $\omega_{it} \equiv p_1 \left(W_{it}-\zeta_i\right) + \left(1-p_1\right)\left( L_{it}-\zeta_i\right)$
+where 
 \begin{itemize}
-	\item fixed cost of war $\zeta_i$
-	\item probabilities $p_1$ of victory, $1 - p_1$ of loss 
-		\begin{itemize}
-			\item can also handle non-decisive war
-		\end{itemize}
+	\item $T\geq0$: Benefit from the other country playing Trust
+	\item $W\geq0$: Additional benefit from playing Fight
+	\item $D\geq0$: Damages due to the other country playing Fight
 \end{itemize}
 \vskip.05in
-and e.g. $Q_{st} \equiv Q_{s,t-1} -\mu + R_{pt} - R_{ct}$
+\pause
+Assume $T>W-D$
 \end{frame}
 
-\section{Status Quo Equilibrium}
-\subsection{}
-
-\begin{frame}{Unrecognized Statehood as Stable Equilibrium}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 1}
-  There exists an equilibrium in which the outcome is perpetual unrecognized statehood. The actions in this equilibrium are 
-	\begin{enumerate}
-		\item in the first period, the patron invests to create a buffer of $\frac{\beta}{1-\delta}$ between the secessionists' payoffs from ceding and the status quo;
-		\item the patron invests up to $\mu$ each period thereafter to maintain the buffer;
-		\item the int'l community invests nothing;
-		\item both inside players choose $Status$ $Quo$ each period.
-	\end{enumerate}
-
-\end{beamerboxesrounded}
+\begin{frame}
+\begin{itemize}[<+->]
+	\item Payoffs: sum the discounted stage game payoffs plus any concessions 
+		\begin{itemize}
+			\item e.g. player's $i$'s payoff if both parties play ``Trust'' in every period: $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}$
+		\end{itemize}
+	\item Parameters are common knowledge with the exception of $\delta_i$, which is country i's private information
+	\item Social welfare measured as sum of high types' expected utilities
+\end{itemize}
 \end{frame}
 
-\begin{frame}{Unrecognized Statehood as Stable Equilibrium (Con't)}
+\section{Benchmark}
+\subsection{No Money Burning}
+
+\begin{frame}{Benchmark Model}
 \pause
-  The following are sufficient conditions for the equilibrium:
-	\begin{enumerate}[<+->]
-		\item \textit{For each inside actor, choosing status quo provides the highest expected payoff at the beginning of the game.}
+Assume two types: $\de_h$ and $\de_l$
+\begin{itemize}[<+->]
+	\item $\de_h > \de^* > \de_l$ where $\de^*$ is the cutoff for sustaining (Trust,Trust) eqm
+	\item value of any concession to recipient = cost to giver
+\end{itemize}
 
-\item  \textit{The patron can afford to deter the int'l community from inducing reunification at the beginning of the game.}
-
-\item \textit{The patron can afford to pay to maintain the status quo.}
-
-\item \textit{Reunification is more important for the patron to avoid than for the int'l community to achieve.}
-
-\item  \textit{Recognition is more important for the int'l community to avoid than for the patron to achieve.}
-
-	\end{enumerate}
+\pause
+\vskip.2in
+Some equilibria of interest
+\begin{itemize}[<+->]
+	\item Pool on `Fight'
+	\item Separating without concessions
+	\item Separating through concessions
+\end{itemize}
 \end{frame}
 
-\section{Sanctions}
-\begin{frame}{Sanctions (I)}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 2}
-  Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect only the secessionists' Status Quo payoffs.
-In order for sanctions to lead to ceding by the secessionists, the following are required:
+\begin{frame}{Separating through concessions}
 \pause
-	\begin{enumerate}[<+->]
-\item The patron must be unable or find it not worthwhile to invest the additional amount now required to maintain the status quo.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 2}
+  In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Low types do not give a concession.
+\end{beamerboxesrounded}
 
-\item The patron must be unable or find it not worthwhile to invest to instigate fighting by the secessionists.
+	\pause
+	\vskip.2in
+	\begin{itemize}
+		\item The smallest concession is $p(T+D)$
+		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
+	\end{itemize}
+\end{frame}
 
-\item The continuation value from Status Quo must fall below that from Cede before it falls below that from Fight.
-\end{enumerate}
+\section{Inefficient Concessions}
+\subsection{Add Money Burning}
+\begin{frame}{S}
+Assume cost of concession is $g$, the concession itself
+\begin{itemize}
+  \item Allow giver of concession to also choose $0 \leq e \leq 1$, where benefit of concession is $eg$
+\end{itemize}
+
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{P}
+  With the
 
@@
 
-\begin{frame}{Sanctions (II)}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Proposition 3}
-  Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect both the secessionists' status quo payoffs and its military capabilities. \\
-	\pause
-	\vskip.05in
-	The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.
+\begin{frame}{S}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{P}
+  A
 \end{beamerboxesrounded}
@@
 \begin{itemize}[<+->]
-	\item We present a unified four-player framework for analyzing unrecognized statehood and its alternatives
-	\item We show unrecognized statehood can emerge in equilibrium even when it is a terrible outcome for all involved
-		\begin{itemize}
-			\item Unfortunately, it is not difficult to imagine Eastern Ukraine on our list of URS in 20 years
-		\end{itemize}
-	\item The model demonstrates why sanctions may be counterproductive and suggests that positive inducements may be more productive
+	\item We present 
 \end{itemize}

### 2016-12-03 presentation.tex
finish first draft of presentation

@@
 \begin{frame}
-\frametitle{Unrecognized States}
-Unrecognized states (URS): control and govern territory, seek recognition
+\frametitle{Inefficient Concessions and Mediation}
+
+In conflict scenarios, concessions are sometimes inefficient 
 \pause
 \begin{itemize}[<+->]
-  \item Six current URS more than 20 yrs old (+ Eastern Ukraine)
-	\item No explanation in the literature for how this can be a stable outcome
+  \item We show inefficient concessions may be preferable if efficient concessions have potential future cost
+	\item Cost: concessions used against you by negotiating partner who violates agreement
+	\item Can you trust that partner will make peace?
+\end{itemize}
+
+\pause
+\vskip.2in
+New explanation for mediation
+\pause
+\begin{itemize}[<+->]
+  \item Can remove uncertainty about ability of negotiating partner to commit to peace
+	\item Removes need for inefficient concessions
 \end{itemize}
@@
 \pause
-We demonstrate unrecognized statehood can be a ``status quo'' outcome
+Start with simple, two-player repeated Prisoners' Dilemma
 \pause
 \begin{itemize}[<+->]
-	\item (SPN) Equilibrium in a repeated game
-	\item Four players
+	\item Asymmetric information about $\de_i$: can partner commit to peace?
+\end{itemize}
+
+\pause
+\vskip.2in
+Add time zero: let partners give concessions with both signaling and material value
+\pause
 \begin{itemize}[<+->]
-			\item Home government
-			\item Secessionist elite
-			\item Patron state
-			\item International community
+	\item Let partners destroy some/all of the material value
+	\item Let material value provide help/harm to the giver
 \end{itemize}
-	\item State variable: Status Quo (SQ) payoffs for secessionists
+
+\pause
+\vskip.2in
+Mediator removes uncertainty about partner's $\de$
+
+\end{frame}
+
+\begin{frame}{Literature}
+\pause
+Signaling: Spence (1973), but signal has material value
+\pause
+		\begin{itemize}
+			\item cost/benefit tradeoff differs b/c of $\de_i$, $C_i(g)$
+		\end{itemize}
+
+\pause
+Gift-Giving: Camerer (1988), Prendergast $\&$ Stole (2001)
+\pause
+		\begin{itemize}
+			\item Source of inefficiency differs: gifts can be used against giver
+		\end{itemize}
+
+\pause
+Conflict: Slantchev (2011), Arena (2013)
+\pause
+		\begin{itemize}[<+->]
+			\item Commitment to peace, not resolve to fight
+			\item Concessions are costly signals instead of bargaining chip
+			\item Costly signals are concessions instead of proof of resolve
+		\end{itemize}
+
+\pause
+Mediation: Fey and Ramsay (2008, 2011), Horner et al. (2010)
+\pause
+		\begin{itemize}
+			\item Information is about ability to commit, not resolve
 		\end{itemize}
@@
 
-\begin{frame}{The General Idea}
-
-\pause
-In each period: secessionists and gov't each choose (simultaneously) among $\left\{\text{Fight, Status Quo, Cede}\right\}$
-\pause
-		\begin{itemize}
-			\item We need Status Quo to be a stage game best response for both secessionists and gov't
-		\end{itemize}
-
-\pause
-\vskip.2in
-We add some more realistic elements:
+\section{Model}
+\subsection{}
+\begin{frame}{Timeline}
 \pause
 \begin{enumerate}[<+->]
-			\item Unrecognized status reduces Status Quo payoffs of secessionists each period
-			\item Patron and int'l community can make investments in both actors' payoffs
+	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
+	\item[0.] Countries simultaneously give costly concessions: $g_1, g_2 \in \mathbb{R}_+$
+	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
 \end{enumerate}
@@
 
-\begin{frame}{Outline of Talk}
-\pause
-\begin{enumerate}[<+->]
-	\item M
-	\item S
-	\item W
-\end{enumerate}
-\end{frame}
-
-\section{Model}
-\subsection{Economic and Political Structure}
-\begin{frame}{Timeline}
-\pause
-\end{frame}
-
-\subsection{The Players}
-
-\begin{frame}{Home State Actors}
-	\pause
-Central Government of Home State ($g$): desires reunification \\
-\pause
-Secessionists ($s$): desire recognized independence
-\pause
-\begin{itemize}	
-	\item Central issue of contention: recognized independence vs. reunification.
-\end{itemize}
-
-\pause
-\vskip.2in
-Assumptions:
-\begin{itemize}[<+->]
-	\item Issue of status is indivisible, highly valued by both sides
-	\item Insufficient credible side payments for easy settlement
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Stage Game between Home Gov't $\&$ Secessionists}
+\begin{frame}{Stage Game}
 \pause
@@
 	\item $\de_h > \de^* > \de_l$ where $\de^*$ is the cutoff for sustaining (Trust,Trust) eqm
-	\item value of any concession to recipient = cost to giver
+	\item $p$: probability of high type
+	\item Low type's cost to give concession $g$: $c_l(g)>c_h(g) =g$
 \end{itemize}
@@
 Some equilibria of interest
+\pause
 \begin{itemize}[<+->]
@@
 	\vskip.2in
-	\begin{itemize}
-		\item The smallest concession is $p(T+D)$
+	\begin{itemize}[<+->]
+		\item The smallest concession is $c_l^{-1}\left(p(T+D)\right)$
 		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
@@
 \subsection{Add Money Burning}
-\begin{frame}{S}
-Assume cost of concession is $g$, the concession itself
-\begin{itemize}
-  \item Allow giver of concession to also choose $0 \leq e \leq 1$, where benefit of concession is $eg$
+\begin{frame}{Burning money is unattractive}
+\pause
+Allow giver of concession to also choose $0 \leq e \leq 1$, where benefit of concession is $eg$
+
+\vskip.1in
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 3}
+  When concessions confer no material help or harm on the giver, it is optimal to give efficient gifts ($e=1$) in a separating eqm.
+\end{beamerboxesrounded}
+\pause
+\begin{itemize}[<+->]
+	\item The benefit of the gift appears on both sides of the incentive constraint for both individuals, so cancels out
+	\item The benefit appears in the high type's expected utility
 \end{itemize}
+\end{frame}
 
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{P}
-  With the
+\begin{frame}[label=hurt]
+\frametitle{Concessions can hurt the giver}
+\pause
+Now assume a low type will use concessions against you, i.e. to increase their payoffs from fighting \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
+\vskip.1in
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 4}
+  There are parameters under which the optimal equilibrium features inefficient concessions.
+\end{beamerboxesrounded}
+\[
+  U_h=(1-\de_h)(-g) + \de_h \left[pT(1+eg)+peg+(1-p)(W-D(1+eg))\right]
+\]
+\pause
 
+\begin{itemize}[<+->]
+	\item If $p$ is low, concessions likely to be used against you, so remove material value
+	\item Conjecture: Pooling on `Fight' optimal over larger set of parameters
+\end{itemize}
+\end{frame}
+
+\section{Mediation}
+\subsection{}
+\begin{frame}{Mediator as mechanism designer}
+\pause
+`Manipulative' mediator: parties report their types, must deliver the stipulated concessions
+\pause
+\begin{itemize}[<+->]
+  \item Mechanism: if two high types, give concession and play `Trust'; Otherwise, no concession and `Fight'
+	\item Concession is necessary to get truthful revelation
+	\item Cost of concession must be greater than benefit for low type
+\end{itemize}
+\vskip.1in
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
+  A mediator can eliminate inefficient concessions.
 \end{beamerboxesrounded}
@@
 
-\begin{frame}{S}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{P}
-  A
-\end{beamerboxesrounded}
+\appendix
+\section{Supplemental}
+\begin{frame}[label=Supplemental,noframenumbering]
+\begin{center}
+Modified Stage Game Payoffs
+\begin{tabular}{|l|c|c|}
+  \hline      & Trust & Fight \\ \hline
+	 Trust& \small$T(s_2+\alpha_2g_1)$, & \small$-D(m_2+(1-\alpha_2)g_1),$ \\
+  & \small$T(s_1+\alpha_1g_2)$ & \small$T(s_1+\alpha_1g_2)  $\\ 
+	&  & $+W(m_2+(1-\alpha_2)g_1) $\\ \hline
+	Fight & \small$T(s_2+\alpha_2g_1)$& \small$W(m_1+(1-\alpha_1)g_2)$ \\
+	      & \small$+W(m_1+(1-\alpha_1)g_2),$  & \small$-D(m_2+(1-\alpha_2)g_1),$ \\
+	 & \small$-D(m_1+(1-\alpha_1)g_2) $ & \small$W(m_2+(1-\alpha_2)g_1)$ \\
+	&  & \small$-D(m_1+(1-\alpha_1)g_2)$ \\ \hline
+\end{tabular}
+\end{center}
 
-\end{frame}
-
-\section{Conclusion}
-\subsection{}
-\begin{frame}{Conclusion}
-\begin{itemize}[<+->]
-	\item We present 
-\end{itemize}
-
+Back to \hyperlink{hurt}{\beamerbutton{Concessions can hurt the giver}}.
 \end{frame}

### 2016-12-03 presentation.tex
finish presentation for Midwest Theory

@@
-%\documentclass{beamer} 
-\documentclass[handout]{beamer} 
+\documentclass{beamer} 
+%\documentclass[handout]{beamer} 
 \usetheme{Ilmenau}
@@
 		\begin{itemize}[<+->]
+			\item Concessions are costly signals instead of bargaining chip
 			\item Commitment to peace, not resolve to fight
-			\item Concessions are costly signals instead of bargaining chip
 			\item Costly signals are concessions instead of proof of resolve
@@
 		\end{itemize} 
-
 \end{frame}
@@
 \pause	
-	\vskip.2in
+\[
+  U_h=(p-1)g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
+\]
+\pause
+\vskip-.1in
+
 	\begin{itemize}[<+->]
@@
 \pause
-Now assume a low type will use concessions against you, i.e. to increase their payoffs from fighting \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
+Now assume a low type will use concessions against you, i.e. to reduce your payoffs when partner fights \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
 \vskip.1in
@@
 \end{beamerboxesrounded}
+\pause
 \[
-  U_h=(1-\de_h)(-g) + \de_h \left[pT(1+eg)+peg+(1-p)(W-D(1+eg))\right]
+  U_h=peg-g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
 \]
 \pause
-
+\vskip-.1in
 \begin{itemize}[<+->]
@@
   \item Mechanism: if two high types, give concession and play `Trust'; Otherwise, no concession and `Fight'
-	\item Concession is necessary to get truthful revelation
+	\item Concession is necessary to get truthful revelation, but only to high type
 	\item Cost of concession must be greater than benefit for low type

### 2016-12-08 draft.tex
minor revisions to draft caught during work on presentation for Midwest Theory

@@
 
-This paper uses a two-sided Spence signaling (1973) model to propose a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
+This paper uses a two-sided signaling model to propose a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
 We then suggest a new explanation for the effectiveness of third-party mediation.
@@
 A low type, though perhaps willing, is unable to do so.
-A low type may posture like the high type, but lacks the political muscle or will to make the necessary concessions for peace.
+A low type may posture like the high type, but lacks the political muscle or will to follow through on a peace agreement.
 Democratic leaders may more often be high types because they are less likely to face coups or other hostilities in reaction to short term decisions.
@@
 
-\section{Analysis of benchmark cases }
+\section{Analysis of benchmark cases}
+\label{sec:bench}
 When countries are faced with doubts about each other's motives, they have several options of how to proceed.
@@
 By giving costly concessions, they signal their intentions in a way that a partner unwilling to make peace would not be willing to signal.
-A mediator can sometimes make this a possibility, as will be shown in section 7, but this equilibrium is also achievable bilaterally in some cases.
+A mediator can sometimes make this a possibility, as will be shown in Section~\ref{sec:med}, but this equilibrium is also achievable bilaterally in some cases.
 
@@
 Both parties gave concessions (Israel a material land concession and Egypt diplomatic recognition of Israel) that signaled their willingness to end the stalemate that had characterized the previous five years.
-Of course this result depended on Carter's use of mediation techniques, including use of manipulative mediation -- a concept we will explore in section 7 below.
+Of course this result depended on Carter's use of mediation techniques, including use of manipulative mediation -- a concept we will explore in Section~\ref{sec:med} below.
 
@@
 \section{Inefficiency and concessions} % Lake says combine this from the start and allow inefficiency
+\label{sec:IC}
 We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
@@
 \emph{Proof:}
-The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
+The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
 However, the expected separation utilities under this game are now
@@
 
-Allow $T,W$ and $D$ to be functions $T(\cdot),W(\cdot)$ and $D(\cdot)$.
-Payoffs depend on arguments $s_i$, the size of country i's civil society and $m_i$, the size of country i's military.
-$s_i$ and $m_i$ are exogenous.
+Allow $T,W$ and $D$ to be functions that depend on arguments $s_i$, the size of country i's civil society and $m_i$, the size of country i's military. $s_i$ and $m_i$ are exogenous.
 
@@
   \hline      & Trust & Fight \\ \hline
-	 Trust& \small$T(s_2+\alpha_2g_1)$, & \small$-D(m_2+(1-\alpha_2)g_1),$ \\
-  & \small$T(s_1+\alpha_1g_2)$ & \small$T(s_1+\alpha_1g_2)  +W(m_2+(1-\alpha_2)g_1) $\\ \hline
-	Fight & \small$T(s_2+\alpha_2g_1)+W(m_1+(1-\alpha_1)g_2),$& \small$W(m_1+(1-\alpha_1)g_2)-D(m_2+(1-\alpha_2)g_1),$ \\
-	 & \small$-D(m_1+(1-\alpha_1)g_2) $ & \small$W(m_2+(1-\alpha_2)g_1)-D(m_1+(1-\alpha_1)g_2)$ \\ \hline
+	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
+  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
+	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
+	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
 \end{tabular}
@@
 \section{Mediation}
+\label{sec:med}
 All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator which will be modeled as a mechanism.
@@
 The countries are bound to send the mandated concessions.
-The benchmark case requires the countries to send the same concession to both types, since types are private information.
+The benchmark case analyzed in Sections~\ref{sec:bench} and \ref{sec:IC} requires the countries to send the same concession to both types, since types are private information.
 $M$ can differentiate based on recipient's type.
@@
 
-Since the low type IC constraint binds, the only way which a mechanism can improve upon the benchmark case is by having asymmetric costs of giving for the types.
+Since the low type IC constraint binds, the only way in which a mechanism can improve upon the benchmark case is by having asymmetric costs of giving for the types.
 As per Theorem 4, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.

### 2017-06-06 notes.tex
add notes.tex to hold work on new result

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.4in}
\addtolength{\oddsidemargin}{-.7in} %left margin
\addtolength{\evensidemargin}{-.7in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.5in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{xcolor}
\hbadness=10000

\newtheorem{proposition}{Proposition}
\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\btw}{\bm{\tau^{tw}}}
\newcommand{\ga}{\gamma}
\newcommand{\Ga}{\Gamma}
\newcommand{\de}{\delta}

\begin{document}
\begin{center}
  Working notes for Inefficient Concessions
\end{center}

\vskip.3in
\un{June 6, 2017}\\
Want to develope result showing that mediator increases potential for peace
\begin{itemize}
	\item I
\end{itemize}

\end{document}

### 2017-06-07 notes.tex
add initial notes for result about mediator making peace more attainable

@@
 \un{June 6, 2017}\\
-Want to develope result showing that mediator increases potential for peace
+Want to develop result showing that mediator increases potential for peace
 \begin{itemize}
-	\item I
+	\item i.e. want to show mediator makes (Trust, Trust) and equilibrium over a larger parameter space than without mediator
 \end{itemize}
 
+\vskip.2in
+What do we know?
+\begin{itemize}
+	\item Theorem 4: Under some parameters, optimal concessions aren't made when there isn't trust
+		\begin{itemize}
+			\item This is still a separating equilibrium, but completely inefficient concessions are given. So welfare is lower because of inefficient concessions. 
+			\item Where there is a possibility of mediation helping to achieve peace where it otherwise would not be attainable (not just improving welfare) is if this reduction in welfare due to the inefficient concessions means that for some parameters it's not worth separating so we don't get peace at all without the mediator.
+				\begin{itemize}
+					\item i.e. when welfare for high type from separating falls below that for pooling, separating is no longer an equilibrium (convo with Jean-Guillaume).
+				\end{itemize}
+		\end{itemize}
+	\item Theorem 5: Mediator eliminates inefficient concessions
+		\begin{itemize}
+			\item Here, we're already in that parameter space where there \emph{are} inefficient concessions
+		\end{itemize}
+\end{itemize}
+
+\vskip.5in
+Will need to start by assuming that $\de_h <$ threshold where separating with no concessions works.
+
 \end{document}

### 2017-06-07 notes.tex
add math for intermediate result on Thm 4

@@
 
+\vskip1in
+Intermediate step for Theorem 4
+\begin{itemize}
+	\item Low type IC constraint to solve for equilibrium high type gift
+	\item Already having shown $g_l = 0$, can set $g_h = g$ for simplicity of notation
+	\item Also, since all the discount factors are for the low type, I'll let $\de_l = \de$
+	\item For the case where $e=1$:
+
+\end{itemize}
+IC constraint:
+\[
+  X_{FF}^l \geq p X_{FT}^l + (1-p) X_{FF}^l - g
+\]
+Expanded in basic terms (without efficiency issues)
+\[
+  \frac{W-D}{1-\de} \geq p \left[T + W + \frac{\de}{1-\de}\left(W-D\right)\right] + (1-p) \frac{W-D}{1-\de} - g
+\]
+Multiply through by $\left(1-\de \right)$
+\[
+  W-D \geq p\left(1-\de \right) \left[T + W\right] + p\de \left(W-D\right) + (1-p) \left[W-D\right] - \left(1-\de \right) g
+\]
+Now add complexity from Table 2
+\begin{multline*}
+  W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1) \geq \\
+	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+(1-\al_1)g_2)\right] + p\de \left(W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+(1-\al_1)g_2)-D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
+\end{multline*}
+Substitute in $\al_1 = 0$ everywhere since this is the IC for a low-type of player 1:
+\begin{multline*}
+  W(1+g_2) - D(1+(1-\al_2)g_1) \geq \\
+	p\left(1-\de \right) \left[T(1+\al_2 g_1) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g_1)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g_1)\right] - \left(1-\de \right) g
+\end{multline*}
+Set $g_1 = 0$ on the LHS and $g_1 = g$ on the RHS:
+\begin{multline*}
+  W(1+g_2) - D \geq \\
+	p\left(1-\de \right) \left[T(1+\al_2 g) + W(1+g_2) \right] + p\de \left(W(1+g_2) - D(1+(1-\al_2)g)\right) \\ + (1-p) \left[W(1+g_2) - D(1+(1-\al_2)g)\right] - \left(1-\de \right) g
+\end{multline*}
+Set $g_2 = 0$ and $\al_2 = 0$ wherever there is a $(1-p)$ and $g_2 = g$ and $\al_2 = 1$ wherever there is a $p$:
+\begin{multline*}
+  pW(1+g) + (1-p)W - D \geq \\
+	p\left(1-\de \right) \left[T(1+g) + W(1+g) \right] + p\de \left(W(1+g) - D\right) \\ + (1-p) \left[W - D(1+g)\right] - \left(1-\de \right) g
+\end{multline*}
+Expand
+\begin{multline*}
+  pW + pWg + W - pW - D \geq \\
+	\left(p-p\de \right) \left[T+Tg + W+Wg \right] + p\de \left(W+Wg - D\right) \\ + (1-p) \left[W - D -Dg\right] - \left(1-\de \right) g
+\end{multline*}
+Cancel some like terms and move $\left(1-\de \right) g$ to LHS
+\begin{multline*}
+  \left(1-\de \right) g + pWg + W - D \geq \\
+	p\left[T+Tg + W+Wg \right] -p\de \left[T+Tg \right] - p\de D \\ + (1-p) \left[W - D -Dg\right] 
+\end{multline*}
+Do some more canceling and expanding
+\begin{multline*}
+  \left(1-\de \right) g + W - D \geq \\
+	p\left[T+Tg + W\right] -p\de T -p\de Tg - p\de D \\ + W - D -Dg -pW +pD +pDg
+\end{multline*}
+\[
+  \left(1-\de \right) g \geq 
+	pT+pTg + pW -p\de T -p\de Tg - p\de D  -Dg -pW +pD +pDg
+\]
+\[
+  \left(1-\de \right) g \geq pT+pTg -p\de T -p\de Tg - p\de D  -Dg +pD +pDg
+\]
+Now just rearrange to get all the $g$ terms on the left
+\[
+  \left(1-\de \right) g -pTg + p\de Tg + Dg - pDg\geq pT -p\de T - p\de D +pD
+\]
+\[
+  \left[\left(1-\de \right) -p(1-\de)T +(1-p)D\right]g \geq p(1-\de)(T + D)
+\]
+\[
+  g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
+\]
+In comparing to the minimum separating gift when $e=0$, which is
+\[
+  g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)}
+\]
+We can simplify to see that the minimum gift when $e=1$ is larger when
+\[
+  (1-\de)pT > (1-p)D
+\]
+
 \end{document}

### 2017-06-09 param-search.R
add .R program to test parameters

@@ -1,0 +1,22 @@
+T=10
+W=8
+D=5
+dl = .45
+p = .4
+
+#Separating w/out concessions for dh such that:
+dh_swoc = W/((1-p)*W +p*(T+D))
+
+#Separating with concessions when alpha = 1 for dh such that:
+dh_swc = W/(T+D)
+
+dh = .6
+#Separating with concessions can be either with e=1 or e=0. Which does high type choose?
+g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) #gift necessary to separate if e = 1
+g0 = p*(D+T)                                   #gift necessary to separate if e = 0   
+
+uh_g1 = (1-dh)*-g1 + dh*(p*T*(1+g1) + p*g1 +(1-p)*(W-D-D*g1))
+uh_g0 = (1-dh)*-g0 + dh*(p*T + (1-p)*(W-D))
+
+dh1Th = W*(1-p)+1-p*T + p*(W-(T+D))/g1
+dh0Th = W*(1-p)+1-p*T + p*(W-(T+D))/g0

### 2017-06-22 presentation.tex
presentation at CesIfo Venice 06/15/17

@@
 \author[Kristy Buzard and Ben Horne]{Kristy Buzard and Ben Horne\\ kbuzard@syr.edu}
-\date{December 3, 2016}
+\date{June 15, 2017}
 \maketitle
@@
 \begin{itemize}[<+->]
+	\item Let material value provide help/harm to the giver
 	\item Let partners destroy some/all of the material value
-	\item Let material value provide help/harm to the giver
 \end{itemize}
@@
 	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
-	\item[0.] Countries simultaneously give costly concessions: $g_1, g_2 \in \mathbb{R}_+$
+	\item[0.] Countries simultaneously give costly concessions: $g_i \in \mathbb{R}_+$
 	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
@@
 \begin{itemize}[<+->]
-	\item Payoffs: sum the discounted stage game payoffs plus any concessions 
+	\item Payoffs: sum the discounted stage game payoffs plus any concessions given or received
 		\begin{itemize}
-			\item e.g. player's $i$'s payoff if both parties play ``Trust'' in every period: $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}$
+			\item e.g. player's $i$'s payoff if both parties give no concession and play ``Fight'' in every period: $$\sum_{t=1}^\infty \de_i^{t-1} (W-D) = \frac{W-D}{1-\de_i}$$
 		\end{itemize}
@@
 \begin{itemize}[<+->]
-	\item $\de_h > \de^* > \de_l$ where $\de^*$ is the cutoff for sustaining (Trust,Trust) eqm
+	\item $\de_h > \de^* > \de_l$ where $\de^*=\frac{W}{T+D}$ is the cutoff for sustaining (Trust,Trust) eqm
 	\item $p$: probability of high type
-	\item Low type's cost to give concession $g$: $c_l(g)>c_h(g) =g$
+	\item Cost of giving concessions $g$: $g = c_l(g)\geq c_h(g) = g$
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Pool on `Fight'
 	\item Separating without concessions
 	\item Separating through concessions
+	\item Pool on `Fight'
 \end{itemize}
@@
 \[
-  U_h=(p-1)g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
+  U_h=pg - c_h(g) + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
 \]
@@
 	\begin{itemize}[<+->]
-		\item The smallest concession is $c_l^{-1}\left(p(T+D)\right)$
+		\item The smallest concession is $p(T+D)$
 		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
@@
 \subsection{Add Money Burning}
+\begin{frame}{Timeline}
+\pause
+\begin{enumerate}[<+->]
+	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
+	\item[0.] Concessions
+		\begin{enumerate}
+			\item[0a.] Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$ 
+			\item[0b.] \textcolor{red!75!green!50!blue!25!gray}{Countries decide what proportion of a received concession to invest in civil society (vs. military capabilities): $\alpha_i \in [0,1]$}
+		\end{enumerate}	
+	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
+\end{enumerate}
+\end{frame}
+
 \begin{frame}{Burning money is unattractive}
 \pause
-Allow giver of concession to also choose $0 \leq e \leq 1$, where benefit of concession is $eg$
+Now benefit of concession is $eg$
 
@@
 	\item The benefit of the gift appears on both sides of the incentive constraint for both individuals, so cancels out
+	\item Costs of giving a concession don't change
 	\item The benefit appears in the high type's expected utility
 \end{itemize}
+\end{frame}
+
+\begin{frame}{Timeline}
+\pause
+\begin{enumerate}[<+->]
+	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
+	\item[0.] Concessions
+		\begin{enumerate}
+			\item[0a.] Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$ 
+			\item[0b.] \textcolor{blue}{Countries decide what proportion of a received concession to invest in civil society (vs. military capabilities): $\alpha_i \in [0,1]$}
+		\end{enumerate}	
+	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
+\end{enumerate}
 \end{frame}
@@
 \pause
-Now assume a low type will use concessions against you, i.e. to reduce your payoffs when partner fights \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
-\vskip.1in
-\pause
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 4}
-  There are parameters under which the optimal equilibrium features inefficient concessions.
+  When the low type country can use concessions to reduce the payoffs of its negotiating partner during a `fight' stage (i.e.
+$\alpha_L < 1$), there are parameters under which the separating-through-concessions equilibrium features inefficient concessions.
 \end{beamerboxesrounded}
+\hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
 \pause
 \[
-  U_h=peg-g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
+  U_h=peg - c_h(g) + \textstyle \frac{\de_h}{1-\de_h} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
 \]
@@
 	\item If $p$ is low, concessions likely to be used against you, so remove material value
-	\item Conjecture: Pooling on `Fight' optimal over larger set of parameters
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Peace not possible in some scenarios}
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
+  When $\alpha_L < 1$ is allowed, peace becomes unachievable for some parameters under which it is achievable when concessions do not have material value.
+\end{beamerboxesrounded}
+
+\pause
+\vskip.1in
+\begin{itemize}[<+->]
+	\item If peace is achievable, concessions may be either efficient or inefficient
+	\item High-type utility may increase or decrease from no-material-value case
 \end{itemize}
@@
 	\item Concession is necessary to get truthful revelation, but only to high type
-	\item Cost of concession must be greater than benefit for low type
+	\item Need cost of concession for low type to be not to large relative to cost for high type
 \end{itemize}
@@
 \pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
-  A mediator can eliminate inefficient concessions.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 6}
+  A mediator restores peace where $\alpha_i < 1$ destroys it, eliminates inefficient concessions, and reduces the threshold $\de_h$ for high types.
 \end{beamerboxesrounded}

### 2017-06-22 param-search.R

@@ -2,21 +2,24 @@ T=10
 W=8
 D=5
 dl = .45
-p = .4
+p = .3
 
 #Separating w/out concessions for dh such that:
 dh_swoc = W/((1-p)*W +p*(T+D))
 
 #Separating with concessions when alpha = 1 for dh such that:
-dh_swc = W/(T+D)
+dh_stc = W/(T+D)
 
-dh = .6
+dh = dh_stc
 #Separating with concessions can be either with e=1 or e=0. Which does high type choose?
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) #gift necessary to separate if e = 1
 g0 = p*(D+T)                                   #gift necessary to separate if e = 0   
 
-uh_g1 = (1-dh)*-g1 + dh*(p*T*(1+g1) + p*g1 +(1-p)*(W-D-D*g1))
-uh_g0 = (1-dh)*-g0 + dh*(p*T + (1-p)*(W-D))
+uh_g1 = (1-dh)*(p-1)*g1 + dh*(p*T*(1+g1) + p*g1 +(1-p)*(W-D-D*g1))
+uh_g0 = (1-dh)*(p-1)*g0 + dh*(p*T + (1-p)*(W-D))
 
 dh1Th = W*(1-p)+1-p*T + p*(W-(T+D))/g1
 dh0Th = W*(1-p)+1-p*T + p*(W-(T+D))/g0
+
+#What would happen for these parameters with the mediator? Only dh_stc matters, 
+#and this is guaranteed by assuption on dh

### 2017-06-22 notes.tex
add notes from presentation and prep for presentation to notes.tex

@@
 \[
-  g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)}
+  g^* \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)}
 \]
@@
 
+\vskip.5in
+Next we get the threshold for $\de_h$ that is necessary for a concessions separating eqm to exist:
+\begin{itemize}
+	\item Use the high-type IC constraint:
+		\[
+		  p X^h_{TT} + (1-p) X^h_{FF} - g_h \geq X^h_{FF}
+		\]
+	\item We'll need to expand for material effects but then solve for both $e=0$ and $e=1$
+	\item For $e=1$:
+		\[
+		  \frac{p}{1-\de_h}T(1+g) + \frac{1-p}{1-\de_h}(W - D(1+g)) - g_h \geq \frac{1}{1-\de_h}(W-D)
+		\]
+		\[
+		  pT + pTg + (1-p)(W - D - Dg) - g_h(1-\de_h) \geq W-D
+		\]
+		\[
+		  pT + pTg + W - D - Dg - pW + pD + pDg - g_h + g_h \de_h \geq W-D
+		\]
+		\[
+		  pT + pTg - Dg - pW + pD + pDg - g_h + g_h \de_h \geq 0
+		\]
+		\[
+		  pT + pTg - Dg - pW + pD + pDg - g_h + g_h \de_h \geq 0
+		\]
+\end{itemize}
+
+\newpage
+To-do list after Venice CesIfo 06/15/17:
+\begin{itemize}
+	\item Add discussion of intuitive criterion to text (if I end up needing it): out of eqm beliefs put zero weight on types that can never gain from deviating from a fixed eqm outcome
+	\item Pin down whether it matters for mediator outcome if $c_h = c$ or $c_h = c(g)$
+	\item Incorporate mediator result into text; re-organize text so it matches June presentation more closely
+	\item Note for mediator result:
+		\begin{itemize}
+			\item For two high types to cooperate in the mechanism, need large enough gift to screen out low types.
+They're still just reporting, so don't give a gift if not matched with another high type.
+PLUS when they're exchanging gifts, the gifts will actually be used for good:
+				\[
+				  T(1+g) \geq (1-\de)[T(1+g) + W] + \de (W-D)
+				\]
+				\[
+				  \de \geq \frac{W}{T + Tg + D}
+				\]
+				Note that this threshold is smaller than $\frac{W}{T + D}$, the one we get without concessions having material benefit / harm
+		\end{itemize}
+	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game; he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
+	\item Someone who \textit{can't} cooperate under either $e=0$ or $e=1$ CAN cooperate under mediator
+		\begin{itemize}
+			\item In the absence of mediation, being able to burn money can help, but you still lose something
+			\item I still have a question about the overall game: if $e=0$ provides higher welfare if it were enforceable but it's not, do we just go with $e=1$?
+This question goes away if I get rid of the repeated game.
+			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$
+				\begin{itemize}
+					\item $p=.4, \de_l = .45, \de_h = \de_{STC} = .53$. Choose $e=1$, but $\de_1 = .65$
+					\item $p=.3, \de_l = .45, \de_h = \de_{STC}  = .53$. Choose $e=1$, but $\de_1 > 1$; even worse at $p=.2$
+					\item $p=.4, \de_l = .5, \de_h = \de_{STC} = .53$. Choose $e=1$, $\de_1 \geq .4$ (works fine)
+					\item $p=.1, \de_l = .1, \de_h = \de_{STC} = .53$. Choose $e=0$, but $\de_0 \geq 6.7$
+					\item $p=.05, \de_l = .5, \de_h = .7$. Choose $e=0$, but $\de_0 = 7.6$
+					\item $p=.1, \de_l = .5, \de_h = .75$. Choose $e=0$, but $\de_0 = 6.7$ and $\de_1 \geq 3$
+				\end{itemize}
+		\end{itemize}
+\end{itemize}
 \end{document}

### 2017-08-25 draft.tex
add notes.tex to hold work on new result
add revision notes to to-do and fix a typo in draft

@@
 \\}
-\date{September 30, 2016}
+\date{\today}
 %To Do : define what is ineffieicncy
@@
 Concessions are given at cost $C(g_i)$ and benefit the recipient $g_i$, where $i\in\left\{l,h\right\}$.
-For simplicity, let us initially assume $C(g_i)= g_i$.
+For simplicity, we initially assume $C(g_i)= g_i$.
 We will relax this assumption later.
@@
 The analysis is conducted with standard Incentive Compatibility and Individual Rationality constraints.
-Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever played forever if Fight is played by any party in any round.
+Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round.
 This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace.

### 2017-09-09 notes.tex
add revision notes to to-do and fix a typo in draft
update notes for progress on static version, other minor details

@@
 \begin{itemize}
-	\item i.e. want to show mediator makes (Trust, Trust) and equilibrium over a larger parameter space than without mediator
+	\item i.e. want to show mediator makes (Trust, Trust) an equilibrium over a larger parameter space than without mediator
 \end{itemize}
@@
 
-\vskip.5in
-Will need to start by assuming that $\de_h <$ threshold where separating with no concessions works.
+\vskip.4in
+Need to start by assuming that $\de_h <$ threshold where separating with no concessions works.
+\begin{itemize}
+	\item \textbf{Check to see whether Theorem 4 proof has to change.}
+\end{itemize}
 
-\vskip1in
+\vskip.4in
 Intermediate step for Theorem 4
@@
 		\end{itemize}
-	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game; he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
+	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost
+		\begin{itemize}
+			\item he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
+		\end{itemize}
 	\item Someone who \textit{can't} cooperate under either $e=0$ or $e=1$ CAN cooperate under mediator
@@
 			\item I still have a question about the overall game: if $e=0$ provides higher welfare if it were enforceable but it's not, do we just go with $e=1$?
-This question goes away if I get rid of the repeated game.
 			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$
@@
 		\end{itemize}
+	\item From Eli four years ago: why can mediator do what the two sides cannot?
+		\begin{itemize}
+			\item How does this differ from binding arbitration?
+		\end{itemize}
+	\item Be clear about assumptions on cost of gifts; make statement in third paragraph of model section match
 \end{itemize}

### 2017-09-09 draft.tex
remove differentiated costs (not necessary)

@@
 In period 0, countries 1 and 2 simultaneously give costly concessions $g_1$ and $g_2$ $\in \mathbb{R} \geq 0$.
-Concessions are given at cost $C(g_i)$ and benefit the recipient $g_i$, where $i\in\left\{l,h\right\}$.
-For simplicity, we initially assume $C(g_i)= g_i$.
-We will relax this assumption later.
+Concessions are given at cost $C(g_i)$ and benefit the recipient in the amount $g_i$, where $i\in\left\{1,2\right\}$.
+For simplicity, we assume $C(g_i)= g_i$.
 
@@
 The revelation principle is used to attain truthful self-identification (Myerson 1979).
-For mediation to be useful, $C_l(\cdot)$ needs to be pointwise greater than $C_h(\cdot)$, and we will assume this.
-This means that a low type is not identical to a high type, and indeed bears greater costs for peaceful actions.
-This can be thought of as a leader who must explain peace to his people.
-If the people want to make peace with the rival, posturing for peace is not costly for the leader.
-But if the people do not want to make peace with the rival, the leader loses credibility by outwardly touting peace.
-Therefore taking a peaceful action is more costly, and perhaps even impossible.
-This low type leader can bluff in the bilateral setting but not, as we will see, when a mediator is present.
-\\
+
 \\
 {\bf Theorem 5:} A mediator can be used to eliminate inefficient concessions. \\
-\emph{Proof:}  $C_l(\cdot)> C_h(\cdot)$ as per the assumption above.
-The low type IC ($pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
+\emph{Proof:}  The low type IC ($pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
 Under $M$, the low type IC can bind without having high types give a concession to low types.
@@
 
-Since the low type IC constraint binds, the only way in which a mechanism can improve upon the benchmark case is by having asymmetric costs of giving for the types.
+The low type leader can bluff in the bilateral setting but not when a mediator is present.
 As per Theorem 4, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.
-If costs are disparate, under certain parameters the mediator can mandate concessions only between declared high types.
+But because the benefits of giving a concession differ between the types (low types get one period of cheater's payoff, while high types get future peace), the mediator is able to mandate concessions only between declared high types.
 This means there is no longer a need for inefficient concessions since concessions will never be used against the giver.

### 2017-09-09 draft.tex
clean up last page of appendix

@@
 \ee
-In terms of original variables, the condition for a concessions separating equilibrium to exist is:
+In terms of fundamentals, the condition for a concessions separating equilibrium to exist is:
 \be
 %p_1(\frac{T+D-W}{1-\delta_h}-p_2(T+D)\geq 0. point is the p's arent the same; i might have gotten them backwards. simplified this is:
-\frac{T+D-W}{1-\delta_h}-(T+D)\geq 0
+\delta_h \geq \frac{W}{T+D}
 \ee
+That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type.
 $\blacksquare$\\
 
-The no-concessions separating equilibrium also will exist if equation (8) holds.
-In the case that both exist, the preferable equilibrium will be the one with a higher  payoff.
-The high types will prefer the concessions separating equilibrium if and only if
+The no-concessions separating equilibrium also will exist if equation (8) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
 \be
@@
 \be
- (1-p)W-p(T+D)\geq0.
+ (1-p)W-p(T+D)\geq 0
+\ee
+i.e.,
+\be
+ W\geq p(W + T+D)\geq 0
 \ee

### 2017-09-09 notes.tex
remove differentiated costs (not necessary)
fix threshold values in param-search

@@
 \begin{itemize}
+	\item From Eli four years ago: why can mediator do what the two sides cannot?
 	\item Add discussion of intuitive criterion to text (if I end up needing it): out of eqm beliefs put zero weight on types that can never gain from deviating from a fixed eqm outcome
-	\item Pin down whether it matters for mediator outcome if $c_h = c$ or $c_h = c(g)$
-	\item Incorporate mediator result into text; re-organize text so it matches June presentation more closely
+	\item Incorporate mediator result into text; re-organize text so it matches June presentation (re-worded Theorem 4, new Theorem 5)
+		\begin{itemize}
+			\item Careful of SWOC being chosen over STC ($\de_h$ threshold restriction?)
+		\end{itemize}
 	\item Note for mediator result:
@@
 		\end{itemize}
-	\item From Eli four years ago: why can mediator do what the two sides cannot?
-		\begin{itemize}
-			\item How does this differ from binding arbitration?
-		\end{itemize}
-	\item Be clear about assumptions on cost of gifts; make statement in third paragraph of model section match
+
 \end{itemize}

### 2017-09-09 param-search.R

@@ -1,8 +1,8 @@
 T=10
 W=8
 D=5
-dl = .45
-p = .3
+dl = .1
+p = .2
 
 #Separating w/out concessions for dh such that:
 dh_swoc = W/((1-p)*W +p*(T+D))
@@ -18,8 +18,10 @@ g0 = p*(D+T)                                   #gift necessary to separate if e 
 uh_g1 = (1-dh)*(p-1)*g1 + dh*(p*T*(1+g1) + p*g1 +(1-p)*(W-D-D*g1))
 uh_g0 = (1-dh)*(p-1)*g0 + dh*(p*T + (1-p)*(W-D))
 
-dh1Th = W*(1-p)+1-p*T + p*(W-(T+D))/g1
-dh0Th = W*(1-p)+1-p*T + p*(W-(T+D))/g0
+dh1Th = D*(1-p)+1-p*T + p*(W-(T+D))/g1
+dh0Th = 1 + p*(W-(T+D))/g0
+
+uh_swoc = p*T/(1-dh) + (1-p)*(dh*(W-D)/(1-dh)-D)
 
 #What would happen for these parameters with the mediator? Only dh_stc matters, 
 #and this is guaranteed by assuption on dh

### 2017-09-11 param-search.R
fix utility calculations in param-search

@@ -1,8 +1,8 @@
 T=10
 W=8
 D=5
-dl = .1
-p = .2
+dl = .2
+p = .3
 
 #Separating w/out concessions for dh such that:
 dh_swoc = W/((1-p)*W +p*(T+D))
@@ -10,18 +10,18 @@ dh_swoc = W/((1-p)*W +p*(T+D))
 #Separating with concessions when alpha = 1 for dh such that:
 dh_stc = W/(T+D)
 
-dh = dh_stc
+dh = .6
 #Separating with concessions can be either with e=1 or e=0. Which does high type choose?
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) #gift necessary to separate if e = 1
 g0 = p*(D+T)                                   #gift necessary to separate if e = 0   
 
-uh_g1 = (1-dh)*(p-1)*g1 + dh*(p*T*(1+g1) + p*g1 +(1-p)*(W-D-D*g1))
-uh_g0 = (1-dh)*(p-1)*g0 + dh*(p*T + (1-p)*(W-D))
+uh_g1 = (p*T*(1+g1))/(1-dh) - g1 + ((1-p)*(W-D-D*g1))/(1-dh)
+uh_g0 = (p*T)/(1-dh) - g0 + ((1-p)*(W-D))/(1-dh)
 
 dh1Th = D*(1-p)+1-p*T + p*(W-(T+D))/g1
 dh0Th = 1 + p*(W-(T+D))/g0
 
 uh_swoc = p*T/(1-dh) + (1-p)*(dh*(W-D)/(1-dh)-D)
-
+uh_pool = (W-D)/(1-dh)
 #What would happen for these parameters with the mediator? Only dh_stc matters, 
 #and this is guaranteed by assuption on dh

### 2017-09-12 draft.tex
move material value above inefficiency; start to soft-code theorem references

@@
   \doublespacing
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
 
@@
 Otherwise, both countries play Fight in all following periods.
-\\
-\\
-{\bf Theorem 1:} The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.\\
+
+\begin{theorem}
+	The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
+	\label{theorem:1}
+\end{theorem}
 \emph{Proof}: See appendix.
@@
 
-\section{Inefficiency and concessions} % Lake says combine this from the start and allow inefficiency
+\section{Material Value of Concession and Inefficiency} 
 \label{sec:IC}
-We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
-For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country.
-The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.
-
-In the model, countries choose a scalar $e$ to multiply by their given concession $g$.
-$0 \leq e \leq 1$.
-As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$.
-The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
-These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
-The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix.
-\\
-\\
-{\bf Theorem 3:} It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium. \\
-\emph{Proof:}
-The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
-However, the expected separation utilities under this game are now
-\be
-U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
-\ee
-and
-\be
-U_l=X_{FF}+peg_h 
-\ee
- $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
-It also holds for any monotone cost function.}$\blacksquare$
-
 We now model concessions to potentially have real material help or harm to the giver.
@@
 \begin{center}
-\captionof{table}{Modified Stage Game Payoffs}
+\captionof{table}{Stage Game Payoffs when Concessions have Material Value}
 \begin{tabular}{|l|c|c|}
   \hline      & Trust & Fight \\ \hline
-	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
-  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
-	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
-	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
+	 Trust& \small$T(s_2+\alpha_2 g_1)$, & \small$-D(m_2+(1-\alpha_2) g_1),$ \\
+  & \small$T(s_1+\alpha_1 g_2)$ & \small$T(s_1+\alpha_1 g_2)  +W(m_2+(1-\alpha_2) g_1) $\\ \hline
+	Fight & \small$T(s_2+\alpha_2 g_1)+W(m_1+(1-\alpha_1) g_2),$& \small$W(m_1+(1-\alpha_1) g_2)-D(m_2+(1-\alpha_2) g_1),$ \\
+	 & \small$-D(m_1+(1-\alpha_1) g_2) $ & \small$W(m_2+(1-\alpha_2) g_1)-D(m_1+(1-\alpha_1) g_2)$ \\ \hline
 \end{tabular}
@@
 $\blacksquare$
+
+We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
+For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country.
+The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.
+
+In the model, countries choose a scalar $e$ to multiply by their given concession $g$.
+$0 \leq e \leq 1$.
+As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$.
+The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
+These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
+The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix.
+\\
+\\
+
+\begin{center}
+\captionof{table}{Stage Game Payoffs when Concessions have Material Value}
+\begin{tabular}{|l|c|c|}
+  \hline      & Trust & Fight \\ \hline
+	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
+  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
+	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
+	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
+\end{tabular}
+\end{center}
+
+{\bf Theorem 3:} It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium. \\
+\emph{Proof:}
+The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
+However, the expected separation utilities under this game are now
+\be
+U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
+\ee
+and
+\be
+U_l=X_{FF}+peg_h 
+\ee
+ $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
+It also holds for any monotone cost function.}$\blacksquare$
+
 %need to also write constraints for high type IC to be satisfied, or appeal to forward induction
@@
 
-\\
 {\bf Theorem 5:} A mediator can be used to eliminate inefficient concessions. \\
@@
  \\
-{\bf Theorem 1:} The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}$.\\
- \emph{Proof}:
+ \emph{Proof of Theorem \ref{theorem:1}}:\\
 Countries with the equilibrium strategy to play Trust in the first round reveal themselves as a high type as per Lemma 2.

### 2017-09-12 draft.tex
soft code all theorems and lemmas

@@
 Active fighting is not necessary; remaining outside of a state of peace is all that is required.
-See Lemma 1 and Lemma 2 in the appendix for a formal characterization of this type of equilibrium.
+See Lemma~\ref{lemma:1} and Lemma~\ref{lemma:2} in the appendix for a formal characterization of this type of equilibrium.
 
@@
 \\
-{\bf \emph{Lemma 3:}} In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium. \\
+\begin{lemma}
+	In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium.
+	\label{lemma:3}
+\end{lemma}
 \emph{Proof:} See appendix.\\
-\\
-{\bf Theorem 2:} In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.\\
+
+\begin{theorem}
+	In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.
+	\label{theorem:2}
+\end{theorem}
 \emph{Proof:} See appendix.
@@
 \vskip.1in
-{\bf Theorem 4:} Under some parameters, the optimal equilibrium uses inefficient concessions. \\
+\begin{theorem}
+	Under some parameters, the optimal equilibrium uses inefficient concessions.
+	\label{theorem:4}
+\end{theorem}
  \emph{Proof}:   Because it is relatively complicated to calculate equilibrium concessions in the general case, a slight simplification of the general model will be made for proof of inefficient concessions.
@@
 
-{\bf Theorem 3:} It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium. \\
+\begin{theorem}
+	It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium.
+	\label{theorem:3}
+\end{theorem}
 \emph{Proof:}
-The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem 2.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
+The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem~\ref{theorem:2}.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
 However, the expected separation utilities under this game are now
@@
 
-{\bf Theorem 5:} A mediator can be used to eliminate inefficient concessions. \\
+\begin{theorem}
+	A mediator can be used to eliminate inefficient concessions.
+	\label{theorem:5}
+\end{theorem}
 \emph{Proof:}  The low type IC ($pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
@@
 The low type leader can bluff in the bilateral setting but not when a mediator is present.
-As per Theorem 4, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.
+As per Theorem~\ref{theorem:4}, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.
 But because the benefits of giving a concession differ between the types (low types get one period of cheater's payoff, while high types get future peace), the mediator is able to mandate concessions only between declared high types.
@@
 
-\noindent {\bf \emph{Pooling equilibrium}\\}
-\emph{Lemma 1:} From period 1 on, playing fight in all periods regardless of beliefs constitutes an equilibrium strategy of the continuation game for both types. \\
+\noindent {\bf \emph{Pooling equilibrium}}
+\begin{lemma}
+	From period 1 on, playing fight in all periods regardless of beliefs constitutes an equilibrium strategy of the continuation game for both types.
+	\label{lemma:1}
+\end{lemma}
 \emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight.
@@
 \\
-\emph{Lemma 2:} From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.\\
+\begin{lemma}
+	From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.
+	\label{lemma:2}
+\end{lemma}
 \emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight.
@@
 One high type equilibrium strategy is to pool with the low types and always play Fight.
-If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, Lemma 2 shows that the low-type of player $i$ best responds by always playing Fight.
-The high-type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior by Lemma 1.
+If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, Lemma~\ref{lemma:2} shows that the low-type of player $i$ best responds by always playing Fight.
+The high-type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior by Lemma~\ref{lemma:1}.
 Given that the stage-game equilibrium will be (Fight,Fight), there is no incentive to give a concession in period 0 because concessions are costly and signaling one's type can give no benefit in this equilibrium.
@@
  \emph{Proof of Theorem \ref{theorem:1}}:\\
-Countries with the equilibrium strategy to play Trust in the first round reveal themselves as a high type as per Lemma 2.
+Countries with the equilibrium strategy to play Trust in the first round reveal themselves as a high type as per Lemma~\ref{lemma:2}.
 This will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from deviating against someone playing the pooling (always Fight) strategy.
@@
 \\
-\emph{Lemma 3:}
-In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium. \\
-\emph{Proof:}
+\emph{Proof of Lemma~\ref{lemma:3}:}\\
 According to the revelation principle, we can assume that in a concessions separating equilibrium countries reveal their types truthfully, allowing period 1 actions where High types only play Trust with other high types, and play Fight with low types.
-Low types play Fight (Lemma 2) and their payoff is $U_l=X_{FF}+ pg_h-g_l$.
+Low types play Fight (Lemma~\ref{lemma:1}) and their payoff is $U_l=X_{FF}+ pg_h-g_l$.
 Though low types might be willing to give a non-zero gift in a separating equilibrium, it must distinguish them from the high types.
@@
 \\
-{\bf Theorem 2:} In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.\\
-\emph{Proof:} Under certain conditions, the high types will be given incentives to send costly concessions in order to reveal their type and separate (Lemma 3).
+\emph{Proof of Theorem \ref{theorem:2}:}\\
+Under certain conditions, the high types will be given incentives to send costly concessions in order to reveal their type and separate (Lemma~\ref{lemma:3}).
 In a separating equilibrium constructed here, any-off equilibrium behavior (a concession not equal to the equilibrium concession) will be considered low type gifts.

### 2017-09-12 draft.tex
new theorem on material value destroying STC, added '\hfill' on proofs

@@
 \newcommand{\de}{\delta}
+\newcommand{\al}{\alpha}
   \usepackage{setspace}
@@
 \\
-\\
 \begin{lemma}
@@
 \begin{theorem}
+	Assume the high types are not patient enough to separate without concessions.
+There are parameters under which the ability of the low-type country to use concessions to reduce the payoffs of its negotiating partner during a 'fight' stage (i.e.
+$\al_L < 1$) destroys the negotiating partners' ability to separate through concessions, i.e.
+to achieve peace.
+	\label{theorem:matval}
+\end{theorem}
+
+ \emph{Proof}: An example suffices as proof.
+Let $T = 10$, $W=8$ and $D = 5$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$.
+Let $\de_h = .6$ and $\de_l = .3$.
+Assume $p = .2$.
+By Theorem~\ref{theorem:2}, separation through concessions is possible.
+
+The patience threshold to separate through concessions is much higher under these parameters when the concessions carry future material value.
+In order to calculate it, we need to know the size of the minimum separating concession, which is again calculated from the low-type incentive constraint.
+The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.
+The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do.
+\hfill $\blacksquare$
+
+\begin{theorem}
 	Under some parameters, the optimal equilibrium uses inefficient concessions.
@@
 It is thus rational under such parameters for inefficient gifts to be given as concessions.
-$\blacksquare$
+\hfill $\blacksquare$
 
@@
  $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
-It also holds for any monotone cost function.}$\blacksquare$
+It also holds for any monotone cost function.} \hfill $\blacksquare$
 
@@
 $U_h^M>U_h^*$.
-Note that no additional wealth is created by $M$, but less is transferred to low types, and welfare is defined as high-type utility.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$}  $\blacksquare$
+Note that no additional wealth is created by $M$, but less is transferred to low types, and welfare is defined as high-type utility.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$} \hfill $\blacksquare$
 
@@
 Thus the stage game equilibrium is (Fight, Fight) and in any repeated game, playing the stage game equilibrium in each period is an equilibrium of the entire game.
-$\blacksquare$\\
+\hfill $\blacksquare$\\
 \\
@@
 Low types, with $\delta_l < \delta^*$ achieve a higher payoff deviation from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
-$\blacksquare$\\
+\hfill $\blacksquare$\\
 
@@
 Let us refer to such an equilibrium as a  \emph{no-concessions separating equilibrium}, since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0.
-$\blacksquare$
+\hfill $\blacksquare$
 \\
@@
 If concessions lead to a separating equilibrium, they must be costly.
-$\blacksquare$
+\hfill $\blacksquare$
 \\
@@
 \ee
-That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type.
-$\blacksquare$\\
+That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$\\
 

### 2017-09-12 draft.tex
turn theorem:3 into lemma:efficiency

@@
 \begin{center}
-\captionof{table}{Stage Game Payoffs}
+\captionof{table}{Stage game payoffs}
 \begin{tabular}{|l|c|c|}
@@
 \label{sec:IC}
+
+\subsection{Concessions with Material Value}
 We now model concessions to potentially have real material help or harm to the giver.
@@
 \begin{center}
-\captionof{table}{Stage Game Payoffs when Concessions have Material Value}
+\captionof{table}{Stage game payoffs when concessions have material value}
 \begin{tabular}{|l|c|c|}
@@
 	Assume the high types are not patient enough to separate without concessions.
-There are parameters under which the ability of the low-type country to use concessions to reduce the payoffs of its negotiating partner during a 'fight' stage (i.e.
+There are parameters under which the low-type country's ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage (i.e.
 $\al_L < 1$) destroys the negotiating partners' ability to separate through concessions, i.e.
-to achieve peace.
+to achieve peace when there are two high types.
 	\label{theorem:matval}
@@
 \hfill $\blacksquare$
+
+\subsection{Material Value of Concession can be Destroyed}
+We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
+For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country.
+The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.
+
+In the model, countries choose a scalar $e$ to multiply by their given concession $g$.
+$0 \leq e \leq 1$.
+As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$.
+The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
+These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
+The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix.
+
+\begin{center}
+\captionof{table}{Stage game payoffs when concessions have material value that can be destroyed}
+\begin{tabular}{|l|c|c|}
+  \hline      & Trust & Fight \\ \hline
+	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
+  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
+	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
+	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
+\end{tabular}
+\end{center}
+
+Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to separate, we first formally establish the welfare implications.
+
+\begin{lemma}
+	Assuming that a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient gifts in a separating equilibrium.
+	\label{lemma:efficiency}
+\end{lemma}
+\emph{Proof:}
+The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem~\ref{theorem:2}.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
+However, the expected separation utilities under this game are now
+\be
+U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
+\ee
+and
+\be
+U_l=X_{FF}+peg_h 
+\ee
+ $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
+It also holds for any monotone cost function.} \hfill $\blacksquare$
+
+%need to also write constraints for high type IC to be satisfied, or appeal to forward induction
+%?
+And, a mechanism improves upon inefficiency because it allows a high types to only give a gift to other high types, thus decreasing their costs and still giving the same equilibrium matches.
+.
+Does this rely on varied costs of giving- i.e with same costs can a mechanism still improve?
+%note damages due to alpha can be understood as political losses/ embarrassment of failure to make peace as much as they can be seen as military damages.
+%{\bf Theorem 12:}\\  
+%When concessions are inefficient, $M$ can still improve over bilateral negotiation. \\
+% \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong.
 
@@
 \hfill $\blacksquare$
-
-We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
-For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country.
-The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.
-
-In the model, countries choose a scalar $e$ to multiply by their given concession $g$.
-$0 \leq e \leq 1$.
-As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$.
-The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
-These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
-The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix.
-\\
-\\
-
-\begin{center}
-\captionof{table}{Stage Game Payoffs when Concessions have Material Value}
-\begin{tabular}{|l|c|c|}
-  \hline      & Trust & Fight \\ \hline
-	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
-  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
-	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
-	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
-\end{tabular}
-\end{center}
-
-\begin{theorem}
-	It is optimal to give efficient gifts (where $e=1$) in a separating equilibrium.
-	\label{theorem:3}
-\end{theorem}
-\emph{Proof:}
-The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem~\ref{theorem:2}.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
-However, the expected separation utilities under this game are now
-\be
-U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
-\ee
-and
-\be
-U_l=X_{FF}+peg_h 
-\ee
- $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
-It also holds for any monotone cost function.} \hfill $\blacksquare$
-
-%need to also write constraints for high type IC to be satisfied, or appeal to forward induction
-%?
-And, a mechanism improves upon inefficiency because it allows a high types to only give a gift to other high types, thus decreasing their costs and still giving the same equilibrium matches.
-.
-Does this rely on varied costs of giving- i.e with same costs can a mechanism still improve?
-%note damages due to alpha can be understood as political losses/ embarrassment of failure to make peace as much as they can be seen as military damages.
-%{\bf Theorem 12:}\\  
-%When concessions are inefficient, $M$ can still improve over bilateral negotiation. \\
-% \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong.
 

### 2017-09-12 draft.tex
revise lemma and inefficiency / mediation theorems

@@
 \begin{lemma}
-	Assuming that a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient gifts in a separating equilibrium.
+	Assuming that a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient concessions in a separating equilibrium.
 	\label{lemma:efficiency}
@@
 \begin{theorem}
-	Under some parameters, the optimal equilibrium uses inefficient concessions.
+		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed.
+There are parameter under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
 	\label{theorem:4}
@@
 Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results.
-The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(T+D)}{1-pT}$.
+The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
 Under an equilibrium with purely inefficient concessions $(e=0)$, the minimum separating concession would be $g'=p(T+D)$.
@@
 \begin{theorem}
-	A mediator can be used to eliminate inefficient concessions.
+	Assume that concessions have future material value.
+	\begin{enumerate}
+		\item[(a)] If future material value cannot be destroyed, a mediator can be used to expanded the parameter space over which peace can be achieved.
+		\item[(b)] If future material value can be destroyed, a mediator can be used to eliminate inefficient concessions and improve welfare.
+	\end{enumerate}
 	\label{theorem:5}

### 2017-09-12 param-search.R

@@ -1,8 +1,8 @@
 T=10
 W=8
 D=5
-dl = .2
-p = .3
+dl = .3
+p = .2
 
 #Separating w/out concessions for dh such that:
 dh_swoc = W/((1-p)*W +p*(T+D))
@@ -13,15 +13,15 @@ dh_stc = W/(T+D)
 dh = .6
 #Separating with concessions can be either with e=1 or e=0. Which does high type choose?
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) #gift necessary to separate if e = 1
-g0 = p*(D+T)                                   #gift necessary to separate if e = 0   
+#g0 = p*(D+T)                                   #gift necessary to separate if e = 0   
 
 uh_g1 = (p*T*(1+g1))/(1-dh) - g1 + ((1-p)*(W-D-D*g1))/(1-dh)
-uh_g0 = (p*T)/(1-dh) - g0 + ((1-p)*(W-D))/(1-dh)
+#uh_g0 = (p*T)/(1-dh) - g0 + ((1-p)*(W-D))/(1-dh)
 
 dh1Th = D*(1-p)+1-p*T + p*(W-(T+D))/g1
-dh0Th = 1 + p*(W-(T+D))/g0
+#dh0Th = 1 + p*(W-(T+D))/g0
 
-uh_swoc = p*T/(1-dh) + (1-p)*(dh*(W-D)/(1-dh)-D)
+#uh_swoc = p*T/(1-dh) + (1-p)*(dh*(W-D)/(1-dh)-D)
 uh_pool = (W-D)/(1-dh)
 #What would happen for these parameters with the mediator? Only dh_stc matters, 
 #and this is guaranteed by assuption on dh

### 2017-09-12 draft.tex
new proof and exposition around theorem 4

@@
 
-\section{Analysis of benchmark cases}
+\section{Analysis of Benchmark Cases}
 \label{sec:bench}
@@
 In order to calculate it, we need to know the size of the minimum separating concession, which is again calculated from the low-type incentive constraint.
-The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.
-The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do.
+The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.\footnote{See proof of Theorem~\ref{theorem:4} below for details.} The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do.
 \hfill $\blacksquare$
@@
 		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed.
-There are parameter under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
+There are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
 	\label{theorem:4}
 \end{theorem}
- \emph{Proof}:   Because it is relatively complicated to calculate equilibrium concessions in the general case, a slight simplification of the general model will be made for proof of inefficient concessions.
-Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
-Also assume that $s_1=s_2=m_1=m_2=1.$ Because of linearity, equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
-Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results.
-The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-Under an equilibrium with purely inefficient concessions $(e=0)$, the minimum separating concession would be $g'=p(T+D)$.
 
-Assuming gifts must be non-negative, $g^*$ will always be greater than $g'$.
-This is not enough to show that inefficient concessions are sometimes optimal.
-To show this, consider high type equilibrium utility and assume that the high types are perfectly patient (that is, $\de_h=1$):
-\be
-U_h=pT(1+eg)+peg+(1-p)(W-D(1+eg))\footnote{Note the gift payment does not enter here: the current period is weighted $1-\de$, which is 0, while the future is weighted $\de=1$.}
-\ee
+\emph{Proof}: See appendix.
 
-Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession needs to be determined by comparing the utility under each.
-For low $p$, the term $(1-p)(W-D(1+eg))$ dominates, showing that clearly, as low an $e$ as possible is best, so $e=0$, that is, complete inefficiency is the best possible equilibrium efficiency level.
-It is thus rational under such parameters for inefficient gifts to be given as concessions.
-\hfill $\blacksquare$
+Inefficient concessions are optimal under low $p$ (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^*$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
 
@@
 \end{theorem}
-\emph{Proof:}  The low type IC ($pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
+\emph{Proof:}  The low type IC ($peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
 Under $M$, the low type IC can bind without having high types give a concession to low types.
@@
 
+\emph{Proof of Theorem \ref{theorem:4}:}\\
+Because it is relatively complicated to calculate equilibrium concessions in the general case, a slight simplification of the general model will be made for proof of inefficient concessions.
+Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
+Also assume that $s_1=s_2=m_1=m_2=1.$ Because of linearity, equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
+Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results.
+The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
+The high type's utility when $e=1$ is $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^*$.
+
+When $e=0$---that is, the future material value of the concessions is destroyed---we are back in the case of Section~\ref{sec:bench} and the minimum separating concession is $g'=p(T+D)$.
+The threshold for high types to cooperate is again $\frac{W}{T+D}$.
+High type utility when $e=0$ is $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - g'$.
+
+Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession needs to be determined by comparing the utility under each, and either can be larger.
+Inefficient concessions are made optimal when $p$ is low (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^*$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
+\hfill $\blacksquare$
+
 \newpage

### 2017-09-12 notes.tex
new proof and exposition around theorem 4

@@
 		\end{itemize}
-	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost
+	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost)
 		\begin{itemize}
@@
 			\item In the absence of mediation, being able to burn money can help, but you still lose something
-			\item I still have a question about the overall game: if $e=0$ provides higher welfare if it were enforceable but it's not, do we just go with $e=1$?
 			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$

### 2017-09-13 draft.tex
rewrite proof of theorem 5

@@
 %LAKE: The psychological literature as applied in political science spent a lot of time in the 1970s and 1980s focusing on Graduated Reductions in Tensions (GRIT) as a form of confidence building.
-See Debbie Larson’s work (she’s at Poli Sci, UCLA, I don’t have the cites handy).
+See Debbie LarsonÕs work (sheÕs at Poli Sci, UCLA, I donÕt have the cites handy).
 This is clearly relevant to your discussion of the laboratory experiments on p.3.
@@
 This is not well represented by the PD.
-You need to make the link – or differentiate – what you’re doing here from the Fearon-Powell models to which you appeal.
+You need to make the link Ð or differentiate Ð what youÕre doing here from the Fearon-Powell models to which you appeal.
 
@@
 \subsection{Material Value of Concession can be Destroyed}
+\label{sec:matval}
 We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
@@
 The countries are bound to send the mandated concessions.
-The benchmark case analyzed in Sections~\ref{sec:bench} and \ref{sec:IC} requires the countries to send the same concession to both types, since types are private information.
+In Sections~\ref{sec:bench} and \ref{sec:IC}, the same concession must be sent to both types since types are private information.
 $M$ can differentiate based on recipient's type.
-Otherwise, the setup is identical to the benchmark case.
+Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value.
 
-Welfare is again considered as the sum of the high type utilities.
+The welfare target is again the sum of the high type utilities.
 Qualitatively, similar results would hold if we also included low types in the analysis with weighting based on $p$.
@@
 	\begin{enumerate}
-		\item[(a)] If future material value cannot be destroyed, a mediator can be used to expanded the parameter space over which peace can be achieved.
-		\item[(b)] If future material value can be destroyed, a mediator can be used to eliminate inefficient concessions and improve welfare.
+		\item[(a)] If future material value can be destroyed, a mediator can be used to eliminate inefficient concessions and improve welfare.
+		\item[(b)] If future material value cannot be destroyed, a mediator can be used to expand the parameter space over which peace can be achieved.
 	\end{enumerate}
@@
 \end{theorem}
-\emph{Proof:}  The low type IC ($peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h$) binds, so the equilibrium benchmark gift is $g^{*}=p(X_{FT}^l-X_{FF}^l)$ and high type utility is $U_h^*= pX_{TT}+(1-p)X_{FF} - (1-p)g^*$).
-Under $M$, the low type IC can bind without having high types give a concession to low types.
-The equilibrium separating gift $g^{*M}$ will be larger than $g^*$ in this case, specifically
-\be
-g^{*M}= \frac{p(X_{FT}^l-X_{FF}^l)}{1-p}
-\ee
+\emph{Proof:} (a) Under $M$, the low type IC can bind without having high types give a concession to low types.
+There is no need then to give inefficient concessions: high types will invest in civil society and improve the giver's welfare and low types will never receive the concession.
+%The equilibrium separating concession $g^{*M}$ will be larger than $g^*$ in this case because the low type who reports truthfully receives a concession with zero probability:
+%\be
+%g^{*M}= \frac{p(X_{FT}^l-X_{FF}^l)}{1-p}
+%\ee
 High type utility under $M$ is 
 \be
-U_h^M= pX_{TT}+(1-p)X_{FF}
+U_h^M= pX_{TT}+(1-p)X_{FF} = p \left( \frac{T(1+g^{*M})}{1-\de_h} \right) + (1-p) \left(\frac{W-D}{1-\de_h} \right)
 \ee
 because high types exchange concessions of the same value.
-$U_h^M>U_h^*$.
-Note that no additional wealth is created by $M$, but less is transferred to low types, and welfare is defined as high-type utility.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$} \hfill $\blacksquare$
+Welfare, defined as high-type utility, is improved because no transfer is made to the low types and no future damage is caused in the case of such a transfer.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$.}
+
+(b) The contraction of the parameter space over which peace could be achieved in Theorem~\ref{theorem:matval} derives from the low types' ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage.
+By ensuring that only high types exchange gifts, the mediator removes this expected cost, thus allowing a wider range of high types to separate through concessions.
+The threshold for high types to prefer the separating-through-mediation equilibrium to the pooling on no concessions equilibrium, $\de_h^*$, differs from $\de^1_h$ of Theorem~\ref{theorem:matval} in that it does not have the term $D(1-p)$ (thus is smaller) and the separating concession $g^* = \frac{g^*}{1-p}$.
+Since the concession is in the denominator, this also reduces the value of $\de_h^*$.
+\hfill $\blacksquare$
 
@@
 The improvements by the mediator here do not rely on the mediator's private information as in the models of Kydd (2003), Rauchhaus (2006) and Smith and Stam (2003).
-Therefore the mediator's preferences need not be a huge factor in her participation.
+Therefore the mediator's preferences need not be an important factor in her participation.
 So long as the costs are small enough to be worth her participation the mediator can effectively enter and assist in solving the conflict.
 
-The value of truth telling by the mediator has been brought up in the literature.
+The value of truth telling by the mediator has been examined in the literature.
 Kydd (2003) studies bias in mediation and how a mediator can credibly communicate information to the parties.
@@
 %This said, if the paper is really about mediation, then the mediator needs more scrutiny.
-What are the mediator’s incentives?
+What are the mediatorÕs incentives?
 Why should he reveal truthfully what the parties tell him?
@@
 \ee
-%note this can be simplified by using primals of X's, DO THIS!!!!!!!!!!!!!!!!
-
+\\
 \emph{Proof of Theorem \ref{theorem:4}:}\\

### 2017-09-14 draft.tex
add intuitive criterion as justification for focus on best eqm for high types

@@
 \end{theorem}
+
 \emph{Proof}: See appendix.
 \\
-\\
-In this equilibrium two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk.
+In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk.
 This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.
@@
 This smallest concession is denoted $g_h^*$ and is calculated in equation (11) in the appendix to be $p(T+D).$
+
+This `best' concessions separating equilibrium, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
 

### 2017-09-14 notes.tex
add intuitive criterion as justification for focus on best eqm for high types
take out notes that have already been addressed

@@
 \begin{itemize}
-	\item From Eli four years ago: why can mediator do what the two sides cannot?
-	\item Add discussion of intuitive criterion to text (if I end up needing it): out of eqm beliefs put zero weight on types that can never gain from deviating from a fixed eqm outcome
-	\item Incorporate mediator result into text; re-organize text so it matches June presentation (re-worded Theorem 4, new Theorem 5)
-		\begin{itemize}
-			\item Careful of SWOC being chosen over STC ($\de_h$ threshold restriction?)
-		\end{itemize}
 	\item Note for mediator result:
@@
 		\end{itemize}
-	\item Someone who \textit{can't} cooperate under either $e=0$ or $e=1$ CAN cooperate under mediator
-		\begin{itemize}
-			\item In the absence of mediation, being able to burn money can help, but you still lose something
-			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$
-				\begin{itemize}
-					\item $p=.4, \de_l = .45, \de_h = \de_{STC} = .53$. Choose $e=1$, but $\de_1 = .65$
-					\item $p=.3, \de_l = .45, \de_h = \de_{STC}  = .53$. Choose $e=1$, but $\de_1 > 1$; even worse at $p=.2$
-					\item $p=.4, \de_l = .5, \de_h = \de_{STC} = .53$. Choose $e=1$, $\de_1 \geq .4$ (works fine)
-					\item $p=.1, \de_l = .1, \de_h = \de_{STC} = .53$. Choose $e=0$, but $\de_0 \geq 6.7$
-					\item $p=.05, \de_l = .5, \de_h = .7$. Choose $e=0$, but $\de_0 = 7.6$
-					\item $p=.1, \de_l = .5, \de_h = .75$. Choose $e=0$, but $\de_0 = 6.7$ and $\de_1 \geq 3$
-				\end{itemize}
-		\end{itemize}
 

### 2017-09-14 draft.tex
make proofreading changes to sections 1 and 2

@@
 When two parties are engaged in conflict and each distrusts the other's ability to pursue peace, concessions can be used to indicate an interest in making peace.
-We demonstrate that a lack of trust can prevent optimal concessions from being made, creating inefficiencies in negotiation that can reduce the possibility of peace.
+However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made or reduce the possibility of peace.
 We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
@@
 Although inefficient, this reduces the possibility of those settlements being used against Israeli interests.
-Without trust, the most efficient concessions cannot be made.
+Without trust, the most efficient concessions often are not made.
 
@@
 Schelling's \emph{Arms and Influence} (1966) modeled war with a game theoretic framework, and Powell (1999) has also defended the use of modeling in understanding war.
-Fearon (1995), Powell (1996a and 1996b, 2006) and others consider war to be a bargaining failure, caused by commitment problems and asymmetric information.
-When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation.
+Fearon (1996), Powell (1996a and 1996b, 2006) and others consider war to be a bargaining failure, caused by commitment problems and asymmetric information.
+When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation (Fearon 1996).
 
@@
 In conflict resolution, concessions may act as signals or as an end in themselves -- or as both simultaneously.
-One contribution of this paper is that it allows concessions to have material value, signaling value, and both.
-We will show that when concessions are used solely for signaling, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.
+One contribution of this paper is that it allows concessions to have future material value, signaling value, and both.
+We will show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.
 
@@
 And the gift giving literature, more so than the concessions literature, focuses specifically on the issue of efficiency.
-Inefficiency is defined for the purposes of this paper as some sort of money burning: giving a gift or concession that is more costly to the giver than it is valuable to the recipient, that is, using a concession as a signal and not taking advantage of its full inherent value.
-It is not problematic for giving to also have a signaling component, but it is ideal if the full value of the gift can be transferred.
-%The theoretical basis for this has its roots in the economics literature on gift giving.
-%this needs lots of work and maybe a cite- use def of "inefficiency" in the camerer paper or others
+Inefficiency is defined for the purposes of this paper as giving a gift or concession that is more costly to the giver than it is valuable to the recipient, that is, using a concession as a signal and not taking advantage of its full inherent value.
 
@@
 
-We propose another theoretical contribution to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle.
+We propose a different conceptual framework to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle.
 The basic formulation of our mechanism-design approach is an expansion of Camerer's (1988) analysis.
@@
 2006).
-But the term mediation encompasses a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation suspect.
+But the term mediation encompasses a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation difficult.
 The type of mediation affects the negotiation outcome (Bercovitch 2000; Beardsley et al.
@@
 $\delta_h >\delta_l$ and both $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
-The type distinction, as explained later in the model, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict with the other specific country.
+The type distinction, as explained later in the model, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict.
 It should not be thought of as an inherent quality of a country, but rather an interactive parameter.
@@
 
- The probability of nature selecting high type for a given player is $p$.
-The probability of nature selecting low type is $1-p$.\footnote{Note that parameters are symmetric across countries, as is consistent with the literature.
+ The probability of nature selecting the high type for a given player is $p$.
+The probability of nature selecting the low type is $1-p$.\footnote{Note that parameters are symmetric across countries, as is consistent with the literature.
 Qualititative results do not depend on this being the case, and equilibria and equilibrium concessions can easily be calculated with asymmetric parameters between players.}  Countries are aware of their own type, but not the type of the other country.
@@
 Concessions are one way in which countries can signal their commitment.
-By modeling the conflict in such a way we can also gain insight from how a third party can affect trust issues inherent to the conflict.
+By modeling the conflict in such a way we can also gain insight as to how a third party can ameliorate trust issues inherent to the conflict.
 %might want to cite fearon and bargaining lit here
@@
 
-The choice of ``Trust'' or ``Fight'' will be referred to as the county's stage game action.
+The county's stage game actions will be referred to as ``Trust'' and ``Fight'':
 
@@
  If $\delta$ is high enough for both countries, the cooperative outcome of ``Peace'' (Trust, Trust) can be sustained with a grim trigger punishment threat.
-The assumption $T>W-D$ ensures that payoffs from Peace (even if it cannot be held as an equilibrium) are higher than for ``War'' (Fight, Fight).\footnote{A country whose payoffs violate this assumption is of a special ``very low'' type that will be considered later in the analysis.}
+The assumption $T>W-D$ ensures that payoffs from Peace are higher than for ``War'' (Fight, Fight).
 For a Peace equilibrium to exist, $\delta$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
@@
 \label{sec:bench}
-When countries are faced with doubts about each other's motives, they have several options of how to proceed.
+When countries are faced with doubts about each other's motives, they can proceed in several different ways.
 There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor for the high type ($\delta_h$) exceeds the cutoff found in expression (1), there are many types of equilibria; consider for instance oscillating every other period between Peace and War with a grim trigger War threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
-These are also always payoff dominated by at least one of the other equilibria discussed, so are not attractive.} A thorough analysis of the different types of equilibria, as well as all proofs for this section, can be found in the appendix.
+These are also always payoff dominated by at least one of the other equilibria discussed, so are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as all proofs for this section.
 \\
@@
 Countries continue to doubt, doing nothing to bridge the credibility gap, and thus not cooperating.
-This is a \emph{pooling equilibrium}, and is likely to happen when countries are in long-set patterns of distrust.
+This \emph{pooling equilibrium} is likely to happen when countries are in long-set patterns of distrust.
 Active fighting is not necessary; remaining outside of a state of peace is all that is required.
@@
 
+\item Fearon, James. (1996). ``Bargaining Over Objects that Influence Future Bargaining Power.'' \emph{Chicago Center on Democracy Working Paper}, University of Chicago.
+
 \item Fey, Mark and Kristopher W. Ramsay. (2009). ``Mechanism Design Goes to War: Peaceful Outcomes with Interdependent and Correlated Types." \emph{Review of Economic Design} 13:3, 233-250.

### 2017-09-14 notes.tex
make proofreading changes to sections 1 and 2

@@
 \begin{itemize}
-	\item Note for mediator result:
-		\begin{itemize}
-			\item For two high types to cooperate in the mechanism, need large enough gift to screen out low types.
-They're still just reporting, so don't give a gift if not matched with another high type.
-PLUS when they're exchanging gifts, the gifts will actually be used for good:
-				\[
-				  T(1+g) \geq (1-\de)[T(1+g) + W] + \de (W-D)
-				\]
-				\[
-				  \de \geq \frac{W}{T + Tg + D}
-				\]
-				Note that this threshold is smaller than $\frac{W}{T + D}$, the one we get without concessions having material benefit / harm
-		\end{itemize}
 	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost)

### 2017-09-14 draft.tex
make proofreading changes to sections 3 through end

@@
 2010; Meirowitz et al.
-2012, 2013).
+2012, 2015).
 This paper expands the theoretical literature by modeling the role of mediation when information is asymmetric about parties' abilities to commit to peace.
@@
 Other prominent examples of this pooling equilibrium include Israel and its neighbors, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
-The mistrust of the other party is perhaps justified- indeed if one party did take the first step and give a concession first, they may indeed be taken advantage of.
+The mistrust of the other party is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
 
@@
 \\
-{\bf \emph{Separating without concessions}\\}
+{\bf \emph{No-Concessions Separating Equilibrium}\\}
 \vskip-.2in
@@
 \end{theorem}
-
 \emph{Proof}: See appendix.
@@
 Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
-Certain relationships between the USA and countries that its wikileaks alienated- such as Italy- would be an example.
+Certain relationships between the USA and countries that its wikileaks alienated -- such as Italy -- would be an example.
 Italy essentially laughed off the criticisms and reassured the USA of its commitment to their relationship.
-Warsaw pact countries generally allowed the USSR similar leeway; it was better to have occasionally imperfect cooperation than conflict.
-Certain things can disrupt trust without completely derailing actions.
+Warsaw Pact countries generally allowed the USSR similar leeway; it was better to have occasionally imperfect cooperation than conflict.
+Certain things can disrupt trust without completely derailing cooperation.
 
 Of course, it is possible that in a \emph{no-concessions separating equilibrium} one country can take advantage of the other.
-It can be argued that indeed that did happen in the Warsaw pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.
+It can be argued that indeed that did happen in the Warsaw Pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.
 
@@
 \\
-{\bf \emph{Separating through concessions}\\}
+{\bf \emph{Concessions Separating Equilibrium}\\}
 \vskip-.2in
@@
 
-The analysis is conducted with standard Incentive Compatibility and Individual Rationality constraints.
+The analysis is conducted with standard incentive compatibility constraints.
 Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round.
@@
 $X_{FT}$ and $X_{TF}$ are still necessary for calculating the equilibrium concession $g_h$.%might make the first one TF for clarity
-\\
+
 \begin{lemma}
@@
 
-This smallest concession is denoted $g_h^*$ and is calculated in equation (11) in the appendix to be $p(T+D).$
+This smallest concession is denoted $g_h^*$ and is calculated in equation (9) in the appendix to be $p(T+D).$
 
@@
 \subsection{Concessions with Material Value}
-We now model concessions to potentially have real material help or harm to the giver.
+We now model concessions to have real future material value that can either help or harm the giver.
 The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society.
@@
 Concessions are immediately converted into civil society or military gifts and incorporated into payoff functions.
- $C_h(\cdot)=C_l(\cdot)=1$ as earlier in the model description. Periods 1 to $\infty$ are as before but with the following stage game payoffs:
+Periods 1 to $\infty$ are as before but with the following stage game payoffs:
 
@@
 \begin{theorem}
-	Assume the high types are not patient enough to separate without concessions.
-There are parameters under which the low-type country's ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage (i.e.
-$\al_L < 1$) destroys the negotiating partners' ability to separate through concessions, i.e.
-to achieve peace when there are two high types.
+	Assume the high types are not patient enough to separate without concessions but can separate using concessions when concessions have no material value.
+When concessions instead have future value that the low-type country can use to reduce the future payoffs of its negotiating partner, there are parameters under which the negotiating partners' ability to separate through concessions is destroyed, i.e.
+peace cannot be achieved when there are two high types.
 	\label{theorem:matval}
@@
 In order to calculate it, we need to know the size of the minimum separating concession, which is again calculated from the low-type incentive constraint.
-The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.\footnote{See proof of Theorem~\ref{theorem:4} below for details.} The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do.
+The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.\footnote{See proof of Theorem~\ref{theorem:4} below for details.} The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
 \hfill $\blacksquare$
@@
 
-In the model, countries choose a scalar $e$ to multiply by their given concession $g$.
+We implement this by allowing countries to choose a scalar $e$ to multiply by their given concession $g$.
 $0 \leq e \leq 1$.
-As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model not relevant to results presented here, we could also think of $e$ as a function $E(\cdot)$.
+As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model, we could also think of $e$ as a function $E(\cdot)$.
 The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
 These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
-The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} From here on in the analysis, we use $g_l=0$ and $g_h=g_h^*$ to denote the equilibrium concenssions as presented in the previous section and calculated in the appendix.
+The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.}
 
@@
 
-(b) The contraction of the parameter space over which peace could be achieved in Theorem~\ref{theorem:matval} derives from the low types' ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage.
+(b) The contraction of the parameter space over which peace could be achieved in Theorem~\ref{theorem:matval} derives from a low type's ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage.
 By ensuring that only high types exchange gifts, the mediator removes this expected cost, thus allowing a wider range of high types to separate through concessions.
-The threshold for high types to prefer the separating-through-mediation equilibrium to the pooling on no concessions equilibrium, $\de_h^*$, differs from $\de^1_h$ of Theorem~\ref{theorem:matval} in that it does not have the term $D(1-p)$ (thus is smaller) and the separating concession $g^* = \frac{g^*}{1-p}$.
+The threshold for high types to prefer this separating-through-mediation equilibrium to the pooling on no concessions equilibrium, $\de_h^*$, differs from $\de^1_h$ of Theorem~\ref{theorem:matval} in that it does not have the term $D(1-p)$ (thus is smaller) and the separating concession $g^* = \frac{g^1}{1-p}$.
 Since the concession is in the denominator, this also reduces the value of $\de_h^*$.
@@
 But while magnitudes vary, the real caveat is that the nature of the concessions is sometimes non-negotiable.
-For instance if one country demands release of hostages, it is not possible-or at least not realistic- for the other country to give the equivalent value in land, cash or weapons.
+For instance if one country demands release of hostages, it is not possible -- or at least not realistic -- for the other country to give the equivalent value in land, cash or weapons.
 
@@
 
-The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy this inefficiency if she is trusted.
+The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy the inefficiency if she is trusted.
 One contribution of this paper is to show the mechanisms through which a mediator can help.
-Since the mediator eliminates inefficient concessions, the observation that inefficient concession may not do the trick only further indicates the value of a mediator even more.
+Since the mediator eliminates inefficient concessions, the observation that inefficient concession may not do the trick only underscores the potential value of a mediator.
 %our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred.
@@
 Therefore, the inefficiencies borne by the inefficient concessions and/ or by the ongoing conflict must not be outweighed by the cost of providing the mediation.
-If the model accurately captures the costs, the expected savings of mediation can be calculated and therefore the usefulness of mediation in a specific scenario can be determined.
+If the model accurately captures the costs, the expected savings of mediation can be calculated and therefore the value of mediation in a specific scenario can be determined.
 This will allow the mediator to analyze whether her involvement is worthwhile.
@@
 The minimax payoff is $W-D$, and punishing a country by playing it every period is the worst possible punishment, hence it gives the greatest potential for a country to be given incentives to play Trust.
-Low types, with $\delta_l < \delta^*$ achieve a higher payoff deviation from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
+Low types, with $\delta_l < \delta^*$ achieve a higher payoff from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
 \hfill $\blacksquare$\\
@@
  \\
- {\bf \emph{Separating without concessions}}
+ {\bf \emph{No-Concessions Separating Equilibrium}}
 
@@
 \\
-{\bf \emph{Separating through concessions}}
+{\bf \emph{Concessions Separating Equilibrium}}
 
@@
 High types have the incentive to play Trust only in the Peace equilibrium, which can only be sustained by a pair of high types.
-Both types benefit from the other country playing Trust because of the payoff structure so all countries have incentive to signal that they are high types if concessions are costless (cheap talk).
+Both types benefit from the other country playing Trust so all countries have incentive to signal that they are high types if concessions are costless (cheap talk).
 Thus costless announcements cannot lead to truthful revelation.
@@
 Under certain conditions, the high types will be given incentives to send costly concessions in order to reveal their type and separate (Lemma~\ref{lemma:3}).
-In a separating equilibrium constructed here, any-off equilibrium behavior (a concession not equal to the equilibrium concession) will be considered low type gifts.
+In a separating equilibrium constructed here, any-off equilibrium behavior (a concession not equal to the equilibrium concession) will be considered a low type gift.
 In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$  is:\\
@@
 High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
-Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation, which is when equation (10) holds with equality.
+Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation, which is when equation (7) holds with equality.
 Substituting in the definitions of the $X$ variables yields the minimum separating gift to be:\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
@@
 
-Combining equations (11) and (12), we have the condition for a concessions separating equilibrium to exist:
+Combining equations (8) and (9), we have the condition for a concessions separating equilibrium to exist:
 \be
@@
 
-The no-concessions separating equilibrium also will exist if equation (8) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
+The no-concessions separating equilibrium also will exist if equation (6) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
 \be
@@
 \be
- W\geq p(W + T+D)\geq 0
+ W\geq p(W + T+D)
 \ee
@@
 \emph{Proof of Theorem \ref{theorem:4}:}\\
-Because it is relatively complicated to calculate equilibrium concessions in the general case, a slight simplification of the general model will be made for proof of inefficient concessions.
+Because it is relatively complicated to calculate equilibrium concessions in the general case, we make a slight simplification of the general model here.
 Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
@@
 Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results.
-The low type's IC constraint binds so with $e=1$, $g^*$ can be calculated to be $g^*= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-The high type's utility when $e=1$ is $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^*$.
+The low type's IC constraint binds so with $e=1$, the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
+The high type's utility when $e=1$ is $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.
 
-When $e=0$---that is, the future material value of the concessions is destroyed---we are back in the case of Section~\ref{sec:bench} and the minimum separating concession is $g'=p(T+D)$.
+When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:bench} and the minimum separating concession is $g^0=p(T+D)$.
 The threshold for high types to cooperate is again $\frac{W}{T+D}$.
-High type utility when $e=0$ is $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - g'$.
+High type utility when $e=0$ is $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - g^0$.
 
-Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession needs to be determined by comparing the utility under each, and either can be larger.
-Inefficient concessions are made optimal when $p$ is low (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^*$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
+Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession is determined by comparing the utility under each, and either can be larger.
+Inefficient concessions are made optimal when $p$ is low (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^1$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
 \hfill $\blacksquare$
@@
 
-\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2013). ``Mediation and Strategic Militarization.'' Unpublished manuscript.
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2012). ``Mediation and Strategic Militarization.'' Unpublished manuscript.
 
-\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2013). ``Dispute Resolution Institutions
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2015). ``Dispute Resolution Institutions
 and Strategic Militarization.'' Unpublished manuscript.

### 2019-10-12 notes.tex
check math for intermediate step for Thm 4; add notes on e=0 case

@@
 		\]
+	\item For $e=0$, you're back in the original case with no material value, i.e. enforceable for same $\de_h$ has no material value case
+		\begin{itemize}
+			\item But check: when $e=0$, also wipe out immediate monetary value?
+				\begin{itemize}
+					\item Not from utility standpoint, but from IC standpoint because direct benefit of gift cancels out
+				\end{itemize}
+		\end{itemize}
+	\item But high type utility goes down
 \end{itemize}

### 2019-10-12 notes.tex
add notes on Thm 5

@@
 	\item \textbf{Check to see whether Theorem 4 proof has to change.}
+\end{itemize}
+
+\vskip.2in
+With $\al = 1$,
+\begin{itemize}
+	\item SWOC (separating without concessions) when $\de_h \geq \frac{W}{(1-p)W + p(T+D)}$
+	\item CSE (concessions separating equilibrium) when $\de_h \geq \frac{W}{T+D}$
+\end{itemize}
+With $\al \in [0,1)$ and $e=1$,
+\begin{itemize}
+	\item SWOC doesn't change because there are no concessions
+	\item WTS there are parameters where can't get STC outcome because of $\al <1$
+		\begin{itemize}
+			\item $e < 1$ means some of these \textit{can} get to peace
+			\item but some can't under \textit{any} value of $e$ [assuming $e$ chosen at same time as $g$]
+		\end{itemize}
+\end{itemize}
+Remember that decision between equilibria is made not by what \textit{can} be achieved in terms of $\de$, but by best response, i.e. ``Does high type do better by not giving concession?''
+\begin{itemize}
+	\item Should check in my numerical examples
 \end{itemize}

### 2019-10-18 notes.tex
add notes on min separating concessions for different values of e

@@
 \end{itemize}
+
+\vskip.2in
+When $e=1$ and no material value, $g_h^* = p(T+D)$ is the smallest concession for CSE. \\
+When $e=1$ and concessions have material value, $g' = \frac{p(1-\de_l)(D+T)}{(1-\de_l)(1-pT) + (1-p)D}$ is the minimum separating concession [Theorem 3]
+I claim in Theorem 5 that the minimum separating concession under mediation is $g^* = \frac{g'}{1-p}$.
 

### 2019-10-26 presentation.tex
change date on presentation for CesIFO session
compile handout version of presentation (fix typo) for integration into paper
update presentation for CPEG

@@
 \author[Kristy Buzard and Ben Horne]{Kristy Buzard and Ben Horne\\ kbuzard@syr.edu}
-\date{June 15, 2017}
+\date{October 25, 2019}
 \maketitle
@@
 \begin{itemize}[<+->]
-	\item Asymmetric information about $\de_i$: can partner commit to peace?
+	\item Asymmetric information about partner's discount factor $\de_i$: can partner commit to peace?
 \end{itemize}
@@
 \pause
-Signaling: Spence (1973), but signal has material value
+Signaling: Spence (1973), but signal has potential future cost
 \pause
 		\begin{itemize}
-			\item cost/benefit tradeoff differs b/c of $\de_i$, $C_i(g)$
+			\item cost/benefit tradeoff b/c of $\de_i$, $C_i(g)$
 		\end{itemize}
@@
 \section{Benchmark}
-\subsection{No Money Burning}
+\subsection{No Money Burning, No Impact on Giver}
 
@@
 \begin{itemize}[<+->]
+	\item Pool on `Fight'
+	\item Separating through concessions
 	\item Separating without concessions
-	\item Separating through concessions
-	\item Pool on `Fight'
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Pooling Equilibrium}
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 4}
+  From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.
+\end{beamerboxesrounded}
+
+\pause
+\vskip.1in
+
+	\begin{itemize}[<+->]
+		\item This equilibrium can always be chosen by both types
 	\end{itemize}
@@
 \pause	
+\vskip.1in
+If $p$ is low enough, high types are better off in the `fight' pooling equilibrium
+\pause
 \[
-  U_h=pg - c_h(g) + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
+  U_h(CSE)=pg - g + \textstyle \frac{1}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
 \]
 \pause
-\vskip-.1in
+\[
+  U_h(POOL)=\textstyle \frac{1}{(1-\de_h)} \left(W-D\right)
+\]
 
+\end{frame}
+
+\begin{frame}{Smallest Separating Concession}
+The smallest concession, $p(T+D)$, comes from the low type's incentive constraint
+\pause
+\[
+  pg +X_{FF}^l \geq -g + pg + pX_{FT}^l+(1-p)X_{FF}^l 
+\]
+\pause
+\[
+  pg +\frac{W-D}{1-\de_l} \geq -g + pg + p\left[T+W + \frac{\de \left(W-D\right)}{1-\de_l} \right]+(1-p)\frac{W-D}{1-\de_l}
+\]
+\pause
+\[
+  g \geq p\left[T+W + \frac{\de \left(W-D\right)}{1-\de_l} \right]-p\frac{\left(W-D\right)}{1-\de_l}
+\]
+\pause
+\[
+  g \geq pT+pW -pW -pD + p\frac{\left(W-D\right)}{1-\de_l} -p\frac{\left(W-D\right)}{1-\de_l}
+\]
+\end{frame}
+
+\section{Inefficient Concessions}
+\subsection{Add Impact of Concessions on Giver (Still no money burning)}
+\begin{frame}[label = hurt]{Timeline}
+\pause
+\begin{enumerate}[<+->]
+	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
+	\item[0.] Concessions
+		\begin{enumerate}
+			\item[0a.] Countries decide what proportion of a received concession to invest in civil society (vs.
+military capabilities): $\alpha_i \in [0,1]$ \hskip.2in \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
+			\item[0b.] \textcolor{red!75!green!50!blue!25!gray}{Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$} 
+		\end{enumerate}	
+	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
+\end{enumerate}
+\end{frame}
+
+\begin{frame}
+\frametitle{Peace not possible in some scenarios}
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 3}
+  When concessions impact the giver's future welfare, peace becomes unachievable for some parameters under which it is achievable when concessions do not impact the giver's future welfare.
+\end{beamerboxesrounded}
+
+\pause
+\vskip.1in
 \begin{itemize}[<+->]
-		\item The smallest concession is $p(T+D)$
-		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
+	\item Effect comes in part through change in minimum separating concession
+	\item High-type utility may increase or decrease from the benchmark case
 \end{itemize}
@@
 
-\section{Inefficient Concessions}
 \subsection{Add Money Burning}
@@
 		\begin{enumerate}
-			\item[0a.] Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$ 
-			\item[0b.] \textcolor{red!75!green!50!blue!25!gray}{Countries decide what proportion of a received concession to invest in civil society (vs. military capabilities): $\alpha_i \in [0,1]$}
+			\item[0a.] Countries decide what proportion of a received concession to invest in civil society (vs. military capabilities): $\alpha_i \in [0,1]$
+			\item[0b.] \textcolor{blue}{Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$}
 		\end{enumerate}	
@@
 
-\begin{frame}{Burning money is unattractive}
+\begin{frame}{Burning money is (obviously) unattractive...}
 \pause
@@
 \pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 3}
-  When concessions confer no material help or harm on the giver, it is optimal to give efficient gifts ($e=1$) in a separating eqm.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 2}
+  If a concessions separating equilibrium exists under no money burning, it is optimal to give efficient gifts ($e=1$) in a concessions separating equilibrium with money burning.
 \end{beamerboxesrounded}
@@
 
-\begin{frame}{Timeline}
-\pause
-\begin{enumerate}[<+->]
-	\item[-1.] Nature independently determines types of Country 1 and Country 2: $\de_i \in \left\{\de_h,\de_l\right\}$
-	\item[0.] Concessions
-		\begin{enumerate}
-			\item[0a.] Countries simultaneously give costly concessions and decide on the efficiency of the concessions: $(g_i, e_i) \in \mathbb{R}_+ \times [0,1]$ 
-			\item[0b.] \textcolor{blue}{Countries decide what proportion of a received concession to invest in civil society (vs. military capabilities): $\alpha_i \in [0,1]$}
-		\end{enumerate}	
-	\item[1--$\infty$.] Countries engage in a simultaneous Prisoners' Dilemma interaction 
-\end{enumerate}
-\end{frame}
-
-\begin{frame}[label=hurt]
-\frametitle{Concessions can hurt the giver}
+\begin{frame}
+\frametitle{...but in some cases countries will burn money}
 \pause
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 4}
-  When the low type country can use concessions to reduce the payoffs of its negotiating partner during a `fight' stage (i.e.
-$\alpha_L < 1$), there are parameters under which the separating-through-concessions equilibrium features inefficient concessions.
+  When concessions affect the future welfare of the giver \textit{and} their value can be destroyed, there are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
 \end{beamerboxesrounded}
-\hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
+\vskip-.1in
 \pause
 \[
-  U_h=peg - c_h(g) + \textstyle \frac{\de_h}{1-\de_h} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
+  U_h=peg - c_h(g) + \textstyle \frac{1}{1-\de_h} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
 \]
@@
 \begin{itemize}[<+->]
-	\item If $p$ is low, concessions likely to be used against you, so remove material value
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Peace not possible in some scenarios}
-\pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
-  When $\alpha_L < 1$ is allowed, peace becomes unachievable for some parameters under which it is achievable when concessions do not have material value.
-\end{beamerboxesrounded}
-
-\pause
-\vskip.1in
-\begin{itemize}[<+->]
-	\item If peace is achievable, concessions may be either efficient or inefficient
-	\item High-type utility may increase or decrease from no-material-value case
+	\item If $p$ is low, concessions likely to be used against you
+	\item If $\de_l$ is low, concession has to be large to deter low type from from mimicking high type
 \end{itemize}
@@
 	\item Concession is necessary to get truthful revelation, but only to high type
-	\item Need cost of concession for low type to be not to large relative to cost for high type
+	\item Need cost of concession for low type to be not too large relative to cost for high type
 \end{itemize}
@@
 \pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 6}
-  A mediator restores peace where $\alpha_i < 1$ destroys it, eliminates inefficient concessions, and reduces the threshold $\de_h$ for high types.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
+  A mediator restores peace where concessions' future welfare impact destroys it and eliminates inefficient concessions elsewhere.
 \end{beamerboxesrounded}
@@
 
-Back to \hyperlink{hurt}{\beamerbutton{Concessions can hurt the giver}}.
+Back to \hyperlink{hurt}{\beamerbutton{Burning money unattractive}}.
 \end{frame}

### 2020-01-07 notes.tex
add notes from CPEG presentation
add more calculations for case of e=0

@@
 		\]
-	\item For $e=0$, you're back in the original case with no material value, i.e. enforceable for same $\de_h$ has no material value case
+		Note that all the $g$'s should be $g_h$'s in the five lines above:
+		\[
+		  g_h \de_h \geq - pT - pT g_h + D g_h + pW - pD - pD g_h + g_h
+		\]
+		\[
+		  \de_h \geq \frac{p(W - D - T)}{g_h} + (1-p)D + 1 - pT 
+		\]
+	\item For $e=0$, you're back in the original case with no material value, i.e. enforceable for same $\de_h$ as no material value case
+		\[
+		  \frac{p}{1-\de_h}T + \frac{1-p}{1-\de_h}(W - D) - g_0 \geq \frac{1}{1-\de_h}(W-D)
+		\]
+		\[
+		  pT + (1-p)(W - D) - (1-\de_h)g_0 \geq (W-D)
+		\]
+		\[
+		  pT -p(W - D) + \de_h g_0 \geq g_0
+		\]
+		\[
+		  \de_h g_0 \geq g_0 + p(W - D - T) 
+		\]
+		\[
+		  \de_h \geq 1 + \frac{p(W - D - T)}{g_0}
+		\]
+		Optimal separating gift in this setting is $g_0 = p(D+T)$. Substituting this in, we have:
+		\[
+		  \de_h \geq 1 + \frac{p(W - D - T)}{p(D+T)} = 1 + \frac{pW - p(D - T)}{p(D+T)} = 1+\frac{pW}{p(D+T)}-1 = \frac{W}{D+T}
+		\]
+
 		\begin{itemize}
 			\item But check: when $e=0$, also wipe out immediate monetary value?
+YES, in terms of benefit, but NOT cost, which is the only part that doesn't cancel out of IC constraints (same for high type and low type; benefit is on both sides; cost is on only one side)
 				\begin{itemize}
@@
 	\item But high type utility goes down
+		\begin{itemize}
+			\item Interestingly, if $e=0$, if high types would have separated without material value, they will here with material value that is destroyed (they don't do better in pooling).
+We see this by calculating the high type utility for the case where $e=0$, which is
+				\[
+				  \frac{1}{1-\de_h}\left[pT + (1-p)(W-D) \right] - g_0
+				\]
+				Substituting in the value of the $g_0$ (the optimal separating gift with $e=0$) and the threshold value to separate when $e=0$, we have
+				\[
+				  \frac{T+D}{T+D-W}\left[pT + (1-p)(W-D) \right] - p(T+D)
+				\]
+				\[
+				  \frac{T+D}{T+D-W}\left[p(T +D -W) + (W-D) \right] - p(T+D)
+				\]
+				\[
+				  p(T+D) + \frac{T+D}{T+D-W}\left[W-D \right] - p(T+D)
+				\]
+				\[
+				  \frac{T+D}{T+D-W}\left[W-D \right]
+				\]
+				This is exactly the payoff to the pooling equilibrium when $\de = \frac{W}{T+D}$.
+So $U_{g_0} = U_{pooling}$ at the cutoff for separating, and $U_{g_0}$ is larger for any discount factor higher than the cutoff.
+The value of the change of peace for ever is outweighed by having to pay for the gift even though the value of the gift will never be received.
+		\end{itemize}
 \end{itemize}
@@
 
+\vskip.3in
+Notes from CPEG, Oct. 25, 2019 presentation:
+\begin{itemize}
+	\item Arnaud
+		\begin{itemize}
+			\item $\de$ are not exogenous (look at Brexit)
+			\item Proposes a one-shot game to replace the repeated game. Simple bayesian game with difference preferences depening on type.
+		\end{itemize}
+	\item Raphael Godefroy
+		\begin{itemize}
+			\item Can $\de_i$ be a function of $g$? That is, likelihood of defection decreases as concession gets better
+		\end{itemize}
+\end{itemize}
+
 \end{itemize}

### 2020-01-07 notes.tex
add EJPE Reviewer 1 comments (Reviewer 2 PDF in repo separately)

@@
 
+\newpage
+Review 1 from EJPE (Email from Toke Aidt, August 19, 2018): \\
+
+While clearly these are interesting issues, I have difficulties reading this paper.
+Everything is presented in a very unclear manner.
+Game-theoretical concepts are invoked, but typically not correctly.
+For instance, an equilibrium is a strategy profile (one strategy for each type of each player).
+Hence it does not make sense to say, as the authors do in Theorem 1 on page 10, that something is an equilibrium strategy for one type without also specifying what others do.
+As another example, on page 18, the authors say that “The revelation principle is used to attain truthful self-identification.” But in reality, the revelation principle is just an argument for why it is without loss of generality to restrict attention to direct mechanisms.
+The truthfulness of messages is guaranteed by requiring the mechanism to be incentive compatible, something the authors do not address.
+\\
+
+Another thing.
+It is not considered a good idea to introduce new assumptions, which have not been mentioned before, in the proof of a proposition, as happens in the alleged proof of Theorem 4 on page 27.
+
 \end{itemize}

### 2020-02-11 draft.tex
move thm 4 assumption out of proof, into text (EJPE ref. 1)

@@
 
+Before turning to our main result for the case where the material value of concessions can be destroyed, we make a slight simplification of the general model here.
+This is not essential for the results to hold; we make these simplifciations for ease of calculation and demonstration of the results.
+First, we restrict the functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
+This linear functional form implies that equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
+To further simplify calculations, we also assume that $s_1=s_2=m_1=m_2=1.$
+
 \begin{theorem}
@@
 \emph{Proof of Theorem \ref{theorem:4}:}\\
-Because it is relatively complicated to calculate equilibrium concessions in the general case, we make a slight simplification of the general model here.
-Restrict functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
-Also assume that $s_1=s_2=m_1=m_2=1.$ Because of linearity, equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
-Note that none of these simplifications is essential for the results to hold but we make them for ease of calculation and demonstration of the results.
-The low type's IC constraint binds so with $e=1$, the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-The high type's utility when $e=1$ is $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.
+Given the functional form restrictions that $T(\cdot),W(\cdot)$ and $D(\cdot)$ are each a scalar multiplied by its arguments and $s_1=s_2=m_1=m_2=1$, high types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$.
+Because the low type's IC constraint binds, with $e=1$ the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
+The high type's utility when $e=1$ is then $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.
 

### 2020-02-21 draft.tex
make small expositional changes; improve reference to revelation principle

@@
 When two parties are engaged in conflict and each distrusts the other's ability to pursue peace, concessions can be used to indicate an interest in making peace.
-However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made or reduce the possibility of peace.
+However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made.
+It can also reduce the possibility of peace.
 We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
-In this process, we open up a rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
+In this process, we open up a new rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
 \end{abstract}
@@
 \label{sec:bench}
-When countries are faced with doubts about each other's motives, they can proceed in several different ways.
+When countries are faced with uncertainty about each other's motives, they can proceed in several different ways.
 There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor for the high type ($\delta_h$) exceeds the cutoff found in expression (1), there are many types of equilibria; consider for instance oscillating every other period between Peace and War with a grim trigger War threat.
@@
 Most agreements come with concessions, and in many cases, though not all, they are used as signals.
-The goal is to use this option to avoid continual distrust; a mediator is one way of enabling this solution.
+The goal is to use this option to avoid continual distrust; we will show in Section 5 that a mediator is one way of enabling this solution.
 
@@
 The analysis is conducted with standard incentive compatibility constraints.
-Consider the commonly held grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round.
+Consider the commonly employed grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round.
 This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace.
@@
 The model setup is as before, but instead of parties being free to give whatever concession they want, the mediator solicits type reports and then enforces incentive compatible concessions.
-This mediator wil be modeled as a mechanism $M$.
+The Revelation Principle tells us that it is without loss of generality to restrict attention to direct mechanisms, that is, mechanisms in which countries simply declare their types (Myerson 1979).
+This mediator will be modeled as a mechanism $M$.
 
@@
 $M$ can differentiate based on recipient's type.
-Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value.
+Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value: both individual rationality and incentive compatibility constraints must be satisfied, leading to truthful self-identification.
 
-The welfare target is again the sum of the high type utilities.
-Qualitatively, similar results would hold if we also included low types in the analysis with weighting based on $p$.
-In the analysis, incentive compatibility and individual rationality constraints must be satisfied.
-The revelation principle is used to attain truthful self-identification (Myerson 1979).
+The welfare target is again the sum of the high type utilities. Qualitatively, similar results would hold if we also included low types in the analysis with weighting based on $p$.
 
@@
 \end{theorem}
-\emph{Proof:} (a) Under $M$, the low type IC can bind without having high types give a concession to low types.
+\emph{Proof:} (a) Under $M$, the low type incentive constraint can bind without having high types give a concession to low types.
 There is no need then to give inefficient concessions: high types will invest in civil society and improve the giver's welfare and low types will never receive the concession.
@@
 Our paper shows a mechanism by which this might work.
-In our model's setup, there are three potential types of equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which is essentially a state of war for all types.
+In our model's setup, there are three classes of interesting equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which is essentially a state of war for all types.
 Second, if prior trust is sufficiently high, a no-concessions pooling equilibrium exists where high types trust in the first period and can maintain that trust if both are high types.

### 2020-02-21 draft.tex
clarify role of mediator

@@
 \begin{theorem}
-	The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
+	When low types give no concessions in period 0 and always play Fight thereafter, the strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
 	\label{theorem:1}
@@
 A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997).
-We will now introduce a mediator who does both.
+We will now introduce a mediator who does the latter.\footnote{Here the parties' actions in the stage game as well as their choices of whether to spend concessions on the civil versus the military sector are assumed to derive from their type, so there is no need for the mediator to enforce these decisions once the type is revealed.
+Thus, we do not assume that the mediator can do either because it is not necessary.}
 

### 2020-02-22 draft.tex
revise conclusion heavily

@@
 While parties generally are better off when concessions are efficient, we have shown that inefficiency may be useful.
-In particular, if concessions may be used for further material harm against the giver, it may be better to give inefficient concessions.
+In particular, if concessions may be used to harm the giver materially, it may be better to give inefficient concessions.
 This explanation captures the hesitancy of nations to fully engage in moving forward with a peace process when there is mutual distrust.
@@
 
-However, there must be a caveat about modeling concessions.
-The initial thought would be that it is somewhat abstract to model a concession as a number.
-However it is not necessarily insufficient as often times concessions really do come in sizes, for example the number of prisoners released, an amount of land ceded, or an amount of time given to carry out actions.
-So the magnitude of concessions can indeed vary.
-But while magnitudes vary, the real caveat is that the nature of the concessions is sometimes non-negotiable.
+At first glance, it may seem somewhat abstract to model a concession as a number.
+However, the magnitude of concessions can indeed vary: often concessions really do come in sizes, for example the number of prisoners released, an amount of land ceded, or an amount of time given to carry out actions.
+But while magnitudes often do vary, this points to a very real caveat.
+The nature of the concessions is sometimes non-negotiable.
 For instance if one country demands release of hostages, it is not possible -- or at least not realistic -- for the other country to give the equivalent value in land, cash or weapons.
 
-In practice, in ``sons of the soil'' conflicts, concessions are indivisible (Walter 2002), therefore if inefficient concessions need to be given, no concessions will be in fact given as an inefficient concession is an impossibility.
-The full value is the only concession worth making because it is the only one that will be accepted.
-Inefficient concessions can have the same signaling value, but unless signaling is the only facet of a concession that is valued, this is not enough.
-Therefore when we think about concessions, we should think about their nature as being fixed.
+In practice, in ``sons of the soil'' conflicts, concessions are indivisible (Walter 2002); if inefficient concessions need to be given to achieve peace, in the absence of a mediator no concessions will be given as an inefficient concession is an impossibility.
+The full value is the only concession worth making because it is the only one that will be accepted: although countries may prefer to give inefficient concessions, they obviously do not prefer to receive them.
+Inefficient concessions can have the same signaling value as efficient concessions, but unless signaling is the only facet of a concession that is valued, this is not necessarily enough to achieve peace.
+
+This points out that when we think about concessions, we should think about their nature as being fixed.
 With this in mind, we can then accurately consider whether concessions are of sufficient size.
 These observations do not undermine the model.
-Countries may prefer to give inefficient concessions; they do not necessarily prefer to receive them.
+The nature of the desired concessions helps determine whether inefficient concessions can help achieve peace when efficient concessions cannot and thus also when a mediator can restore the efficiency of concessions.
 
-The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy the inefficiency if she is trusted.
+The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy a particular kind of inefficiency if she is trusted.
 One contribution of this paper is to show the mechanisms through which a mediator can help.
-Since the mediator eliminates inefficient concessions, the observation that inefficient concession may not do the trick only underscores the potential value of a mediator.
+Since the mediator eliminates inefficient concessions, the observation that inefficient concessions may not do the trick only underscores the potential value of a mediator.
 %our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred.
 
-While this model uses manipulative mediation, which is indeed used in resolving conflicts, the usefulness of mediation relies on perfect trust of the mediator.
-Such an all-powerful mediator is a strong assumption, and while useful as a benchmark, it is unlikely to exist in most scenarios.
+This model uses manipulative mediation, which is indeed used in resolving conflicts.
+However, the usefulness of mediation relies on perfect trust of the mediator.
+Such an all-powerful mediator is a strong assumption, and while useful as a benchmark, it is unlikely to exist in all scenarios.
 It would be useful as a further exercise to examine the effectiveness of mediators with different strengths of enforcement capabilities.
 
-While it is an important theoretical result to show how a mediator can help conflict situations, it should also be noted that mediation is not free, at least to the providing (third) party.
-Therefore, the inefficiencies borne by the inefficient concessions and/ or by the ongoing conflict must not be outweighed by the cost of providing the mediation.
+While it is important theoretically to show how a mediator can help in conflict situations, it should also be noted that mediation is not free, at least to the providing (third) party.
+Therefore, the inefficiencies borne by the inefficient concessions and/or by the ongoing conflict must not be outweighed by the cost of providing the mediation.
 If the model accurately captures the costs, the expected savings of mediation can be calculated and therefore the value of mediation in a specific scenario can be determined.
@@
 
-This paper succeeds in showing a role for inefficient concessions, and shows how a mediator can remedy this situation.
+This paper shows that inefficient concessions may be used to achieve peace when efficient concessions are not sufficient to do so; it also demonstrates how a mediator can achieve peace in these situations without resorting to inefficient concessions.
 Opportunities for further research clearly include looking at the roles of different types of mediation.

### 2020-02-29 notes.tex
add to notes on comparison of pooling and separating eqm utilities

@@
 				\]
-				Substituting in the value of the $g_0$ (the optimal separating gift with $e=0$) and the threshold value to separate when $e=0$, we have
+				Substituting in the value of the $g_0$ (the optimal separating gift with $e=0$, which I have as $p(T+D)$ but I should check again to make sure it's correct for this situation) and the threshold value to separate when $e=0$ (i.e.
+$\de = \frac{W}{T+D}$), we have
 				\[
@@
 				\]
-				This is exactly the payoff to the pooling equilibrium when $\de = \frac{W}{T+D}$.
+				This is exactly the payoff to the pooling equilibrium (that is, both types pool on fight with no gift giving) when $\de = \frac{W}{T+D}$, since $U_{pooling} = \frac{W-D}{1-\de}$.
+
 				So $U_{g_0} = U_{pooling}$ at the cutoff for separating, and $U_{g_0}$ is larger for any discount factor higher than the cutoff. 
-The value of the change of peace for ever is outweighed by having to pay for the gift even though the value of the gift will never be received.
+					\begin{itemize}
+						\item This can be seen, for instance, by decomposing $U_{pooling}$ along the same lines as $U_{g_0}$ above into components for the cooperation vs.
+punishment and cost of the gift (even though that's not what's going on in pooling).
+The whole thing increases, including the cost of the gift portion for the pooling when $\de$ increases.
+But the cost of the gift does not scale up in $U_{g_0}$.
 					\end{itemize}
+		\end{itemize}
+		We can also do this more generally. Take
+			\[
+			  U_{g_0} = \frac{1}{1-\de}\left(W-D\right)
+			\]
+			\[
+				U_{pooling} = \frac{1}{1-\de_h}\left[pT + (1-p)(W-D) \right] - p(T+D) 
+			\]
+			\[
+			  = pT + pD +\frac{\de}{1-\de}\left(pT + pD\right) + \frac{1}{1-\de} \left( W -D -pW\right) - pT -pD
+			\]
+			\[
+			  = \frac{\de}{1-\de}\left(pT + pD\right) + \frac{1}{1-\de} \left( W -pW -D\right)
+			\]
+		Now compare the two, $U_{g_0} \lessgtr U_{pooling}$:
+				\[
+				  \frac{\de}{1-\de}\left(pT + pD\right) + \frac{1}{1-\de} \left( W -pW -D\right) \lessgtr \frac{1}{1-\de}\left(W-D\right)
+				\]
+				\[
+				  \frac{\de}{1-\de}\left(pT + pD\right) - \frac{1}{1-\de} \left( pW \right) \lessgtr 0
+				\]
+				\[
+				  \de\left(pT + pD\right) \lessgtr pW 
+				\]
+				\[
+				  \de \lessgtr \frac{pW}{pT + pD} = \frac{W}{T+D}
+				\]
+			So that the utility from $U_{g_0}$ is greater exactly when the discount factor is above the threshold for concessions separating equilibrium to be possible without material value.
 \end{itemize}

### 2020-03-18 notes.tex
add notes on utility differences between e=0 and e=1 cases

@@
 
+\vskip.2in
+How does utility compare under $e=1$ and $e=0$? Compare the two, $U_{g_1} \lessgtr U_{g_0}$:
+				\[
+				  \frac{p}{1-\de_h}T(1+g) + \frac{1-p}{1-\de_h}(W - D(1+g)) - g_h \lessgtr \frac{1}{1-\de_h}\left[pT + (1-p)(W-D) \right] - g_0
+				\]
+				\[
+				  pT(1+g_1) + \left(1-p\right)(W - D(1+g_1)) - \left(1-\de_h\right)g_1 \lessgtr pT + (1-p)(W-D) - \left(1-\de_h\right)g_0
+				\]
+				\[
+				  pTg_1 + \left(1-p\right)(W - D -Dg_1) - \left(1-\de_h\right)g_1 \lessgtr (1-p)(W-D) - \left(1-\de_h\right)g_0
+				\]
+				\[
+				  pTg_1 - \left(1-p\right)Dg_1 - \left(1-\de_h\right)g_1 \lessgtr - \left(1-\de_h\right)g_0
+				\]
+				\[
+				  pTg_1 - \left(1-p\right)Dg_1  \lessgtr \left(1-\de_h\right)g_1 - \left(1-\de_h\right)g_0
+				\]
+				\begin{equation}
+				  pT - \left(1-p\right)D  \lessgtr \frac{\left(1-\de_h\right)\left(g_1 - g_0 \right)}{g_1}
+					\label{eq:util}
+				\end{equation}
+
+We know (from above) that the minimum gift when $e=1$ is larger than the minimum gift when $e=0$ when
+\[
+  (1-\de)pT > (1-p)D
+\]
+
+\vskip.2in
+Let's case this out.
+\begin{enumerate}
+	\item Assume $g_0 = g_1$; then $(1-\de)pT = (1-p)D$. The right hand side of \ref{eq:util} is 0 and the left hand side is
+		\[
+			pT - (1-\de)pT = pT - pT + \de pT = \de pT 
+		\]
+		And utility under $e=1$ is higher.
+	\item When $g_0 > g_1$; then $(1-\de)pT < (1-p)D$.
+The right hand side of \ref{eq:util} is negative and the left hand side is larger (more positive) than in case 1, so utility under $e=1$ is also higher in this case.
+	\item When $g_1 > g_0$; then $(1-\de)pT > (1-p)D$.
+The right hand side of \ref{eq:util} becomes positive and the left hand side becomes smaller (less positive, and possibly negative) than in case 1, so utility under $e=1$ is higher when $g_1$ is only a little larger than $g_0$, but eventually as $g_1$ gets much larger than $g_0$, utility under $e=0$ becomes larger than utility under $e=1$.
+\end{enumerate}
+
 \newpage

### 2020-04-07 draft.tex
add reference to Watson 1999 and explanation of Horner 2010 benchmark as suggested by reviewers

@@
 
-Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts.
-In order to explain inefficiency, Camerer adds in an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts.
+Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts.\footnote{In an environment with repeated opportunities for concessions Watson (1999) is able to show that a strong relationship can be reached by starting with small ``gifts'' and increasing their size as the relationship becomes more committed.
+See Van de Ven (2000) for an overview of this literature.} In order to explain inefficiency, Camerer adds in an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts.
 If types separate in the pre-play period with low types not being willing to pay, high types are saved the cost of sending a signal to low types in the main game.
@@
 Conversely Horner et al.
-(2010) rely on the mediator to ``hoard'' information in order to be able to improve on unmediated interaction.
-In our model, a successful mediator relies on the parties trusting her.
+(2010) rely on the mediator to ``hoard'' information in order to be able to improve on unmediated interaction.\footnote{Horner et al.
+(2010) take cheap talk communication as their benchmark of unmediated communication, whereas we take the unmediated signaling game as our benchmark.} In our model, a successful mediator relies on the parties trusting her.
 However, here the mediator had no incentive to lie: lying can only potentially hurt the high types, the only type who the mediator can possibly help.
@@
 
-\item Watson, Joel (1996). ``Building a Relationship,'' Unpublished manuscript.
+%\item Watson, Joel (1996). ``Building a Relationship,'' Unpublished manuscript.
 

### 2020-11-29 notes.tex
create sections in notes.tex; start mediator section with IC constraints

@@
 \vskip.3in
-\un{June 6, 2017}\\
-Want to develop result showing that mediator increases potential for peace
+
+\section{Make mediator work}
+\un{November 29, 2020}\\
+In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation.
+Here I will see what adjustments might make the mediator work.\\
+
+IC constraints for Mediation
+\begin{itemize}
+	\item low type IC:
+		$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
+			\begin{itemize}
+				\item If a low type reveals truthfully: you get $X_{FF}$ and no gift with probability $p$; you get the same with probability $(1-p)$ (you need both countries to be high types in order to do anything)
+				\item If a low type lies: get $X_{FT}$ and give gift ($g_h$) and receive gift ($eg_h$) with probability $p$; $X_{FF}$ again with probability $(1-p)$
+					\begin{itemize}
+						\item High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out
+					\end{itemize}
+				\item Relative to Section 4.2, there is no $peg_h$ on the RHS: no benefit of getting the gift from the high type
+					\begin{itemize}
+						\item NEXT STEP: CHECK THESE CLAIMS ABOUT THE RELATIONSHIP TO SECTION 4.2
+					\end{itemize}
+			\end{itemize}
+	\item high type IC:
+		$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
+\end{itemize}
+
+\vskip.5in
+\section{Develop result: mediator increases potential for peace}
+\un{June 6, 2017}
+
 \begin{itemize}
@@
 \newpage
-To-do list after Venice CesIfo 06/15/17:
+\section{To-do list after Venice CesIfo 06/15/17}
 \begin{itemize}
@@
 \newpage
-Review 1 from EJPE (Email from Toke Aidt, August 19, 2018): \\
+\section{Review 1 from EJPE (Email from Toke Aidt, August 19, 2018)}
 

### 2020-11-30 notes.tex
add calculations low type IC doesn't hold with e=1 under mediation

@@
 \section{Make mediator work}
-\un{November 29, 2020}\\
-In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation.
+\un{November 29-30, 2020}: In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation.
 Here I will see what adjustments might make the mediator work.\\
 
-IC constraints for Mediation
+\subsection{IC constraints for Mediation}
 \begin{itemize}
-	\item low type IC:
+	\item High type IC:
+		$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
+			\begin{itemize}
+				\item Relative to Section 4.2, $-g_h$ there becomes $-pg_h$ here (again, only give gift if matched with high type). Also $+peg_h$ in Section 4.2 disappears on RHS.
+			\end{itemize}
+	\item Low type IC:
 		$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
@@
 				\item If a low type lies: get $X_{FT}$ and give gift ($g_h$) and receive gift ($eg_h$) with probability $p$; $X_{FF}$ again with probability $(1-p)$
-					\begin{itemize}
-						\item High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out
-					\end{itemize}
-				\item Relative to Section 4.2, there is no $peg_h$ on the RHS: no benefit of getting the gift from the high type
-					\begin{itemize}
-						\item NEXT STEP: CHECK THESE CLAIMS ABOUT THE RELATIONSHIP TO SECTION 4.2
+				\item Relative to Section 4.2, there is no $peg_h$ on the LHS (in Section 4.2, it cancels out with the $peg_h$ on the RHS): no benefit of getting the gift from the high type.
+Also, $-g_h$ on the RHS becomes $-pg_h$ since you only send the gift if matched with a high type
 			\end{itemize}
 \end{itemize}
-	\item high type IC:
-		$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
+
+\subsection{Why does low type IC not hold when $e=1$?}
+$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
+\begin{itemize}
+	\item With our restrictions (mostly the linear assumption, IIRC), High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out. This leaves
+		$$X_{FF}^l \geq pX_{FT}^l + X_{FF}^l - pX_{FF}^l$$
+		which simplifies to 
+		$$X_{FF}^l \geq X_{FT}^l.$$
+		Expanding, we have
+		\[
+			\frac{W\left( \right)-D\left( \right)}{1-\de^l} \geq T\left( \right) + W\left( \right) + \frac{\de^l}{1-\de^l}\left(W\left( \right) -D\left( \right) \right)
+		\]
+		Now we have to fill in all the complicated bits in parentheses from Table 3 in Section 4.2
+		\begin{multline*}
+			W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right) \geq \\
+			\left(1-\de^l\right) \left[T\left(s_2 + \al_2eg_1\right) + W\left(m_1 + \left(1-\al_1\right)eg_2\right) \right] \\
+			+ \de^l \left(W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right)\right)
+		\end{multline*}
+
+		We've already assumed $e=1$ here as given in Lemma 2 for a concessions separating equilibrium 
+			\begin{itemize}
+				\item \textbf{Mediator could instruct them to give $e<1$ gifts without having to disturb the rest of the theory (I think). This I'll come back to.}
+				\item We \textit{should} assume $s_1,s_2,m_1,m_2$ to all be 1 to be consistent with the theory though. If we implement all that AND $e=1$, we get
+					\begin{multline*}
+							W\left(1 + \left(1-\al_1\right)g_2\right)-D\left(1 + \left(1-\al_2\right)g_1\right) \geq \left(1-\de^l\right) \left[T\left(1 + \al_2g_1\right) + W\left(1 + \left(1-\al_1\right)g_2\right) \right] \\
+							+ \de^l \left(W\left(1 + \left(1-\al_1\right)g_2\right)-D\left(1 + \left(1-\al_2\right)g_1\right)\right)
+					\end{multline*}
+				\item We also know that there are no gifts exchanged for $X^l_{FF}$, so $g_1 = g_2 = 0$ on the LHS.
+On the RHS, gifts ARE exchanged because player 2 is a high type and the low type of player 1 lied.
+So we can set $g_1 = g_2 = g_M$
+					\begin{multline*}
+							W - D \geq \left(1-\de^l\right) \left[ T\left(1 + \al_2g_M\right) + W\left(1 + \left(1-\al_1\right)g_M\right) \right] \\
+							+ \de^l \left(W\left(1 + \left(1-\al_1\right)g_M\right)-D\left(1 + \left(1-\al_2\right)g_M\right)\right)
+					\end{multline*}
+				\item Now for the $\al$'s. The low type of player 1 sets $\al_1 = 0$ (this is the amount that goes to civil society). Player 2 is a high type here, so sets $\al_2 = 1$.
+					\[
+							W - D \geq \left(1-\de^l\right) \left[ T\left(1 + g_M\right) + W\left(1 + g_M\right) \right] + \de^l \left(W\left(1 + g_M\right)-D\right)
+					\]
+				\item Distributing, we have 
+					\[
+							W - D \geq T + Tg_M + W + Wg_M - \de^l T - \de^l Tg_M - \de^l W - \de^l Wg_M + \de^l W + \de^l Wg_M - \de^l D
+					\]
+				\item Canceling terms:
+					\[
+							- D \geq T + Tg_M + Wg_M - \de^l T - \de^l Tg_M - \de^l D
+					\]
+				\item Rearranging:
+					\[
+							0 \geq \left(1 - \de^l \right) T + \left(1 - \de^l \right) Tg_M + Wg_M + \left(1 - \de^l \right) D
+					\]
+					Assuming $g_M > 0$, this inequality can never hold since each of $T,W,D\geq0$ and $0 \leq \left(1 - \de^l \right) \leq 1$	
+					\begin{itemize}
+						\item What would it mean to have negative gifts?
+					\end{itemize}
+
+			\end{itemize}
 \end{itemize}

### 2020-12-01 notes.tex
Add notes on civil society vs military choices

@@
 
+\subsection{Civil society investment choices}
+In a concessions separating equilibrium or in the mechanism, the high type always has the incentive to invest all of the gift in civil socity
+	\begin{itemize}
+		\item If there is an exchange of gifts (whether in the mechanism or a truthfully revealed separating equilibrium), you know you're both receiving from and giving to a high type
+		\item \textbf{I should check this in all the scenarios to make sure we don't invoke it when it's not right}
+			\begin{itemize}
+				\item \textbf{I also want to know whether it depends on the linear form}
+				\item \textbf{Make more explicit in the text}
+			\end{itemize}
+	\end{itemize}
+$\al_i$ is the proportion of the gift that country $i$ receives that it invests in civil society.
+	\begin{itemize}
+		\item $\al_i = 1$ means the whole value of the gift is invested in civil society. High types make this choice
+			\begin{itemize}
+				\item $\al_i = 0$ means the whole value of the gift is invested in military buildup
+			\end{itemize}
+
+		\item High type of Country 1 chooses $\al_1=1$ (all into civil society) 
+			\begin{itemize}
+				\item $(1-\al_1) = 0$ (nothing into military)
+			\end{itemize}
+		\item Low type of Country 1 chooses $\al_1=0$ (nothing into civil society) 
+			\begin{itemize}
+				\item $(1-\al_1) = 1$ (all into military)
+			\end{itemize}
+		\item High type of Country 2 chooses $\al_2=1$ (all into civil society) 
+			\begin{itemize}
+				\item $(1-\al_2) = 0$ (nothing into military)
+			\end{itemize}
+		\item Low type of Country 2 chooses $\al_2=0$ (nothing into civil society) 
+			\begin{itemize}
+				\item $(1-\al_2) = 1$ (all into military)
+			\end{itemize}	
+	\end{itemize}
+
 \subsection{Why does low type IC not hold when $e=1$?}
@@
 					\end{itemize}					
-
 			\end{itemize}
 \end{itemize}
+
+\subsection{What if gifts are inefficient?}
+*** THIS IS THE NEXT STEP IN THE ANALYSIS *** Here we would be using inefficient gifts to get the low type to truthfully reveal.
 

### 2020-12-01 notes.tex
extend e=1 analysis of low type IC constraint to e<1

@@
 \section{Make mediator work}
-\un{November 29-30, 2020}: In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation.
-Here I will see what adjustments might make the mediator work.\\
+November 29, 2020: In making revisions in April 2020 to respond to the EJPE referee reports, I discovered the IC constraint does not hold for the low type in Section 5: Mediation.
+Here I will see what adjustments might make the mediator work.
+\begin{itemize}
+	\item November 30: I showed formally and in great detail in Section \ref{sec:e1} that the IC constraint does not bind for $e=1$ with our standard assumptions.
+	\item December 1: I began working on the $e < 1$ case in Section \ref{sec:eless}
+\end{itemize}
+
+\subsection{Mediation: Basic Details and Overview}
+\begin{itemize}
+	\item If the mediator gets two `high' reports, both countries are instructed to exchange gifts and play `Trust'
+	\item If the mediator gets one or zero `high' reports, there is no gift and they both play `Fight'
+\end{itemize}
+I show the constraints for both types in Section \ref{sec:const}.\\
+I detail the choices of all types in regards to investments in civil society in Section \ref{sec:civ}.\\
+I show in Section \ref{sec:e1} that the low type's IC constraint cannot hold if $e=1$.\\
 
 \subsection{IC constraints for Mediation}
+\label{sec:const}
 \begin{itemize}
@@
 \subsection{Civil society investment choices}
+\label{sec:civ}
 In a concessions separating equilibrium or in the mechanism, the high type always has the incentive to invest all of the gift in civil socity
@@
 
-\subsection{Why does low type IC not hold when $e=1$?}
-$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
-\begin{itemize}
-	\item With our restrictions (mostly the linear assumption, IIRC), High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out. This leaves
+\subsection{Why does low type IC not hold with efficient gifts?}
+\label{sec:e1}
+\begin{equation}
+	X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h
+	\label{eqn:IClow}
+\end{equation}
+With our restrictions (mostly the linear assumption, IIRC), High type gives gift with efficiency $e=1$, so gift giving and receiving cancels out. This leaves
 		$$X_{FF}^l \geq pX_{FT}^l + X_{FF}^l - pX_{FF}^l$$
@@
 		Now we have to fill in all the complicated bits in parentheses from Table 3 in Section 4.2
-		\begin{multline*}
+		\begin{multline}
 			W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right) \geq \\
@@
 			+ \de^l \left(W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right)\right)
-		\end{multline*}
+			\label{eq:lowICex}
+		\end{multline}
 
@@
 	\begin{itemize}
-				\item \textbf{Mediator could instruct them to give $e<1$ gifts without having to disturb the rest of the theory (I think). This I'll come back to.}
 		\item We \textit{should} assume $s_1,s_2,m_1,m_2$ to all be 1 to be consistent with the theory though. If we implement all that AND $e=1$, we get
@@
 			\end{multline*}
-				\item Now for the $\al$'s. The low type of player 1 sets $\al_1 = 0$ (this is the amount that goes to civil society). Player 2 is a high type here, so sets $\al_2 = 1$.
-					\[
+		\item The $\al_i$'s. Recall $\al_i$ represents the portion of the received gift that Player $i$ invests in civil society.
+			\begin{itemize}
+				\item Player 1 is low type (it is the low type IC constraint that I'm analyzing) and so $\al_1 = 0$.
+				\item Player 2 is a high type in what's left of the RHS, so $\al_2 = 1$.
+					\begin{itemize}
+						\item The $(1-p)$ part of the RHS was combined with the LHS; it was for the low type of Player 2, so it matched with the LHS where there are no gifts since the mediator instructs no gifts if one low-type player tells the truth, which Player 2 does when we're looking at Player 1's IC constraint.
+					\end{itemize}
+				\item With $a_1 = 0$ and $a_2 = 1$, we have
+					\begin{equation}
 							W - D \geq \left(1-\de^l\right) \left[ T\left(1 + g_M\right) + W\left(1 + g_M\right) \right] + \de^l \left(W\left(1 + g_M\right)-D\right)
-					\]
+							\label{eqn:alphas}
+					\end{equation}
+			\end{itemize}
+
 		\item Distributing, we have 
@@
 		\end{itemize}
+
+\subsection{What if gifts are inefficient?}
+\label{sec:eless}
+Here I attempt to use inefficient gifts to get the low type to truthfully reveal.\\
+
+Equation \ref{eqn:IClow} is the general form of the IC constraint.
+In the next step in Section~\ref{sec:e1}, I let the gifts cancel out because we assume in that section that $e=1$.
+I need to go back to Equation \ref{eqn:IClow} here since $e$ is not assumed to be 1.
+\[
+	X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h
+\]
+Leaving the two gift terms on the end intact, I simplify in the same way as in Section $\ref{sec:e1}$ to arrive at the correct analog to Equation~\ref{eq:lowICex}.
+		\begin{multline*}
+			W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right) \geq \\
+			\left(1-\de^l\right) \left[T\left(s_2 + \al_2eg_1\right) + W\left(m_1 + \left(1-\al_1\right)eg_2\right) \right] \\
+			+ \de^l \left(W\left(m_1 + \left(1-\al_1\right)eg_2\right)-D\left(m_2 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
+		\end{multline*}
+	\begin{itemize}
+		\item We assume $s_1,s_2,m_1,m_2$ to all be 1 to be consistent with Section 4.2
+			\begin{multline*}
+				W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right) \geq \\
+			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_1\right) + W\left(1 + \left(1-\al_1\right)eg_2\right) \right] \\
+			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_2\right)-D\left(1 + \left(1-\al_2\right)eg_1\right)\right) -pg_h+peg_h
+			\end{multline*}
+		\item We know that there are no gifts exchanged for $X^l_{FF}$, so $g_1 = g_2 = 0$ on the LHS.
+On the RHS, gifts ARE exchanged because player 2 is a high type and the low type of player 1 lied.
+So we can set $g_1 = g_2 = g_M$:
+			\begin{multline*}
+				W\left(1 \right)-D\left(1 \right) \geq
+			\left(1-\de^l\right) \left[T\left(1 + \al_2eg_M\right) + W\left(1 + \left(1-\al_1\right)eg_M\right) \right] \\
+			+ \de^l \left(W\left(1 + \left(1-\al_1\right)eg_M\right)-D\left(1 + \left(1-\al_2\right)eg_M\right)\right) -pg_M+peg_M
+			\end{multline*}
+		\item With $a_1 = 0$ and $a_2 = 1$ (Recall the discussion above Equation~\ref{eqn:alphas}), we have
+			\[
+				W - D \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
+			+ \de^l \left(W\left(1 + eg_M\right) - D\right) -pg_M+peg_M
+			\]
+		\item It's time to start rearranging:
+			\[
+				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
+			+ \de^l W\left(1 + eg_M\right) - \de^l D - W + D
+			\]
+			\[
+				pg_M\left(1 - e\right) \geq \left(1-\de^l\right) \left[T\left(1 + eg_M\right) + W\left(1 + eg_M\right) \right] 
+			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
+			\]
+			\begin{multline*}
+			  	pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) -\de^l W\left(1 + eg_M\right) \\
+			+ \de^l W\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
+			\end{multline*}
+			\[
+				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + W\left(1 + eg_M\right) -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D - W
+			\]
+			\[
+				pg_M\left(1 - e\right) \geq T\left(1 + eg_M\right) + Weg_M -\de^l T\left(1 + eg_M\right) + \left(1 - \de^l\right) D
+			\]
+			\[
+				pg_M\left(1 - e\right) \geq \left(1 - \de^l\right) T\left(1 + eg_M\right) + Weg_M + \left(1 - \de^l\right) D
+			\]
 	\end{itemize}
 
-\subsection{What if gifts are inefficient?}
-*** THIS IS THE NEXT STEP IN THE ANALYSIS *** Here we would be using inefficient gifts to get the low type to truthfully reveal.
+\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}
+\begin{itemize}
+	\item Digitize handwritten notes pages 1-3
+\end{itemize}
+
+\vskip.2in
+Notes:
+\begin{itemize}
+	\item I think Mediator could instruct them to give $e<1$ gifts without having to disturb the rest of the theory. 
+		\begin{itemize}
+			\item \textbf{If I go with $e<1$, I need to come back to verify this.}
+		\end{itemize}
+\end{itemize}
 

### 2020-12-02 notes.tex
Develop notes on e<1 mediation case

@@
 \DeclareMathOperator*{\argmax}{arg\,max}
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 \hbadness=10000
@@
 			\]
+			\begin{equation}
+				pg_M\left(1 - e\right) \geq \left(1 - \de^l\right) T\left(1 + eg_M\right) + Weg_M + \left(1 - \de^l\right) D
+				\label{eq:examine}
+			\end{equation}
+	\end{itemize}
+
+\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}.
+Continuing on from Equation~\ref{eq:examine} and simplifying so that $g_M = g$ and $\de^l = \de$,
 \[
-				pg_M\left(1 - e\right) \geq \left(1 - \de^l\right) T\left(1 + eg_M\right) + Weg_M + \left(1 - \de^l\right) D
+	pg\left(1 - e\right) \geq \left(T - \de T \right) \left(1 + eg\right) + Weg + \left(1 - \de \right) D
+\]
+	\begin{itemize}
+		\item Distributing AGAIN
+			\[
+				pg	\left(1 - e\right) \geq T + Teg - \de T - \de T eg + Weg + \left(1 - \de \right) D
+			\]
+			\[
+				pg	\left(1 - e\right) \geq \left(1 - \de \right) T + \left(1 - \de \right) D + Teg - \de T eg + Weg
+			\]
+			\begin{equation}
+				pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)
+				\label{eq:split}
+			\end{equation}
+		\item From here we can solve either for the constraint in terms of $g$ or in terms of $e$
+			\begin{itemize}
+				\item First solve for $g$ starting from Expression~\ref{eq:split}:
+					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
+					$$pg - pge - eg \left( T - \de T + W \right)\geq \left(1 - \de \right) \left( T + D \right)$$
+					\begin{equation}
+						g \left(p - e \left( p + T - \de T + W \right) \right) \geq \left(1 - \de \right) \left( T + D \right)
+						\label{eq:g1}
+					\end{equation}
+					\begin{equation}
+						g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
+						\label{eq:g2}
+					\end{equation}
+						\begin{itemize}
+							\item THIS ASSUMES {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
+								\begin{itemize}
+									\item Note that if we set $e=0$, this is a very simple constraint on $g$
+										\begin{equation}
+											g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p}
+											\label{eq:g3}
+										\end{equation}
+								\end{itemize}
+							\item $T+D$, $1 - \de $ non-negative by assumption $\Rightarrow$ RHS of Expression~\ref{eq:g1} non-negative
+								\begin{itemize}
+									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$. AGAIN WITH THE NEGATIVE GIFTS.
+								\end{itemize}
+							\item To compare to the optimal gift size in the other sections:
+								\begin{itemize}
+									\item In Section 3 (Concessions Separating Equilibrium): $p\left(T+D\right)$
+									\item Material value with $e=0$ same as in Section 3: $p\left(T+D\right)$
+									\item Material value with $e=1$:
+										\begin{equation}
+											g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
+											\label{eq:g4}
+										\end{equation}
+									\item Under the assumption that payoffs are multiplied by something linear like $1 + \al_2 g_1$, there's no reason to choose any intermediate value of $e$.
+The mediator, of course, can specify an intermediate value.
+									\item We can simplify to see that the minimum gift when $e=1$ is larger when
+										\[
+											(1-\de)pT > (1-p)D
 										\]
 								\end{itemize}
+						\end{itemize}
 
-\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}
+				\item Now solve for $e$ starting from Expression~\ref{eq:split}:
+					$$pg - \left(1 - \de \right) \left( T + D \right) \geq pge + eg \left( T - \de T + W \right)$$
+					\begin{equation}
+						pg - \left(1 - \de \right) \left( T + D \right) \geq eg \left( p + T - \de T + W \right)
+						\label{eq:g5}
+					\end{equation}
 						\begin{itemize}
-	\item Digitize handwritten notes pages 1-3
+							\item {\color{red} $g \left( p + T - \de T + W \right)$ is non-negative as long as $g$ is positive}: $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive.
+It can only possibly be zero if $p=0$ and $\de = 1$.
+								\begin{itemize}
+									\item For the IC constraint to hold then (with non-negative gifts), we must at least have {\color{red} $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative, which requires $g$ to be set according to Expression~\ref{eq:g3}}.
+This only works if $e$ is set to zero; otherwise we need to look back at Expression~\ref{eq:g2}.
+This is just a weak condition that, if violated, means the IC constraint does not hold.
+								\end{itemize}
+							\item If {\color{red} $g \left( p + T - \de T + W \right)$ is positive}, we can divide through to get
+								$$\frac{pg - \left(1 - \de \right) \left( T + D \right)}{g \left( p + T - \de T + W \right)} \geq e$$
+						\end{itemize}
+					\item To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}.
+First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
+						\begin{equation}
+							p - \frac{\left(1 - \de \right) \left( T + D \right)}{g} \geq e \left( p + T - \de T + W \right)
+							\label{eq:g6}
+						\end{equation}
+						$$p - \frac{\left(1 - \de \right) \left( T + D \right)}{p \left(T+D\right)} \geq e \left( p + T - \de T + W \right)$$
+						$$p - \frac{1 - \de}{p } \geq e \left( p + T - \de T + W \right)$$
+							\begin{itemize}
+								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
+								\item Parameterization that is in the paper now:
+									\begin{itemize}
+										\item Let $T = 10$, $W=8$ and $D = 5$
+										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$.
+Let $\de_h = .6$ and $\de_l = .3$.
+Assume $p = .2$.
+By Theorem 2, separation through concessions is possible.
+										\item Minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$
+										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+									\end{itemize}
+							\end{itemize}
+
+			\end{itemize}
+		\item \color{ForestGreen} No notes to digitize right now
+			\begin{itemize}
+				\item Calculate maximum $e$ from Expression~\ref{eq:g6} using parameterization from paper
+					\begin{itemize}
+						\item Do it under simple $g$ and the more complicated $g$ from Expression~\ref{eq:g4}
+						\item Compare to calculations in example from text
+						\item Try another parameterization with $p$ larger so it works
+					\end{itemize}
+				\item Check parameter restrictions for existence of equilibria in Section 4.2
+			\end{itemize}
 	\end{itemize}
@@
 \[
-  g^* \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)}
+  g^* \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right)} = p(T + D)
 \]

### 2020-12-05 notes.tex
Add calculations for minimum gift in e<1 case

@@
 										\item Let $T = 10$, $W=8$ and $D = 5$
+										\item Let $\de_h = .6$ and $\de_l = .3$. Assume $p = .2$. 
 										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$.
-Let $\de_h = .6$ and $\de_l = .3$.
-Assume $p = .2$.
 By Theorem 2, separation through concessions is possible.
@@
 										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+										\item Minimum $e$ from Expression~\ref{eq:g6}:
+											\[
+											  0.2 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.2 + 10 - 0.3\cdot 10 + 8 \right)
+											\]
+											\[
+											  0.2 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.2 \right)
+											\]
+											\[
+											  \frac{0.2}{11.2} - \frac{0.7 \left( 15 \right)}{11.2g} \geq e 
+											\]
+											\[
+											  0.01786 - \frac{9.375}{g} \geq e 
+											\]
+										To keep $e \geq 0$, we need $g \geq 525$ (this is REALLY big compared to $W$ for instance). It's also huge compared to the optimal gifts when $e=0$ of 3 and when $e=1$ of $0.\overline{63}$.
+									\end{itemize}
+								\item Now let's try the same parameterization with $p=0.9$.
+									\begin{itemize}
+										\item Minimum $e$ from Expression~\ref{eq:g6}:
+											\[
+											  0.9 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.9 + 10 - 0.3\cdot 10 + 8 \right)
+											\]
+											\[
+											  0.9 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.9 \right)
+											\]
+											\[
+											  \frac{0.9}{11.9} - \frac{0.7 \left( 15 \right)}{11.9g} \geq e 
+											\]
+											\[
+											  0.07563 - \frac{8.8235}{g} \geq e 
+											\]
+										To keep $e \geq 0$, we need $g \geq 116.66$.
+This is still nearly an order of magnitude larger than $W$, and both the optimal gifts when $e=0$ of 13.5 and when $e=1$ of $\frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = \frac{0.9(0.7)(15)}{0.7 \cdot (1-0.9)+(.1)5} = \frac{0.63\cdot15}{0.7 \cdot 0.1+.5} = 16.58$.
 									\end{itemize}
@@
 			\begin{itemize}
-				\item Calculate maximum $e$ from Expression~\ref{eq:g6} using parameterization from paper
+				\item Check parameter restrictions for existence of equilibria in Section 4.2
+				\item Obviously we can come up with other parameterizations in which this may look a little more reasonable
 					\begin{itemize}
-						\item Do it under simple $g$ and the more complicated $g$ from Expression~\ref{eq:g4}
-						\item Compare to calculations in example from text
-						\item Try another parameterization with $p$ larger so it works
+						\item But I think the first step is to calculate the high-type utility under the different scenarios and the different gifts and see what happens (since you get the indirect benefit of the gift--or do you since $e$ is too small?)
 					\end{itemize}
-				\item Check parameter restrictions for existence of equilibria in Section 4.2
 			\end{itemize}

### 2020-12-07 notes.tex
add section on welfare calcuations; create subsections for easier reference

--- 2020-12-02 notes.tex
@@
 
+\subsubsection{Is it possible to pick e and g to satisfy low-type IC?}
+
 \textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}.
@@
 		\item From here we can solve either for the constraint in terms of $g$ or in terms of $e$
-			\begin{itemize}
-				\item First solve for $g$ starting from Expression~\ref{eq:split}:
+	\end{itemize}
+
+\subsubsection{Solve for g}			
+			First solve for $g$ starting from Expression~\ref{eq:split}:
 					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
@@
 
-				\item Now solve for $e$ starting from Expression~\ref{eq:split}:
-					$$pg - \left(1 - \de \right) \left( T + D \right) \geq pge + eg \left( T - \de T + W \right)$$
+\subsubsection{Solve for e}
+				Now solve for $e$ starting from Expression~\ref{eq:split}:
+					$$pg - \left(1 - \de \right) \left( T + D \right) \geq peg + eg \left( T - \de T + W \right)$$
 					\begin{equation}
@@
 						\end{itemize}
-					\item To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}.
+				To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}.
 First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
@@
 								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
-								\item Parameterization that is in the paper now:
+							\end{itemize}
+
+\subsubsection{Check with some parameterizations}								
+								Parameterization that is in the paper now:
 									\begin{itemize}
 										\item Let $T = 10$, $W=8$ and $D = 5$
+										\item Let $\de_h = .6$ and $\de_l = .3$. Assume $p = .2$. 
 										\item Threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$.
-Let $\de_h = .6$ and $\de_l = .3$.
-Assume $p = .2$.
 By Theorem 2, separation through concessions is possible.
@@
 										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+										\item Minimum $e$ from Expression~\ref{eq:g6}:
+											\[
+											  0.2 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.2 + 10 - 0.3\cdot 10 + 8 \right)
+											\]
+											\[
+											  0.2 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.2 \right)
+											\]
+											\[
+											  \frac{0.2}{11.2} - \frac{0.7 \left( 15 \right)}{11.2g} \geq e 
+											\]
+											\[
+											  0.01786 - \frac{9.375}{g} \geq e 
+											\]
+										To keep $e \geq 0$, we need $g \geq 525$ (this is REALLY big compared to $W$ for instance). It's also huge compared to the optimal gifts when $e=0$ of 3 and when $e=1$ of $0.\overline{63}$.
+									\end{itemize}
+
+							\vskip.2in	
+							Now let's try the same parameterization with $p=0.9$.
+									\begin{itemize}
+										\item Minimum $e$ from Expression~\ref{eq:g6}:
+											\[
+											  0.9 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.9 + 10 - 0.3\cdot 10 + 8 \right)
+											\]
+											\[
+											  0.9 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.9 \right)
+											\]
+											\[
+											  \frac{0.9}{11.9} - \frac{0.7 \left( 15 \right)}{11.9g} \geq e 
+											\]
+											\[
+											  0.07563 - \frac{8.8235}{g} \geq e 
+											\]
+										To keep $e \geq 0$, we need $g \geq 116.66$.
+This is still nearly an order of magnitude larger than $W$, and both the optimal gifts when $e=0$ of 13.5 and when $e=1$ of $\frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = \frac{0.9(0.7)(15)}{0.7 \cdot (1-0.9)+(.1)5} = \frac{0.63\cdot15}{0.7 \cdot 0.1+.5} = 16.58$.
+									\end{itemize}
+
+						\vskip.3in
+						Utility comparisons (always for high type)
+							\begin{itemize}
+								\item When $e=1$: $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
+								\item When $e=0$: $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
+								\item When $0<e<1$ under a mediator: $\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
+									\begin{itemize}
+										\item Figure out optimal $g_M$
+										\item Expression~\ref{eq:g2} creates a menu of $(e,g)$ pairs that satisfy the constraint:
+											\[
+												g_M \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
+											\]
+										\item We're assuming $p - e \left( p + T - \de T + W \right) > 0$ (assuming gifts must be non-negative)
+										\item Also $pg - \left(1 - \de \right) \left( T + D \right) \geq 0$ ($e$ version; this is WEAKER than the condition on $e$)
 									\end{itemize}
@@
 
+\subsubsection{To do and Notes}		
+	\color{ForestGreen} No notes to digitize right now
+			\begin{itemize}
+				\item Check parameter restrictions for existence of equilibria in Section 4.2
+					\begin{itemize}
+						\item Go back to 4 or 4.1; didn't find them in 4.2
 					\end{itemize}
-		\item \color{ForestGreen} No notes to digitize right now
+				\item Obviously we can come up with other parameterizations in which this may look a little more reasonable
 					\begin{itemize}
-				\item Calculate maximum $e$ from Expression~\ref{eq:g6} using parameterization from paper
-					\begin{itemize}
-						\item Do it under simple $g$ and the more complicated $g$ from Expression~\ref{eq:g4}
-						\item Compare to calculations in example from text
-						\item Try another parameterization with $p$ larger so it works
-					\end{itemize}
-				\item Check parameter restrictions for existence of equilibria in Section 4.2
+						\item But I think the first step is to calculate the high-type utility under the different scenarios and the different gifts and see what happens (since you get the indirect benefit of the gift--or do you since $e$ is too small?)
 					\end{itemize}					
@@
 \vskip.2in
-Notes:
+\color{Black}Notes:
 \begin{itemize}

### 2020-12-07 notes.tex
Add R script for welfare calcuations and results of paper parameterization to notes

@@
 								\item When $e=1$: $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
+									\begin{itemize}
+										\item \color{red} For the parameterization in the paper, welfare is 7.18; gift is 0.63
+									\end{itemize}
 								\item When $e=0$: $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
+									\begin{itemize}
+										\item \color{red} For the parameterization in the paper, welfare is 8; gift is 3
+									\end{itemize}
 								\item When $0<e<1$ under a mediator: $\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
@@
 										\item Also $pg - \left(1 - \de \right) \left( T + D \right) \geq 0$ ($e$ version; this is WEAKER than the condition on $e$)
+										\item \color{red} For the parameterization in the paper, welfare is negative for $e=0$ and $e=0.01$, the only values of $e$ that lead to non-negative gifts; gifts range from 52.5 to 218.75
 									\end{itemize}

### 2020-12-07 e-g calculations.R

@@ -1,0 +1,25 @@
+#Parameterization from Theorem 3 in the paper
+T = 10
+W = 8
+D = 5
+p = .2
+dl = .3
+dh = .6
+
+e = seq(0, 1, 0.01)
+g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
+condition = data.frame((p - e*(p + T - dl*T +W)))
+eg = e*g #effective gift
+
+# Welfare calculations 
+# e=0
+g0 = p*(T+D)
+W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
+# e=1
+g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
+W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
+# 0 < e < 1 with mediator
+We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
+
+g1denom = (1-dl)*(1-p*T)+(1-p)*D #checks to see if denominator is positive
+    

### 2020-12-08 notes.tex
add parameterization that makes mediator welfare optimal

@@
 										\]
+										\color{red} BIG NEW NOTE: This condition only true if denominator above is positive
 								\end{itemize}
@@
 \vskip.3in
+``Parameterization 2'': goal was to make welfare higher under mediator
+\begin{itemize}
+	\item \color{orange} T = 7, W = 8, D = 5, p = .9, $\de_l = .3$, $\de_h = .6$
+	\item Minimum $e$ from Expression~\ref{eq:g6}
+	  $$0.9 - \frac{\left(1 - 0.3 \right) \left( 7 + 5 \right)}{g} \geq e \left( 0.9 + 7 - 0.3 \cdot 7 + 8 \right)$$
+		$$0.9 - \frac{8.4}{g} \geq e \left(18 \right)$$
+		$$0.05 - \frac{0.466}{g} \geq e $$
+	\item The highest welfare comes from $e=.06$, which implies $g = 116.67$ (see e-g calculations.R)
+
+\end{itemize}
+
+						\vskip.3in
 						Utility comparisons (always for high type)
@@
 									\begin{itemize}
-										\item \color{red} For the parameterization in the paper, welfare is 7.18; gift is 0.63
+										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
+										\item \color{orange} Parameterization 2: $g1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
 									\end{itemize}
@@
 									\begin{itemize}
-										\item \color{red} For the parameterization in the paper, welfare is 8; gift is 3
+										\item \color{red} Parameterization in the paper: welfare is 8; gift is 3
+										\item \color{orange} Parameterization 2: welfare is 5.7; gift is 10.8
 									\end{itemize}
@@
 									\begin{itemize}
-										\item Figure out optimal $g_M$
-										\item Expression~\ref{eq:g2} creates a menu of $(e,g)$ pairs that satisfy the constraint:
+										\item Optimal $g_M$: Expression~\ref{eq:g2} creates a menu of $(e,g)$ pairs that satisfy the constraint:
 											\[
@@
 										\item \color{red} For the parameterization in the paper, welfare is negative for $e=0$ and $e=0.01$, the only values of $e$ that lead to non-negative gifts; gifts range from 52.5 to 218.75	
+										\item \color{orange} Parameterization 2: welfare is 10.083 at optimal gift-efficiency $e=0.06$, $g = 116.67$, $eg = 7$
 									\end{itemize}
@@
 \subsubsection{To do and Notes}		
-	\color{ForestGreen} No notes to digitize right now
+	\color{ForestGreen} 
 			\begin{itemize}
-				\item Check parameter restrictions for existence of equilibria in Section 4.2
-					\begin{itemize}
-						\item Go back to 4 or 4.1; didn't find them in 4.2
-					\end{itemize}
 				\item Obviously we can come up with other parameterizations in which this may look a little more reasonable
@@
 						\item But I think the first step is to calculate the high-type utility under the different scenarios and the different gifts and see what happens (since you get the indirect benefit of the gift--or do you since $e$ is too small?)
+					\end{itemize}
+				\item When g1 turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g1$, not sure we'd need the mediator? It's not about $g1$, but the $\de_h^1$ condition.
+					\begin{itemize}
+						\item When g1 is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
 					\end{itemize}

### 2020-12-08 e-g calculations.R

@@ -6,20 +6,44 @@ p = .2
 dl = .3
 dh = .6
 
+#Let's find an alternate where W1 > W0
+T = 7
+W = 8
+D = 5
+p = .5
+dl = .25
+dh = .6
+# This works to make both the gift and welfare higher under e=1.
+# But welfare under mediator is never even positive (for non-negative gift)
+
+#Let's forget about where e=1 is possible; then mediator isn't as important
+#I think this works, but need to check it b/c "We" is weird!
+T = 7
+W = 8
+D = 5
+p = .9
+dl = .3
+dh = .6
+
 e = seq(0, 1, 0.01)
 g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
 condition = data.frame((p - e*(p + T - dl*T +W)))
 eg = e*g #effective gift
 
 # Welfare calculations 
+# 0 < e < 1 with mediator
+We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
 # e=0
 g0 = p*(T+D)
 W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
 W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
-# 0 < e < 1 with mediator
-We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
 
-g1denom = (1-dl)*(1-p*T)+(1-p)*D #checks to see if denominator is positive
-    
+#If g1 is negative, this is an UPPER BOUND
+d_h1 = D*(1-p)+1-p*T + (p*(W-(T+D)))/g1  #Minimum delta_h for separation
+
+
+
+
+

### 2020-12-08 notes.tex
add next steps to notes; save R script with updates

@@
 					\begin{itemize}
-						\item But I think the first step is to calculate the high-type utility under the different scenarios and the different gifts and see what happens (since you get the indirect benefit of the gift--or do you since $e$ is too small?)
+						\item Go through welfare expressions carefully to understand where the welfare improvement is coming from
+						\item Can I derive an analytical expression for when the mediator enhances welfare?
+							\begin{itemize}
+								\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE
+							\end{itemize}
 					\end{itemize}
@@
 						\item When g1 is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
+						\item I need a formal result to see clearly what is going on here
 					\end{itemize}

### 2020-12-08 e-g calculations.R

@@ -17,7 +17,7 @@ dh = .6
 # But welfare under mediator is never even positive (for non-negative gift)
 
 #Let's forget about where e=1 is possible; then mediator isn't as important
-#I think this works, but need to check it b/c "We" is weird!
+#This makes welfare highest under mediator
 T = 7
 W = 8
 D = 5

### 2020-12-11 e-g calculations.R
add sandbox for welfare comparisons, code for optimal mediator choice

@@ -40,10 +40,37 @@ W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
 W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
 
+We_max = We[min(which(g<=0)) - 1,1]
+g_max = g[min(which(g<=0)) - 1,1]
+ge_max = eg[min(which(g<=0)) - 1,1]
+
 #If g1 is negative, this is an UPPER BOUND
 d_h1 = D*(1-p)+1-p*T + (p*(W-(T+D)))/g1  #Minimum delta_h for separation
 
+#Explore parameters that make mediator better
+## Reducing dl from 0.3 to 0.4 makes the mediator even more attractive
+T = 7
+W = 8
+D = 5
+p = .9
+dl = .4
+dh = .6
 
+e = seq(0, 1, 0.01)
+g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
+condition = data.frame((p - e*(p + T - dl*T +W)))
+eg = e*g #effective gift
 
+# Welfare calculations 
+# 0 < e < 1 with mediator
+We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
+# e=0
+g0 = p*(T+D)
+W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
+# e=1
+g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
+W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
 
-
+We_max = We[min(which(g<=0)) - 1,1]
+g_max = g[min(which(g<=0)) - 1,1]
+ge_max = eg[min(which(g<=0)) - 1,1]

### 2020-12-11 notes.tex
add details on parameterized welfare comparisons (mediator vs e=0)

@@
 						\vskip.3in
-						Utility comparisons (always for high type)
+						Welfare comparisons (always for high type)
 							\begin{itemize}
@@
 										\item \color{orange} Parameterization 2: welfare is 10.083 at optimal gift-efficiency $e=0.06$, $g = 116.67$, $eg = 7$
+											\begin{itemize}
+												\item Compared to $e=0$, welfare (gross of gift) goes up from 16.5 to 126.75.
+The entire difference is due to the positive effect of the material value of the gift (the full term is $\frac{1}{1-\de_h}pTeg$).
+The effective gift is $7$, which is much larger than the 1 in $\frac{1}{1-\de_h}pT\cdot 1$ that is there in both terms.
+												\item The increase in the size (cost) of the gift from 10.8 to 116.67 is smaller than the increase in gross-of-gift welfare
+											\end{itemize}
 									\end{itemize}
@@
 					\begin{itemize}
-						\item Go through welfare expressions carefully to understand where the welfare improvement is coming from
 						\item Can I derive an analytical expression for when the mediator enhances welfare?

### 2020-12-11 notes.tex
reorganize calculations to easily compare parameterizations; reorganize to-do

@@
 
+\subsubsection{Welfare under Mediator vs. e=0}
+\label{sec:WM0}
+Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\
+
+When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
+$$\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
+
+When $e=0$, welfare is $$\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+
+We compare them to find when the welfare under the mediator is larger:
+	\begin{multline*}
+		\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+	\end{multline*}							
+Eliminating common terms:
+	\begin{equation*}
+		\frac{1}{1-d_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
+	\end{equation*}	
+Rearranging:
+	\begin{equation*}
+		\frac{pTeg_M}{1-d_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
+	\end{equation*}	
+Here we can clearly see the increase in welfare from the impact of the effective gift on the left has to be greater than the increase in the size of the gift.
+	\begin{itemize}
+		\item \color{blue} I'm not sure anything reasonable can come from this
+	\end{itemize}
+
 \subsubsection{To do and Notes}		
@@
 			\begin{itemize}
-				\item Obviously we can come up with other parameterizations in which this may look a little more reasonable
+					\item NEXT STEP: check condition for sustainable $e=1$ but prefer mediator with $e < 1$ (I've found parameterizations where $e=1$ is preferred so far, but I derived an expression in my notes for when mediator is better $$g^M(pTe - 1) \geq g^1(pT + pD - D - 1)$$
 						\begin{itemize}
-						\item Can I derive an analytical expression for when the mediator enhances welfare?
+							\item I'll probably need to type these notes up
+						\end{itemize}
+					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
 						\begin{itemize}
-								\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE
+							\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE.
+							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
 						\end{itemize}
-					\end{itemize}
-				\item When g1 turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g1$, not sure we'd need the mediator? It's not about $g1$, but the $\de_h^1$ condition.
+				\item When $g^1$ turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g^1$, not sure we'd need the mediator? It's not about $g^1$, but the $\de_h^1$ condition.
 					\begin{itemize}
-						\item When g1 is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
+						\item When $g^1$ is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
 						\item I need a formal result to see clearly what is going on here

### 2020-12-11 e-g calculations.R

@@ -6,71 +6,60 @@ p = .2
 dl = .3
 dh = .6
 
-#Let's find an alternate where W1 > W0
-T = 7
-W = 8
-D = 5
-p = .5
-dl = .25
-dh = .6
-# This works to make both the gift and welfare higher under e=1.
-# But welfare under mediator is never even positive (for non-negative gift)
-
-#Let's forget about where e=1 is possible; then mediator isn't as important
-#This makes welfare highest under mediator
+#P2 in notes: e=1 not possible (negative gift)
+#This makes welfare highest under mediator, 2nd under e=0, e=1 not possible
 T = 7
 W = 8
 D = 5
 p = .9
 dl = .3
 dh = .6
+## Note: reducing dl from 0.3 to 0.4 makes the mediator even more attractive
 
-e = seq(0, 1, 0.01)
-g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
-condition = data.frame((p - e*(p + T - dl*T +W)))
-eg = e*g #effective gift
 
-# Welfare calculations 
-# 0 < e < 1 with mediator
-We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
-# e=0
-g0 = p*(T+D)
-W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
-# e=1
-g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
-W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
-
-We_max = We[min(which(g<=0)) - 1,1]
-g_max = g[min(which(g<=0)) - 1,1]
-ge_max = eg[min(which(g<=0)) - 1,1]
-
-#If g1 is negative, this is an UPPER BOUND
-d_h1 = D*(1-p)+1-p*T + (p*(W-(T+D)))/g1  #Minimum delta_h for separation
-
-#Explore parameters that make mediator better
-## Reducing dl from 0.3 to 0.4 makes the mediator even more attractive
+#Here W1 > W0 and g1 > g0. Welfare under mediator is never positive. 
 T = 7
 W = 8
 D = 5
[…]

### 2020-12-14 notes.tex
fix max calculations in R script; add results from R to notes

@@
 \vskip.3in
-``Parameterization 2'': goal was to make welfare higher under mediator
+``Parameterization 2'': goal was to make welfare higher under mediator; $We > W0$ and $e=1$ is not incentive compatible
 \begin{itemize}
@@
 	\item The highest welfare comes from $e=.06$, which implies $g = 116.67$ (see e-g calculations.R)
+\end{itemize}
 
+\vskip.3in
+Here $W1 > W0$ and $g1 > g0$. Welfare under mediator is never positive. 
+\begin{itemize}
+	\item T = 7, W = 8, D = 5, p = .5, dl = .25, dh = .6
+\end{itemize}
+
+\vskip.3in
+Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses e=0 anyway
+\begin{itemize}
+	\item T = 7, W = 8, D = 5, p = .3, dl = .4, dh = .9
+\end{itemize}
+
+\vskip.3in
+Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses $e=0.03$
+\begin{itemize}
+	\item T = 6, W = 8, D = 5, p = .5, dl = .2, dh = .9
 \end{itemize}
@@
 										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
-										\item \color{orange} Parameterization 2: $g1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
+										\item \color{orange} Parameterization 2: $g^1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
 									\end{itemize}

### 2020-12-14 e-g calculations.R

@@ -43,6 +43,12 @@ dl = .2
 dh = .9
 
 ## To do: Find parameters that make e=1 possible, test against mediator
+T = 6
+W = 8
+D = 5
+p = .4
+dl = .5
+dh = .8
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
@@ -57,9 +63,12 @@ W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
 # 0 < e < 1 with mediator
 e = seq(0, 1, 0.01)
 g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
-condition = data.frame((p - e*(p + T - dl*T +W)))
-eg = e*g #effective gift
+#condition = data.frame((p - e*(p + T - dl*T +W)))
+#eg = e*g #effective gift
 We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
-We_max = We[min(which(g<=0)) - 1,1]
-g_max = g[min(which(g<=0)) - 1,1]
-ge_max = eg[min(which(g<=0)) - 1,1]
+We_max = max(We[which(g>=0),1])
+g_max = g[which.max(We[which(g>=0),1]),1]
+#eg_max = eg[which.max(We[which(g>=0),1]),1]
+
+# condition for mediator to be better than e = 1
+WM1 = g_max*(p*T*e[min(which(g<=0)) - 1] - 1) - g1*(p*T + p*D - D - 1)

### 2020-12-29 notes.tex
add calculations for We > W1, correct P5 in notes

@@
 
-\vskip.3in
-Here $W1 > W0$ and $g1 > g0$. Welfare under mediator is never positive. 
+\vskip.2in
+Parameterization 3: $W1 > W0$ and $g1 > g0$. Welfare under mediator is never positive. 
 \begin{itemize}
-	\item T = 7, W = 8, D = 5, p = .5, dl = .25, dh = .6
+	\item $T = 7, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .25, \ \de_h = .6$
 \end{itemize}
 
-\vskip.3in
-Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses e=0 anyway
+\vskip.2in
+Parameterization 4: $W0 > W1 > We$ (mediator). Mediator optimally chooses e=0 anyway
 \begin{itemize}
-	\item T = 7, W = 8, D = 5, p = .3, dl = .4, dh = .9
+	\item $T = 7, \ W = 8, \ D = 5, \ p = .3, \ \de_l = .4, \ \de_h = .9$
 \end{itemize}
 
-\vskip.3in
-Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses $e=0.03$
+\vskip.2in
+Parameterization 5: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$
 \begin{itemize}
-	\item T = 6, W = 8, D = 5, p = .5, dl = .2, dh = .9
+	\item $T = 6, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .2, \ \de_h = .9$
 \end{itemize}
@@
 							\begin{itemize}
-								\item When $e=1$: $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
+								\item When $e=1$: $\frac{1}{1-\de_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
 									\begin{itemize}
 										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
-										\item \color{orange} Parameterization 2: $g^1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
+										\item \color{orange} Parameterization 2: $g^1$ is negative, creates negative upper bound for $\de_h$. Separating with concessions equilibrium can't be sustained.
 									\end{itemize}
-								\item When $e=0$: $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
+								\item When $e=0$: $\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
 									\begin{itemize}
@@
 									\end{itemize}
-								\item When $0<e<1$ under a mediator: $\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
+								\item When $0<e<1$ under a mediator: $\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
 									\begin{itemize}
@@
 When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
-$$\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
+$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
 
-When $e=0$, welfare is $$\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
 
@@
 	\begin{multline*}
-		\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
-		\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
 	\end{multline*}							
@@
 	\begin{equation*}
-		\frac{1}{1-d_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
 	\end{equation*}	
@@
 	\begin{equation*}
-		\frac{pTeg_M}{1-d_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
+		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
 	\end{equation*}	
@@
 
+\subsubsection{Welfare under Mediator vs. e=1}
+\label{sec:WM1}
+Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=1$ separating with concessions equilibrium. \\
+
+When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
+$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
+
+When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\
+
+We compare them to find when the welfare under the mediator is larger:
+	\begin{multline*}
+		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
+	\end{multline*}
+
+Eliminating common terms:
+	\begin{multline*}
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
+	\end{multline*}			
+Rearranging:
+	\begin{equation*}
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - g_M \geq \frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - g^1
+	\end{equation*}
+
+\color{blue} I think it's possible that this condition can never be satisfied (i.e. if e=1 is IC, you'd never want to call in the mediator). But I haven't tried to prove it yet
+
 \subsubsection{To do and Notes}		
@@
 			\begin{itemize}
-					\item NEXT STEP: check condition for sustainable $e=1$ but prefer mediator with $e < 1$ (I've found parameterizations where $e=1$ is preferred so far, but I derived an expression in my notes for when mediator is better $$g^M(pTe - 1) \geq g^1(pT + pD - D - 1)$$
+					\item NEXT STEP: check condition for sustainable $e=1$ but prefer mediator with $e < 1$ 
 						\begin{itemize}
-							\item I'll probably need to type these notes up
+							\item I've found parameterizations where $e=1$ is preferred (P5)
+							\item Try to find a parameterization that shows the reverse (counterexample to my hypothesis that if $e=1$ is sustainable, you never invoke mediator) or see if I can prove that it never happens
 						\end{itemize}

### 2020-12-29 e-g calculations.R

@@ -17,7 +17,7 @@ dh = .6
 ## Note: reducing dl from 0.3 to 0.4 makes the mediator even more attractive
 
 
-#Here W1 > W0 and g1 > g0. Welfare under mediator is never positive. 
+#P3: W1 > W0 and g1 > g0. Welfare under mediator is never positive. 
 T = 7
 W = 8
 D = 5
@@ -26,7 +26,7 @@ dl = .25
 dh = .6
 
 
-## Here, W0 > W1 > We (mediator). Mediator optimally chooses e=0 anyway
+## P4: W0 > W1 > We (mediator). Mediator optimally chooses e=0 anyway
 T = 7
 W = 8
 D = 5
@@ -34,7 +34,7 @@ p = .3
 dl = .4
 dh = .9
 
-## Here, W0 > W1 > We (mediator). Mediator optimally chooses e=0.03
+## P5: Here, W1 > W0 > We (mediator). Mediator optimally chooses e=0.03
 T = 6
 W = 8
 D = 5
@@ -71,4 +71,5 @@ g_max = g[which.max(We[which(g>=0),1]),1]
 #eg_max = eg[which.max(We[which(g>=0),1]),1]
 
 # condition for mediator to be better than e = 1
-WM1 = g_max*(p*T*e[min(which(g<=0)) - 1] - 1) - g1*(p*T + p*D - D - 1)
+WM1 = 1/(1-dh)*g_max*p*T*e[min(which(g<=0))] - g_max - 1/(1-dh)*g1*(p*T + p*D - D) - g1
+test = We_max - W1

### 2021-01-01 e-g calculations.R
add parameterizations from Mathematica calculations and fix We_max to ignore non-finite entries

@@ -42,13 +42,21 @@ p = .5
 dl = .2
 dh = .9
 
-## To do: Find parameters that make e=1 possible, test against mediator
-T = 6
-W = 8
-D = 5
-p = .4
+## Parameters that make e=1 possible, but mediator still better
+T = .5
+W = 1
+D = 1
+p = .5
 dl = .5
-dh = .8
+dh = 61/64
+
+## Parameters that make mediator better than e=0 (have to check about e1)
+T = 1
+W = 1
+D = 1
+p = .5
+dl = .5
+dh = 15/16
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)

### 2021-01-01 e-g calculations.R
actually save changes to R file from previous step

@@ -74,7 +74,7 @@ g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
 #condition = data.frame((p - e*(p + T - dl*T +W)))
 #eg = e*g #effective gift
 We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
-We_max = max(We[which(g>=0),1])
+We_max = max(We[which(g[is.finite(g$X.1...dl.....T...D...p...e....p...T...dl...T...W..),1]>=0),1])
 g_max = g[which.max(We[which(g>=0),1]),1]
 #eg_max = eg[which.max(We[which(g>=0),1]),1]
 

### 2021-01-01 notes.tex
add Parameterization 6: mediator better than W1 or W0

@@
 
+\vskip.2in
+Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$. Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
+\begin{itemize}
+	\item $T = 1, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 15/16=0.9375$
+\end{itemize}
+
 						\vskip.3in
@@
 	\begin{equation*}
+		\frac{1}{1-\de_h}\left\{pTe - 1 \right\} \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
+	\end{equation*}
+
+Rearranging:
+\begin{equation*}
 		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
 	\end{equation*}	
-Here we can clearly see the increase in welfare from the impact of the effective gift on the left has to be greater than the increase in the size of the gift.
+This is what I implement in Mathematica Notebook ``We greater than W0.nb''
 \begin{itemize}
-		\item \color{blue} I'm not sure anything reasonable can come from this
+	\item So far, I've been able to find an instance that satisfies this equation: e = 11/64, $\de_h = 15/16$, $\de_l = 0.5$, $p = 0.5$, T = 1, W = 1, D = 1
+	\item This is ``Parameterization 6'' above and in R file ``e-g calculations.R''
 \end{itemize}

### 2021-01-01 e-g calculations.R

@@ -42,6 +42,14 @@ p = .5
 dl = .2
 dh = .9
 
+## P6: make mediator better than e=0: We > W1 > W0. All gifts are positive
+T = 1
+W = 1
+D = 1
+p = .5
+dl = .5
+dh = 15/16
+
 ## Parameters that make e=1 possible, but mediator still better
 T = .5
 W = 1
@@ -50,19 +58,12 @@ p = .5
 dl = .5
 dh = 61/64
 
-## Parameters that make mediator better than e=0 (have to check about e1)
-T = 1
-W = 1
-D = 1
-p = .5
-dl = .5
-dh = 15/16
-
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
 W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
 # e = 1 incentive compatible? Minimum dh for separation is
 dh_min = D*(1-p) + 1 - p*T + (p*(W - T -D))/g1 #If g1<0, this is UPPER BOUND
+rm(dh_min) #get rid of this after checking that it is lower than dh
 
 # e=0
 g0 = p*(T+D)
@@ -72,11 +73,11 @@ W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
 e = seq(0, 1, 0.01)
 g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
 #condition = data.frame((p - e*(p + T - dl*T +W)))
-#eg = e*g #effective gift
+eg = e*g #effective gift
 We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
 We_max = max(We[which(g[is.finite(g$X.1...dl.....T...D...p...e....p...T...dl...T...W..),1]>=0),1])
 g_max = g[which.max(We[which(g>=0),1]),1]
-#eg_max = eg[which.max(We[which(g>=0),1]),1]
+eg_max = eg[which.max(We[which(g>=0),1]),1]
 
 # condition for mediator to be better than e = 1
 WM1 = 1/(1-dh)*g_max*p*T*e[min(which(g<=0))] - g_max - 1/(1-dh)*g1*(p*T + p*D - D) - g1

### 2021-01-02 notes.tex
add constraints for g1 case

@@
 
-\color{blue} I think it's possible that this condition can never be satisfied (i.e. if e=1 is IC, you'd never want to call in the mediator). But I haven't tried to prove it yet
+I've used Mathematica to find a parameterization under which this is true.
+\begin{itemize}
+	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''.
+Here is the constraint on $\de_h$:
+		\[
+		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
+		\]
+\end{itemize}
 

### 2021-01-04 e-g calculations.R
print value of optimal e and use in other calculations in R

@@ -76,8 +76,9 @@ g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
 eg = e*g #effective gift
 We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - g
 We_max = max(We[which(g[is.finite(g$X.1...dl.....T...D...p...e....p...T...dl...T...W..),1]>=0),1])
-g_max = g[which.max(We[which(g>=0),1]),1]
-eg_max = eg[which.max(We[which(g>=0),1]),1]
+e_max = which.max(We[which(g>=0),1])
+g_max = g[e_max,1]
+eg_max = eg[e_max,1]
 
 # condition for mediator to be better than e = 1
 WM1 = 1/(1-dh)*g_max*p*T*e[min(which(g<=0))] - g_max - 1/(1-dh)*g1*(p*T + p*D - D) - g1

### 2021-01-10 notes.tex
complete WM > W1 calculations to match Mathematica
add welfare ordering table to parameterizations section
add list of weapon decommisioning agreements and other conflict to investigate

@@
 \vskip.3in
+
+\section{Alternative Examples}
+
+\subsection{Destroying weapons}
+I'm not sure this is perfect, since it's a bit of a stretch to say they could be used for civil society (police?)
+\begin{itemize}
+	\item FARC in 2017 (Colombia): https://colombiareports.com/final-un-figures-destruction-farcs-arsenal/,
+		\begin{itemize}
+			\item https://www.crisisgroup.org/latin-america-caribbean/andes/colombia/statement-transitional-justice-agreement-between-colombian-government-and-farc
+		\end{itemize}
+	\item Philippines / Bangsamoro region: https://www.crisisgroup.org/asia/south-east-asia/philippines/301-philippines-militancy-and-new-bangsamoro
+	\item Northern Ireland: Oct 7 2007 deadline to start weapons decommissioning (https://www.crisisgroup.org/crisiswatch/october-2007)
+	\item Yemen, https://www.crisisgroup.org/crisiswatch/print?page=1&location%255B%255D=28&date_range=custom&from_month=01&from_year=2020&to_month=04&to_year=2020&t=CrisisWatch+Database+Filter
+		\begin{itemize}
+			\item  As part of “Phase 2” agreement, govt and STC exchanged 53 prisoners 12 Jan.
+Rival Yemeni groups 24 Jan completed transfer of heavy weapons in Aden to Saudi-controlled base in city within fifteen-day timeframe.
+After early redeployments from Aden, process again stalled late Jan, with local appointments still not made.
+		\end{itemize}
+	\item Timor L'este, July 2007, https://www.crisisgroup.org/crisiswatch/july-2006
+		\begin{itemize}
+			\item Situation showed signs of improvement as former Foreign and Defence Minister Ramos-Horta sworn in as new PM 10 July, prompting more rebels to surrender weapons.
+New cabinet sworn in 14 July with PM retaining defence portfolio.
+TL asked UN Security Council for 800 international police for 2 to 5 years.
+UN Special Envoy told UNSC substantial long-term military and police presence required.
+Peacekeepers arrested 20 for illegal possession of weapons, including rebel leader Reinado.
+UN commission of inquiry set October deadline for its investigations into April-May violence.
+Former PM Alkatiri questioned over allegations he paid rebels to attack opponents.
+International police force gradually replacing military patrols in Dili as first Australian troops withdrew.
+Violent attacks by teenage gangs increased, including attack on UNICEF worker
+		\end{itemize}
+	\item Turkey and the PKK, Nov 6, 2014
+\end{itemize}
+
+Other conflicts to investigate
+\begin{itemize}	
+	\item Liberia
+	\item What happened to make peace in Sudan?
+	\item Taliban in Afghanistan? February 29, 2020
+		\begin{itemize}
+			\item No help from International Crisis Group
+		\end{itemize}
+	\item Iran deal with the U.S.: JCPOA
+	\item North and South Korea
+\end{itemize}
 
@@
 \[
-	pg\left(1 - e\right) \geq \left(T - \de T \right) \left(1 + eg\right) + Weg + \left(1 - \de \right) D
+	pg_M\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_M\right) + Weg_M + \left(1 - \de_l \right) D
 \]
@@
 			\begin{equation}
-				pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)
+				pg_M - pg_Me \geq \left(1 - \de_l \right) \left( T + D \right) + eg_M \left( T - \de_l T + W \right)
 				\label{eq:split}
@@
 					\begin{equation}
-						g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
+						g_M \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}
 						\label{eq:g2}
@@
 										\begin{equation}
-											g \geq \frac{p(1-\de)(T + D)}{\left(1-\de \right) -p(1-\de)T +(1-p)D}
+											g^1 \geq \frac{p(1-\de_l)(T + D)}{\left(1-\de_l \right) -p(1-\de_l)T +(1-p)D}
 											\label{eq:g4}
@@
 								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
+							\end{itemize}
+
+\subsubsection{Welfare under Mediator vs. e=0}
+\label{sec:WM0}
+Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\
+
+When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
+$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
+
+When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+
+We compare them to find when the welfare under the mediator is larger:
+	\begin{multline*}
+		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+	\end{multline*}							
+Eliminating common terms:
+	\begin{equation*}
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
+	\end{equation*}	
+Rearranging:
+	\begin{equation*}
+		\frac{1}{1-\de_h}\left\{pTe - 1 \right\} \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
+	\end{equation*}
+
+Rearranging:
+\begin{equation*}
+		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
+	\end{equation*}	
+This is what I implement in Mathematica Notebook ``We greater than W0.nb''
+\begin{itemize}
+	\item So far, I've been able to find an instance that satisfies this equation: e = 11/64, $\de_h = 15/16$, $\de_l = 0.5$, $p = 0.5$, T = 1, W = 1, D = 1
+	\item This is ``Parameterization 6'' above and in R file ``e-g calculations.R''
+\end{itemize}
+
+\subsubsection{Welfare under Mediator vs. e=1}
+\label{sec:WM1}
+Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=1$ separating with concessions equilibrium. \\
+
+When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
+$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
+
+When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\
+
+We compare them to find when the welfare under the mediator is larger:
+	\begin{multline*}
+		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
+	\end{multline*}
+
+Eliminating common terms:
+	\begin{multline*}
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
+		\frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
+	\end{multline*}			
+Rearranging:
+	\begin{equation*}
+		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - g_M \geq \frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - g^1
+	\end{equation*}		
+Rearranging again:
+	\begin{equation*}
+		pTeg_M - \left(1-\de_h\right)g_M \geq pTg^1 + (1-p)(- Dg^1)) - \left(1-\de_h\right)g^1
+	\end{equation*}	
+	\begin{equation*}
+		g_M\left[pTe - \left(1-\de_h\right)\right] \geq pTg^1 -Dg^1 + pDg^1 - \left(1-\de_h\right)g^1
+	\end{equation*}
+	\begin{equation*}
+		g_M\left[pTe - \left(1-\de_h\right)\right] \geq g^1\left[pT - D + pD - \left(1-\de_h\right)\right]
+	\end{equation*}	
+Substituting in the minimum gifts from Expression~\ref{eq:g2} and \ref{eq:g4}:				
+	\begin{equation*}
+		\frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \left[pTe - \left(1-\de_h\right)\right] \geq \frac{p(1-\de_l)(T + D)}{\left(1-\de_l \right)(1-pT) +(1-p)D} \left[pT - D + pD - \left(1-\de_h\right)\right]
+	\end{equation*}	
+Simplifying again because of common term in the numerators:
+	\begin{equation*}
+		\frac{1}{p - e \left( p + T - \de_l T + W \right)} \left[pTe - \left(1-\de_h\right)\right] \geq \frac{p}{\left(1-\de_l \right)(1-pT) +(1-p)D} \left[pT - D + pD - \left(1-\de_h\right)\right]
+	\end{equation*}	
+		\begin{equation*}
+		\left[\left(1-\de_l \right)(1-pT) +(1-p)D\right] \left[pTe - \left(1-\de_h\right)\right] \geq \left[p - e \left( p + T - \de_l T + W \right)\right]p \left[pT - D + pD - \left(1-\de_h\right)\right]
+	\end{equation*}
+
+I've used Mathematica to find a parameterization under which this is true.
+\begin{itemize}
+	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''.
+Here is the constraint on $\de_h$:
+		\[
+		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
+		\]
 \end{itemize}
@@
 							\begin{itemize}
-								\item When $e=1$: $\frac{1}{1-\de_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
+								\item When $e=1$ (``W1''): $\frac{1}{1-\de_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
 									\begin{itemize}
@@
 									\end{itemize}
-								\item When $e=0$: $\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
+								\item When $e=0$ (``W0''): $\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
 									\begin{itemize}
@@
 									\end{itemize}
-								\item When $0<e<1$ under a mediator: $\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
+								\item When $0<e<1$ under a mediator (``WM''): $\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
 									\begin{itemize}
@@
 
-\subsubsection{Welfare under Mediator vs. e=0}
-\label{sec:WM0}
-Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\
-
-When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
-$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
-
-When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
-
-We compare them to find when the welfare under the mediator is larger:
-	\begin{multline*}
-		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
-		\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
-	\end{multline*}							
-Eliminating common terms:
-	\begin{equation*}
-		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
-	\end{equation*}	
-Rearranging:
-	\begin{equation*}
-		\frac{1}{1-\de_h}\left\{pTe - 1 \right\} \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
-	\end{equation*}
-
-Rearranging:
-\begin{equation*}
-		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
-	\end{equation*}	
-This is what I implement in Mathematica Notebook ``We greater than W0.nb''
+			\vskip.2in
+			There are six cases of welfare ordering: \\
+			\vskip.1in
+				\begin{tabular}{ l c c }
+					\un{Ordering}       & \un{$WM < 0$} & \un{$WM > 0$} \\
+					$WM > W1 > W0$ &  & P6 \\
+					$WM > W0 > W1$ &  & P2 (W1 not IC) \\
+					$W1 > WM > W0$ &  &  \\
+					$W1 > W0 > WM$ & P3 & P5 \\
+					$W0 > W1 > WM$ & P1 (paper) & P4 \\
+					$W0 > WM > W1$ &    &
+				\end{tabular}
+				P5 result is wrong: $WM \Rightarrow \infty$.
 					\begin{itemize}
-	\item So far, I've been able to find an instance that satisfies this equation: e = 11/64, $\de_h = 15/16$, $\de_l = 0.5$, $p = 0.5$, T = 1, W = 1, D = 1
-	\item This is ``Parameterization 6'' above and in R file ``e-g calculations.R''
-\end{itemize}
-
-\subsubsection{Welfare under Mediator vs. e=1}
-\label{sec:WM1}
-Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=1$ separating with concessions equilibrium. \\
-
-When $0<e<1$ under a mediator, the optimal $g_M$ is the one that chooses the highest welfare from a menu of $(e,g)$ pairs:
-$$\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)}$$
-
-When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\
-
-We compare them to find when the welfare under the mediator is larger:
-	\begin{multline*}
-		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
-		\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
-	\end{multline*}
-
-Eliminating common terms:
-	\begin{multline*}
-		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
-		\frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - \frac{p(1-d_l)(T+D)}{(1-d_l)(1-pT)+(1-p)D}
-	\end{multline*}			
-Rearranging:
-	\begin{equation*}
-		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - g_M \geq \frac{1}{1-\de_h}\left\{pTg^1 + (1-p)(- Dg^1))\right\} - g^1
-	\end{equation*}
-
-I've used Mathematica to find a parameterization under which this is true.
-\begin{itemize}
-	\item I implemented the constraint in Mathematica to make sure the gift under $e=1$ is positive, BUT I did not implement the constraint on $\de_h$ that makes it IC (although I have a check in ``e-g calculations.R''.
-Here is the constraint on $\de_h$:
-		\[
-		  \de_h \geq D + 1 - p(T+D) + \frac{p(W-(T+D))}{g^1}
-		\]
+						\item It's going to be very hard to find WM as intermediate. It has to be a case where it asymptotes to $-\infty$ and choosing $e=0$ is optimal anyway.
+						\item It would be nice to show that it's possible to want to pick $e=0$ under mediator 
 					\end{itemize}

### 2021-01-10 notes.tex
clean up notes on weapons decommissioning

@@
 \subsection{Destroying weapons}
-I'm not sure this is perfect, since it's a bit of a stretch to say they could be used for civil society (police?)
+I'm not sure this is perfect: it's a bit of a stretch to say the weapons could be given to the negotiating partner who could use them to build up civil society, but I guess if they're given to non-militarized police to enforce law and order...
 \begin{itemize}
-	\item FARC in 2017 (Colombia): https://colombiareports.com/final-un-figures-destruction-farcs-arsenal/,
+	\item FARC in 2017 (Colombia)
 		\begin{itemize}
 			\item https://www.crisisgroup.org/latin-america-caribbean/andes/colombia/statement-transitional-justice-agreement-between-colombian-government-and-farc
+			\item https://news.un.org/en/story/2017/06/560442-colombia-un-mission-collects-nearly-all-remaining-weapons-farc-ep
+			\item https://unmc.unmissions.org/en/un-mission-finalises-extraction-arms-caches-and-laying-down-weapons-farc-ep
+		\end{itemize}
+	\item Northern Ireland
+		\begin{itemize}
+			\item Report of the Independent International Commission on Decomissioning: https://cain.ulster.ac.uk/events/peace/decommission/iicd260905.pdf
+			\item Note two years later: https://www.crisisgroup.org/crisiswatch/october-2007
+			\item Summary: https://cain.ulster.ac.uk/events/peace/decommission.htm
 		\end{itemize}
 		\item Philippines / Bangsamoro region: https://www.crisisgroup.org/asia/south-east-asia/philippines/301-philippines-militancy-and-new-bangsamoro
-	\item Northern Ireland: Oct 7 2007 deadline to start weapons decommissioning (https://www.crisisgroup.org/crisiswatch/october-2007)
-	\item Yemen, https://www.crisisgroup.org/crisiswatch/print?page=1&location%255B%255D=28&date_range=custom&from_month=01&from_year=2020&to_month=04&to_year=2020&t=CrisisWatch+Database+Filter
+	\item Yemen, \url{https://www.crisisgroup.org/crisiswatch/print?page=1&location%255B%255D=28&date_range=custom&from_month=01&from_year=2020&to_month=04&to_year=2020&t=CrisisWatch+Database+Filter}
 		\begin{itemize}
-			\item  As part of “Phase 2” agreement, govt and STC exchanged 53 prisoners 12 Jan.
-Rival Yemeni groups 24 Jan completed transfer of heavy weapons in Aden to Saudi-controlled base in city within fifteen-day timeframe.
+			\item https://www.arabnews.com/node/1292091/middle-east
+			\item As part of “Phase 2” agreement...Rival Yemeni groups 24 Jan completed transfer of heavy weapons in Aden to Saudi-controlled base in city within fifteen-day timeframe.
 After early redeployments from Aden, process again stalled late Jan, with local appointments still not made.
 		\end{itemize}
-	\item Timor L'este, July 2007, https://www.crisisgroup.org/crisiswatch/july-2006
-		\begin{itemize}
-			\item Situation showed signs of improvement as former Foreign and Defence Minister Ramos-Horta sworn in as new PM 10 July, prompting more rebels to surrender weapons.
-New cabinet sworn in 14 July with PM retaining defence portfolio.
-TL asked UN Security Council for 800 international police for 2 to 5 years.
-UN Special Envoy told UNSC substantial long-term military and police presence required.
-Peacekeepers arrested 20 for illegal possession of weapons, including rebel leader Reinado.
-UN commission of inquiry set October deadline for its investigations into April-May violence.
-Former PM Alkatiri questioned over allegations he paid rebels to attack opponents.
-International police force gradually replacing military patrols in Dili as first Australian troops withdrew.
-Violent attacks by teenage gangs increased, including attack on UNICEF worker
-		\end{itemize}
-	\item Turkey and the PKK, Nov 6, 2014
 \end{itemize}
 
-Other conflicts to investigate
+\subsection{Other conflicts to investigate}
 \begin{itemize}	

### 2021-01-12 notes.tex
add notes on other examples of inefficient concessions

@@
 \begin{itemize}
+	\item On disarmament in general: https://cain.ulster.ac.uk/events/peace/docs/disarmament.htm
 	\item FARC in 2017 (Colombia)
@@
 		\end{itemize}
+	\item Liberia: https://peaceaccords.nd.edu/accord/accra-peace-agreement, https://www.un.org/press/en/1999/19990726.SGSM7078.html
 \end{itemize}
 
-\subsection{Other conflicts to investigate}
+\subsection{Other conflicts}
+I investigated these for different types of inefficiencies but did not find anything useful
 \begin{itemize}	
-	\item Liberia
+	\item North and South Korea
 	\item What happened to make peace in Sudan?
+	\item Liberia--don't see anything in the Accra accords
 	\item Taliban in Afghanistan? February 29, 2020
@@
 			\item No help from International Crisis Group
+			\item Read agreement on state.gov; it's only four pages long, not much too it
 		\end{itemize}
 	\item Iran deal with the U.S.: JCPOA
-	\item North and South Korea
 \end{itemize}

### 2021-01-12 notes.tex
update to-do section

@@
 			\begin{itemize}
-					\item NEXT STEP: check condition for sustainable $e=1$ but prefer mediator with $e < 1$ 
-						\begin{itemize}
-							\item I've found parameterizations where $e=1$ is preferred (P5)
-							\item Try to find a parameterization that shows the reverse (counterexample to my hypothesis that if $e=1$ is sustainable, you never invoke mediator) or see if I can prove that it never happens
-						\end{itemize}
 					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}

### 2021-01-12 draft.tex
add IC constraints to mediation section. Realize they don't hold.
Copy edit Section 2, with eye for clarity of model

@@
 } are of two possible types, high and low.
-A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$.
-$\delta_h >\delta_l$ and both $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
-The type distinction, as explained later in the model, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict.
-It should not be thought of as an inherent quality of a country, but rather an interactive parameter.
-Thus it is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
+A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
+The type distinction, as explained in detail later, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict.
+It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
 
- The probability of nature selecting the high type for a given player is $p$.
+ The probability of nature selecting the high type for a given country is $p$.
 The probability of nature selecting the low type is $1-p$.\footnote{Note that parameters are symmetric across countries, as is consistent with the literature.
@@
 
-In period 0, countries 1 and 2 simultaneously give costly concessions $g_1$ and $g_2$ $\in \mathbb{R} \geq 0$.
-Concessions are given at cost $C(g_i)$ and benefit the recipient in the amount $g_i$, where $i\in\left\{1,2\right\}$.
-For simplicity, we assume $C(g_i)= g_i$.
+In period 0, countries 1 and 2 simultaneously give costly concessions $g_i$ $\in \mathbb{R} \geq 0$, where $i\in\left\{1,2\right\}$.
+Concessions are given at cost $C(g_i)$ and are valued by the recipient in the amount $g_i$.
+For simplicity, we assume throughout that the cost of giving the gift is equal to the value to the recipient, that is $C(g_i)= g_i$.
 
-Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs represented below.
-While not a good representation of all-out war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict, not a zero-sum short term war.
+Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.
+While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 
-The county's stage game actions will be referred to as ``Trust'' and ``Fight'':
+The countries' stage game actions will be referred to as ``Trust'' and ``Fight'' as represented in Table 1, where Country 1 is the row player and Country 2 is the column player.
 
@@
   \hline      & Trust & Fight \\ \hline
-	 Trust& T, T& -D, T+W \\ \hline
-	Fight & T+W,-D& W-D, W-D \\ \hline
+	 Trust& $T$, $T$& $-D$, $T+W$ \\ \hline
+	Fight & $T+W$, $-D$& $W-D$, $W-D$ \\ \hline
 \end{tabular}
@@
 
-$T\geq0$: Benefit from the other country playing Trust
+Here $T\geq0$ represents the benefit from the other country playing Trust.
+$D\geq0$ represents the damages incurred when the other country plays Fight, while $W\geq0$ is the additional benefit a country receives when it plays Fight itself.
+We assume $T>W-D$ in line with the assumption that the countries play a Prisoner's Dilemma in the stage game.
 
-$W\geq0$: Additional benefit from playing Fight
-
-$D\geq0$: Damages due to the other country playing Fight
-
-Assume $T>W-D$. 
- Payoffs for a country are the sum the stage game payoffs, discounted by $\delta.$ For example, if both parties play ``Trust'' in every period, the payoff for a player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$ Parameters are common knowledge with the exception of $\delta_i$, which is country i's private information.
+Payoffs for a country are the sum the stage game payoffs, discounted by $\delta_i$.
+For example, if both parties play ``Trust'' in every period, the payoff for a player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$ Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
 %Countries' utility is calculated as ex interim utility (Holmstrom and Myerson 1983),  i.e.
@@
 Depending on parameters, multiple equilibria are often possible.
-The measure of social welfare, and thus the determinant of the optimal equilibrium, will be the sum of participating high types' expected utilities.
+We will take the measure of social welfare, and thus the determinant of the optimal equilibrium, to be the sum of participating high types' expected utilities.
 
- If $\delta$ is high enough for both countries, the cooperative outcome of ``Peace'' (Trust, Trust) can be sustained with a grim trigger punishment threat.
-The assumption $T>W-D$ ensures that payoffs from Peace are higher than for ``War'' (Fight, Fight).
-For a Peace equilibrium to exist, $\delta$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
-The threshold $\delta^*$ needed is \be
- \delta^* = \frac{W}{T+D}
+The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles.
+If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
+
+For a Peace equilibrium to exist, $\delta_i$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
+The threshold $\delta_i^*$ needed is \be
+ \delta_i^* = \frac{W}{T+D}
  \ee
-Assume $\delta_h> \delta^*$ and $\delta_l < \delta^*$.
+We differentiate the high and low types by assuming $\delta_h> \delta_i^*$ and $\delta_l < \delta_i^*$.
+This implies that, with perfect information about the $\delta_i$'s, two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
 
@@
 Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value: both individual rationality and incentive compatibility constraints must be satisfied, leading to truthful self-identification.
+
+low type IC
+$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
+
+high type IC:
+$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
 

### 2021-01-13 draft.tex
copy edit first part of Section 4

@@
 Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.
-Let $X_{ij}$ represent the sum of discounted payoffs for country i where subscripts represent first round strategies of that country.
-If both countries play T in round 1, the corresponding payoff to country i is represented as $ X_{TT}=\frac {T}{1- \delta_i}$.
+Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
+If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}=\frac {T}{1- \delta_i}$.
 Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
@@
 The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society.
-The former hurts the giver of the concessions in war; the latter helps the giver in peace.
+Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil socity helps the giver in peace.
 The Golan heights is such an example: if Syria is an ally of Israel, the Golan Heights is a reasonable concession to make, but if Syria later turns out to betray a trust, surrender of the strategic land would be disastrous for Israel.
@@
 
-Allow $T,W$ and $D$ to be functions that depend on arguments $s_i$, the size of country i's civil society and $m_i$, the size of country i's military. $s_i$ and $m_i$ are exogenous.
+We incorporate future material value into the model by allowing $T,W$ and $D$ to be functions that depend on arguments $s_i$, the size of country $i$'s civil society and $m_i$, the size of country $i$'s military.
+$s_i$ and $m_i$ are assumed to be exogenous.
 
-In period 0, after receiving his concession, a country makes the decision to allocate it between military and civil society.
-$\alpha_i$ is the portion of his received concession that country i chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country i dedicates to military buildup.
+In period 0, after receiving its concession, a country makes the decision to allocate the value of the concession between military and civil society.
+$\alpha_i$ is the portion of the received concession that country $i$ chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country $i$ dedicates to military buildup.
 This decision is a simple optimization problem for each country.

### 2021-01-13 draft.tex
Remove generality of s_i, m_i since we never use it

@@
 
-We incorporate future material value into the model by allowing $T,W$ and $D$ to be functions that depend on arguments $s_i$, the size of country $i$'s civil society and $m_i$, the size of country $i$'s military.
-$s_i$ and $m_i$ are assumed to be exogenous.
-
-In period 0, after receiving its concession, a country makes the decision to allocate the value of the concession between military and civil society.
+We add two elements to the benchmark model in Section 2 in order to incorporate future material value.
+The first is an additional decision for the negotiating parties.
+In Period 0, after receiving a concession each country makes a decision about how to allocate the value of the concession between military and civil society.
 $\alpha_i$ is the portion of the received concession that country $i$ chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country $i$ dedicates to military buildup.
@@
 
+The second new element is a change to the payoffs.
+We add a term to each of $T$, $W$, and $D$ that represents the additional benefit or harm flowing from the future material value of the concession.
+When both countries play trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion that was invested in civil socity as well as the base benefit of $T$.
+
+If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
+However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the give it \textit{gave} and how much of that was invested in the miliary by Country 2.
+The (Fight,Trust) and (Trust,Fight) payoffs are modified in the same way.
+
 \begin{center}
@@
   \hline      & Trust & Fight \\ \hline
-	 Trust& \small$T(s_2+\alpha_2 g_1)$, & \small$-D(m_2+(1-\alpha_2) g_1),$ \\
-  & \small$T(s_1+\alpha_1 g_2)$ & \small$T(s_1+\alpha_1 g_2)  +W(m_2+(1-\alpha_2) g_1) $\\ \hline
-	Fight & \small$T(s_2+\alpha_2 g_1)+W(m_1+(1-\alpha_1) g_2),$& \small$W(m_1+(1-\alpha_1) g_2)-D(m_2+(1-\alpha_2) g_1),$ \\
-	 & \small$-D(m_1+(1-\alpha_1) g_2) $ & \small$W(m_2+(1-\alpha_2) g_1)-D(m_1+(1-\alpha_1) g_2)$ \\ \hline
+	 Trust& \small$T+T\alpha_2 g_1$, & \small$-[D+D(1-\alpha_2) g_1],$ \\
+  & \small$T+T\alpha_1 g_2$ & \small$[T+T\alpha_1 g_2] + [W+W(1-\alpha_2) g_1] $\\ \hline
+	Fight & \small$[T+T\alpha_2 g_1]+[W+W(1-\alpha_1) g_2],$& \small$[W+W(1-\alpha_1) g_2]-[D+D(1-\alpha_2) g_1],$ \\
+	 & \small$-[D+D(1-\alpha_1) g_2] $ & \small$[W+W(1-\alpha_2) g_1]-[D+D(1-\alpha_1) g_2]$ \\ \hline
 \end{tabular}
@@
   \hline      & Trust & Fight \\ \hline
-	 Trust& \small$T(s_2+\alpha_2 e g_1)$, & \small$-D(m_2+(1-\alpha_2)e g_1),$ \\
-  & \small$T(s_1+\alpha_1 e g_2)$ & \small$T(s_1+\alpha_1 e g_2)  +W(m_2+(1-\alpha_2)e g_1) $\\ \hline
-	Fight & \small$T(s_2+\alpha_2 e g_1)+W(m_1+(1-\alpha_1) e g_2),$& \small$W(m_1+(1-\alpha_1)e g_2)-D(m_2+(1-\alpha_2)e g_1),$ \\
-	 & \small$-D(m_1+(1-\alpha_1) e g_2) $ & \small$W(m_2+(1-\alpha_2)e g_1)-D(m_1+(1-\alpha_1)e g_2)$ \\ \hline
+	 Trust& \small$T+T\alpha_2 e g_1$, & \small$-[D+D(1-\alpha_2) eg_1],$ \\
+  & \small$T+T\alpha_1 eg_2$ & \small$[T+T\alpha_1 eg_2] + [W+W(1-\alpha_2) eg_1] $\\ \hline
+	Fight & \small$[T+T\alpha_2 eg_1]+[W+W(1-\alpha_1) eg_2],$& \small$[W+W(1-\alpha_1) eg_2]-[D+D(1-\alpha_2) eg_1],$ \\
+	 & \small$-[D+D(1-\alpha_1) eg_2] $ & \small$[W+W(1-\alpha_2) eg_1]-[D+D(1-\alpha_1) eg_2]$ \\ \hline
 \end{tabular}
@@
 This linear functional form implies that equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
-To further simplify calculations, we also assume that $s_1=s_2=m_1=m_2=1.$
 
@@
 \emph{Proof of Theorem \ref{theorem:4}:}\\
-Given the functional form restrictions that $T(\cdot),W(\cdot)$ and $D(\cdot)$ are each a scalar multiplied by its arguments and $s_1=s_2=m_1=m_2=1$, high types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$.
+High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$.
 Because the low type's IC constraint binds, with $e=1$ the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.

### 2021-01-13 draft.tex
clarify mediator set up (R1)

@@
 \newcommand{\ei}{\end{itemize*}}
-\newcommand{\bgd}{\begin{gathered}}
-\newcommand{\egd}{\end{gathered}}
-\newcommand{\bgr}{\begin{gather}}
-\newcommand{\edgr}{\end{gather}}
 \newcommand{\mb}{\mathbf}
@@
 \date{\today}
-%To Do : define what is ineffieicncy
 
@@
 If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the give it \textit{gave} and how much of that was invested in the miliary by Country 2.
-The (Fight,Trust) and (Trust,Fight) payoffs are modified in the same way.
+However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the miliary by Country 2.
+The (Fight,Trust) and (Trust,Fight) payoffs are modified analogously.
 
@@
 \label{sec:med}
-All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator which will be modeled as a mechanism.
+All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator.
 
@@
 
-The model setup is as before, but instead of parties being free to give whatever concession they want, the mediator solicits type reports and then enforces incentive compatible concessions.
+The model setup is as before, but instead of parties being free to choose their concession levels, the mediator solicits type reports and then enforces incentive compatible concessions.
 The Revelation Principle tells us that it is without loss of generality to restrict attention to direct mechanisms, that is, mechanisms in which countries simply declare their types (Myerson 1979).
@@
 
-$M$ inputs the reports of types $t_1$ and $t_2$ and outputs the required concessions $g_1$ and $g_2$ so that $ M:(t_1,t_2)\rightarrow( g_1(\cdot), g_2(\cdot))$.
+After learning their type, each country chooses to participate in the mechanism or not; that is, whether to send a message that declares its type to be High or Low.
+By the revelation principle, it is again without loss of generality to consider equilibria in which both countries participate and send truthful reports.
+Therefore we have a mechanism $M$ that inputs the reports $t_i \in \left\{High,Low\right\}$ for $i \in \left\{1,2\right\}$ and outputs the required concessions $g_i$ and efficiency levels $e_i$ so that $ M:(t_1,t_2)\rightarrow( e_1, g_1; e_2,g_2)$.
 The countries are bound to send the mandated concessions.
+
 In Sections~\ref{sec:bench} and \ref{sec:IC}, the same concession must be sent to both types since types are private information.
-$M$ can differentiate based on recipient's type.
-Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value: both individual rationality and incentive compatibility constraints must be satisfied, leading to truthful self-identification.
+Importantly, here the mechanism $M$ can differentiate based on recipient's type.
+Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value.
+
+[both individual rationality and incentive compatibility constraints must be satisfied, leading to truthful self-identification. ]
+
+[Further, it can be shown that restricting attention to symmetric recommendations is without loss of generality, because the optimal arbitration programme is linear.]
 

### 2021-01-13 notes.tex
wrestle with optimal e under mediator in notes

@@
 						\end{itemize}
-				To get a sense of the magnitudes, I will plug $g = p \left(T+D\right)$ from the $e=0$ CSE case (just because it's easier to work with than the optimal gift when $e=1$ into Expression~\ref{eq:g5}.
-First I divide through by $g$ {\color{blue}(this is okay if $g$ is assumed to be positive)}
-						\begin{equation}
-							p - \frac{\left(1 - \de \right) \left( T + D \right)}{g} \geq e \left( p + T - \de T + W \right)
-							\label{eq:g6}
-						\end{equation}
-						$$p - \frac{\left(1 - \de \right) \left( T + D \right)}{p \left(T+D\right)} \geq e \left( p + T - \de T + W \right)$$
-						$$p - \frac{1 - \de}{p } \geq e \left( p + T - \de T + W \right)$$
+
+I did a lot of work in Mathematica to try to find out when the welfare under the mediator is better than the welfare under either the $e=0$ or $e=1$ concessions separating equilibria (CSE) [see Sections~\ref{sec:WM0} and \ref{sec:WM1}]
 \begin{itemize}
-								\item For the LHS to be positive, we need $p^2 \geq 1 - \de$, e.g. if $p = 0.5$, we need $\de \geq .75$
+	\item In the midst of this, I realized that, at the optimal $e$ (probably the largest one that satisfies the equation immediately above), both the gift and welfare $\rightarrow \infty$
+		\begin{itemize}
+			\item So we don't get a finite size of the gift or welfare value at the optimum
+			\item In practice, there will be some upper bound on the size of the gift (even, say, total national wealth)
+		\end{itemize}
 \end{itemize}
@@
 										\item Minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
-										\item Minimum $e$ from Expression~\ref{eq:g6}:
+										\item Maximum $e$ from Expression~\ref{eq:g5}:
 											\[
@@
 									\begin{itemize}
-										\item Minimum $e$ from Expression~\ref{eq:g6}:
+										\item Maximum $e$ from Expression~\ref{eq:g5}:
 											\[
@@
 	\item \color{orange} T = 7, W = 8, D = 5, p = .9, $\de_l = .3$, $\de_h = .6$
-	\item Minimum $e$ from Expression~\ref{eq:g6}
+	\item Maximum $e$ from Expression~\ref{eq:g5}
 	  $$0.9 - \frac{\left(1 - 0.3 \right) \left( 7 + 5 \right)}{g} \geq e \left( 0.9 + 7 - 0.3 \cdot 7 + 8 \right)$$
@@
 							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
+							\item \textbf{Find the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote}
+								\begin{itemize}
+									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)
+								\end{itemize}
 						\end{itemize}

### 2021-01-15 e-g calculations.R
add min dh for e=0, defn of high type, fix parameterizations that violated high type defn

@@ -13,20 +13,20 @@ W = 8
 D = 5
 p = .9
 dl = .3
-dh = .6
+dh = .7
 ## Note: reducing dl from 0.3 to 0.4 makes the mediator even more attractive
 
 
-#P3: W1 > W0 and g1 > g0. Welfare under mediator is never positive. 
+#P3: W1 > W0 and g1 > g0. Welfare under mediator is never positive (asymptotes to -infty) 
 T = 7
 W = 8
 D = 5
 p = .5
 dl = .25
-dh = .6
+dh = .7
 
 
-## P4: W0 > W1 > We (mediator). Mediator optimally chooses e=0 anyway
+## P4: W0 > W1 > We (mediator). Mediator optimally chooses e=0 anyway (asymptotes to -infty)
 T = 7
 W = 8
 D = 5
@@ -50,13 +50,16 @@ p = .5
 dl = .5
 dh = 15/16
 
-## Parameters that make e=1 possible, but mediator still better
+## P7: Parameters that make e=1 possible, but mediator still better
 T = .5
 W = 1
 D = 1
 p = .5
 dl = .5
 dh = 61/64
+
+# cutoff for definition of high type
+di = W/(T+D)
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
@@ -68,6 +71,8 @@ rm(dh_min) #get rid of this after checking that it is lower than dh
 # e=0
 g0 = p*(T+D)
 W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
+dh_min0 = 1 - p*T + (p*(W - T -D))/g0 #If g1<0, this is UPPER BOUND
+rm(dh_min0)
 
 # 0 < e < 1 with mediator
 e = seq(0, 1, 0.01)

### 2021-01-16 e-g calculations.R
add sufficient condition for positive WM at asymptote to calculations

@@ -60,6 +60,11 @@ dh = 61/64
 
 # cutoff for definition of high type
 di = W/(T+D)
+# WM asymptotes to +infty when the following is positive (sufficient condition)
+suff = e*p*T - 1 + dh
+# problem is that we need the asymptote for e (I think)
+e_s = p/(p + T - T*dl +W)
+suff = e_s*p*T - 1 + dh
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)

### 2021-01-16 notes.tex
Add results on e-asymptote

@@
 			\item In practice, there will be some upper bound on the size of the gift (even, say, total national wealth)
+				\begin{itemize}
+					\item Interestingly, $g*e$ (the effective gift) appears to be a line for a given set of parameters $W,T,D,\de_h,\de_l,p$
+				\end{itemize}
 		\end{itemize}
@@
 								\begin{itemize}
-									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)
+									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)?
+										\begin{itemize}
+											\item No, it's not possible. Asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
+											\item I still don't have intuition for the asymptote. Need to look back at IC constraint to get it.
 										\end{itemize}
 								\end{itemize}
-				\item When $g^1$ turns negative, is that exactly when $e=1$ can't be sustained? If we can get positive $g^1$, not sure we'd need the mediator? It's not about $g^1$, but the $\de_h^1$ condition.
+						\end{itemize}
+					\item Ideally would want to combine $WM > W0$ and $WM > W1$ to get WM = max$\left\{WM, W1,W0\right\}$
 						\begin{itemize}
-						\item When $g^1$ is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
-						\item I need a formal result to see clearly what is going on here
+							\item I basically CAN do this with asymptote conditions...or at least try
+						\end{itemize}
+					\item Maybe I can just do comparative statics on the condition? \url{http://people.duke.edu/~dgraham/scripts/MathematicaLaTeX-to-LaTeX/ComparativeStatics-none.pdf}
+					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
+						\[
+						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
+						\]
+						\[
+						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
+						\]
+						\[
+						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
+						\]
+						\[
+						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
+						\]
+						\[
+						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
+						\]
+						\[
+							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
+						\]
+						\[
+							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
+						\]
+						I have a page of math that shows that this is strictly smaller than $d^h$.
+This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.
+							\begin{itemize}
+								\item This is nice, but I'm not sure it helps with the narrative of the story.
 							\end{itemize}
@@
 \begin{itemize}
-	\item I think Mediator could instruct them to give $e<1$ gifts without having to disturb the rest of the theory. 
+	\item I'm ignoring the following question for the JCR submission: When $g^1$ turns negative, is that exactly when $e=1$ can't be sustained? It's not about $g^1$, but the $\de_h^1$ condition.
 		\begin{itemize}
-			\item \textbf{If I go with $e<1$, I need to come back to verify this.}
+			\item When $g^1$ is negative, the constraint on $\de_h^1$ (see proof of Thm 3) becomes an upper bound. If it's negative, it means that no $\de_h$ exists to make separating possible.
+			\item I need a formal result to see clearly what is going on here
 		\end{itemize}

### 2021-01-17 e-g calculations.R
fix min dh for e=0 case in calculations file

@@ -76,7 +76,7 @@ rm(dh_min) #get rid of this after checking that it is lower than dh
 # e=0
 g0 = p*(T+D)
 W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
-dh_min0 = 1 - p*T + (p*(W - T -D))/g0 #If g1<0, this is UPPER BOUND
+dh_min0 = W/((1-p)*(T+D)) - p/(1-p)
 rm(dh_min0)
 
 # 0 < e < 1 with mediator

### 2021-01-17 notes.tex
fix min dh for e=0 case in calculations file
clean up mediator case to-do list

@@
 						\begin{itemize}
-							\item This is likely (surely?) to be when efficient gifts can't be sustained as a CSE.
-							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator?
+							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator? YES
 							\item \textbf{Find the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote}
@@
 											\item No, it's not possible. Asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
-											\item I still don't have intuition for the asymptote. Need to look back at IC constraint to get it.
-										\end{itemize}
-								\end{itemize}
-						\end{itemize}
-					\item Ideally would want to combine $WM > W0$ and $WM > W1$ to get WM = max$\left\{WM, W1,W0\right\}$
-						\begin{itemize}
-							\item I basically CAN do this with asymptote conditions...or at least try
-						\end{itemize}
-					\item Maybe I can just do comparative statics on the condition? \url{http://people.duke.edu/~dgraham/scripts/MathematicaLaTeX-to-LaTeX/ComparativeStatics-none.pdf}
+										\end{itemize}
+									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
+										\[
+											\frac{e p T}{1 - \de_h} > 1
+										\]
+										\begin{itemize}
+											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
+											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
+										\end{itemize}
+								\end{itemize}
+						\end{itemize}
 					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
@@
 						\]
-						I have a page of math that shows that this is strictly smaller than $d^h$.
+							\begin{itemize}
+								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
+							\end{itemize}
+						The following shows that this is strictly smaller than $\de^h$.
 This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.
 							\begin{itemize}
+								\item $T+D>W$
+								\item $-(T+D)<-W$
+								\item $-p(T+D)<-pW$
+								\item $W-p(T+D)<W-pW$
+								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
+								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
 								\item This is nice, but I'm not sure it helps with the narrative of the story.

### 2021-01-17 notes.tex
consolidate to-do list for revision of mediator section

@@
 	\item Iran deal with the U.S.: JCPOA
+\end{itemize}
+
+\section{No material value CSE vs. repeated game}
+Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
+						\[
+						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
+						\]
+						\[
+						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
+						\]
+						\[
+						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
+						\]
+						\[
+						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
+						\]
+						\[
+						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
+						\]
+						\[
+							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
+						\]
+						\[
+							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
+						\]
+							\begin{itemize}
+								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
+							\end{itemize}
+						The following shows that this is strictly smaller than $\de^h$.
+\textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
+							\begin{itemize}
+								\item $T+D>W$
+								\item $-(T+D)<-W$
+								\item $-p(T+D)<-pW$
+								\item $W-p(T+D)<W-pW$
+								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
+								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
+								\item This is nice, but I'm not sure it helps with the narrative of the story.
+									\begin{itemize}
+										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
+											\begin{itemize}
+												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
+												\item Should I compare grim trigger welfare to see which is higher?
+											\end{itemize}
+									\end{itemize}
 							\end{itemize}
@@
 		\]
+It turns out that there aren't really separate conditions.
+If the welfare under the mediator asymptotes to positive infinity to the left of the asymptote (i.e.
+where the gift is positive), then the mediator is better than any CSE.
+					\item I've given up on deriving an analytical expression for when the mediator enhances welfare (see Mathematica programs for more detail)
+					\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard. But I have developed an intuitive sufficient condition
+								\begin{itemize}
+									\item First, note that it is not possible to have the $e$ asymptote be negative (in which case mediator can't ever work).
+The asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$.
+Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
+									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
+										\[
+											\frac{e p T}{1 - \de_h} > 1
+										\]
+										\begin{itemize}
+											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
+											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
+										\end{itemize}
+								\end{itemize}
 \end{itemize}
@@
 			\begin{itemize}
-					\item Can I derive an analytical expression for when the mediator enhances welfare? See Section~\ref{sec:WM0}
-						\begin{itemize}
-							\item If you can sustain $e=1$ with no mediator, would you ever want a mediator? YES
-							\item \textbf{Find the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote}
-								\begin{itemize}
-									\item Is it possible to have the $e$ asymptote be negative (in which case mediator can't ever work)?
-										\begin{itemize}
-											\item No, it's not possible. Asymptote is at $e=\frac{p}{p + T(1-\de_l) +W}$. Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
-										\end{itemize}
-									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
-										\[
-											\frac{e p T}{1 - \de_h} > 1
-										\]
-										\begin{itemize}
-											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
-											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 
-										\end{itemize}
-								\end{itemize}
-						\end{itemize}
-					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
-						\[
-						  \frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g_0 \geq \frac{1}{1-\de_h} (W-D)
-						\]
-						\[
-						  pT + (1-p)(W-D) - (1-\de_h)(1-p) g^0 \geq W-D
-						\]
-						\[
-						  \de_h (1-p) g^0 \geq W-D - pT - (1-p)(W-D) +g^0(1-p)
-						\]
-						\[
-						  \de_h (1-p) g^0 \geq p(W-D-T) +g^0(1-p)
-						\]
-						\[
-						  \de_h \geq \frac{p(W-D-T)}{g^0(1-p)} + 1 = \frac{p(W-D-T)}{p(T+D)(1-p)} + 1 
-						\]
-						\[
-							\de_h \geq \frac{W}{(T+D)(1-p)} + \frac{(-D-T)}{(T+D)(1-p)} + 1 = \frac{W}{(T+D)(1-p)} - \frac{1}{1-p} + 1
-						\]
-						\[
-							\de_h \geq \frac{W}{(T+D)(1-p)} - \frac{p}{1-p}
-						\]
-							\begin{itemize}
-								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
-							\end{itemize}
-						The following shows that this is strictly smaller than $\de^h$.
-This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.
-							\begin{itemize}
-								\item $T+D>W$
-								\item $-(T+D)<-W$
-								\item $-p(T+D)<-pW$
-								\item $W-p(T+D)<W-pW$
-								\item $\frac{W-p(T+D)}{T+D}<\frac{W-pW}{T+D} = \frac{(1-p)W}{T+D}$
-								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
+					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
+					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
+					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
+						\begin{itemize}
+							\item If you can sustain $e=1$ with no mediator, mediator can still be better
+						\end{itemize}
+					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
+						\begin{itemize}
+							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard.
+But I have developed an intuitive sufficient condition.
+See end of Section~\ref{sec:WM1}
+						\end{itemize}
+					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable is strictly smaller than $\de^h$.
+\textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
+							\begin{itemize}
 								\item This is nice, but I'm not sure it helps with the narrative of the story.
+									\begin{itemize}
+										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
+											\begin{itemize}
+												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
+												\item Should I compare grim trigger welfare to see which is higher?
+											\end{itemize}
+									\end{itemize}
 							\end{itemize}

### 2021-01-17 notes.tex
add intuition for remaining mediator to-dos

@@
 						\begin{itemize}
+							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
+						\end{itemize}
 					\item If you can sustain $e=1$ with no mediator, mediator can still be better
+						\begin{itemize}
+							\item Again, if mediator is good, it's REALLY good.
+							\item The benefit of $eg_M$ is muted versus $g^1$, but there is no harm from $g_M$ while there is harm from $g^1$.
+Cost of gift will always be larger under mediator because it goes to infinity at the optimal $e$
 						\end{itemize}

### 2021-01-18 draft.tex
revise for \de issue through no concessions separting eqm

@@
 The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles.
-If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
+If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
 
 For a Peace equilibrium to exist, $\delta_i$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
-The threshold $\delta_i^*$ needed is \be
- \delta_i^* = \frac{W}{T+D}
+The threshold needed is \be
+ \delta^{gt} = \frac{W}{T+D}
  \ee
-We differentiate the high and low types by assuming $\delta_h> \delta_i^*$ and $\delta_l < \delta_i^*$.
-This implies that, with perfect information about the $\delta_i$'s, two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
+where the superscript $gt$ stand for `grim trigger.' Here, as in each further iteration of the model, we define a high type as a country who prefers to play the ``Peace'' equilibrium, i.e.
+$\delta_h^{gt} \geq \delta^{gt}$.
+Any country with $\delta_l^{gt} < \delta^{gt}$ is a low type.
+This means that two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
 
@@
 \label{sec:bench}
-When countries are faced with uncertainty about each other's motives, they can proceed in several different ways.
-There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor for the high type ($\delta_h$) exceeds the cutoff found in expression (1), there are many types of equilibria; consider for instance oscillating every other period between Peace and War with a grim trigger War threat.
+When countries are faced with uncertainty about each other's motives, they can proceed in several different ways, including giving concessions in order to signal their willingness and ability to make peace.
+There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor is high enough, there are many types of equilibria.
+Consider for instance oscillating every other period between Peace and War with a grim trigger War threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
-These are also always payoff dominated by at least one of the other equilibria discussed, so are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as all proofs for this section.
+These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as all proofs for this section.
 \\
@@
 Active fighting is not necessary; remaining outside of a state of peace is all that is required.
-See Lemma~\ref{lemma:1} and Lemma~\ref{lemma:2} in the appendix for a formal characterization of this type of equilibrium.
+See Lemma~\ref{lemma:1} and Lemma~\ref{lemma:2} in the Appendix for a formal characterization of this type of equilibrium.
 
@@
 
-In any case, these long lasting stalemates are the types of conflict which are most appropriate for mediator involvement.
 Without a third party, there is little hope of overcoming mistrust.
-In some sense then, these are the cases that are most interesting because the international community might play a positive role.
-A mediator will be added to the model later to illustrate exactly how this role can be played.
+These long lasting stalemates are the types of conflict which are most appropriate for mediator involvement.
+A mediator will be added to the model later to illustrate exactly how mediation can help achieve peace in this context.
+In some sense, these are the cases that are most interesting because the international community might play a positive role.
 \\
@@
 \vskip-.2in
-The other two equilibria are separating equilibria in which low types and high types have different strategies.
+The other two equilibria on which we focus are separating equilibria in which low types and high types have different strategies.
 In a \emph{no-concessions separating equilibrium}, no concessions are given by either type in period 0.
@@
 \begin{theorem}
-	When low types give no concessions in period 0 and always play Fight thereafter, the strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
+	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}=\de^{nc}$.
+A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give no concessions in period 0 and play Trust unless the other country defects to Fight.
 	\label{theorem:1}
 \end{theorem}
-\emph{Proof}: See appendix.
+\emph{Proof}: See Appendix.
 \\
@@
 Warsaw Pact countries generally allowed the USSR similar leeway; it was better to have occasionally imperfect cooperation than conflict.
-Certain things can disrupt trust without completely derailing cooperation.
+Some events can disrupt trust without completely derailing cooperation.
 
-Of course, it is possible that in a \emph{no-concessions separating equilibrium} one country can take advantage of the other.
+Of course, it is possible that one country can take advantage of the other in a \emph{no-concessions separating equilibrium}.
 It can be argued that indeed that did happen in the Warsaw Pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.
-
-Though it will not be modeled here, a stochastic component -- when countries occasionally unilaterally defect -- can explain why powerful countries like the USSR more often ``get away'' with cheating: the payoffs to the relationship are not symmetric.
-Losing the USA or USSR as an ally is much more devastating for a satellite country than vise versa, therefore big countries can have their alliances and take advantage of them too.
 \\
 \\
+
+%Though it will not be modeled here, a stochastic component -- when countries occasionally unilaterally defect -- can explain why powerful countries like the USSR more often ``get away'' with cheating: the payoffs to the relationship are not symmetric.
+Losing the USA or USSR as an ally is much more devastating for a satellite country than vise versa, therefore big countries can have their alliances and take advantage of them too.
 {\bf \emph{Concessions Separating Equilibrium}\\}
@@
 \end{lemma}
-\emph{Proof:} See appendix.\\
+\emph{Proof:} See Appendix.\\
 
@@
 \end{theorem}
-\emph{Proof:} See appendix.
+\emph{Proof:} See Appendix.
 
-This smallest concession is denoted $g_h^*$ and is calculated in equation (9) in the appendix to be $p(T+D).$
+This smallest concession is denoted $g_h^*$ and is calculated in equation (9) in the Appendix to be $p(T+D).$
 
@@
 \end{theorem}
-\emph{Proof}: See appendix.
+\emph{Proof}: See Appendix.
 
@@
 \end{lemma}
-\emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight.
+\emph{Proof}: Because $W\geq0$, the dominant stage game action for all types is to play Fight.
 Playing Trust is only possible in equilibrium where there is punishment for playing Fight.
 The minimax payoff is $W-D$, and punishing a country by playing it every period is the worst possible punishment, hence it gives the greatest potential for a country to be given incentives to play Trust.
-Low types, with $\delta_l < \delta^*$ achieve a higher payoff from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
+Low types, with $\delta_l < \delta^{gt}$ achieve a higher payoff from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
 \hfill $\blacksquare$\\
@@
 
- Let us examine the conditions for a separating equilibrium held in place by a grim trigger.\\
- \\
- \emph{Proof of Theorem \ref{theorem:1}}:\\
-Countries with the equilibrium strategy to play Trust in the first round reveal themselves as a high type as per Lemma~\ref{lemma:2}.
-This will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from deviating against someone playing the pooling (always Fight) strategy.
+ We examine the conditions for a separating equilibrium held in place by a grim trigger.
+
+ \noindent{\emph{Proof of Theorem \ref{theorem:1}}:\\
+Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Fight in the first period and then every period thereafter by the one-shot deviation principle.
 If both countries play Trust in a period, a Peace equilibrium takes place and both countries continue to play peace in every period with the grim trigger threat of the War equilibrium.
 Low types play Fight in the first period, so a high type that observed Fight being played would respond by playing Fight in period 2 and in all future periods.
-If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, a high type will be given incentives to play Trust in the first round rather than Fight.
-To play Trust, the following must be satisfied:%Make clearer language!!!!!!!
-%FUTURE WORK ON DELY OF PEACE- IF PEACE WILL E THERE, YOU MIGHT BE VERY RISK AVERSE TO GETTING SCREWED BY THE LOW TYPE SO KEEP PUTTING OFF THE RISKY FIRST TRUST ROUND
+A country plays Trust if and only if the following condition is satisfied:
 \be
-p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )\geq p (T + W + \frac{\de_h}{1-\de_h}(W-D)) +(1-p)\frac{W-D}{1- \delta_h}
+  p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)\geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)\frac{W-D}{1- \delta_h}
 \ee
-
-This simplifies to the condition of high types choosing Trust in period 1 if and only if: 
+Simplifying, we have
+\be
+  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
+\ee
+\be
+  pT \geq p \left((1-\de_h)(T + W) + \de_h (W-D)\right) + (1-\de_h)(1-p)W
+\ee
+\be
+  pT \geq pT -p\de_hT +pW -p\de_h W + p \de_h W -p \de_h D  + W -\de_h W -pW + p\de_hW
+\ee
+\be
+  p\de_hT +p \de_h D + \de_h W - p\de_hW  \geq W 
+\ee
 \be
@@
 \ee
-Since under some parameter sets this condition will hold, this type of separating equilibrium can exist.
-Let us refer to such an equilibrium as a  \emph{no-concessions separating equilibrium}, since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0.
-\hfill $\blacksquare$
+
+If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, a country with $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$ has the incentive to play Trust in the first round rather than Fight.
+Any player with $\de < \de_h^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
+Thus we call these countries low types for purposes of this equilibrium.
+\hfill $\blacksquare$\\
+
+This type of separating equilibrium can exist for some sets of parameters.
+Since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0, we refer to such an equilibrium as a \emph{no-concessions separating equilibrium}.
+This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
 \\

### 2021-01-18 draft.tex
Revisions of Section 2 and 3 up to when I realized that nc sep eqm is the same as the repeated game in Section 2

@@
 The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles.
-If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
+If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
 
@@
 \\
-In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk.
+In this equilibrium, two mutually distrustful countries behave as if they trust anyway, taking a risk.
 This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.
 This is representative of a case where countries have suspicions about each other, but proceed anyway.
+
+\begin{corollary}
+	The threshold patience level for a country to play Trust in a no-concessions separating equilibrium, $\de_h^{nc}$, is higher than for the grim-trigger repeated game equilibrium. 
+	\label{corollary:1}
+\end{corollary}
+\emph{Proof}: See Appendix.
 
@@
 
-This type of separating equilibrium can exist for some sets of parameters.
+\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
+High-type welfare under the no-concessions separating equilibrium is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D) \right\} = \frac{1}{1-\de_h}\left\{pT + (1-p)\left[W-D + \de_h(W-D)\right]\right\}$$
+High-type welfare under the grim trigger repeated game equilibrium is $\frac{1}{1-\de_h}\left\{pT + (1-p)\left[-D + \de_h(W-D) \right]\right\}$
+When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+%This type of separating equilibrium can exist for some sets of parameters.
 Since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0, we refer to such an equilibrium as a \emph{no-concessions separating equilibrium}.
@@
 \\
-%This section could use some cleanup and streamlining
 \\

### 2021-01-18 draft.tex
revise Section 2 and pooling eqm given removal of repeated game high type in section 2

@@
 A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
-The type distinction, as explained in detail later, is relevant in that it encompasses the country's willingness to cooperate in solving the conflict.
+The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict; that is, throughout the analysis we will define a low type as a player whose only sequentially rational strategy is to remain in conflict in all periods.
 It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
@@
 
+We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' The assumption $T>W-D$ ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
+
 Payoffs for a country are the sum the stage game payoffs, discounted by $\delta_i$.
@@
 
-The assumption $T>W-D$ ensures that the joint payoffs from (Trust, Trust)---which we will refer to as ``Peace''---are the highest among all the stage-game action profiles.
-If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat; that is, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.'' We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.''
-
-For a Peace equilibrium to exist, $\delta_i$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
-The threshold needed is \be
- \delta^{gt} = \frac{W}{T+D}
- \ee
-where the superscript $gt$ stand for `grim trigger.' Here, as in each further iteration of the model, we define a high type as a country who prefers to play the ``Peace'' equilibrium, i.e.
-$\delta_h^{gt} \geq \delta^{gt}$.
-Any country with $\delta_l^{gt} < \delta^{gt}$ is a low type.
-This means that two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
-
 \section{Analysis of Benchmark Cases}
@@
 When countries are faced with uncertainty about each other's motives, they can proceed in several different ways, including giving concessions in order to signal their willingness and ability to make peace.
-There are three basic types of equilibria that this analysis will examine.\footnote{If the discount factor is high enough, there are many types of equilibria.
-Consider for instance oscillating every other period between Peace and War with a grim trigger War threat.
+We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
+Consider for instance oscillating every other period between (Trust,Trust) and (Fight,Fight) with a grim trigger War threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
-These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as all proofs for this section.
+These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as most proofs for this section.
 \\
@@
 Active fighting is not necessary; remaining outside of a state of peace is all that is required.
-See Lemma~\ref{lemma:1} and Lemma~\ref{lemma:2} in the Appendix for a formal characterization of this type of equilibrium.
+See the Appendix for a formal characterization of this type of equilibrium.
 
@@
 The other two equilibria on which we focus are separating equilibria in which low types and high types have different strategies.
-In a \emph{no-concessions separating equilibrium}, no concessions are given by either type in period 0.
+If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat.
+We call this a \emph{no-concessions separating equilibrium}.
+In this equilibrium, no concessions are given by either type in period 0.
 In period 1, high types play Trust while low types play Fight.
@@
 
+%In this equilibrium, no concessions are given by either type in period 0.
+In all periods starting at period 1, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.''
+
+%For a Peace equilibrium to exist, $\delta_i$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
+%The threshold needed is \be
+ %\delta^{gt} = \frac{W}{T+D}
+ %\ee
+%where the superscript $gt$ stand for `grim trigger.'
+
 \begin{theorem}
-	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}=\de^{nc}$.
+	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}=\de^{nc}$.
 A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give no concessions in period 0 and play Trust unless the other country defects to Fight.
@@
 \\
+Here, as in each further iteration of the model, we define a high type as a country who prefers to play the ``Peace'' equilibrium, i.e.
+$\delta_h \geq \delta^{nc}$.
+Any country with $\delta_l < \delta^{nc}$ is a low type.
+This means that two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
+
 In this equilibrium, two mutually distrustful countries behave as if they trust anyway, taking a risk.
@@
 
-\begin{corollary}
-	The threshold patience level for a country to play Trust in a no-concessions separating equilibrium, $\de_h^{nc}$, is higher than for the grim-trigger repeated game equilibrium. 
-	\label{corollary:1}
-\end{corollary}
-\emph{Proof}: See Appendix.
+%\begin{corollary}
+%	The threshold patience level for a country to play Trust in a no-concessions separating equilibrium, $\de_h^{nc}$, is higher than for the grim-trigger repeated game equilibrium. 
+%	\label{corollary:1}
+%\end{corollary}
+%\emph{Proof}: See Appendix.
 
@@
 \hfill $\blacksquare$\\
-\\
+
+\begin{comment}
 \begin{lemma}
@@
 \hfill $\blacksquare$\\
+\end{comment}
 
-One high type equilibrium strategy is to pool with the low types and always play Fight.
-If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, Lemma~\ref{lemma:2} shows that the low-type of player $i$ best responds by always playing Fight.
-The high-type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior by Lemma~\ref{lemma:1}.
+That is, one high type equilibrium strategy is to pool with the low types---who always play ``Fight'' by definition---and always play Fight.
+If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, then either type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior.
 Given that the stage-game equilibrium will be (Fight,Fight), there is no incentive to give a concession in period 0 because concessions are costly and signaling one's type can give no benefit in this equilibrium.
@@
 \be
-  p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)\geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)\frac{W-D}{1- \delta_h}
+  p\left(\frac{T}{1- \delta_i}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_i} \right)\geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)\frac{W-D}{1- \delta_h}
 \ee
@@
 \hfill $\blacksquare$\\
-
-\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
-High-type welfare under the no-concessions separating equilibrium is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D) \right\} = \frac{1}{1-\de_h}\left\{pT + (1-p)\left[W-D + \de_h(W-D)\right]\right\}$$
-High-type welfare under the grim trigger repeated game equilibrium is $\frac{1}{1-\de_h}\left\{pT + (1-p)\left[-D + \de_h(W-D) \right]\right\}$
-When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+%\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
+%High-type welfare under the no-concessions separating equilibrium is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D) \right\} = \frac{1}{1-\de_h}\left\{pT + (1-p)\left[W-D + \de_h(W-D)\right]\right\}$$
+%High-type welfare under the grim trigger repeated game equilibrium is $\frac{1}{1-\de_h}\left\{pT + (1-p)\left[-D + \de_h(W-D) \right]\right\}$
+%When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
 %This type of separating equilibrium can exist for some sets of parameters.
@@
 This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
-\\
 \\

### 2021-01-19 draft.tex
Finish with revisions to Section 3 given removal of repeated game high type definition

@@
 
-Here $T\geq0$ represents the benefit from the other country playing Trust.
-$D\geq0$ represents the damages incurred when the other country plays Fight, while $W\geq0$ is the additional benefit a country receives when it plays Fight itself.
+Here $T>0$ represents the benefit from the other country playing Trust.
+$D>0$ represents the damages incurred when the other country plays Fight, while $W>0$ is the additional benefit a country receives when it plays Fight itself.
 We assume $T>W-D$ in line with the assumption that the countries play a Prisoner's Dilemma in the stage game.
@@
 Payoffs for a country are the sum the stage game payoffs, discounted by $\delta_i$.
-For example, if both parties play ``Trust'' in every period, the payoff for a player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$ Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
+For example, if both parties play ``Trust'' in every period, the payoff for a player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$
+
+We will use grim trigger punishments throughout: that is, (Fight, Fight) will be played forever if Fight is played by any party in any round.
+Because we use grim trigger punishments, there are only 4 interesting paths of play after concessions are given:
+1) Both countries play Trust always, 
+2) Both play Fight always, 
+3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
+4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.
+
+Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.
+Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
+If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}=\frac {T}{1- \delta_i}$.
+Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
+Note that because types have different discount rates, the payoffs differ by type, and when ambiguous will be superscripted to indicate the type (e.g.
+$X_{FT}^h$ represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period).
+
+Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
 %Countries' utility is calculated as ex interim utility (Holmstrom and Myerson 1983),  i.e.
@@
 These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as most proofs for this section.
-\\
-\\
-{\bf \emph{Pooling equilibrium}\\}
-\vskip-.2in
+
+\subsection{Pooling equilibrium}
 In the \emph{pooling equilibrium}, both countries do not give concessions in period 0, then always play Fight in every period beginning with period 1. 
@@
 In some sense, these are the cases that are most interesting because the international community might play a positive role.
-\\
-\\
-{\bf \emph{No-Concessions Separating Equilibrium}\\}
-\vskip-.2in
+
+\subsection{No-Concessions Separating Equilibrium}
+\label{sec:ncse}
 The other two equilibria on which we focus are separating equilibria in which low types and high types have different strategies.
@@
 \begin{theorem}
+\emph{No Concessions Separating Equilibrium}\\
 	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}=\de^{nc}$.
@@
 
-%\begin{corollary}
-%	The threshold patience level for a country to play Trust in a no-concessions separating equilibrium, $\de_h^{nc}$, is higher than for the grim-trigger repeated game equilibrium. 
-%	\label{corollary:1}
-%\end{corollary}
-%\emph{Proof}: See Appendix.
-
 Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
@@
 It can be argued that indeed that did happen in the Warsaw Pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.
-\\
-\\
 
@@
 Losing the USA or USSR as an ally is much more devastating for a satellite country than vise versa, therefore big countries can have their alliances and take advantage of them too.
-{\bf \emph{Concessions Separating Equilibrium}\\}
-\vskip-.2in
-The third option is for distrustful countries to use concessions as a way of building trust.
-In the model this is the \emph{concessions separating equilibrium}.
-This equilibrium is costly, but can be worth the investment if the other country also cooperates.
-It is also not as risky as cooperating without concessions, as in the previous equilibrium.
+\subsection{Concessions Separating Equilibrium}
+The other separating equilibrium of interest involves distrustful countries to using concessions as a way of building trust.
+We call this the \emph{concessions separating equilibrium}.
+In this equilibrium, the cost of giving a concession can be worth the investment if the other country also cooperates.
+It is also not as risky as the \emph{no-concession separating equilibrium}.
 The concessions are given before more substantive actions, thus concessions are a costly signal that the other country is serious about cooperating.
 Most agreements come with concessions, and in many cases, though not all, they are used as signals.
-The goal is to use this option to avoid continual distrust; we will show in Section 5 that a mediator is one way of enabling this solution.
+The goal is to use this option to avoid continual distrust.
+That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing Peace.
 
-In the \emph{concessions separating equilibrium}, low types do not give concessions while high types give a concession of a certain size in period 0.
+In the \emph{concessions separating equilibrium}, low types do not give concessions while high types give a concession in period 0.
 If both countries receive concessions, they know the other is a high type and both play Trust in subsequent periods.
-Otherwise, if both players do not receive concessions, there is at least one low type so both countries play Fight in subsequent periods.
+Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Fight in subsequent periods.
+Because of the signaling value of the concessions given in period 0, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Fight.
 
-The analysis is conducted with standard incentive compatibility constraints.
-Consider the commonly employed grim trigger punishment path of the ``Fight, Fight'' equilibrium being played forever if Fight is played by any party in any round.
-This paper will focus on separating equilibria in which high types make use of concessions to identify themselves in hopes of establishing Peace.
-Because we look at grim trigger punishments, there are essentially only 4 equilibrium combinations of strategies after concessions are given:
-1) Both countries play Trust always, 
-2) Both play Fight always, 
-3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
-4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.
-
-Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.
-Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
-If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}=\frac {T}{1- \delta_i}$.
-Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
-Note that because types have different discount rates, these quantities are different by type, and when ambiguous will be superscripted to indicate the type (e.g.
-$X_{FT}^h$ represents the high type).
-Note that because of the signaling value of the concessions given in period 0, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium (both play Trust if there were two high signals; otherwise both play Fight).
-$X_{FT}$ and $X_{TF}$ are still necessary for calculating the equilibrium concession $g_h$.%might make the first one TF for clarity
+Details of the analysis, which uses standard incentive compatibility constraints, are in the Appendix.
+We begin by characterizing the concession (or \emph{gift}) giving behavior of the low type.
+We then present the patience threshold and gift giving behavior of the high type.
 
@@
 \end{lemma}
-\emph{Proof:} See Appendix.\\
+\emph{Proof:} See Appendix.
 
 \begin{theorem}
-	In the best concessions separating equilibrium, high types give the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs.
+\emph{Concessions Separating Equilibrium (CSE)}
+	\begin{enumerate}
+		\item[(a)] Assume $\delta_h \geq \frac{W}{T+D} = \de^{c}$.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
+		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
+Equilibria with higher concessions yield strictly lower payoffs.
+\end{enumerate}
 	\label{theorem:2}
@@
 
-This smallest concession is denoted $g_h^*$ and is calculated in equation (9) in the Appendix to be $p(T+D).$
-
 This `best' concessions separating equilibrium, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
 
-In general, a high probability of a high type will make this no-concessions separating equilibrium very attractive. Under low $p$, high types are better off choosing the pooling equilibrium.
+ Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.
+Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
 
-Concessions separating equilibria are a way for countries to solve their disputes.
+We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no concessions separating equilibrium} in Section~\ref{sec:ncse}.
+
+\begin{corollary}
+	The \emph{no-concessions separating equilibrium} requires countries to be more patient than the \emph{concessions separating equilibrium}.
+If both equilibria exist, the \emph{no-concessions separating equilibrium} is preferred when the probability of encountering a high type is sufficiently large.
+	\label{corollary:1}
+\end{corollary}
+\emph{Proof}: See Appendix.
+
+A large probability of a high type makes the \emph{no-concessions separating equilibrium} very attractive because the risk of ending up in the cheater's corner of the Prisoner's Dilemma is low and no concessions have to be made.
+Conversely, for smaller values of $p$, high types are better off paying the gift to avoid the possibility of being taken advantage of by a low type.
+
+Concessions separating equilibria are a way for countries to solve their disputes when the \emph{no concessions separating equilibrium} is unavailable or unattractive.
 By giving costly concessions, they signal their intentions in a way that a partner unwilling to make peace would not be willing to signal.
-A mediator can sometimes make this a possibility, as will be shown in Section~\ref{sec:med}, but this equilibrium is also achievable bilaterally in some cases.
 
-One example of such an equilibrium includes Israel and Egypt at the Camp David Accords.
+One example of such an equilibrium is Israel and Egypt at the Camp David Accords.
 Both parties gave concessions (Israel a material land concession and Egypt diplomatic recognition of Israel) that signaled their willingness to end the stalemate that had characterized the previous five years.
@@
 A country plays Trust if and only if the following condition is satisfied:
-\be
+\begin{equation*}
   p\left(\frac{T}{1- \delta_i}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_i} \right)\geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)\frac{W-D}{1- \delta_h}
-\ee
+\end{equation*}
 Simplifying, we have
-\be
-  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
-\ee
-\be
+%\be
+%  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
+%\ee
+\begin{equation*}
   pT \geq p \left((1-\de_h)(T + W) + \de_h (W-D)\right) + (1-\de_h)(1-p)W
-\ee
-\be
+\end{equation*}
+\begin{equation*}
   pT \geq pT -p\de_hT +pW -p\de_h W + p \de_h W -p \de_h D  + W -\de_h W -pW + p\de_hW
-\ee
-\be
+\end{equation*}
+\begin{equation*}
   p\de_hT +p \de_h D + \de_h W - p\de_hW  \geq W 
-\ee
+\end{equation*}
 \be
 	\delta_h \geq \frac{W}{(1-p)W + p(T+D)}
+	\label{eq:ncse}
 \ee
 
-If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, a country with $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$ has the incentive to play Trust in the first round rather than Fight.
+If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
 Any player with $\de < \de_h^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
@@
 
-If the condition in equation (8) is not met, in the absence of period 0 concessions\footnote{Countries need to deliver concessions in period 0, not just promise them.
-A concession that is promised but not delivered will count as cheap talk.} two high types would play Fight in every period because both would not have the incentive to play Trust.
-If instead high types are provided sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1.
-Two high types would avoid the trap of War that would occur under pooling.
+If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessionsin period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
+A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of War that would occur under pooling.
 
-This type of equilibrium will be called a \emph{concessions separating equilibrium}.
-We refer to the optimal equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type.
+Below are the details of the \emph{concessions separating equilibrium} analysis.
+We refer to the equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type.
 These equilibrium gifts will mean that when period 1 is reached, countries know which type the other country is and choose to play accordingly.
 The concessions phase acts as a coordination device to match countries' actions.
-To play different actions from each other is an off equilibrium contingency.
-These off equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession.
+To play different actions from each other is an off-equilibrium contingency.
+These off-equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession.
 \\
@@
 \emph{Proof of Lemma~\ref{lemma:3}:}\\
-According to the revelation principle, we can assume that in a concessions separating equilibrium countries reveal their types truthfully, allowing period 1 actions where High types only play Trust with other high types, and play Fight with low types.
-Low types play Fight (Lemma~\ref{lemma:1}) and their payoff is $U_l=X_{FF}+ pg_h-g_l$.
-Though low types might be willing to give a non-zero gift in a separating equilibrium, it must distinguish them from the high types.
-Thus it cannot help them to achieve a higher payoff, and because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is 0.
+In accord with the revelation principle, we focus on concessions separating equilibrium in which countries reveal their types truthfully.
+This allows high types to only play ``Trust'' in period 1 with other high types and to play Fight with low types.
+Low types play Fight (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
+
+Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it distinguishes them from the high types \emph{and} this gives them some advantage.
+Here, high types only cooperate with other high types, so giving a concession cannot help low types to achieve a higher payoff in the repeated game.
+Because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is therefore 0.
+
 High types have the incentive to play Trust only in the Peace equilibrium, which can only be sustained by a pair of high types.
@@
 Thus costless announcements cannot lead to truthful revelation.
-If concessions lead to a separating equilibrium, they must be costly.
+If concessions are to lead to a separating equilibrium, they must be costly.
 \hfill $\blacksquare$
@@
 \emph{Proof of Theorem \ref{theorem:2}:}\\
-Under certain conditions, the high types will be given incentives to send costly concessions in order to reveal their type and separate (Lemma~\ref{lemma:3}).
-In a separating equilibrium constructed here, any-off equilibrium behavior (a concession not equal to the equilibrium concession) will be considered a low type gift.
+In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low type gift.
 In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$  is:\\
-\be
+\begin{equation*}
 	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h 
-\ee
-This equation represents the low types' incentives by truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift.
-Rearranging and simplifying this inequality, in order to separate the high types need give a gift
+\end{equation*}
+This expression represents the low types' incentives by truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift.
+Simplifying this inequality, we see that the high types need give a gift
 \be
 	g_h \geq p(X_{FT}^l-X_{FF}^l). 
+	\label{eq:cse}
 \ee 
+in order to separate from the low type.
+
 High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
-Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation, which is when equation (7) holds with equality.
-Substituting in the definitions of the $X$ variables yields the minimum separating gift to be:\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
+Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation.
+This occurs when Expression~\ref{eq:cse} holds with equality.
+Substituting in the definitions of $X_{FT}^l$ and $X_{FF}^l$ yields the minimum separating gift:\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
 Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils.
@@
 	g_h^*=p(T+D) 
+	\label{eq:cse2}
 \ee 
- In order to incentivize high types to send nonzero concessions, the high type IC must not be violated. The payoff from separating must be higher than the payoff from pooling with the low types. 
+ In order to incentivize high types to send nonzero concessions, the high type incentive constraint must not be violated.
+That is, the payoff from separating must be higher than the payoff from pooling with the low types.
 \be
 pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h
+\label{eq:cse3}
 \ee
 
-Combining equations (8) and (9), we have the condition for a concessions separating equilibrium to exist:
+Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a concessions separating equilibrium to exist:
 \be
@@
 That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$\\
+\\
+\emph{Proof of Corollary~\ref{corollary:1}:}\\
+To show that the patience threshold for the \emph{no concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption
+$$T+D>W.$$
+We can multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
+$$(T+D) > (1-p)W +p(T+D).$$
+Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positve and so we can divide through by both and multiply both sides by $W$:
+$$\de_h^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de_h^{c} $$
 
-The no-concessions separating equilibrium also will exist if equation (6) holds. In the case that both exist, the high types will prefer the concessions separating equilibrium if and only if
+In the case that both types of equilibria exist, i.e. $\de_h \geq \de_h^{nc}$, the high types will prefer the \emph{concessions separating equilibrium} if and only if
+\begin{equation*}
+p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - g_h \geq p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)
+\end{equation*}
+This is simplified to preferring the concessions separating equilibrium if and only if
+
+$$(1-p)W-p(T+D)\geq 0$$
+Rearranging,
 \be
-pX_{TT}^h+(1-p)X_{FF}^h - g_h \geq p(\frac{T}{1- \delta_h}) +(1-p)({-D}+\frac{\delta_h(W-D)}{1- \delta_h} )
+ \frac{W}{W+T+D}\geq p
 \ee
-This is simplified to preferring the concessions separating equilibrium if and only if
-\be
- (1-p)W-p(T+D)\geq 0
-\ee
-i.e.,
-\be
- W\geq p(W + T+D)
-\ee
+i.e. The high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{W+T+D}$. \hfill $\blacksquare$\\
 \\
+{\bf \emph{Mediation}}\\
 \emph{Proof of Theorem \ref{theorem:4}:}\\

### 2021-01-20 notes.tex
fix mistake in W0 and W1 calculations (there's more to do but I don't think I need it for this revision)

@@
 When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
+\textbf{THE ABOVE EQUATION IS wrong. We should subtract off $(1-p)g^0$ since $p$ of the time you receive a gift} \\
 
@@
 When $e=1$, welfare is $\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$ \\
+\textbf{THE ABOVE EQUATION IS wrong. We should subtract off $(1-p)g^1$ since $p$ of the time you receive a gift} \\
 
@@
 \vskip.2in
-Parameterization 5: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$
+Parameterization 5: $We > W1 > W0$. Asymptote at $e = 03759...$ (Was incorrect before I understood the asymptote: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$(
 \begin{itemize}
@@
 \vskip.2in
-Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$. Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
+Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$ (0.25 is the asymptote). Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
 \begin{itemize}
 	\item $T = 1, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 15/16=0.9375$
+\end{itemize}
+
+\vskip.2in
+Parameterization 7: $We > W0 > W1$, $42.33 > 4.96 > 2.83$. Mediator optimally chooses $e=0.28$ (0.28571 is the asymptote). Optimal gift is 75, effective gift is 21, vs. $g1 = .428$ and $g0 = .75$
+\begin{itemize}
+	\item $T = 0.5, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 61/64=0.953125$
 \end{itemize}
@@
 			\begin{itemize}
+					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
 					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
-					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
 					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
@@
 See end of Section~\ref{sec:WM1}
-						\end{itemize}
-					\item Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable is strictly smaller than $\de^h$.
-\textbf{This means that the set of types who can make and sustain peace under the CSE with no material value / CSE with material value and $e=0$ is larger than the set of types who can make and sustain peace under the repeated game.}
-							\begin{itemize}
-								\item This is nice, but I'm not sure it helps with the narrative of the story.
-									\begin{itemize}
-										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
-											\begin{itemize}
-												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
-												\item Should I compare grim trigger welfare to see which is higher?
-											\end{itemize}
-									\end{itemize}
 						\end{itemize}

### 2021-01-20 e-g calculations.R

@@ -58,24 +58,24 @@ p = .5
 dl = .5
 dh = 61/64
 
-# cutoff for definition of high type
-di = W/(T+D)
+# grim trigger cutoff
+d_gt = W/(T+D)
 # WM asymptotes to +infty when the following is positive (sufficient condition)
-suff = e*p*T - 1 + dh
+# suff = e*p*T - 1 + dh
 # problem is that we need the asymptote for e (I think)
 e_s = p/(p + T - T*dl +W)
 suff = e_s*p*T - 1 + dh
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
-W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - g1
+W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - (1-p)*g1
 # e = 1 incentive compatible? Minimum dh for separation is
-dh_min = D*(1-p) + 1 - p*T + (p*(W - T -D))/g1 #If g1<0, this is UPPER BOUND
-rm(dh_min) #get rid of this after checking that it is lower than dh
+dh_min1 = D*(1-p) + 1 - p*T + (p*(W - T -D))/g1 #If g1<0, this is UPPER BOUND
+rm(dh_min1) #get rid of this after checking that it is lower than dh
 
 # e=0
 g0 = p*(T+D)
-W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - g0
+W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - (1-p)*g0
 dh_min0 = W/((1-p)*(T+D)) - p/(1-p)
 rm(dh_min0)
 
@@ -91,5 +91,5 @@ g_max = g[e_max,1]
 eg_max = eg[e_max,1]
 
 # condition for mediator to be better than e = 1
-WM1 = 1/(1-dh)*g_max*p*T*e[min(which(g<=0))] - g_max - 1/(1-dh)*g1*(p*T + p*D - D) - g1
+WM1 = 1/(1-dh)*g_max*p*T*e[min(which(g<=0))] - g_max - 1/(1-dh)*g1*(p*T + p*D - D) - (1-p)g1
 test = We_max - W1

### 2021-01-21 draft.tex
Revise Section 4.1, including fixing min discount factor

@@
 
-\section{Model} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING.
+\section{Model}
+\label{sec:model} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING.
 EMPHASIZE SCENARION (EGYPT USRAEL ETC) THAT ARE BETTER TO MODEL WITH Our MODEL.
@@
 We now model concessions to have real future material value that can either help or harm the giver.
+To be clear, in Sections~\ref{sec:model} and \ref{sec:bench}, the gift only benefits the party who receives it in the period in which it is received, that is, Period 0.
+In this section, we assume that this is an additional value from the gift in each period that the repeated game is played, that is, Period 1 and onward.
+
 The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society.
@@
 The first is an additional decision for the negotiating parties.
-In Period 0, after receiving a concession each country makes a decision about how to allocate the value of the concession between military and civil society.
+In Period 0, after receiving a concession, each country makes a decision about how to allocate the value of the concession between military and civil society.
 $\alpha_i$ is the portion of the received concession that country $i$ chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country $i$ dedicates to military buildup.
@@
 Parameters are common knowledge so the result of this decision is well known should the country's type be known.
-Concessions are immediately converted into civil society or military gifts and incorporated into payoff functions.
-Periods 1 to $\infty$ are as before but with the following stage game payoffs:
-
-The second new element is a change to the payoffs.
-We add a term to each of $T$, $W$, and $D$ that represents the additional benefit or harm flowing from the future material value of the concession.
-When both countries play trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion that was invested in civil socity as well as the base benefit of $T$.
-
-If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the miliary by Country 2.
-The (Fight,Trust) and (Trust,Fight) payoffs are modified analogously.
+
+Concessions are immediately converted into civil society or military gifts.
+They are incorporated into payoff functions starting in Period 1.
+Periods 1 to $\infty$ are as before but with the modified stage game payoffs shown in Table 2.
 
@@
 \vskip.1in
+
+This modification to the payoffs is the second change in the model relative to Sections~\ref{sec:model} and \ref{sec:bench}.
+We add a term to each of $T$, $W$, and $D$ that represents the additional benefit or harm flowing from the future material value of the concession.
+When both countries play Trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion that was invested in civil socity as well as the base benefit of $T$.
+
+If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
+However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the miliary by Country 2.
+The (Fight,Trust) and (Trust,Fight) payoffs are modified analogously.
+
+Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the ``Peace'' outcome will be played.
+Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
+
 \begin{theorem}
+\emph{Concessions Separating Equilibrium (CSE) with Material Value}
+	\begin{enumerate}
+		\item[(a)] Assume $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
+		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
+Equilibria with higher concessions yield strictly lower payoffs.
+\end{enumerate}
+	\label{theorem:csemv}
+\end{theorem}
+\emph{Proof:} See Appendix.
+
+\begin{corollary}
 	Assume the high types are not patient enough to separate without concessions but can separate using concessions when concessions have no material value.
@@
 	\label{theorem:matval}
-\end{theorem}
+\end{corollary}
 
@@
 The patience threshold to separate through concessions is much higher under these parameters when the concessions carry future material value.
-In order to calculate it, we need to know the size of the minimum separating concession, which is again calculated from the low-type incentive constraint.
-The minimum separating concession is $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.\footnote{See proof of Theorem~\ref{theorem:4} below for details.} The minimum patience level required for separation is $\de_h^1 = D(1-p)+1-pT + \frac{p(W-(T+D))}{g^1} = .7\overline{9}.$ Because the specified $\de_h$ is not involved in any of these calculations, we can see that for any $\de_h \in [.5\overline{3},.7\overline{9})$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+The minimum patience level required for separation is $\de_h^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = 2.4$, with a minimum separating concession of $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.
+Since discount factors can be no larger than 1, we have shown that under this set of parameters, the concessions separating equilibrium when concessions have material value cannot be sustained.
+
+$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5\overline{3},1)$\footnote{Recall that we restrict $p<1$ since there is no imperfect information when only one type is possible.} Thus, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
 \hfill $\blacksquare$
@@
 
-Before turning to our main result for the case where the material value of concessions can be destroyed, we make a slight simplification of the general model here.
-This is not essential for the results to hold; we make these simplifciations for ease of calculation and demonstration of the results.
-First, we restrict the functional forms of $T(\cdot),W(\cdot)$ and $D(\cdot)$ so that each is a scalar multiplied by its arguments.
-This linear functional form implies that equilibrium optimization has high types choosing $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choosing $\alpha=0$.
+We next turn to our main result for the case where the material value of concessions can be destroyed...
 
@@
 In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low type gift.
-In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$  is:\\
+In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$ following Lemma~\ref{lemma:3} is:\\
 \begin{equation*}
@@
 \begin{equation*}
-p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - g_h \geq p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)
+p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h \geq p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)
 \end{equation*}
-This is simplified to preferring the concessions separating equilibrium if and only if
-
-$$(1-p)W-p(T+D)\geq 0$$
+This simplifies to preferring the concessions separating equilibrium if and only if
+$$(1-p)W-p(1-p)(T+D)\geq 0$$
 Rearranging,
 \be
- \frac{W}{W+T+D}\geq p
+ \frac{W}{T+D}\geq p
 \ee
-i.e. The high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{W+T+D}$. \hfill $\blacksquare$\\
+i.e. The high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$\\
+\\
+{\bf \emph{Concessions Separating Equilibrium with Material Value}}\\
+\emph{Proof of Theorem \ref{theorem:csemv}:}\\
+In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g^1$ is a low type gift.
+In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$ following Lemma~\ref{lemma:3} is:
+\begin{equation}
+	pg^1 +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g^1+pg^1
+	\label{eq:matval1}
+\end{equation}
+The $\al_i$'s vary depending on the situation.
+On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg^1$).
+Then (Fight, Fight) is played, and the payoffs depend on whether this low type is facing a high type or a low type because the implications for future material value are different.
+With probability $p$, the low type received a gift and invested in the military.
+With probability $(1-p)$ there were no concessions given by either side.
+The left side of Expression~\ref{eq:matval1} is then $pg^1 + \frac{1}{1-\de_l}\left[p(W+Wg^1-D) + (1-p)(W-D) \right]$.
+
+On the left side, the low type is giving a gift and also receiving a gift from the high type with probability $p$.
+With probability $p$, this low type faces a high type who invests the gift in civil society.
+With probability $(1-p)$, the low type's gift goes to another low type who invests in the military and low type does not receive a gift.
+So the right hand side of Expression~\ref{eq:matval1} becomes $-g^1 + pg^1 + p\left(T + Tg^1 +W + Wg^1 + \frac{\de_l}{1-\de_l}\left(W + Wg^1-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg^1 \right) \right)$.
+
+Substituting into Expression~\ref{eq:matval1} and simplifying a bit, we have
+%\begin{multline*}
+%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg^1-D) + (1-p)(W-D) \right] \geq \\
+%-g_1 + pg_1 + p\left(T + Tg^1 +W + Wg^1 + \frac{\de_l}{1-\de_l}\left(W + Wg^1-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg^1 \right) \right)
+%\end{multline*}
+\begin{equation*}
+	g^1 + p(W+Wg^1-D) \geq p\left(T + Tg^1 +W + Wg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
+\end{equation*}
+%\begin{equation*}
+%	g_1 - pD \geq p\left(T + Tg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
+%\end{equation*}
+\begin{equation*}
+	\left(1-\de_l\right)g^1\left(1 - pT \right) \geq \left(1-\de_l\right)p\left(D +	 T\right) - (1-p) Dg^1
+\end{equation*}
+%\begin{equation*}
+%	\left(1-\de_l\right)g^1\left(1 - pT \right) + (1-p) Dg^1 \geq \left(1-\de_l\right)p\left(D +	 T\right)
+%\end{equation*}
+\begin{equation}
+	g^1 \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g_h^1
+	\label{eq:matval2}
+\end{equation}
+
+This implies that the high types need give a gift at least as large as $g_h^1$ in order to separate from the low type; that is, if the high types give a gift smaller than $g_h^1$, the low types will have an incentive to mimic the high type and the separating equilibrium will be destroyed.
+
+High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
+Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation.
+This occurs when Expression~\ref{eq:matval2} holds with equality.
+That is, the optimal high type gift in this equilibrium is $g^1 \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
+Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils.
+Thus, a more powerful country would be more able to plunder, and hence has to make a greater concession to convincingly convey its type as being high.
+}
+
+In order to incentivize high types to send nonzero concessions, the high type incentive constraint must not be violated.
+That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types.
+Note that if the high type pools with the low type, it knows it will be playing Fight and so invests any concession received in military buildup.
+\begin{multline*}
+	\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 \geq \\
+	\frac{1}{1-\de_h}\left[p(W+Wg^1-D) + (1-p)(W-D) \right] +pg^1
+\label{eq:matval3}
+\end{multline*}
+
+Simplifying, we have
+$$pT(1+g^1) + (1-p)(W-D(1+g^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
+$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
+$$\de_h g^1 \geq p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1$$
+%$$\de_h \geq \frac{p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1 }{g^1}$$
+$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
+$$\de_h \geq \frac{p(W-D-T)}{g^1} + p (W-T) + (1-p)D + 1$$
+
+Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a concessions separating equilibrium to exist in terms of fundamentals:
+\be
+	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1
+\ee
+That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$\\
 \\

### 2021-01-21 e-g calculations.R

@@ -58,8 +58,16 @@ p = .5
 dl = .5
 dh = 61/64
 
+## P8: Looking for parameters that make dh_min1 < dh_min0
+T = 1
+W = 1
+D = 1
+p = .5
+dl = .5
+dh = ?61/64
+
 # grim trigger cutoff
-d_gt = W/(T+D)
+dh_min_nc = W/((1-p)*W+p*(T+D)) 
 # WM asymptotes to +infty when the following is positive (sufficient condition)
 # suff = e*p*T - 1 + dh
 # problem is that we need the asymptote for e (I think)
@@ -67,16 +75,17 @@ e_s = p/(p + T - T*dl +W)
 suff = e_s*p*T - 1 + dh
 
 # e=1
-g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D)
+g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) # must be positive
 W1 = 1/(1-dh)*(p*T*(1+g1) + (1-p)*(W-D*(1+g1))) - (1-p)*g1
 # e = 1 incentive compatible? Minimum dh for separation is
-dh_min1 = D*(1-p) + 1 - p*T + (p*(W - T -D))/g1 #If g1<0, this is UPPER BOUND
+#D*(1-p) + 1 - p*T + (p*(W - T -D))/g1 #This was Ben's calculation, wrong (I think)
+dh_min1 = (p*(W - T -D))/g1 + p*(W-T) + (1-p)*D + 1
 rm(dh_min1) #get rid of this after checking that it is lower than dh
 
 # e=0
 g0 = p*(T+D)
 W0 = 1/(1-dh)*(p*T + (1-p)*(W-D)) - (1-p)*g0
-dh_min0 = W/((1-p)*(T+D)) - p/(1-p)
+dh_min0 = W/(T+D)
 rm(dh_min0)
 
 # 0 < e < 1 with mediator

### 2021-01-21 draft.tex
Revise Section 4.2; Thm 4 not quite finished, but proof moved

@@
 \subsection{Concessions Separating Equilibrium}
+\label{sec:cse}
 The other separating equilibrium of interest involves distrustful countries to using concessions as a way of building trust.
@@
 
-We implement this by allowing countries to choose a scalar $e$ to multiply by their given concession $g$.
-$0 \leq e \leq 1$.
-As before, $C(g)= g$ but while the receiving country observes the full concession $g$, its benefit is now only $eg$.\footnote{In a more general model, we could also think of $e$ as a function $E(\cdot)$.
-The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession, not only a numerical value.
-These gifts will be converted into utilities by cost and benefit functions, which then allow the possibility of a gift having efficiency greater than 1.
-The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.}
+We implement this by allowing countries to choose a scalar $e$ to multiply by their given concession $g$ where $0 \leq e \leq 1$.
+As before, $C(g)= g$ but while the receiving country observes the full concession $g$, the future benefit to the recipient is now only $eg$.\footnote{In a more general model, we could also think of $e$ as a function $E(\cdot)$.
+The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession.
+In particular, this allows the transformation to increase the value of the concession.
+The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} Table 3 provides the modified payoffs in the repeated game.
 
@@
 
-Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to separate, we first formally establish the welfare implications.
+Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to achieve peace, we first formally establish the welfare implications.
 
 \begin{lemma}
-	Assuming that a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient concessions in a separating equilibrium.
+	If a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient concessions in a separating equilibrium if and only if $pT \geq (1-p)D$.
 	\label{lemma:efficiency}
 \end{lemma}
-\emph{Proof:}
-The benefit of a gift appears on both sides of the IC for both types and thus cancels out in the low type IC $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type IC:  $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.\footnote{Elaboration and explanation of the IC constraints is in the proof of Theorem~\ref{theorem:2}.} Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
-However, the expected separation utilities under this game are now
-\be
-U_h= pX_{TT}+(1-p)X_{FF} - g_h+peg_h 
-\ee
-and
-\be
-U_l=X_{FF}+peg_h 
-\ee
- $\frac{dU}{de}>0$ for both countries so it is never optimal have $e<1$.\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function.
-It also holds for any monotone cost function.} \hfill $\blacksquare$
+\emph{Proof:} See Appendix.
 
@@
 % \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong.
+
+The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens $p$ of the time.
+On other other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
+The future material of concessions increase the expected utility from a separating equilibrium when both the payoffs from Trust and the probability of a high type are relatively large.
 
@@
 
-\noindent {\bf \emph{Pooling equilibrium}}
+\subsection{Pooling equilibrium}
 \begin{lemma}
@@
  \\
- {\bf \emph{No-Concessions Separating Equilibrium}}
+\subsection{No-Concessions Separating Equilibrium}
 
@@
 Thus we call these countries low types for purposes of this equilibrium.
-\hfill $\blacksquare$\\
+\hfill $\blacksquare$
 %\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
@@
 This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
-\\
-{\bf \emph{Concessions Separating Equilibrium}}
+
+\subsection{Concessions Separating Equilibrium}
 
@@
 \ee
-i.e. The high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$\\
-\\
-{\bf \emph{Concessions Separating Equilibrium with Material Value}}\\
+i.e. The high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$
+
+\subsection{Concessions Separating Equilibrium with Material Value}
 \emph{Proof of Theorem \ref{theorem:csemv}:}\\
@@
 \ee
-That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$\\
+That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$
+
+\subsection{Material Value of Concessions can be Destroyed}
+\emph{Proof of Lemma~\ref{lemma:efficiency}:}\\
+%The benefit of a gift appears on both sides of the incentive compatibility constraint for both types and thus cancels out in the low type incentive compatibility constraint $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type incentive compatibility constraint: $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.
+Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
+The expected separation utility for the hight type under the game with material value that can be destroyed is
+$$\frac{1}{1-\de_h}\left\{pT(1+eg^1) + (1-p)(W-D(1+eg^1))\right\} - (1-p)g^1$$
+The derivative with respect to $e$ is
+$$\frac{1}{1-\de_h}\left\{pTg^1 - (1-p)Dg^1)\right\}$$
+This is non-negative when $pT \geq (1-p)D$.
+High type welfare is thus non-decreasing in $e$ when this condition is met.
+The largest admissible value of $e$, i.e.
+$e=1$ thus maximizes welfare when $pT \geq (1-p)D$.\footnote{If $pT = (1-p)D$, $e=1$ is not the unique maximizer, but it is still a maximizer.} \hfill $\blacksquare$\\
+%\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function. It also holds for any monotone cost function.} 
 \\
-{\bf \emph{Mediation}}\\
 \emph{Proof of Theorem \ref{theorem:4}:}\\
-High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$.
-Because the low type's IC constraint binds, with $e=1$ the optimal concession can be calculated to be $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-The high type's utility when $e=1$ is then $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - g^1$.
-
-When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:bench} and the minimum separating concession is $g^0=p(T+D)$.
+High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$. The high type's utility when $e=1$ is
+$$\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 $$
+where $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
+
+When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:cse}.
+High type utility when $e=0$ is $$\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g^0$$ where the minimum separating concession is $g^0=p(T+D)$.
 The threshold for high types to cooperate is again $\frac{W}{T+D}$.
-High type utility when $e=0$ is $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - g^0$.
 
@@
 \hfill $\blacksquare$
+
+\subsection{Mediation}
 

### 2021-01-23 draft.tex
Complete revision of Section 4.2

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{fact}{Fact}
 \newtheorem{corollary}{Corollary}
@@
 
+We have established the results for the concessions separating equilibrium when no material value is destroyed, i.e.
+$e=1$, in Section~\ref{sec:IC}.
+It turns out that we have also established the results for the concessions separating equilibrium when all material value is destroyed, i.e.
+$e=0$.
+Notice that if $e=0$, the payoffs in Table 3 are the same as the payoffs in Table 1 and thus the results of Section~\ref{sec:cse} apply.
+
 Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to achieve peace, we first formally establish the welfare implications.
@@
 \begin{lemma}
-	If a separating equilibrium exists when concessions have material value and are efficient (where $e=1$), it is optimal to give efficient concessions in a separating equilibrium if and only if $pT \geq (1-p)D$.
+	If both the \emph{concessions separating equilibrium with efficient concessions} and the \emph{concessions separating equilibrium with inefficient concessions} exist, the \emph{concessions separating equilibrium with efficient gifts} is preferred when both the probability of encountering a high type and the benefit from making peace are sufficiently large.
 	\label{lemma:efficiency}
@@
 On other other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
-The future material of concessions increase the expected utility from a separating equilibrium when both the payoffs from Trust and the probability of a high type are relatively large.
-
-We next turn to our main result for the case where the material value of concessions can be destroyed...
+Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type, and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
+
+Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$.
+As we turn to our result about the incentive capatibility of the \emph{concessions separating equilibria with material value}, we focus on these two cases going forward as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
+This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive constraint.}
+
+\begin{lemma}
+	The \emph{concessions separating equilibrium with efficient concessions} requires countries to be more patient than the \emph{concessions separating equilibrium with inefficient concessions}. 
+	\label{lemma:e-patient}
+\end{lemma}
+\emph{Proof}: See Appendix.
+
+This means that there are parameters under which Peace cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but Peace can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
+This is one of the reasons that Theorem~\ref{theorem:4} is true.
 
@@
 \end{theorem}
-\emph{Proof}: See Appendix.
-
-Inefficient concessions are optimal under low $p$ (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^*$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
-
-This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, the desired inefficiency of  pre-play communication can also be found in our model.
+\emph{Proof}: We invoke Lemmas~\ref{lemma:efficiency} and \ref{lemma:e-patient}.
+There are two reasons for which the parties would choose the \emph{concessions separating equilibrium with inefficient gifts}.
+First, they may be patient enough to separate when gifts are inefficient but not when gifts are efficient (Lemma~\ref{lemma:e-patient}).
+In this case, the \emph{concessions separating equilibrium with efficient gifts} is not available to them.
+
+However, even if the negotiating parties are patient enough to separate when gifts are efficient, Lemma~\ref{lemma:efficiency} tells us that welfare will be higher with efficient gifts only when the probability of encountering a high type and the benefit from making peace are sufficiently large.
+Otherwise, welfare is higher under the \emph{concessions separating equilibrium with inefficient gifts} and this equilibrium is thus optimal.
+\hfill $\blacksquare$\\
+
+Inefficient concessions are optimal under low $p$ (there's a good chance of facing a low type who will use the concession against you) as well as when the benefits from Peace are low relative to the damages from War.
+This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication can also be found in our model.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
 In Prendergast and Stole the two types are equal except in labeling; in our model, high types and low types are used so there is an incentive for low types to try to pose as high types.
-Aside from this difference, essentially the same result is found: if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.
+However, putting this difference aside, the inefficiency result can be viewed as similar to that in Prendergast and Stole (2001).
+That is, if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.
 
@@
 
+$$p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}$$
+\begin{multline*}
+	\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - g^1 \geq \\
+	\frac{1}{1-\de_h}\left[p(W+Wg^1-D) + (1-p)(W-D) \right]
+\end{multline*}
 Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a concessions separating equilibrium to exist:
@@
 %\begin{equation*}
-%	g_1 - pD \geq p\left(T + Tg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
+%	g^1 - pD \geq p\left(T + Tg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
 %\end{equation*}
@@
 \\
-\emph{Proof of Theorem \ref{theorem:4}:}\\
-High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$. The high type's utility when $e=1$ is
-$$\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 $$
-where $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-
-When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:cse}.
+\emph{Proof of Lemma \ref{lemma:e-patient}:}\\
+The proof will be by contradiction.
+Suppose that the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}.
+Since low types have patience levels below the threshold, we have that
+\begin{equation}
+	\de^c = \frac{W}{T+D} \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1> \de_l.
+	\label{eq:cont}
+\end{equation}
+It follows directly that $W > \de_l(T+D)$. Since $\de_l < 1$, it is also true that $\frac{1-p}{1-\de_l p} < 1$. Combining this with the previous fact, we have
+\begin{equation}
+	W > \de_l(T+D) > \frac{\de_l(T+D)(1-p)}{1-\de_l p}.
+	\label{eq:cont2}
+\end{equation}
+We will invoke Expression~\ref{eq:cont2} below. First we go back to Expression~\ref{eq:cont}, simplifying and creating a common denominator for $\de^1$, we have
+\begin{multline*}
+	\frac{W}{T+D} \geq \frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
+	+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} \\
+	= \frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{multline*}
+Subtract $\frac{W}{T+D}$ from both sides to get
+\begin{multline*}
+	0 \geq \frac{-W(1-\de_l) + W\left(1-\de_l\right)-(D+T)\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT}{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+	+ \frac{(W-(D+T))(1-p) D + p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{multline*}
+Cancelling the first two terms as well as the third and last terms, we have
+\begin{multline*}
+	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{multline*}
+Expanding and cancelling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
+%\begin{multline*}
+%	0 \geq \frac{-W\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+%	+ \frac{pW\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+%\end{multline*}
+%Expand even more and then cancel out $(1-p)D\left(D +	 T\right)$ terms
+\begin{equation*}
+	0 \geq \frac{-W\left(1-\de_l\right)pT +W(1-p) D + pW\left(1-\de_l\right)\left(D +	 T\right) }{\left(1-\de_l\right)\left(D +	 T\right)} 
+	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{equation*}
+Expanding once more and then cancelling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
+%\begin{equation*}
+%	0 \geq \frac{W(1-p) D + pW(1-\de_l)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
+%	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+%\end{equation*}
+%Expand everything from the first fraction and cancel out $-pWD$ terms
+\begin{equation*}
+	0 \geq \frac{WD - \de_lpWD}{\left(1-\de_l\right)\left(D +	 T\right)} 
+	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{equation*}
+Combining with the inequality in Expression~\ref{eq:cont2}, we arrive at
+\begin{equation*}
+	0 \geq \frac{WD(1- \de_lp)}{\left(1-\de_l\right)\left(D +	 T\right)} 
+	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} > \frac{\frac{\de_l(T+D)(1-p)}{1-\de_l p}\left[D(1 - \de_lp)\right]}{\left(1-\de_l\right)\left(D +	 T\right)} 
+	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
+\end{equation*}
+Simplifying, we have
+\begin{equation*}
+	0 > \frac{\de_l(T+D)(1-p)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
+	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = 0
+\end{equation*}
+We have arrived at a contradiction from Expression~\ref{eq:cont} and therefore it must be that 
+\begin{equation}
+	\frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 > \frac{W}{D+T}
+\end{equation}
+ \hfill $\blacksquare$ 
+%\\
+%\emph{Proof of Theorem \ref{theorem:4}:}\\
+%High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$. The high type's utility when $e=1$ is
+%$$\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 $$
+%where $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
+
+%When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:cse}.
 High type utility when $e=0$ is $$\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g^0$$ where the minimum separating concession is $g^0=p(T+D)$.
@@
 
-Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession is determined by comparing the utility under each, and either can be larger.
+%Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession is determined by comparing the utility under each, and either can be larger.
 Inefficient concessions are made optimal when $p$ is low (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^1$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).

### 2021-01-23 notes.tex
Complete revision of Section 4.2

@@
 
+\section{Would negotiating parties choose intermediate e in CSD?}
+
+High type's IC with potentially interior $e$
+$$pT(1+eg) + (1-p)(W-D(1+eg)) - (1-\de_h)g \geq p(W+Weg-D) + (1-p)(W-D)$$
+$$pT(1+eg) - (1-p)Deg - (1-\de_h)g \geq p(W+Weg-D)$$
+$$\de_h g \geq p(W+Weg-D) - pT(1+eg) + (1-p)Deg + g$$
+$$\de_h \geq \frac{p(W-D-T) + peg (W-T) + (1-p)Deg + g }{g}$$
+$$\de_h \geq \frac{p(W-D-T)}{g} + p e(W-T) + (1-p)eD + 1$$
+
+I need to add calculations for $g$ from my written notes
+
 \vskip.5in

### 2021-01-24 draft.tex
Integrate Ben G.'s new opening into introduction

@@
 
-In negotiations with its neighbors, Israel is hesitant to give certain concessions.
-The Golan Heights, captured from Syria during the 1967 War, is a particular point of contention in Israeli-Syrian relations.
-While the Golan Heights does not have the West Bank's historic or religious importance, Israel values it for its highly strategic location.
-The Golan Heights could be a useful concession, but Israel senses that were she to give over the land, Syria may ultimately use the concession against them.
-This same hesitancy exists with the West Bank settlements.
-Many are located on hilltops that could offer strategic military outposts for forces hostile to Israel.
-When it occasionally abandons settlements, Israel generally dismantles all infrastructure, including water and electricity, and bulldozes the buildings.
-Although inefficient, this reduces the possibility of those settlements being used against Israeli interests.
-Without trust, the most efficient concessions often are not made.
-
-This holds for concessions other than land.
-Russia is loathe to cede further autonomy to Chechnya, even though it could hypothetically relieve tensions and reduce violence.
-If Chechen autonomy could in fact lead to lowered violence, it is possible that this move would be in Russia's best interest.
-But the Russians perceive, perhaps correctly, that any move towards autonomy might only give Chechens further leverage against the Kremlin.
-From the Russian perspective, granting the concession of increased autonomy might have large future costs.
-
-This paper uses a two-sided signaling model to propose a new theoretical explanation for why inefficiency might occur in a conflict setting: inefficient concessions may be preferred if the most efficient concessions are seen as having additional, future costs.\footnote{The type of inefficient concessions addressed here are those whose value to the recipient are lower than the cost to the giver.} The Golan Heights, for example, will not be conceded if Israel foresees future security risks that outweigh the immediate benefits of peace.
-We then suggest a new explanation for the effectiveness of third-party mediation.
+In the course of a military conflict, settlement negotiations often occur simultaneously with continued fighting.
+If settlement can be achieved, lives are saved and destruction averted.
+Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective (CHAIN CITE).
+This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that combatants can offer.
+In our context, the efficiency of a concession is determined by how much of the material value of the concession is intact when the recipient receives it.
+If the party who gives the concession destroys any of its material value, the concession is deemed to be less than fully efficient.
+
+We introduce a two-sided signaling model in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
 Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to peace.
+
+Two archetypal situations demonstrate the significance and difficulty of efficient concession-making in war settlement.
+The first is the case of disarmament and the second is the concession of control over strategically valuable territory.
+
+Barbara Walter identified disarmament as the ``critical barrier to civil war settlement'' (1997).
+Particularly in conflicts between a rebel group and a central government, the best-achievable negotiated settlement often involves policy concessions by the government in exchange for disarmament and recognition of government authority by the rebels.
+Disarmament by rebels is an efficient concession if fully-operational weapons are turned over to the central government for its own use, while disarmament accompanied by decommissioning is inefficient because the value of the arms is destroyed.
+Disarming and turning over fully functional weapons is an incredibly difficult concession for rebels to make: once they turn over their arms, they lose future bargaining leverage and have no guarantee that their own weapons won't later be used against them.
+If the rebels can instead decommission those weapons, an important stumbling block to peace is removed.\footnote{Other stumbling blocks remain, including the fact that government retains its weapons.
+Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.
+
+Control of strategically valuable territory can pose similar challenges in both civil and interstate wars.
+Even if transferring control of the territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide military advantage in a future conflict.
+
+Following the 1992 war between Armenia and Azerbaijan over the disputed region of Ngorno-Karabakh, Armenia retained control of a significant amount of Azeribaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland.
+Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory.
+Thus, it might have been efficient in the mid-1990s for the Armenian/Karabahk side to cede control of that territory to Azerbaijan as part of a deal in which Azeribaijan recognized Karabakh's independence.
+However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor, which connects Ngorno-Karabakh and Armenia.
+Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Ngorno-Karabakh and Armenia.
+The territory was not conceded and the conflict persisted in costly stalemate for almost twenty years until war broke out anew in 2020.
+
+Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
+Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (CITE).
+Can mediation offer a path to settlement in these challenging contexts?
+
+This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can help increase the efficiency of concessions that are possible.
+Weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
+One way to address this concern is to destroy the future value of the concession---e.g.
+decommission weapons or attempt to reduce the strategic value of the territory.
+Another option, and the one on which we focus in this paper, is third-party mediation.
+We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling combatants to make more efficient concessions, even when there is a risk those concessions might increase the bargaining power of their opponent in the future.
 

### 2021-01-24 draft.tex
Reword results in Section 4.2 (R2); begin revisions to mediator Section

@@
 Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
-		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
+		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
 Equilibria with higher concessions yield strictly lower payoffs.
@@
 \begin{corollary}
-	Assume the high types are not patient enough to separate without concessions but can separate using concessions when concessions have no material value.
-When concessions instead have future value that the low-type country can use to reduce the future payoffs of its negotiating partner, there are parameters under which the negotiating partners' ability to separate through concessions is destroyed, i.e.
+	Assume that high types are not patient enough to separate without concessions but that they can separate using concessions when gifts have no material value.
+If negotiating parties use concessions with future material value that the low-type country can use to reduce the future payoffs of its negotiating partner instead of concessions with no future material value, there are parameters under which the future material value of gifts destroys negotiating partners' ability to separate through concessions, i.e.
 peace cannot be achieved when there are two high types.
@@
 
-Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz, 2002), much of the literature has focused on self-enforcing mechanisms.
-If however a credible third party does exist, then results beyond self enforcing agreements can be relevant.
+Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz 2002), much of the literature has focused on self-enforcing mechanisms.
+If however a credible third party exists, then results beyond self enforcing agreements can be relevant.
 A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997).
@@
 Importantly, here the mechanism $M$ can differentiate based on recipient's type.
-Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value.
-
-[both individual rationality and incentive compatibility constraints must be satisfied, leading to truthful self-identification. ]
-
-[Further, it can be shown that restricting attention to symmetric recommendations is without loss of generality, because the optimal arbitration programme is linear.]
+Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value that can optionally be destroyed.
+As usual, truthful self-revelation requires that the individual rationality and incentive compatibility constraint for each type must be satisfied
+
+\textbf{First result: can't have $e=1$}
 
@@
 
-The welfare target is again the sum of the high type utilities. Qualitatively, similar results would hold if we also included low types in the analysis with weighting based on $p$.
+The welfare target is again the sum of the high type utilities. Qualitatively, similar results would hold if weighted high- and low-type welfare by the relevant probabilities.
 

### 2021-01-24 draft.tex
Add new result at start of mediation section; fix small issues throughout

@@
 \label{sec:med}
-All results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator.
+All the results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator.
 
@@
 
-\textbf{First result: can't have $e=1$}
-
-low type IC
-$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
+\begin{lemma}
+	A manipulative mediator cannot facilitate the most efficient concessions---that is, $e=1$. 
+	\label{lemma:med}
+\end{lemma}
+\emph{Proof}: See Appendix.
 
@@
 
-\subsection{Concessions Separating Equilibrium with Material Value}
+\subsection{Concessions with Material Value}
 \emph{Proof of Theorem \ref{theorem:csemv}:}\\
@@
 \subsection{Mediation}
+\emph{Proof of Lemma \ref{lemma:med}:}\\
+We proceed by showing that the low type's incentive compatibility constraint cannot hold when the mediator specifies fully efficient gifts.
+The low type's incentive compatibility constraint in the mechanism $M$ is
+$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h $$
+
+Here was have assumed that the mediator specifies $e=1$, which means that gift giving and receiving cancels out.
+The left hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type.
+The mediator only specifies strictly positive gifts if there are two reports of `High.' Likewise, there are no gifts in the $(1-p)X_{FF}^l$ term on the right because the negotiating partner has made a report of `Low.' This leaves
+		$$X_{FF}^l \geq X_{FT}^l.$$
+		Expanding, we have
+		\[
+			\frac{W-D}{1-\de_l} \geq T + \left(\cdot \right) + W + \left(\cdot \right) + \frac{\de_l}{1-\de_l}\left(W+ \left(\cdot \right) -D - \left(\cdot \right) \right)
+		\]
+There are no gifts on the left hand side and so the payoffs from Table 1 apply.
+The right hand side has place holders $\left(\cdot\right)$ for the impact of the material value of gifts.
+On the right hand side, we have only the case where both parties declare themselves to be high types.
+Both parties are instructed to give efficient gifts.
+The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the `Peace' equilibrium.
+The low-type player under consideration knows it will defect and end up in a War equilibrium and so invests entirely in the military.
+%		\begin{multline}
+%			W-D \geq 
+%			\left(1-\de_l\right) \left[T + \al_2Tg^M + W + \left(1-\al_1\right)Wg_2 \right] \\
+%			+ \de_l \left(W + \left(1-\al_1\right)Wg_2-D - \left(1-\al_2\right)Dg^M\right)
+%			\label{eq:lowICex}
+%		\end{multline}
+		\begin{equation*}
+			W-D \geq 
+			\left(1-\de_l\right) \left[T + Tg^M + W + Wg^M \right] + \de_l \left(W + Wg^M -D \right)
+			\label{eq:med}
+		\end{equation*}
+Cancelling like terms and rearranging, we have
+			\[
+					0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg^M + Wg^M + \left(1 - \de_l \right) D
+			\]
+			Since we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are positive and $0 \leq \de_l \leq 1$, this inequality can never hold.
+
+\hfill $\blacksquare$\\
 

### 2021-01-25 draft.tex
Revise partway through mediation section; spell check

@@
 Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory.
-Thus, it might have been efficient in the mid-1990s for the Armenian/Karabahk side to cede control of that territory to Azerbaijan as part of a deal in which Azeribaijan recognized Karabakh's independence.
+Thus, it might have been efficient in the mid-1990s for the Armenian/Karabahk side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence.
 However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor, which connects Ngorno-Karabakh and Armenia.
@@
 This demonstration of the incentives for inefficient concessions leads to a new explanation for the role of mediators in conflict resolution.
-Third party involvement is ubiquitious in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
+Third party involvement is ubiquitous in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
 Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others insist that a correct analysis finds mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al.
@@
 The probability of nature selecting the low type is $1-p$.\footnote{Note that parameters are symmetric across countries, as is consistent with the literature.
-Qualititative results do not depend on this being the case, and equilibria and equilibrium concessions can easily be calculated with asymmetric parameters between players.}  Countries are aware of their own type, but not the type of the other country.
+Qualitative results do not depend on this being the case, and equilibria and equilibrium concessions can easily be calculated with asymmetric parameters between players.}  Countries are aware of their own type, but not the type of the other country.
 Similar scenarios have been modeled as credible commitment problems in the bargaining literature.
@@
 Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
-Note that because types have different discount rates, the payoffs differ by type, and when ambiguous will be superscripted to indicate the type (e.g.
+Note that because types have different discount rates, the payoffs differ by type, and when ambiguous will be super-scripted to indicate the type (e.g.
 $X_{FT}^h$ represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period).
@@
 The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society.
-Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil socity helps the giver in peace.
+Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil society helps the giver in peace.
 The Golan heights is such an example: if Syria is an ally of Israel, the Golan Heights is a reasonable concession to make, but if Syria later turns out to betray a trust, surrender of the strategic land would be disastrous for Israel.
@@
 We add a term to each of $T$, $W$, and $D$ that represents the additional benefit or harm flowing from the future material value of the concession.
-When both countries play Trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion that was invested in civil socity as well as the base benefit of $T$.
+When both countries play Trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion that was invested in civil society as well as the base benefit of $T$.
 
 If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the miliary by Country 2.
+However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
 The (Fight,Trust) and (Trust,Fight) payoffs are modified analogously.
@@
 Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$.
-As we turn to our result about the incentive capatibility of the \emph{concessions separating equilibria with material value}, we focus on these two cases going forward as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
+As we turn to our result about the incentive compatibility of the \emph{concessions separating equilibria with material value}, we focus on these two cases going forward as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
 This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive constraint.}
@@
 \label{sec:med}
-All the results in this paper thus far have relied on bilateral engagement. We will now consider the involvement of a mediator.
+All the results in this paper thus far have relied on bilateral engagement.
+We will now consider the involvement of a mediator when concessions have future material value that can benefit or harm the giver.
 
@@
 Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value that can optionally be destroyed.
-As usual, truthful self-revelation requires that the individual rationality and incentive compatibility constraint for each type must be satisfied
+As usual, truthful self-revelation requires that the individual rationality and incentive compatibility constraint for each type must be satisfied.
+
+%The individual rationality constraints are satisfied for both types.
+The individual rationality constraint of the low types is satisfied because they have the same outcome as they do outside of the mechanism---that is, they remain in the `War' equilibrium and neither give nor receive concessions.
+For the high type, the constraint is looser.
+Outside of the mechanism, they would also remain in the `War' equilibrium and neither give nor receive concessions.
+If they participate, they receive the `War' payoffs with probability $(1-p)$ but they receive `Peace' payoffs with probability $p$.
+Because the `Peace' payoffs are higher than the `War' payoffs, this average is above their reservation payoffs.
+High types give and receive gifts of the same size
 
@@
 \emph{Proof}: See Appendix.
+
+In order to make the mechanism incentive compatible for the low types, some value of the concessions must be destroyed, i.e.
+$e<1$.
+The constraint that determines how efficient concessions can be comes from the low type incentive compatibility constraint.
+As in the concessions separating equilibria, this shows up in the optimal concession size.
+
+\begin{theorem}
+\emph{Mediation}
+\begin{enumerate}
+		\item[(a)] The mediation mechanism $M$ is incentive compatible when the specified concession is at least as large as $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}$.
+		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
+Equilibria with higher concessions yield strictly lower payoffs.
+\end{enumerate}
+	\label{theorem:med}
+\end{theorem}
+\emph{Proof:} See Appendix.
 
@@
 
-If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessionsin period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
+If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessions-in period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
 A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of War that would occur under pooling.
@@
 $$(T+D) > (1-p)W +p(T+D).$$
-Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positve and so we can divide through by both and multiply both sides by $W$:
+Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positive and so we can divide through by both and multiply both sides by $W$:
 $$\de_h^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de_h^{c} $$
@@
 Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
-The expected separation utility for the hight type under the game with material value that can be destroyed is
+The expected separation utility for the high type under the game with material value that can be destroyed is
 $$\frac{1}{1-\de_h}\left\{pT(1+eg^1) + (1-p)(W-D(1+eg^1))\right\} - (1-p)g^1$$
@@
 \end{multline*}
-Cancelling the first two terms as well as the third and last terms, we have
+Canceling the first two terms as well as the third and last terms, we have
 \begin{multline*}
@@
 \end{multline*}
-Expanding and cancelling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
+Expanding and canceling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
 %\begin{multline*}
@@
 \end{equation*}
-Expanding once more and then cancelling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
+Expanding once more and then canceling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
 %\begin{equation*}
@@
 %		\end{multline}
+		\begin{equation}
+			W-D \geq 
+			\left(1-\de_l\right) \left[T + Tg_h + W + Wg_h \right] + \de_l \left(W + Wg_h -D \right)
+			\label{eq:med}
+		\end{equation}
+Canceling like terms and rearranging, we have
+			\[
+					0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg_h + Wg_h + \left(1 - \de_l \right) D
+			\]
+			Since we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are positive and $0 \leq \de_l \leq 1$, this inequality can never hold.	\hfill $\blacksquare$\\
+			\\
+\emph{Proof of Theorem~\ref{theorem:med}:}\\
+For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}.
+So we start from
 \begin{equation*}
 			W-D \geq 
-			\left(1-\de_l\right) \left[T + Tg^M + W + Wg^M \right] + \de_l \left(W + Wg^M -D \right)
-			\label{eq:med}
+			\left(1-\de_l\right) \left[T + Teg_h + W + Weg_h \right] + \de_l \left(W + Weg_h -D \right) + peg_h - pg_h
 		\end{equation*}
-Cancelling like terms and rearranging, we have
+Simplifying, we have
 \[
-					0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg^M + Wg^M + \left(1 - \de_l \right) D
+	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
 \]
-			Since we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are positive and $0 \leq \de_l \leq 1$, this inequality can never hold.
-
-\hfill $\blacksquare$\\
+Gathering the terms involving $g_h$ on the left hand side:
+\[
+	g_h\left[p\left(1 - e\right) -(1-\de_l)eT -eW \right] \geq \left(T - \de_l T \right) + \left(1 - \de_l \right) D
+\]
+Isolating $g_h$ on the left hand side and gathering terms, we have 
+\begin{equation}
+	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)} = g^M
+	\label{ex:med3}
+\end{equation}
+As before, the optimal gift is the one where Expression~\ref{ex:med3} holds with equality.
+We call this value $g^M$.
+We see here that $g^M$ depends on $e$, which is also the choice of the mediator \emph{and} that we must have $\overline{e} = p - e \left( p + T - \de_l T + W \right) > 0$ in order for the optimal concession to be both positive and finite.
+Both the optimal concession increases toward infinity as $e$ approaches $\frac{p}{p + \left(1-\de_l\right) + W}$, which is the value that makes the denominator of $g^M$ equal to 0.
+
+There are now two cases to consider.
+Depending on parameter values, welfare either increases toward infinity or decreases toward negative infinity as $e \rightarrow \overline{e}$.
+A sufficient condition In the welfare-maximizing mediation mechanism, the mediator sets $e$ to be as large as is feasible given the resources available to be given as concessions as long as $e < \frac{p}{p + \left(1-\de_l\right) + W}$
+
+\[
+	\frac{e p T}{1 - \de_h} > 1
+\]
 

### 2021-01-25 draft.tex
Copy edit Sections 2 through first half of 5

@@
 
-Countries\footnote{Players will be referred to as countries, though it could also be appropriate to think of players as intra-state actors, as in a civil war.
-} are of two possible types, high and low.
+Countries\footnote{Players will be referred to as countries, though it could also be appropriate to think of players as intra-state actors, as in a civil war.} are of two possible types, high and low.
 A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
@@
 Similar scenarios have been modeled as credible commitment problems in the bargaining literature.
-Our model can be thought of as a reduced form bargaining model, but it can also be considered somewhat differently -- when trust is the issue to be solved, there are several solutions to conflict.
+Our model can be thought of as a reduced form bargaining model, but it can also be considered somewhat differently.
+That is, when trust is the issue to be solved, there are several solutions to conflict.
 Concessions are one way in which countries can signal their commitment.
@@
 
-Here $T>0$ represents the benefit from the other country playing Trust.
-$D>0$ represents the damages incurred when the other country plays Fight, while $W>0$ is the additional benefit a country receives when it plays Fight itself.
-We assume $T>W-D$ in line with the assumption that the countries play a Prisoner's Dilemma in the stage game.
-
-We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' The assumption $T>W-D$ ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
+Here $T>0$ represents the benefit from a country's negotiating partner playing Trust.
+$D>0$ represents the damages incurred when a country's negotiating partner plays Fight, while $W>0$ is the additional benefit a country receives when it plays Fight itself.
+We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
+This also ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
 
@@
 Because we use grim trigger punishments, there are only 4 interesting paths of play after concessions are given:
-1) Both countries play Trust always, 
-2) Both play Fight always, 
-3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards and 
+1) Both countries play Trust always; 
+2) Both play Fight always; 
+3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards; and 
 4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.
@@
 Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
-Note that because types have different discount rates, the payoffs differ by type, and when ambiguous will be super-scripted to indicate the type (e.g.
-$X_{FT}^h$ represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period).
+Note that because types have different discount factors, the payoffs differ by type, and when ambiguous will be super-scripted to indicate the type, e.g.
+$X_{FT}^h$ represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period.
 
@@
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
-Consider for instance oscillating every other period between (Trust,Trust) and (Fight,Fight) with a grim trigger War threat.
+Consider for instance oscillating every other period between (Trust,Trust) and (Fight,Fight) with a grim trigger ``War'' threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
-These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as most proofs for this section.
+These are also always payoff dominated by at least one of the other equilibria discussed and thus 	are not attractive.} The Appendix provides a thorough analysis of the various equilibria as well as most proofs.
 
 \subsection{Pooling equilibrium}
-In the \emph{pooling equilibrium}, both countries do not give concessions in period 0, then always play Fight in every period beginning with period 1. 
+In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Fight in every period beginning with period 1.
 Countries continue to doubt, doing nothing to bridge the credibility gap, and thus not cooperating.
@@
 These long lasting stalemates are the types of conflict which are most appropriate for mediator involvement.
-A mediator will be added to the model later to illustrate exactly how mediation can help achieve peace in this context.
+In Section~\ref{sec:med}, we will present a mediation mechanism that illustrates how mediation can help achieve peace in this context.
 In some sense, these are the cases that are most interesting because the international community might play a positive role.
@@
 In period 1, high types play Trust while low types play Fight.
-So long as there are two high types, as revealed by their period 1 play, both countries continue to play Trust in all following periods.
+So long as there are two high types as revealed by their period 1 play, both countries play Trust in all following periods.
 Otherwise, both countries play Fight in all following periods.
@@
 Any country with $\delta_l < \delta^{nc}$ is a low type.
-This means that two high types---and only two high types---can sustain the Peace outcome in a simple repeated game.
-
-In this equilibrium, two mutually distrustful countries behave as if they trust anyway, taking a risk.
+This means that two high types---and only two high types---can sustain the ``Peace'' outcome in a simple repeated game.
+
+In this equilibrium, two mutually distrustful countries \emph{behave} as if they trust each other, taking a risk.
 This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small.
@@
 Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
-Certain relationships between the USA and countries that its wikileaks alienated -- such as Italy -- would be an example.
+Certain relationships between the USA and countries that its WikiLeaks alienated -- such as Italy -- would be an example.
 Italy essentially laughed off the criticisms and reassured the USA of its commitment to their relationship.
@@
 \label{sec:cse}
-The other separating equilibrium of interest involves distrustful countries to using concessions as a way of building trust.
+The other separating equilibrium of interest involves distrustful countries using concessions as a way of building trust.
 We call this the \emph{concessions separating equilibrium}.
@@
 It is also not as risky as the \emph{no-concession separating equilibrium}.
-The concessions are given before more substantive actions, thus concessions are a costly signal that the other country is serious about cooperating.
-Most agreements come with concessions, and in many cases, though not all, they are used as signals.
-The goal is to use this option to avoid continual distrust.
-That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing Peace.
+In this equilibrium, concessions are given before more substantive actions and thus remove the possibility of playing one of the cheating corners of the Prisoner's Dilemma.
+Concessions are a costly signal that the other country is serious about cooperating and can be sued to avoid continual distrust.
+That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing peace.
 
@@
 
-Details of the analysis, which uses standard incentive compatibility constraints, are in the Appendix.
+Details of the analysis are in the Appendix.
 We begin by characterizing the concession (or \emph{gift}) giving behavior of the low type.
@@
 
-A large probability of a high type makes the \emph{no-concessions separating equilibrium} very attractive because the risk of ending up in the cheater's corner of the Prisoner's Dilemma is low and no concessions have to be made.
+A large probability of a high type makes the \emph{no-concessions separating equilibrium} very attractive because the risk of ending up in the cheating corner of the Prisoner's Dilemma is low and no concessions have to be made.
 Conversely, for smaller values of $p$, high types are better off paying the gift to avoid the possibility of being taken advantage of by a low type.
@@
 To be clear, in Sections~\ref{sec:model} and \ref{sec:bench}, the gift only benefits the party who receives it in the period in which it is received, that is, Period 0.
-In this section, we assume that this is an additional value from the gift in each period that the repeated game is played, that is, Period 1 and onward.
-
-The interpretation is that the country which receives the concessions can use them to build up their military or to build up their civil society.
+In this section, we assume that there is an additional value from the gift in each period that the repeated game is played, that is, Period 1 and onward.
+
+The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society.
 Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil society helps the giver in peace.
@@
 
-Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the ``Peace'' outcome will be played.
+Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the ``Peace'' outcome will be played.
 Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
@@
 
-$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5\overline{3},1)$\footnote{Recall that we restrict $p<1$ since there is no imperfect information when only one type is possible.} Thus, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5\overline{3},1)$.\footnote{Recall that we restrict $p<1$ since there is no imperfect information when only one type is possible.} For this range of $\de_h$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+That is, future material value destroys the opportunity for peace.
 \hfill $\blacksquare$
@@
 
-We implement this by allowing countries to choose a scalar $e$ to multiply by their given concession $g$ where $0 \leq e \leq 1$.
-As before, $C(g)= g$ but while the receiving country observes the full concession $g$, the future benefit to the recipient is now only $eg$.\footnote{In a more general model, we could also think of $e$ as a function $E(\cdot)$.
-The argument is still $g$, but instead of a scalar, $E(\cdot)$ can transform $g$ into any concession.
-In particular, this allows the transformation to increase the value of the concession.
-The transformation function $E(\cdot)$ can be thought of as the type of gift, and has a cost to the sender and a direct benefit to the receiver in addition to its signaling value.} Table 3 provides the modified payoffs in the repeated game.
+We implement this assumption by allowing countries to choose a scalar $e \in[0,1]$ by which to multiply their given concession $g$.
+$C(g)= g$ as before, but while the receiving country incurs the full cost of the concession $g$, the future benefit to the recipient is now only $eg$.\footnote{More generally, we could think of $e$ as a function $E(g)$ instead of a simple scalar transformation.
+Without further restriction, $E(\cdot)$ could increase the value of the concession.} Table 3 provides the modified payoffs in the repeated game.
 
@@
 On other other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
-Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type, and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
+Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
 
 Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$.
-As we turn to our result about the incentive compatibility of the \emph{concessions separating equilibria with material value}, we focus on these two cases going forward as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
-This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive constraint.}
+As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
+This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}
 
@@
 
-This means that there are parameters under which Peace cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but Peace can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
-This is one of the reasons that Theorem~\ref{theorem:4} is true.
+This means that there are parameters under which ``Peace'' cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but ``Peace'' can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
+This is part of the substance of Theorem~\ref{theorem:4}.
 
@@
 \end{theorem}
-\emph{Proof}: We invoke Lemmas~\ref{lemma:efficiency} and \ref{lemma:e-patient}.
-There are two reasons for which the parties would choose the \emph{concessions separating equilibrium with inefficient gifts}.
+\emph{Proof}: We invoke Lemmas~\ref{lemma:efficiency} and \ref{lemma:e-patient} as two different reasons for which the parties would choose the \emph{concessions separating equilibrium with inefficient gifts}.
 First, they may be patient enough to separate when gifts are inefficient but not when gifts are efficient (Lemma~\ref{lemma:e-patient}).
@@
 
-Inefficient concessions are optimal under low $p$ (there's a good chance of facing a low type who will use the concession against you) as well as when the benefits from Peace are low relative to the damages from War.
-This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication can also be found in our model.
+Inefficient concessions are optimal when there's a good chance of facing a low type who will use the concession against you (i.e.
+$p$ is small) as well as when the benefits from ``Peace'' are low relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication can also be found in our model.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
@@
 However, putting this difference aside, the inefficiency result can be viewed as similar to that in Prendergast and Stole (2001).
-That is, if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types for entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against oneself in the future.
+That is, if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types from entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against the giver of the concessions in the future.
 
@@
 Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value that can optionally be destroyed.
-As usual, truthful self-revelation requires that the individual rationality and incentive compatibility constraint for each type must be satisfied.
+As usual, truthful self-revelation requires that the incentive compatibility constraint for each type must be satisfied.
 
@@
 \begin{lemma}
-	A manipulative mediator cannot facilitate the most efficient concessions---that is, $e=1$. 
+	A manipulative mediator cannot facilitate the most efficient concessions, i.e. $e=1$ is not incentive compatible under mechanism $M$. 
 	\label{lemma:med}
@@
 \end{theorem}
-\emph{Proof:} (a) Under $M$, the low type incentive constraint can bind without having high types give a concession to low types.
+\emph{Proof:} (a) Under $M$, the low type incentive compatibility constraint can bind without having high types give a concession to low types.
 There is no need then to give inefficient concessions: high types will invest in civil society and improve the giver's welfare and low types will never receive the concession.
@@
 As per Theorem~\ref{theorem:4}, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.
-But because the benefits of giving a concession differ between the types (low types get one period of cheater's payoff, while high types get future peace), the mediator is able to mandate concessions only between declared high types.
+But because the benefits of giving a concession differ between the types (low types get one period of cheating payoff, while high types get future peace), the mediator is able to mandate concessions only between declared high types.
 This means there is no longer a need for inefficient concessions since concessions will never be used against the giver.
@@
 Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Fight in the first period and then every period thereafter by the one-shot deviation principle.
-If both countries play Trust in a period, a Peace equilibrium takes place and both countries continue to play peace in every period with the grim trigger threat of the War equilibrium.
+If both countries play Trust in a period, a ``Peace'' equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
 Low types play Fight in the first period, so a high type that observed Fight being played would respond by playing Fight in period 2 and in all future periods.
@@
 
-If the potential advantages of Peace are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
+If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
 Any player with $\de < \de_h^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
@@
 If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessions-in period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
-A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of War that would occur under pooling.
+A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of the ``War'' outcome that would occur under pooling.
 
@@
 
-High types have the incentive to play Trust only in the Peace equilibrium, which can only be sustained by a pair of high types.
+High types have the incentive to play Trust only in the ``Peace'' equilibrium, which can only be sustained by a pair of high types.
 Both types benefit from the other country playing Trust so all countries have incentive to signal that they are high types if concessions are costless (cheap talk).
@@
 \ee 
- In order to incentivize high types to send nonzero concessions, the high type incentive constraint must not be violated.
+ In order to incentivize high types to send nonzero concessions, the high type incentive compatibility constraint must not be violated.
 That is, the payoff from separating must be higher than the payoff from pooling with the low types.
@@
 
-In order to incentivize high types to send nonzero concessions, the high type incentive constraint must not be violated.
+In order to incentivize high types to send nonzero concessions, the high type incentive compatibility constraint must not be violated.
 That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types.
@@
 Both parties are instructed to give efficient gifts.
-The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the `Peace' equilibrium.
-The low-type player under consideration knows it will defect and end up in a War equilibrium and so invests entirely in the military.
+The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium.
+The low-type player under consideration knows it will defect and end up in a ``War'' equilibrium and so invests entirely in the military.
 %		\begin{multline}

### 2021-01-29 draft.tex
Fill out mediation theorem, but see a mistake in high type IC (to be fixed next)

@@
 %LAKE: The psychological literature as applied in political science spent a lot of time in the 1970s and 1980s focusing on Graduated Reductions in Tensions (GRIT) as a form of confidence building.
-See Debbie LarsonÕs work (sheÕs at Poli Sci, UCLA, I donÕt have the cites handy).
+See Debbie Larson’s work (she’s at Poli Sci, UCLA, I don’t have the cites handy).
 This is clearly relevant to your discussion of the laboratory experiments on p.3.
@@
 This is not well represented by the PD.
-You need to make the link Ð or differentiate Ð what youÕre doing here from the Fearon-Powell models to which you appeal.
+You need to make the link – or differentiate – what you’re doing here from the Fearon-Powell models to which you appeal.
 
@@
 \begin{lemma}
-	If both the \emph{concessions separating equilibrium with efficient concessions} and the \emph{concessions separating equilibrium with inefficient concessions} exist, the \emph{concessions separating equilibrium with efficient gifts} is preferred when both the probability of encountering a high type and the benefit from making peace are sufficiently large.
+	If the \emph{concessions separating equilibrium with efficient concessions} exists, it is preferred to the \emph{concessions separating equilibrium with inefficient gifts} when both the probability of encountering a high type and the benefit from making peace are sufficiently large.
 	\label{lemma:efficiency}
@@
 % \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong. 
-
 The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens $p$ of the time.
@@
 \begin{enumerate}
-		\item[(a)] The mediation mechanism $M$ is incentive compatible when the specified concession is at least as large as $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}$.
-		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
-Equilibria with higher concessions yield strictly lower payoffs.
+		\item[(a)] The mediation mechanism $M$ is incentive compatible for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}$ and $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+		\item[(b)] The mediation mechanism $M$ is incentive compatible for the high type when
+			\begin{itemize}
+				\item[(i)] $\de_h(T+D)\geq W$ and $e(T-W) >1 -\de_h$;
+				\item[(ii)] $\de_h(T+D)\geq W$, $e(T-W) <1 -\de_h$ and the specified concession is less than or equal to $\frac{\de_h(T+D)-W}{1-\de_h - e\left(T +W \right)}$; or
+				\item [(iii)] $\de_h(T+D)\leq W$, $e(T-W) >1 -\de_h$ and the specified concession is greater than or equal to $\frac{\de_h(T+D)-W}{1-\de_h - e\left(T +W \right)}$.
+			\end{itemize}
+		\item[(c)] The mediation mechanism $M$ is always individually rational for the low type.
+If $Te > (1-\de_h)(1-e)$, the high type's individual rationality constraint implies an additional restriction that the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
 \end{enumerate}
@@
 \emph{Proof:} See Appendix.
-
-high type IC:
-$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
 
@@
 %This said, if the paper is really about mediation, then the mediator needs more scrutiny.
-What are the mediatorÕs incentives?
+What are the mediator’s incentives?
 Why should he reveal truthfully what the parties tell him?
@@
 \emph{Proof of Theorem~\ref{theorem:med}:}\\
-For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}.
+(a) For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}.
 So we start from
@@
 \]
-Isolating $g_h$ on the left hand side and gathering terms, we have 
+The right hand side is positive.
+If the left hand side were negative, we would have a negative upper bound on the size of the gift.
+Given the requirement that the gift be non-negative, the low type's incentive constraint cannot be satisfied  in this case.
+Therefore we must assume that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+Using this to isolate $g_h$ on the left hand side and gathering terms, we have
 \begin{equation}
-	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)} = g^M
-	\label{ex:med3}
+	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}
+	\label{eq:med3}
 \end{equation}
-As before, the optimal gift is the one where Expression~\ref{ex:med3} holds with equality.
+If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
+(b) We now turn to the high type, whose incentive compatibility constraint is
+$$pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h $$
+It is always optimal for the high type to invest in civil society when they truthfully reveal and to invest in the military when they lie about their type. Thus the constraint becomes
+\begin{multline*}
+  \frac{p}{1-\de_h}\left(T + Teg \right) - pg +peg+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \\
+	p\left(T + W + Weg +eg + \frac{\de_h}{1-\de_h}\left(W + Weg -D\right)\right) + \frac{1-p}{1-\de_h}\left(W-D\right)
+\end{multline*}
+This simplifies to 
+\begin{equation*}
+  \frac{1}{1-\de_h}\left(T + Teg \right) - g \geq T + W + Weg + \frac{\de_h}{1-\de_h}\left(W + Weg -D\right)
+\end{equation*}
+%\begin{equation*}
+%  T + Teg - ( 1-\de_h)g \geq ( 1-\de_h)\left(T + W + Weg\right) + \de_h\left(W + Weg -D\right)
+%\end{equation*}
+\begin{equation*}
+  T + Teg - ( 1-\de_h)g \geq ( 1-\de_h)T + W + Weg - \de_h D
+\end{equation*}
+%\begin{equation*}
+%  Teg - Weg -( 1-\de_h)g \geq -\de_h T + W - \de_h D
+%\end{equation*}
+\begin{equation}
+  g\left(Te - We -( 1-\de_h)\right) \geq W - \de_h (D+T)
+	\label{eq:med4}
+\end{equation}
+We have four cases to consider depending on signs:
+\begin{itemize}
+	\item [(i)] When $\de_h(T+D)\geq W$ and $e(T-W) >1-\de_h$, then we have a lower bound on the size of the gift that is non-positive, i.e.
+no additional restriction beyond the restrictions needed to satisfy the low type incentive compatibility constraint.
+	\item [(ii)] When $\de_h(T+D)\geq W$ and $e(T-W) <1-\de_h$, Expression~\ref{eq:med4} is a non-negative upper bound on the size of the gift.
+	\item [(iii)] When $\de_h(T+D)\leq W$ and $e(T-W) >1-\de_h$, Expression~\ref{eq:med4} is a non-negative lower bound on the size of the gift, which may be larger or smaller than the bound in Expression~\ref{eq:med3}.
+This is an additional restriction beyond that for the low type only when the bound is larger than the one in Expression~\ref{eq:med3}.
+	\item [(iv)] When $\de_h(T+D)\leq W$ and $e(T-W) <1-\de_h$, Expression~\ref{eq:med4} is a non-positive upper bound on the size of the gift and therefore there is no incentive compatible mechanism.
+\end{itemize}
+(c): The low type's individual rationality constraint is satisfied trivially: the low type gets the `War' payoff forever outside the mechanism; it also gets the `War' payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
+
+For the high type, we need
+\begin{equation*}
+  \frac{p}{1-\de_h}\left(T + Teg \right) - pg +peg+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right)
+\end{equation*}
+This simplifies to
+\begin{equation*}
+  \frac{1}{1-\de_h}\left(T + Teg \right) - g +eg \geq \frac{1	}{1-\de_h}\left(W-D\right)
+\end{equation*}
+\begin{equation*}
+  T + Teg - (1-\de_h)(1-e)g \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + Teg - (1-\de_h)(1-e)g \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g 
+\end{equation*}
+If $Te < (1-\de_h)(1-e)$, this is a negative lower bound on the size of the concession and thus implies no additional restriction.
+If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption.
+If $Te > (1-\de_h)(1-e)$, the high type's individual rationality constraint requires that $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g$.
+
+\hfill $\blacksquare$\\
+
+As before, the optimal gift is the one where Expression~\ref{eq:med3} holds with equality [NOT NECESSARILY BECAUSE OF HIGH TYPE IC].
 We call this value $g^M$.

### 2021-01-29 draft.tex
Fix mediator theorem

--- 2021-01-25 draft.tex
@@
 \begin{enumerate}
-		\item[(a)] The mediation mechanism $M$ is incentive compatible when the specified concession is at least as large as $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}$.
-		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
-Equilibria with higher concessions yield strictly lower payoffs.
+		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}$ and $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type when the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
 \end{enumerate}
@@
 \emph{Proof of Theorem~\ref{theorem:med}:}\\
+(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the `War' payoff forever outside the mechanism; it also gets the `War' payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
+
 For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}.
@@
 \]
-Isolating $g_h$ on the left hand side and gathering terms, we have 
+The right hand side is positive.
+If the left hand side were negative, we would have a negative upper bound on the size of the gift.
+Given the requirement that the gift be non-negative, the low type's incentive constraint cannot be satisfied  in this case.
+Therefore we must assume that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+Using this to isolate $g_h$ on the left hand side and gathering terms, we have
 \begin{equation}
-	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)} = g^M
-	\label{ex:med3}
+	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}
+	\label{eq:med3}
 \end{equation}
-As before, the optimal gift is the one where Expression~\ref{ex:med3} holds with equality.
+If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
+(b) We now turn to the high type, whose incentive compatibility constraint is
+\begin{equation}
+	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h
+	\label{eq:med4}
+\end{equation}
+It is always optimal for the high type to invest in civil society when they truthfully reveal.
+When a high type misrepresents itself as a low type, the mechanism specifies that gifts are exchanged only when there are two high types.
+This means that there will be no concessions when a high type lies.
+This implies that Expression~\ref{eq:med4} is also the individual rationality constraint since outside the mechanism they get the `War' payoff and exchange no concessions.
+
+Thus the constraint for both incentive compatibility and individual rationality is
+\begin{equation*}
+  \frac{p}{1-\de_h}\left(T + Teg \right) - pg +peg+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right)
+\end{equation*}
+This simplifies to
+\begin{equation*}
+  \frac{1}{1-\de_h}\left(T + Teg \right) - g +eg \geq \frac{1	}{1-\de_h}\left(W-D\right)
+\end{equation*}
+\begin{equation*}
+  T + Teg - (1-\de_h)(1-e)g \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + Teg - (1-\de_h)(1-e)g \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g 
+\end{equation*}
+If $Te < (1-\de_h)(1-e)$, this is a negative lower bound on the size of the concession and thus implies no additional restriction.
+If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption.
+If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g$.
+\hfill $\blacksquare$\\
+
+As before, the optimal gift is the one where Expression~\ref{eq:med3} holds with equality [NOT NECESSARILY BECAUSE OF HIGH TYPE IC].
 We call this value $g^M$.

### 2021-01-30 draft.tex
Finish mediator section, including proofs!

@@
 Assume $p = .2$.
-By Theorem~\ref{theorem:2}, separation through concessions is possible.
-
-The patience threshold to separate through concessions is much higher under these parameters when the concessions carry future material value.
+By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.separation through concessions is possible.
+
+The patience threshold to separate through concessions with efficient gifts () is 
+is much higher under these parameters when the concessions carry future material value.
 The minimum patience level required for separation is $\de_h^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = 2.4$, with a minimum separating concession of $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.
@@
 \begin{enumerate}
-		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}$ and $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)},$ with the denominator of this expression strictly positive.
 		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type when the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
@@
 
-The welfare target is again the sum of the high type utilities. Qualitatively, similar results would hold if weighted high- and low-type welfare by the relevant probabilities.
+Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that the mediation mechanism $M$ can do both.
 
 \begin{theorem}
-	Assume that concessions have future material value.
+	When concessions have future material value, the mediation mechanism $M$ can be used to
 	\begin{enumerate}
-		\item[(a)] If future material value can be destroyed, a mediator can be used to eliminate inefficient concessions and improve welfare.
-		\item[(b)] If future material value cannot be destroyed, a mediator can be used to expand the parameter space over which peace can be achieved.
+		\item[(a)] improve welfare by increasing the efficiency of concessions when only a \emph{concessions separating equilibrium with inefficient gifts} is possible; or
+		\item[(b)] improve welfare despite reducing the efficient of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
+		\item[(c)] achieve peace when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
 	\end{enumerate}
-	\label{theorem:5}
+	\label{theorem:medwel}
 \end{theorem}
-\emph{Proof:} (a) Under $M$, the low type incentive compatibility constraint can bind without having high types give a concession to low types.
-There is no need then to give inefficient concessions: high types will invest in civil society and improve the giver's welfare and low types will never receive the concession.
-%The equilibrium separating concession $g^{*M}$ will be larger than $g^*$ in this case because the low type who reports truthfully receives a concession with zero probability:
-%\be
-%g^{*M}= \frac{p(X_{FT}^l-X_{FF}^l)}{1-p}
-%\ee
-High type utility under $M$ is 
-\be
-U_h^M= pX_{TT}+(1-p)X_{FF} = p \left( \frac{T(1+g^{*M})}{1-\de_h} \right) + (1-p) \left(\frac{W-D}{1-\de_h} \right)
-\ee
-because high types exchange concessions of the same value.
-Welfare, defined as high-type utility, is improved because no transfer is made to the low types and no future damage is caused in the case of such a transfer.\footnote{Low types IR constraint still binds and $U_l=X_{FF}$.}
-
-(b) The contraction of the parameter space over which peace could be achieved in Theorem~\ref{theorem:matval} derives from a low type's ability to use concessions to reduce the payoffs of its negotiating partner during a `fight' stage.
-By ensuring that only high types exchange gifts, the mediator removes this expected cost, thus allowing a wider range of high types to separate through concessions.
-The threshold for high types to prefer this separating-through-mediation equilibrium to the pooling on no concessions equilibrium, $\de_h^*$, differs from $\de^1_h$ of Theorem~\ref{theorem:matval} in that it does not have the term $D(1-p)$ (thus is smaller) and the separating concession $g^* = \frac{g^1}{1-p}$.
-Since the concession is in the denominator, this also reduces the value of $\de_h^*$.
-\hfill $\blacksquare$
-
-The low type leader can bluff in the bilateral setting but not when a mediator is present.
-As per Theorem~\ref{theorem:4}, inefficiency is due to the high types giving an inefficient gift in order to separate while still being able to prevent low types from using concessions against the high types.
-But because the benefits of giving a concession differ between the types (low types get one period of cheating payoff, while high types get future peace), the mediator is able to mandate concessions only between declared high types.
-This means there is no longer a need for inefficient concessions since concessions will never be used against the giver.
-Thus, a mediator is able to remove inefficiency in concession giving and bring willing parties to the table to give the gifts necessary to achieve peace.
-
+\emph{Proof:} See Appendix.
+
+To understand part (a), remember that concessions are not exchanged if there is even one report of ``Low.'' Since a concession is only given to the high types and high types invest in civil society, the efficiency of the concession can be increased subject to satisfying the low type's constraints without creating extra damages when matched with a low type.
+High-type welfare is improved because no transfer is made to the low types and there is no threat of future damage from the concession that is made since it goes only to a high type.
+
+Here, inefficiency can be mitigated because the mediator is able to mandate concessions only between declared high types.
+The inefficiency is no longer need to prevent low types from using concessions against high types.
+However, some inefficiency is needed in order to incentivize low types to truthfully reveal their type.
+
+Part (b) may be somewhat surprising.
+Here, a mediator would insert inefficiency when it is not necessary to make peace.
+This happens when the possibility of the low type using concessions against their negotiating partner and the magnitude of the damages that can be imposed are small enough that efficient gifts are possible but large enough that the full efficiency of the gifts has a large, negative impact on welfare.
+The mediator removes the possibility of the future damages, but has to require some inefficiency in order to, gain, incentivize low types to truthfully reveal.
+
+(c) When the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the benefits and damages from investing in military power are too large, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
+By ensuring that only high types exchange gifts, the mediator removes this threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
+This allows types with lower patience levels to separate through the mechanism when those same types cannot separate in the bilateral game with concessions with future material value.
+
+Thus a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve peace.
 The improvements by the mediator here do not rely on the mediator's private information as in the models of Kydd (2003), Rauchhaus (2006) and Smith and Stam (2003).
@@
 \hfill $\blacksquare$\\
-
-As before, the optimal gift is the one where Expression~\ref{eq:med3} holds with equality [NOT NECESSARILY BECAUSE OF HIGH TYPE IC].
-We call this value $g^M$.
-We see here that $g^M$ depends on $e$, which is also the choice of the mediator \emph{and} that we must have $\overline{e} = p - e \left( p + T - \de_l T + W \right) > 0$ in order for the optimal concession to be both positive and finite.
-Both the optimal concession increases toward infinity as $e$ approaches $\frac{p}{p + \left(1-\de_l\right) + W}$, which is the value that makes the denominator of $g^M$ equal to 0.
-
-There are now two cases to consider.
-Depending on parameter values, welfare either increases toward infinity or decreases toward negative infinity as $e \rightarrow \overline{e}$.
-A sufficient condition In the welfare-maximizing mediation mechanism, the mediator sets $e$ to be as large as is feasible given the resources available to be given as concessions as long as $e < \frac{p}{p + \left(1-\de_l\right) + W}$
-
-\[
-	\frac{e p T}{1 - \de_h} > 1
-\]
+\\
+\emph{Proof of Theorem~\ref{theorem:medwel}:}\\
+An example suffices to prove each part.
+	\begin{enumerate}
+		\item[(a)] Let $T = 1$, $W=1$ and $D = 1$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$.
+Let $\de_h = 0.7$ and $\de_l = .3$ and $p = .9$.
+By Theorem~\ref{theorem:2}, separation through concessions is possible.
+
+By Theorem~\ref{theorem:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.979$ so that the \emph{concessions separating equilibrium with efficient gifts} is not possible while the \emph{concessions separating equilibrium with inefficient gifts} is possible.
+
+Using the mediation mechanism $M$ with $e=0.29$ and $g=12.99$, we satisfy both the low type constraint the $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
+Welfare is 5.0784, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
+
+		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$.
+Let $\de_h = \frac{13}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
+By Theorem~\ref{theorem:2}, separation through concessions is possible.
+
+By Theorem~\ref{theorem:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.75$.
+Using Lemma~\ref{lemma:e-patient}, we see that both the \emph{concessions separating equilibrium with efficient gifts} and the \emph{concessions separating equilibrium with inefficient gifts} are possible.
+
+Using the mediation mechanism $M$ with $e=0.18$ and $g=7.7669$, we satisfy both the low type constraint the $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$.
+Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with efficient gifts}.
+		\item[(c)] Let $T = 1$, $W=1$ and $D = 1$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when concessions have no future material value is $\de = \frac{1}{1+1} = 0.5$.
+Let $\de_h = 0.49$ and $\de_l = 0.25$ and $p = \frac{15}{16} = 0.9375$.
+
+Because the calculations are the same for the \emph{concessions separating equilibrium} and the \emph{concessions separating equilibrium with inefficient gifts}, we use Theorem~\ref{theorem:2}(a) to find the patience threshold to separate through concessions with inefficient concessions is $0.5$.
+This combined with Lemma~\ref{lemma:e-patient} shows that neither the \emph{concessions separating equilibrium with efficient gifts} nor the \emph{concessions separating equilibrium with inefficient gifts} is possible.
+
+Using the mediation mechanism $M$ with $e=0$ and $g=1.6$, we satisfy both the low type constraint $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=1.6$ and there is no high type constraint because $0=Te<(1-\de_h)(1-e)=0.0625$.
+Welfare is approximately 0.24, compared to 0 outside the mechanism.
+	\end{enumerate}
+	\hfill $\blacksquare$\\
 

### 2021-01-31 draft.tex
change corollary 2 to theorem 6a parameterization; simplify e-g calculations.R

@@
 Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to peace.
+Perhaps more importantly, the mediator can also sometimes facilitate peace when the negotiating parties cannot achieve it through bilateral interaction.
 
@@
 peace cannot be achieved when there are two high types.
-	\label{theorem:matval}
+	\label{corollary:matval}
 \end{corollary}
@@
 \emph{Proof}: An example suffices as proof.
-Let $T = 10$, $W=8$ and $D = 5$.
-The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de = \frac{8}{10+5} = .5\overline{3}$.
-Let $\de_h = .6$ and $\de_l = .3$.
-Assume $p = .2$.
-By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.separation through concessions is possible.
-
-The patience threshold to separate through concessions with efficient gifts () is 
-is much higher under these parameters when the concessions carry future material value.
-The minimum patience level required for separation is $\de_h^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = 2.4$, with a minimum separating concession of $g^1 = \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = .\overline{63}$.
-Since discount factors can be no larger than 1, we have shown that under this set of parameters, the concessions separating equilibrium when concessions have material value cannot be sustained.
-
-$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5\overline{3},1)$.\footnote{Recall that we restrict $p<1$ since there is no imperfect information when only one type is possible.} For this range of $\de_h$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
+Let $T = 1$, $W=1$ and $D = 1$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de = \frac{1}{1+1} = .5$.
+Let $\de_h = 0.7$ and $\de_l = .3$ and $p = .9$.
+
+By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.
+
+The patience threshold to separate through concessions with efficient gifts is much higher under these parameters when the concessions carry future material value: by Theorem~\ref{theorem:csemv}(a), this threshold is $0.979$.
+Thus the \emph{concessions separating equilibrium with efficient gifts} is \emph{not} possible.
+
+$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5,.979)$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
 That is, future material value destroys the opportunity for peace.
@@
 	\begin{enumerate}
-		\item[(a)] Let $T = 1$, $W=1$ and $D = 1$.
-The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$.
-Let $\de_h = 0.7$ and $\de_l = .3$ and $p = .9$.
-By Theorem~\ref{theorem:2}, separation through concessions is possible.
-
-By Theorem~\ref{theorem:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.979$ so that the \emph{concessions separating equilibrium with efficient gifts} is not possible while the \emph{concessions separating equilibrium with inefficient gifts} is possible.
-
-Using the mediation mechanism $M$ with $e=0.29$ and $g=12.99$, we satisfy both the low type constraint the $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
-Welfare is 5.0784, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
+		\item[(a)] Examine the parameterization in Corollary~\ref{corollary:matval}.
+$\de_h = 0.7$ and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is the same as when there is no material value, i.e.
+0.5.
+By Corollary~\ref{corollary:matval}, the \emph{concessions separating equilibrium with inefficient gifts} is possible.
+Corollary~\ref{corollary:matval} also showed that the \emph{concessions separating equilibrium with efficient gifts} is not possible because the relevant patience threshold of $0.979$ is too high.
+
+Using the mediation mechanism $M$ with $e=0.29$ and $g=12.98$, we satisfy both the low type constraint that $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
+Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
 
@@
 The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$.
-Let $\de_h = \frac{13}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
+Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
 By Theorem~\ref{theorem:2}, separation through concessions is possible.

### 2021-01-31 e-g calculations.R

@@ -1,48 +1,13 @@
-#Parameterization from Theorem 3 in the paper
-T = 10
-W = 8
-D = 5
-p = .2
-dl = .3
-dh = .6
-
-#P2 in notes: e=1 not possible (negative gift)
-#This makes welfare highest under mediator, 2nd under e=0, e=1 not possible
-T = 7
-W = 8
-D = 5
+#P1: WM > W0, e=1 not possible (Corollary 2, Theorem 6(a))
+T = 1
+W = 1
+D = 1
 p = .9
 dl = .3
 dh = .7
 ## Note: reducing dl from 0.3 to 0.4 makes the mediator even more attractive
 
-
-#P3: W1 > W0 and g1 > g0. Welfare under mediator is never positive (asymptotes to -infty) 
-T = 7
-W = 8
-D = 5
-p = .5
-dl = .25
-dh = .7
-
-
-## P4: W0 > W1 > We (mediator). Mediator optimally chooses e=0 anyway (asymptotes to -infty)
-T = 7
-W = 8
-D = 5
-p = .3
-dl = .4
-dh = .9
-
-## P5: Here, W1 > W0 > We (mediator). Mediator optimally chooses e=0.03
-T = 6
-W = 8
-D = 5
-p = .5
-dl = .2
-dh = .9
-
-## P6: make mediator better than e=0: We > W1 > W0. All gifts are positive
+## P2: make mediator better than e=0 or e=1: We > W1 > W0 (Theorem 6(b))
 T = 1
 W = 1
 D = 1
@@ -50,55 +15,60 @@ p = .5
 dl = .5
 dh = 15/16
 
-## P7: Parameters that make e=1 possible, but mediator still better
-T = .5
-W = 1
-D = 1
-p = .5
-dl = .5
-dh = 61/64
-
-## P8: Looking for parameters that make dh_min1 < dh_min0
+## P3: Mediator works while e=0 doesn't (Theorem 6(c))
 T = 1
 W = 1
 D = 1
-p = .5
-dl = .5
-dh = ?61/64
+p = 13/16
+dl = .25
+dh = .49
 
-# grim trigger cutoff
-dh_min_nc = W/((1-p)*W+p*(T+D)) 
-# WM asymptotes to +infty when the following is positive (sufficient condition)
-# suff = e*p*T - 1 + dh
-# problem is that we need the asymptote for e (I think)
[…]

### 2021-01-31 draft.tex
Streamline corollary 2 proof and add intuition

@@
 	\begin{enumerate}
-		\item[(a)] Assume $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$.
+		\item[(a)] Assume $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D$ is positive and $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$.
 Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
@@
 
+The problem with concessions with material value is that when the potential for the low type to invest the concessions in the military can make the high type unwilling to take a chance that it will be matched with a high type because the costs of being matched with a low type are too high.
+
 \begin{corollary}
@@
 $\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5,.979)$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
-That is, future material value destroys the opportunity for peace.
+That is, future material value can destroy the opportunity for peace.
 \hfill $\blacksquare$
+
+Comparative statics provide intuition for why using concessions with future material value makes it harder to make peace.
+The patience threshold is decreasing in $T$, that is, the benefit from the additional future value when a high type achieves `Peace' with another high type who used the material value for civil society.
+Similarly, the threshold is increasing in $D$ because the magnitude of future damages from pairing with a low type increases.
+Perhaps less obvious is the impact of $W$: here the threshold is again increasing.
+This is because the high type's own temptation to not give a gift and to use a received concession for military purposes increases in $W$.
+
+When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type.
+Finally, and perhaps surprisingly, the patience threshold is increasing in $p$.
+This happens because the size of gift must be increased in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}
+
+Thus only an increase in the benefit from `Peace' and an increase in the low type's patience level make it easier to achieve `Peace' when gifts have future material value.
+Increases in all other parameters make it harder to achieve `Peace.'
 
@@
 \begin{equation*}
-	\left(1-\de_l\right)g^1\left(1 - pT \right) \geq \left(1-\de_l\right)p\left(D +	 T\right) - (1-p) Dg^1
-\end{equation*}
+	\left(1-\de_l\right)g^1\left(1 - pT \right) + (1-p) Dg^1\geq \left(1-\de_l\right)p\left(D +	 T\right)
+\end{equation*}
+We have assumed that $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D > 0$ so we can divide to get
 %\begin{equation*}

### 2021-02-01 draft.tex
remove claim about effect of 0<e<1 on high type IC

@@
 Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$.
-As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.
-This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}
+As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.} %This is not at all obvious because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}
 
@@
 Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
-
 		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$.

### 2021-02-01 draft.tex
standardize use of superscripts and subscripts on \de and g

@@
 $e<1$.
-The constraint that determines how efficient concessions can be comes from the low type incentive compatibility constraint.
-As in the concessions separating equilibria, this shows up in the optimal concession size.
+The low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism; this puts an upper bound on how efficient concessions can be.
+In some cases, the high type incentive constraint also provides an upper bound on the size of the concession, which puts a lower bound on efficiency.
 
@@
 
-\begin{comment}
-\begin{lemma}
-	From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.
-	\label{lemma:2}
-\end{lemma}
-\emph{Proof}: Because $W\geq0$, the dominant stage game action for all types is to play Fight.
+%\begin{lemma}
+%	From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.
+%	\label{lemma:2}
+%\end{lemma}
+%\emph{Proof}: Because $W\geq0$, the dominant stage game action for all types is to play Fight.
 Playing Trust is only possible in equilibrium where there is punishment for playing Fight.
@@
 \hfill $\blacksquare$\\
-\end{comment}
 
@@
 \begin{equation*}
-  p\left(\frac{T}{1- \delta_i}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_i} \right)\geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)\frac{W-D}{1- \delta_h}
+  p\left(\frac{T}{1- \delta}\right) +(1-p)\left({-D}+\frac{\delta(W-D)}{1- \delta} \right)\geq p \left(T + W + \frac{\de}{1-\de}(W-D)\right) +(1-p)\frac{W-D}{1- \delta}
 \end{equation*}
@@
 \begin{equation*}
-  pT \geq p \left((1-\de_h)(T + W) + \de_h (W-D)\right) + (1-\de_h)(1-p)W
-\end{equation*}
-\begin{equation*}
-  pT \geq pT -p\de_hT +pW -p\de_h W + p \de_h W -p \de_h D  + W -\de_h W -pW + p\de_hW
-\end{equation*}
-\begin{equation*}
-  p\de_hT +p \de_h D + \de_h W - p\de_hW  \geq W 
+  pT \geq p \left((1-\de)(T + W) + \de (W-D)\right) + (1-\de)(1-p)W
+\end{equation*}
+\begin{equation*}
+  pT \geq pT -p\de T +pW -p\de W + p \de W -p \de D  + W -\de W -pW + p\de W
+\end{equation*}
+\begin{equation*}
+  p\de T +p \de D + \de W - p\de W  \geq W 
 \end{equation*}
 \be
-	\delta_h \geq \frac{W}{(1-p)W + p(T+D)}
+	\delta \geq \frac{W}{(1-p)W + p(T+D)} = \de^{nc}
 	\label{eq:ncse}
@@
 
-If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \frac{W}{(1-p)W + p(T+D)} = \de_h^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
-Any player with $\de < \de_h^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
+If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
+Any player with $\de < \de_{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
 Thus we call these countries low types for purposes of this equilibrium.
@@
 %p_1(\frac{T+D-W}{1-\delta_h}-p_2(T+D)\geq 0. point is the p's arent the same; i might have gotten them backwards. simplified this is:
-\delta_h \geq \frac{W}{T+D}
+\delta_h \geq \frac{W}{T+D} = \de^c
 \ee
@@
 Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positive and so we can divide through by both and multiply both sides by $W$:
-$$\de_h^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de_h^{c} $$
-
-In the case that both types of equilibria exist, i.e. $\de_h \geq \de_h^{nc}$, the high types will prefer the \emph{concessions separating equilibrium} if and only if
+$$\de^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de^{c} $$
+
+In the case that both types of equilibria exist, i.e. $\de_h \geq \de^{nc}$, the high types will prefer the \emph{concessions separating equilibrium} if and only if
 \begin{equation*}
@@
 \emph{Proof of Theorem \ref{theorem:csemv}:}\\
-In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g^1$ is a low type gift.
+In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low type gift.
 In this case, the binding incentive compatibility constraint is the low type IC constraint, which when simplified to allow $g_l=0$ following Lemma~\ref{lemma:3} is:
 \begin{equation}
-	pg^1 +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g^1+pg^1
+	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h
 	\label{eq:matval1}
@@
 The $\al_i$'s vary depending on the situation.
-On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg^1$).
+On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$).
 Then (Fight, Fight) is played, and the payoffs depend on whether this low type is facing a high type or a low type because the implications for future material value are different.
@@
 With probability $(1-p)$ there were no concessions given by either side.
-The left side of Expression~\ref{eq:matval1} is then $pg^1 + \frac{1}{1-\de_l}\left[p(W+Wg^1-D) + (1-p)(W-D) \right]$.
+The left side of Expression~\ref{eq:matval1} is then $pg_h + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right]$.
 
@@
 With probability $(1-p)$, the low type's gift goes to another low type who invests in the military and low type does not receive a gift.
-So the right hand side of Expression~\ref{eq:matval1} becomes $-g^1 + pg^1 + p\left(T + Tg^1 +W + Wg^1 + \frac{\de_l}{1-\de_l}\left(W + Wg^1-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg^1 \right) \right)$.
+So the right hand side of Expression~\ref{eq:matval1} becomes $-g_h + pg_h + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)$.
 
@@
 %\begin{multline*}
-%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg^1-D) + (1-p)(W-D) \right] \geq \\
-%-g_1 + pg_1 + p\left(T + Tg^1 +W + Wg^1 + \frac{\de_l}{1-\de_l}\left(W + Wg^1-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg^1 \right) \right)
+%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right] \geq \\
+%-g_1 + pg_1 + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)
 %\end{multline*}
 \begin{equation*}
-	g^1 + p(W+Wg^1-D) \geq p\left(T + Tg^1 +W + Wg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
+	g_h + p(W+Wg_h-D) \geq p\left(T + Tg_h +W + Wg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
 \end{equation*}
 %\begin{equation*}
-%	g^1 - pD \geq p\left(T + Tg^1 \right) + (1-p)\left( \frac{-Dg^1}{1-\de_l}  \right)
+%	g_h - pD \geq p\left(T + Tg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
 %\end{equation*}
 \begin{equation*}
-	\left(1-\de_l\right)g^1\left(1 - pT \right) + (1-p) Dg^1\geq \left(1-\de_l\right)p\left(D +	 T\right)
+	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h\geq \left(1-\de_l\right)p\left(D +	 T\right)
 \end{equation*}
@@
 %\begin{equation*}
-%	\left(1-\de_l\right)g^1\left(1 - pT \right) + (1-p) Dg^1 \geq \left(1-\de_l\right)p\left(D +	 T\right)
+%	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h \geq \left(1-\de_l\right)p\left(D +	 T\right)
 %\end{equation*}
 \begin{equation}
-	g^1 \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g_h^1
+	g_h \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g^1
 	\label{eq:matval2}
@@
 
-This implies that the high types need give a gift at least as large as $g_h^1$ in order to separate from the low type; that is, if the high types give a gift smaller than $g_h^1$, the low types will have an incentive to mimic the high type and the separating equilibrium will be destroyed.
+This implies that the high types need give a gift at least as large as $g^1$ in order to separate from the low type; that is, if the high types give a gift smaller than $g^1$, the low types will have an incentive to mimic the high type and the separating equilibrium will be destroyed.
 
@@
 The expected separation utility for the high type under the game with material value that can be destroyed is
-$$\frac{1}{1-\de_h}\left\{pT(1+eg^1) + (1-p)(W-D(1+eg^1))\right\} - (1-p)g^1$$
+$$\frac{1}{1-\de_h}\left\{pT(1+eg_h) + (1-p)(W-D(1+eg_h))\right\} - (1-p)g_h$$
 The derivative with respect to $e$ is
-$$\frac{1}{1-\de_h}\left\{pTg^1 - (1-p)Dg^1)\right\}$$
+$$\frac{1}{1-\de_h}\left\{pTg_h - (1-p)Dg_h)\right\}$$
 This is non-negative when $pT \geq (1-p)D$.
@@
 If the left hand side were negative, we would have a negative upper bound on the size of the gift.
-Given the requirement that the gift be non-negative, the low type's incentive constraint cannot be satisfied  in this case.
+Given the requirement that the gift be non-negative, the low type's incentive compatibility constraint cannot be satisfied  in this case.
 Therefore we must assume that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
@@
 \begin{equation*}
-  \frac{p}{1-\de_h}\left(T + Teg \right) - pg +peg+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right)
+  \frac{p}{1-\de_h}\left(T + Teg_h \right) - pg_h +peg_h+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right)
 \end{equation*}
@@
 \begin{equation*}
-  \frac{1}{1-\de_h}\left(T + Teg \right) - g +eg \geq \frac{1	}{1-\de_h}\left(W-D\right)
-\end{equation*}
-\begin{equation*}
-  T + Teg - (1-\de_h)(1-e)g \geq W-D
-\end{equation*}
-\begin{equation*}
-  T + Teg - (1-\de_h)(1-e)g \geq W-D
-\end{equation*}
-\begin{equation*}
-  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g 
+  \frac{1}{1-\de_h}\left(T + Teg_h \right) - g_h +eg_h \geq \frac{1	}{1-\de_h}\left(W-D\right)
+\end{equation*}
+\begin{equation*}
+  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
+\end{equation*}
+\begin{equation*}
+  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g_h 
 \end{equation*}
@@
 If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption.
-If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g$.
+If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g_h$.
 \hfill $\blacksquare$\\
@@
 
-Using the mediation mechanism $M$ with $e=0.29$ and $g=12.98$, we satisfy both the low type constraint that $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
+Using the mediation mechanism $M$ with $e=0.29$ and $g_h=12.98$, we satisfy both the low type constraint that $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
 Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
@@
 
-Using the mediation mechanism $M$ with $e=0.18$ and $g=7.7669$, we satisfy both the low type constraint the $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$.
+Using the mediation mechanism $M$ with $e=0.18$ and $g_h=7.7669$, we satisfy both the low type constraint the $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$.
 Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with efficient gifts}.
@@
 
-Using the mediation mechanism $M$ with $e=0$ and $g=1.6$, we satisfy both the low type constraint $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=1.6$ and there is no high type constraint because $0=Te<(1-\de_h)(1-e)=0.0625$.
+Using the mediation mechanism $M$ with $e=0$ and $g_h=1.6$, we satisfy both the low type constraint $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=1.6$ and there is no high type constraint because $0=Te<(1-\de_h)(1-e)=0.0625$.
 Welfare is approximately 0.24, compared to 0 outside the mechanism.

### 2021-02-02 draft.tex
standardize math punctuation throughout appendix

@@
 If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
-Any player with $\de < \de_{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
+Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
 Thus we call these countries low types for purposes of this equilibrium.
@@
 That is, the payoff from separating must be higher than the payoff from pooling with the low types.
+$$pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h$$
+In terms of fundamentals, we have
 \be
-	pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h
+	p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}
 	\label{eq:cse3}
 \ee
-
-$$p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}$$
-\begin{multline*}
-	\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - g^1 \geq \\
-	\frac{1}{1-\de_h}\left[p(W+Wg^1-D) + (1-p)(W-D) \right]
-\end{multline*}
 Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a concessions separating equilibrium to exist:
-\be
-pX_{TT}^h-pX_{FF}^h - p(X_{FT}^l-X_{FF}^l) \geq 0
-\ee
-In terms of fundamentals, the condition for a concessions separating equilibrium to exist is:
 \be
@@
 \ee
-That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$\\
+That is, we simply need the high types to have a sufficiently large discount factor. \hfill $\blacksquare$\\
 \\
 \emph{Proof of Corollary~\ref{corollary:1}:}\\
-To show that the patience threshold for the \emph{no concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption
-$$T+D>W.$$
-We can multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
+To show that the patience threshold for the \emph{no concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$
+
+We multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
 $$(T+D) > (1-p)W +p(T+D).$$
@@
 This occurs when Expression~\ref{eq:matval2} holds with equality.
-That is, the optimal high type gift in this equilibrium is $g^1 \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
+That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
 Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils.
@@
 Note that if the high type pools with the low type, it knows it will be playing Fight and so invests any concession received in military buildup.
-\begin{multline*}
-	\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 \geq \\
-	\frac{1}{1-\de_h}\left[p(W+Wg^1-D) + (1-p)(W-D) \right] +pg^1
+\begin{equation*}
+	p\frac{T+Tg^1}{1-\de_h} + (1-p)\frac{W-D-Dg^1}{1-\de_h} - (1-p)g^1 \geq 
+	p\frac{W+Wg^1-D}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} +pg^1
 \label{eq:matval3}
-\end{multline*}
+\end{equation*}
 
 Simplifying, we have
-$$pT(1+g^1) + (1-p)(W-D(1+g^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
-$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
+$$p(T+Tg^1) + (1-p)(W-D-Dg^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
+%$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
 $$\de_h g^1 \geq p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1$$
@@
 The expected separation utility for the high type under the game with material value that can be destroyed is
-$$\frac{1}{1-\de_h}\left\{pT(1+eg_h) + (1-p)(W-D(1+eg_h))\right\} - (1-p)g_h$$
+$$p\frac{T+Teg_h}{1-\de_h} + (1-p)\frac{W-D-Deg_h}{1-\de_h} - (1-p)g_h$$
 The derivative with respect to $e$ is
@@
 If the left hand side were negative, we would have a negative upper bound on the size of the gift.
-Given the requirement that the gift be non-negative, the low type's incentive compatibility constraint cannot be satisfied  in this case.
-Therefore we must assume that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
+Given the requirement that the gift be non-negative, the low type's incentive compatibility constraint cannot be satisfied when the left hand side is negative and we must have that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
 Using this to isolate $g_h$ on the left hand side and gathering terms, we have

### 2021-02-02 notes.tex
Add notes on 0<e<1 cse case

@@
 
+The question is this: if $\de^c < \de_h < \de^1$, would the high types ever want to choose an intermediate value of $e$?
+The idea is that $0<e<1$ could loosen the incentive constraint from the $e=0$ case.\\
+
 High type's IC with potentially interior $e$
@@
 
-I need to add calculations for $g$ from my written notes
+Now, what would $g$ need to be?
+Substituting into Expression eq:matval1 from draft.tex and simplifying, we have
+\begin{multline*}
+	peg + \frac{1}{1-\de_l}\left[p(W+Weg-D) + (1-p)(W-D) \right] \geq \\
+-g + peg + p\left(T + Teg +W + Weg + \frac{\de_l}{1-\de_l}\left(W + Weg-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Deg \right) \right)
+\end{multline*}
+\begin{equation*}
+	-\frac{pD}{1-\de_l} \geq -g + p\left(T + Teg +\frac{\de_l}{1-\de_l}\left(-D \right) \right) + \left( \frac{1-p}{1-\de_l}\left(-Deg \right) \right)
+\end{equation*}
+\begin{equation*}
+	(1-\de_l) g-pD \geq p\left((1-\de_l)(T + Teg) -\de_l D \right) + \left( (1-p)\left(-Deg \right) \right)
+\end{equation*}
+\begin{equation*}
+	(1-\de_l) g\geq p(1-\de_l)(T + Teg+D) + \left( (1-p)\left(-Deg \right) \right)
+\end{equation*}
+\begin{equation*}
+	(1-\de_l) g + (1-p)\left(Deg \right)-p(1-\de_l)Teg\geq p(1-\de_l)(T +D) 
+\end{equation*}
+\begin{equation*}
+	g \left[(1-\de_l)(1-pTe) + (1-p)De \right]\geq p(1-\de_l)(T +D) 
+\end{equation*}
+As long as $(1-\de_l)(1-pTe) + (1-p)De>0$, we have
+\begin{equation*}
+	g \geq \frac{p(1-\de_l)(T +D) }{(1-\de_l)(1-pTe) + (1-p)De}
+\end{equation*}
+Compared to the constraint on the gift when $e=1$, when $e<1$, $-pTe$ makes the denominator larger and $De$ makes the denominator smaller. Not clear what the balance will be.
+\begin{itemize}
+	\item If the constraint gets tighter, you have to increase $g$.
+	\item But remember that if the constraint gets looser, you can choose same $g$ if you want.
+\end{itemize}
+It's therefore not clear that we should just stick $g = \frac{p(1-\de_l)(T +D) }{(1-\de_l)(1-pTe) + (1-p)De}$ into the incentive constraint
+\begin{itemize}
+	\item For a particular example, we can wade through this to find the optimal $e$, but it might also involve letting $g$ get larger
+	\item This is something I never considered in the $e=1$ and $e=0$ cases. I don't think it matters in $e=0$ case (check), but it might in $e=1$ case 
+\end{itemize}
 

### 2021-02-02 notes.tex
add notes on cse vs grim trigger welfare

@@
 \section{No material value CSE vs. repeated game}
+\subsection{Patience threshold}
 Minimum $\de$ for $e=0$ CSE / no material value case to be sustainable. Remember that $g^0 = p(T+D)$
@@
 							\end{itemize}
+
+\subsection{Welfare}
+Welfare under no material value CSE is always at least as large as welfare under repeated-game grim trigger
+\[
+  p\frac{T}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} - p(T+D) \geq p\frac{T}{1-\de_h} + (1-p)\frac{-D}{1-\de_h} + (1-p)\frac{\de_h}{1-\de_h}(W-D)
+\]
+\[
+  (1-p)\frac{W-D}{1-\de_h} - p(T+D) \geq (1-p)\frac{-D}{1-\de_h} + (1-p)\frac{\de_h}{1-\de_h}(W-D)
+\]
+\[
+  (1-p)(W-D) - p(1-\de_h)(T+D) \geq -(1-p)D + (1-p)\de_h(W-D)
+\]
+\[
+  (1-p)W - p(1-\de_h)(T+D) \geq (1-p)\de_h(W-D)
+\]
+\[
+  (1-p)W -(1-p)\de_h(W-D)\geq  p(1-\de_h)(T+D) 
+\]
+\[
+  W-pW - \de_hW+\de_hD +p\de_hW-p\de_hD\geq  pT + pD -p\de_hT - p\de_hD 
+\]
+\[
+  W-pW - \de_hW+\de_hD +p\de_hW \geq  pT + pD -p\de_hT 
+\]
+\[
+  W - \de_hW+\de_hD +p\de_hW \geq  pT + pD + pW -p\de_hT 
+\]
+Because $T +D > W$, we have 
+\[
+  W - \de_hW+\de_hD +p\de_hW \geq  pT + pD + pW -p\de_hT > -p\de_hT 
+\]
+\[
+  (1-\de_h)W +\de_hD +p\de_hW + p\de_hT > 0 
+\]
+Each term on the left is strictly larger than 0, so this statement is always true.
 

### 2021-02-03 draft.tex
integrate written notes into notes.tex and shorted proof of Lemma 3

@@
 \begin{multline*}
-	\frac{W}{T+D} \geq \frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
-	+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} \\
-	= \frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+	\frac{W}{T+D} \geq %\frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
+	%+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = \\
+	\frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
 	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
@@
 \end{multline*}
-Canceling the first two terms as well as the third and last terms, we have
-\begin{multline*}
-	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
-	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{multline*}
-Expanding and canceling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
+Canceling the first two terms as well as the third and last terms and then 
+%\begin{multline*}
+%	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
+%	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 %T\right)}
+%\end{multline*}
+expanding and canceling out the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
 %\begin{multline*}

### 2021-02-03 notes.tex
integrate written notes into notes.tex and shorted proof of Lemma 3

@@
 						\begin{itemize}
-							\item THIS ASSUMES {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
-								\begin{itemize}
-									\item Note that if we set $e=0$, this is a very simple constraint on $g$
-										\begin{equation}
-											g \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p}
-											\label{eq:g3}
-										\end{equation}
-								\end{itemize}
 							\item $T+D$, $1 - \de $ non-negative by assumption $\Rightarrow$ RHS of Expression~\ref{eq:g1} non-negative
 								\begin{itemize}
-									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$. AGAIN WITH THE NEGATIVE GIFTS.
-								\end{itemize}
+									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$.
+									\item SO WE MUST ASSUME {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
+								\end{itemize}
+							\item In the complicated environment of the mechanism, I haven't actually shown that the minimum low type IC gift is optimal
 							\item To compare to the optimal gift size in the other sections:
@@
 
-\subsubsection{Welfare under Mediator vs. e=0}
+\subsubsection{High type incentive constraint}
+\begin{equation}
+	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h 
+	%\label{eq:med4}
+\end{equation}
+Turns out to be same as high type individual rationality constraint.\\
+
+If a high type lies, there would be at least one low type, and thus no gifts and they would fight forever. So there's no investment choice for high type who lies.
+\begin{itemize}
+	\item This is all in the paper now.
+\end{itemize}
+
+How to choose the optimal $e$ when both the low type and high type IC bind is still done informally in R.
+
+\subsubsection{Welfare under Mediator vs. CSE with inefficient gifts}
 \label{sec:WM0}
+I tried to derive a necessary condition relating the IC/IR constraints to this welfare comparison but didn't find anything easily.
+I think I explored this in Mathematica, but I'd need to look more carefully through the Mathematica files.
+
 Here I'll try to derive a general result for when the welfare under a mediator would be higher than under $e=0$ separating with concessions equilibrium. \\
@@
 											\item This is a sufficient condition, not necessary. It only looks at the direct impact of the gift; there is another positive term that this ignores
+												\begin{itemize}
+													\item This makes welfare increasing in the gift, holding everything else constant, WHEN GIFT IS SET TO BE MINIMUM LOW-TYPE GIFT. I haven't show that's the optimal thing to do.
+												\end{itemize}
 											\item The welfare impact of the future value $(epT)$, summed over the whole future $\left(\frac{e p T}{1-h}g^M\right)$ has to be greater than the cost of giving the gift ($g^M$). 

### 2021-02-13 notes.tex
rename mathematica file

@@
 
-We compare them to find when the welfare under the mediator is larger:
-	\begin{multline*}
-		\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq \\
-		\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
-	\end{multline*}							
-Eliminating common terms:
-	\begin{equation*}
-		\frac{1}{1-\de_h}\left\{pTeg_M \right\} - \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
-	\end{equation*}	
-Rearranging:
-	\begin{equation*}
-		\frac{1}{1-\de_h}\left\{pTe - 1 \right\} \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} \geq - p(T+D)
-	\end{equation*}
-
-Rearranging:
-\begin{equation*}
-		\frac{pTeg_M}{1-\de_h} \geq \frac{\left(1 - \de_l \right) \left( T + D \right)}{p - e \left( p + T - \de_l T + W \right)} - p(T+D)
-	\end{equation*}	
-This is what I implement in Mathematica Notebook ``We greater than W0.nb''
-\begin{itemize}
-	\item So far, I've been able to find an instance that satisfies this equation: e = 11/64, $\de_h = 15/16$, $\de_l = 0.5$, $p = 0.5$, T = 1, W = 1, D = 1
-	\item This is ``Parameterization 6'' above and in R file ``e-g calculations.R''
+Ultimately I gave up on this because Mathematica couldn't solve the expressions with welfare under the mediator -- I believe this is because of the asymptote.
+\begin{itemize}
+	\item Instead, I looked for a sufficient condition to make welfare increase to the left of the asymptote (i.e. when the gift is positive).
 \end{itemize}

### 2021-02-16 notes.tex
clean up calculations file and remove unused parameterizations from notes

@@
 \subsubsection{Check with some parameterizations}								
-								Parameterization that is in the paper now:
+Parameterization that was in the previou version of the paper:
 									\begin{itemize}
@@
 \vskip.2in	
-							Now let's try the same parameterization with $p=0.9$.
-									\begin{itemize}
-										\item Maximum $e$ from Expression~\ref{eq:g5}:
-											\[
-											  0.9 - \frac{\left(1 - 0.3 \right) \left( 10 + 5 \right)}{g} \geq e \left( 0.9 + 10 - 0.3\cdot 10 + 8 \right)
-											\]
-											\[
-											  0.9 - \frac{0.7 \left( 15 \right)}{g} \geq e \left( 11.9 \right)
-											\]
-											\[
-											  \frac{0.9}{11.9} - \frac{0.7 \left( 15 \right)}{11.9g} \geq e 
-											\]
-											\[
-											  0.07563 - \frac{8.8235}{g} \geq e 
-											\]
-										To keep $e \geq 0$, we need $g \geq 116.66$.
-This is still nearly an order of magnitude larger than $W$, and both the optimal gifts when $e=0$ of 13.5 and when $e=1$ of $\frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D} = \frac{0.9(0.7)(15)}{0.7 \cdot (1-0.9)+(.1)5} = \frac{0.63\cdot15}{0.7 \cdot 0.1+.5} = 16.58$.
-									\end{itemize}
-
-\vskip.3in
-``Parameterization 2'': goal was to make welfare higher under mediator; $We > W0$ and $e=1$ is not incentive compatible
-\begin{itemize}
-	\item \color{orange} T = 7, W = 8, D = 5, p = .9, $\de_l = .3$, $\de_h = .6$
-	\item Maximum $e$ from Expression~\ref{eq:g5}
-	  $$0.9 - \frac{\left(1 - 0.3 \right) \left( 7 + 5 \right)}{g} \geq e \left( 0.9 + 7 - 0.3 \cdot 7 + 8 \right)$$
-		$$0.9 - \frac{8.4}{g} \geq e \left(18 \right)$$
-		$$0.05 - \frac{0.466}{g} \geq e $$
-	\item The highest welfare comes from $e=.06$, which implies $g = 116.67$ (see e-g calculations.R)
-\end{itemize}
-
-\vskip.2in
-Parameterization 3: $W1 > W0$ and $g1 > g0$. Welfare under mediator is never positive. 
-\begin{itemize}
-	\item $T = 7, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .25, \ \de_h = .6$
-\end{itemize}
-
-\vskip.2in
-Parameterization 4: $W0 > W1 > We$ (mediator). Mediator optimally chooses e=0 anyway
-\begin{itemize}
-	\item $T = 7, \ W = 8, \ D = 5, \ p = .3, \ \de_l = .4, \ \de_h = .9$
-\end{itemize}
-
-\vskip.2in
-Parameterization 5: $We > W1 > W0$. Asymptote at $e = 03759...$ (Was incorrect before I understood the asymptote: $W1 > W0 > We$ (mediator). Mediator optimally chooses $e=0.03$(
-\begin{itemize}
-	\item $T = 6, \ W = 8, \ D = 5, \ p = .5, \ \de_l = .2, \ \de_h = .9$
-\end{itemize}
-
-\vskip.2in
-Parameterization 6: $We > W1 > W0$, $54 > 7.33 > 7$. Mediator optimally chooses $e=0.24$ (0.25 is the asymptote). Optimal gift is 50, effective gift is 12, vs. $g1 = .667$ and $g0 = 1$
+In the version sent to the JCR, I used three parameterizations; the calculations are done in ``e-g calculations.R'' Here, for instance, is Parameterization 2: $We > W1 > W0$, $54 > 7.33 > 7$.
+Mediator optimally chooses $e=0.24$ (0.25 is the asymptote).
+Optimal gift is 50, effective gift is 12, vs.
+$g1 = .667$ and $g0 = 1$
 \begin{itemize}
 	\item $T = 1, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 15/16=0.9375$
-\end{itemize}
-
-\vskip.2in
-Parameterization 7: $We > W0 > W1$, $42.33 > 4.96 > 2.83$. Mediator optimally chooses $e=0.28$ (0.28571 is the asymptote). Optimal gift is 75, effective gift is 21, vs. $g1 = .428$ and $g0 = .75$
-\begin{itemize}
-	\item $T = 0.5, \ W = 1, \ D = 1, \ p = .5, \ \de_l = .5, \ \de_h = 61/64=0.953125$
 \end{itemize}
@@
 							\begin{itemize}
-								\item When $e=1$ (``W1''): $\frac{1}{1-\de_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
-									\begin{itemize}
-										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
-										\item \color{orange} Parameterization 2: $g^1$ is negative, creates negative upper bound for $\de_h$. Separating with concessions equilibrium can't be sustained.
-									\end{itemize}
-								\item When $e=0$ (``W0''): $\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
-									\begin{itemize}
-										\item \color{red} Parameterization in the paper: welfare is 8; gift is 3
-										\item \color{orange} Parameterization 2: welfare is 5.7; gift is 10.8
-									\end{itemize}
-								\item When $0<e<1$ under a mediator (``WM''): $\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
+								\item When $e=1$ (``W1''): $\frac{1}{1-\de_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - (1-p)\frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
+								\item When $e=0$ (``W0''): $\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)(T+D)$
+								\item When $0<e<1$ under a mediator (``WM''): $\frac{1}{1-\de_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - (1-e)g_M$
 									\begin{itemize}
@@
 										\item Also $pg - \left(1 - \de \right) \left( T + D \right) \geq 0$ ($e$ version; this is WEAKER than the condition on $e$)
-										\item \color{red} For the parameterization in the paper, welfare is negative for $e=0$ and $e=0.01$, the only values of $e$ that lead to non-negative gifts; gifts range from 52.5 to 218.75	
-										\item \color{orange} Parameterization 2: welfare is 10.083 at optimal gift-efficiency $e=0.06$, $g = 116.67$, $eg = 7$
-											\begin{itemize}
-												\item Compared to $e=0$, welfare (gross of gift) goes up from 16.5 to 126.75.
-The entire difference is due to the positive effect of the material value of the gift (the full term is $\frac{1}{1-\de_h}pTeg$).
-The effective gift is $7$, which is much larger than the 1 in $\frac{1}{1-\de_h}pT\cdot 1$ that is there in both terms.
-												\item The increase in the size (cost) of the gift from 10.8 to 116.67 is smaller than the increase in gross-of-gift welfare
-											\end{itemize}
-									\end{itemize}
-							\end{itemize}
-
-			\vskip.2in
-			There are six cases of welfare ordering: \\
-			\vskip.1in
-				\begin{tabular}{ l c c }
-					\un{Ordering}       & \un{$WM < 0$} & \un{$WM > 0$} \\
-					$WM > W1 > W0$ &  & P6 \\
-					$WM > W0 > W1$ &  & P2 (W1 not IC) \\
-					$W1 > WM > W0$ &  &  \\
-					$W1 > W0 > WM$ & P3 & P5 \\
-					$W0 > W1 > WM$ & P1 (paper) & P4 \\
-					$W0 > WM > W1$ &    &
-				\end{tabular}
-				P5 result is wrong: $WM \Rightarrow \infty$.
-					\begin{itemize}
+
+									\end{itemize}
 								\item It's going to be very hard to find WM as intermediate. It has to be a case where it asymptotes to $-\infty$ and choosing $e=0$ is optimal anyway.
-						\item It would be nice to show that it's possible to want to pick $e=0$ under mediator 
 							\end{itemize}
@@
 			\begin{itemize}
-					\item Need to say clearly that $e=1$ doesn't work in a lot of situations
-					\item Can I do new mediator theorem in the same form as the one that's currently in the paper?
 					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is

### 2021-02-16 e-g calculations.R

@@ -1,11 +1,13 @@
-#P1: WM > W0, e=1 not possible (Corollary 2, Theorem 6(a))
+# These are the parameterizations and calculations for the version of the paper
+# submitted to the JCR
+
+# P1: WM > W0, e=1 not possible (Corollary 2, Theorem 6(a))
 T = 1
 W = 1
 D = 1
 p = .9
 dl = .3
 dh = .7
-## Note: reducing dl from 0.3 to 0.4 makes the mediator even more attractive
 
 ## P2: make mediator better than e=0 or e=1: We > W1 > W0 (Theorem 6(b))
 T = 1
@@ -26,11 +28,13 @@ dh = .49
 # no concessions cutoff (only matters when no material value)
 # dh_min_nc = W/((1-p)*W+p*(T+D)) 
 
-# the asymptote for e
+# asymptote for e
 e_s = p/(p + T - T*dl +W)
 # WM asymptotes to +infty when this is positive (sufficient condition)
 suff = e_s*p*T - 1 + dh
-suff = e*p*T - 1 + dh #when e can't reach the asymptote
+# when e can't reach the asymptote, use this to calculate for another value of e
+e =
+suff = e*p*T - 1 + dh
 
 # e=1
 g1 = (p*(1-dl)*(D+T))/((1-dl)*(1-p*T)+(1-p)*D) # must be positive
@@ -48,22 +52,17 @@ rm(dh_min0)
 
 # 0 < e < 1 with mediator
 e = seq(0, 1, 0.01)
-# if we set gift to satisfy low type IC with equality
+# set gift to satisfy low type IC with equality (not necessarily optimal)
 g = data.frame((1-dl)*(T+D)/(p - e*(p + T - dl*T +W)))
-# if we set gift to satisfy low type IC with equality
+# Does high type IC/IR hold? If this is negative, no additional restriction on g:
+HTir = data.frame(T*e - (1-dh)*(1-e))
+# If HTir is positive, we need g <= g_HTir 
 g_HTir = data.frame((T+D-W)/(T*e - (1-dh)*(1-e))) #see below for when this binds
 # High type welfare when gift set so that low type IC binds
 We = 1/(1-dh)*(p*T*(1+e*g) + (1-p)*(W-D)) - (1-e)*g
 We_max = max(We[which(g[is.finite(g$X.1...dl.....T...D...p...e....p...T...dl...T...W..),1]>=0),1])
[…]

### 2021-02-18 draft.tex
clean up notes for JCR submission; fix one typo in draft

@@
 		\item[(a)] improve welfare by increasing the efficiency of concessions when only a \emph{concessions separating equilibrium with inefficient gifts} is possible; or
-		\item[(b)] improve welfare despite reducing the efficient of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
+		\item[(b)] improve welfare despite reducing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
 		\item[(c)] achieve peace when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.

### 2021-02-18 notes.tex
clean up notes for JCR submission; fix one typo in draft

@@
 						\]
-							\begin{itemize}
-								\item For P6 this is zero, for P1 and P2 it's negative, and it's positive for the rest
-							\end{itemize}
 						The following shows that this is strictly smaller than $\de^h$.
@@
 								\item $\frac{W-p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p(T+D)}{(1-p)(T+D)} = \frac{W}{(1-p)(T+D)} - \frac{p}{1-p}< \frac{W}{T+D}$. Q.E.D.
-								\item This is nice, but I'm not sure it helps with the narrative of the story.
-									\begin{itemize}
-										\item \textbf{Do I want to re-cast the $\de_h$ definitions, changing them throughout the story?}
-											\begin{itemize}
-												\item e.g. With the defn of high type as a country who can sustain the grim trigger equilibrium, high type is always patient enough to sustain $e=0$ CSE / no material value CSE
-												\item Should I compare grim trigger welfare to see which is higher?
-											\end{itemize}
-									\end{itemize}
 							\end{itemize}
@@
 Each term on the left is strictly larger than 0, so this statement is always true.
+\begin{itemize}
+	\item The above calculations are not quite right: the LHS subtracts off the full value of the gift, but I forgot to include that you also receive the gift $p$ of the time.
+So the LHS is strictly larger than what I have here, which means this result is even a bit stronger.
+\end{itemize}
 
@@
 	\item If the mediator gets two `high' reports, both countries are instructed to exchange gifts and play `Trust'
+		\begin{itemize}
 			\item If the mediator gets one or zero `high' reports, there is no gift and they both play `Fight'
 		\end{itemize}
-I show the constraints for both types in Section \ref{sec:const}.\\
-I detail the choices of all types in regards to investments in civil society in Section \ref{sec:civ}.\\
-I show in Section \ref{sec:e1} that the low type's IC constraint cannot hold if $e=1$.\\
+	\item I show the constraints for both types in Section \ref{sec:const}.
+	\item I detail the choices of all types in regards to investments in civil society in Section \ref{sec:civ}.
+	\item I show in Section \ref{sec:e1} that the low type's IC constraint cannot hold if $e=1$.
+	\item Section \ref{sec:eless} develops the model with $0<e<1$.
+\end{itemize}
 
@@
 			\begin{itemize}
-				\item Relative to Section 4.2, $-g_h$ there becomes $-pg_h$ here (again, only give gift if matched with high type). Also $+peg_h$ in Section 4.2 disappears on RHS.
+				\item Relative to Section 4.2 in the draft, $-g_h$ there becomes $-pg_h$ here (again, only give gift if matched with high type). Also $+peg_h$ in Section 4.2 disappears on RHS.
 			\end{itemize}
@@
 \label{sec:civ}
-In a concessions separating equilibrium or in the mechanism, the high type always has the incentive to invest all of the gift in civil socity
+In the mechanism, the high type has the incentive to invest all of the gift in civil society if it reports truthfully.
+A high country doesn't make any investment when it reports as a low type because no gift will be specified.
 	\begin{itemize}
 		\item If there is an exchange of gifts (whether in the mechanism or a truthfully revealed separating equilibrium), you know you're both receiving from and giving to a high type
-		\item \textbf{I should check this in all the scenarios to make sure we don't invoke it when it's not right}
-			\begin{itemize}
-				\item \textbf{I also want to know whether it depends on the linear form}
-				\item \textbf{Make more explicit in the text}
+			\begin{itemize}
+				\item \textbf{I want to know whether it depends on the linear form, but that is beyond the scope of the paper at this point}
 			\end{itemize}
@@
 			Assuming $g_M > 0$, this inequality can never hold since each of $T,W,D\geq0$ and $0 \leq \left(1 - \de^l \right) \leq 1$			
-			\begin{itemize}
-				\item What would it mean to have negative gifts?
-			\end{itemize}					
 		\end{itemize}
@@
 
-\textbf{NOW, it's time to explore this equation and see if it's even possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint}.
-Continuing on from Equation~\ref{eq:examine} and simplifying so that $g_M = g$ and $\de^l = \de$,
+Here I explore Expression~\ref{eq:examine} to see when it's possible to pick a gift high enough and an $e$ low enough to satisfy the low type's incentive constraint.
+Continuing on from Expression~\ref{eq:examine}:
 \[
@@
 			\[
-				pg	\left(1 - e\right) \geq T + Teg - \de T - \de T eg + Weg + \left(1 - \de \right) D
-			\]
-			\[
-				pg	\left(1 - e\right) \geq \left(1 - \de \right) T + \left(1 - \de \right) D + Teg - \de T eg + Weg
+				pg	\left(1 - e\right) \geq T + Teg - \de_l T - \de_l T eg + Weg + \left(1 - \de_l \right) D
+			\]
+			\[
+				pg	\left(1 - e\right) \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) D + Teg - \de_l T eg + Weg
 			\]
@@
 \subsubsection{Solve for g}			
-			First solve for $g$ starting from Expression~\ref{eq:split}:
+			First solve for $g$ starting from Expression~\ref{eq:split}, simplifying so that $g_M = g$ and $\de_l = \de$:
 					$$pg - pge \geq \left(1 - \de \right) \left( T + D \right) + eg \left( T - \de T + W \right)$$
@@
 									\item If $\left(p - pe - e \left( T - \de T + W \right) \right)$ is negative, the only way the IC constraint in Expression~\ref{eq:g1} can hold is if $g<0$.
-									\item SO WE MUST ASSUME {\color{red} $p - e \left( p + T - \de T + W \right)$ IS POSITIVE}
+									\item SO WE MUST ASSUME $p - e \left( p + T - \de T + W \right)$ IS POSITIVE
 								\end{itemize}
@@
 										\]
-										\color{red} BIG NEW NOTE: This condition only true if denominator above is positive
 								\end{itemize}
@@
 						\begin{itemize}
-							\item {\color{red} $g \left( p + T - \de T + W \right)$ is non-negative as long as $g$ is positive}: $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive.
-It can only possibly be zero if $p=0$ and $\de = 1$.
-								\begin{itemize}
-									\item For the IC constraint to hold then (with non-negative gifts), we must at least have {\color{red} $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative, which requires $g$ to be set according to Expression~\ref{eq:g3}}.
-This only works if $e$ is set to zero; otherwise we need to look back at Expression~\ref{eq:g2}.
-This is just a weak condition that, if violated, means the IC constraint does not hold.
-								\end{itemize}
-							\item If {\color{red} $g \left( p + T - \de T + W \right)$ is positive}, we can divide through to get
+							\item $p, 1-\de, T$ and $W$ are all assumed non-negative and $T+D > W$ so that $T$ is strictly positive.
+Since we also assume that gifts are always non-negative, $g \left( p + T - \de T + W \right)$ is non-negative
+								\begin{itemize}
+									\item For the IC constraint to hold then (with non-negative gifts), we must at least have $pg - \left(1 - \de \right) \left( T + D \right)$ non-negative.
+								\end{itemize}
+							\item If $g \left( p + T - \de T + W \right)$ is non-zero, we can divide through to get
 								$$\frac{pg - \left(1 - \de \right) \left( T + D \right)}{g \left( p + T - \de T + W \right)} \geq e$$
@@
 		\begin{itemize}
-			\item So we don't get a finite size of the gift or welfare value at the optimum
-			\item In practice, there will be some upper bound on the size of the gift (even, say, total national wealth)
-				\begin{itemize}
-					\item Interestingly, $g*e$ (the effective gift) appears to be a line for a given set of parameters $W,T,D,\de_h,\de_l,p$
+			\item So we don't get a finite size of the gift or welfare value at the optimum with the low type IC constraint alone
+				\begin{itemize}
+					\item Interestingly, $g\cdot e$ (the effective gift) appears to be a line for a given set of parameters $W,T,D,\de_h,\de_l,p$
 				\end{itemize}
@@
 \begin{itemize}
-	\item This is all in the paper now.
-\end{itemize}
-
-How to choose the optimal $e$ when both the low type and high type IC bind is still done informally in R.
+	\item How to choose the optimal $e$ when both the low type and high type IC bind is still done informally in R.
+\end{itemize}
 
@@
 I tried to derive a necessary condition relating the IC/IR constraints to this welfare comparison but didn't find anything easily.
-I think I explored this in Mathematica, but I'd need to look more carefully through the Mathematica files.
+I did this informally in Mathematica, but I don't think I kept the notes.
 
@@
 		\]
-It turns out that there aren't really separate conditions.
+It turns out that there aren't really separate conditions for when the mediator is better in welfare terms than CSE with either efficient or inefficient gifts.
 If the welfare under the mediator asymptotes to positive infinity to the left of the asymptote (i.e.
@@
 Everything is positive, and numerator strictly smaller than denominator, so $0 < e < 1$
-									\item Both examining the IC constraint directly and taking a derivative in Mathematica program `We greater than W0.txt' give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
+									\item Both examining the IC constraint directly and taking a derivative in Mathematica give the following condition for when welfare under the mediator increases as $e$ increases; this is the case when the mediator is better than CSE $e=0$ or CSE $e=1$:
 										\[
@@
 \subsubsection{Check with some parameterizations}								
-Parameterization that was in the previou version of the paper:
+Parameterization that was in the previous version of the paper:
 									\begin{itemize}
@@
 
-\subsubsection{To do and Notes}		
-	\color{ForestGreen} 
-			\begin{itemize}
-					\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
-						\begin{itemize}
-							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
-						\end{itemize}
-					\item If you can sustain $e=1$ with no mediator, mediator can still be better
-						\begin{itemize}
-							\item Again, if mediator is good, it's REALLY good.
-							\item The benefit of $eg_M$ is muted versus $g^1$, but there is no harm from $g_M$ while there is harm from $g^1$.
-Cost of gift will always be larger under mediator because it goes to infinity at the optimal $e$
-						\end{itemize}
-					\item Sufficient condition for where welfare goes to positive $\infty$ to the left of the $e$ asymptote
-						\begin{itemize}
-							\item Characterizing exactly the region where Welfare goes to positive $\infty$ to the left of the $e$ asymptote seems hard.
-But I have developed an intuitive sufficient condition.
-See end of Section~\ref{sec:WM1}
-						\end{itemize}
-			\end{itemize}
-
-\vskip.2in
-\color{Black}Notes:
+\subsubsection{Notes}
+
 \begin{itemize}
@@
 		\end{itemize}
+	\item I'm leaving the following out since we're already over the word limit and it's the least interesting of the results
+		\begin{itemize}			
+			\item Mediator with $e=0$ can be better than CSE with $e=0$. Need to say why this is
+						\begin{itemize}
+							\item Two differences: Mediator gets you some value of the gift $pTeg_M$; gift under mediator typically has to be larger--it takes more to disincentivize low type from lying because the payoff is better
+						\end{itemize}
+		\end{itemize}
 \end{itemize}
@@
 
-High type's IC with potentially interior $e$
+High type's IC with potentially interior $e$ \\
+\textbf{AGAIN, I don't have the gift right: you also receive the gift $p$ of the time; so everything below is off}
 $$pT(1+eg) + (1-p)(W-D(1+eg)) - (1-\de_h)g \geq p(W+Weg-D) + (1-p)(W-D)$$
@@
 \section{Develop result: mediator increases potential for peace}
-\un{June 6, 2017}
+\un{June 6, 2017; deprecated since this mechanism isn't IC for the low type}
 
@@
 		\end{itemize}
-
-\vskip.3in
-Notes from CPEG, Oct. 25, 2019 presentation:
+\end{itemize}
+
+\section{Notes from CPEG, Oct. 25, 2019}
 \begin{itemize}
@@
 
-\newpage
-\section{Review 1 from EJPE (Email from Toke Aidt, August 19, 2018)}
-
-While clearly these are interesting issues, I have difficulties reading this paper.
-Everything is presented in a very unclear manner.
-Game-theoretical concepts are invoked, but typically not correctly.
-For instance, an equilibrium is a strategy profile (one strategy for each type of each player).
-Hence it does not make sense to say, as the authors do in Theorem 1 on page 10, that something is an equilibrium strategy for one type without also specifying what others do.
-As another example, on page 18, the authors say that “The revelation principle is used to attain truthful self-identification.” But in reality, the revelation principle is just an argument for why it is without loss of generality to restrict attention to direct mechanisms.
-The truthfulness of messages is guaranteed by requiring the mechanism to be incentive compatible, something the authors do not address.
-\\
-
-Another thing.
-It is not considered a good idea to introduce new assumptions, which have not been mentioned before, in the proof of a proposition, as happens in the alleged proof of Theorem 4 on page 27.
-
-\end{itemize}
 \end{document}

### 2021-02-21 draft.tex
add Ben's revisions to intro/literature

@@
 If settlement can be achieved, lives are saved and destruction averted.
-Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective (CHAIN CITE).
+Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective (e.g., Bercovitch 2000; Greig 2005a; Beardsley et al.
+2006; Duursma 2020).
 This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that combatants can offer.
@@
 
-Two archetypal situations demonstrate the significance and difficulty of efficient concession-making in war settlement.
+Two archetypal situations illustrate the significance and difficulty of efficient concession-making in war settlement.
 The first is the case of disarmament and the second is the concession of control over strategically valuable territory.
@@
 Control of strategically valuable territory can pose similar challenges in both civil and interstate wars.
-Even if transferring control of the territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide military advantage in a future conflict.
+Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide military advantage in a future conflict.
 
@@
 Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
-Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (CITE).
+Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996).
 Can mediation offer a path to settlement in these challenging contexts?
@@
 The type of mediation affects the negotiation outcome (Bercovitch 2000; Beardsley et al.
-2006) and timing is important (Greig 2005a).
+2006), as does the legitimacy of the mediator (e.g., Duursma 2020) and the timing of the mediator's intervention (Greig 2005a).
 
@@
 Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
-Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010).
+Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).
 
@@
 Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil society helps the giver in peace.
-The Golan heights is such an example: if Syria is an ally of Israel, the Golan Heights is a reasonable concession to make, but if Syria later turns out to betray a trust, surrender of the strategic land would be disastrous for Israel.
+The Golan heights is such an example: if Syria maintains peaceful relations with Israel, the Golan Heights is a reasonable concession to make, but if Syria renews military conflict with Israel, surrender of the strategic land would be disastrous for Israel.
 %Another example is ADD more examples
@@
 
+\item Beardsley, Kyle and Nigel Lo. (2014). ``Third-Party Conflict Management and the Willingness to Make Concessions." \emph{The Journal of Conflict Resolution} 58:2, 363-392.
+
 \item Bercovitch, Jacob, ed. (1996). \emph{Resolving International Conflicts: The Theory and Practice of Mediation.} Boulder, CO: Lynne Rienner.
@@
 
+\item Duursma, Allard. (2020). ``African Solutions to African Challenges: The Role of Legitimacy in Mediating Civil Wars in Africa." \emph{International Organization} 74:2, 295-330.
+
 \item Fearon, James. (1996). ``Bargaining Over Objects that Influence Future Bargaining Power.'' \emph{Chicago Center on Democracy Working Paper}, University of Chicago.
@@
 
+\item Hensel, Paul. (1996). ``Charting A Course To Conflict: Territorial Issues and Interstate Conflict, 1816-1992," \emph{Journal of Conflict Resolution} 15:1, 43-73.
+
 \item Horner, Johannes, Massimo Morelli and Francesco Squintani. (2010). ``Mediation and Peace.'' \emph{The Review of Economic Studies} 84, 1483-1501.

### 2021-02-23 draft.tex
copy edit for JCR

@@
 \usepackage[hmargin=1in,vmargin=1in]{geometry}
-%\usepackage[left=0.9in,top=0.9in,right=0.9in,nohead]{geometry}
 
@@
   \usepackage{setspace}
-  \doublespacing
+  \onehalfspacing
 
@@
 \title{Inefficient Concessions and Mediation}
-\author{Kristy Buzard\\
-Syracuse University \\
-kbuzard@syr.edu\\
-\\
-Ben Horne\\ 
-University of California, San Diego\\
-\\}
+%\author{Kristy Buzard\\ \footnote{We thank Eli Berman, Renee Bowen, Ben Graham, Joel Watson as well as seminar
+%participants at ... for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance.}
+%Syracuse University \\
+%kbuzard@syr.edu\\
+%\\
+%Ben Horne\\ 
+%University of California, San Diego\\
+%\\}
 \date{\today}
@@
 \begin{document}
+
 \maketitle
@@
 We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
-In this process, we open up a new rationale for mediation: to remove the inefficiencies of signaling in a preliminary round of negotiations.
+In this process, we open up a new rationale for mediation: to increase the inefficiency of signaling in a preliminary round of negotiations.
 \end{abstract}
 
-\section{Introduction} %LAKE For instance, the problem you begin with in the cases of Israel/Syria and West Bank are well understood as bargaining over assets that confer future power.
-But this is not understood as a problem of private information, as you treat it here, but as one of credible commitment.
-Its not clear how your types map onto the commitment problem.
-HOW: THAT TYPES COULD CHANGE OVER TIME?
+\section{Introduction}
 
@@
 
-This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can help increase the efficiency of concessions that are possible.
+This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can both help increase the efficiency of concessions and make peace.
 Weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
@@
 Mahmous Abbas may be a low type, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.
-%MORE commitment literature needs to be cited here.
-
-%Concessions form the centerpiece of the GRIT (graduated and reciprocated initiatives in tension reduction) theory in the psychological literature (Osgood 1962) and have shown ample success in lab settings.
-Komorita (1973) conducts lab experiments using a repeated Prisoner's Dilemma similar to the setup in our paper and finds costly conciliatory acts (concessions) to be useful in promoting cooperation.
-De Dreu (1995) likewise uses a lab setting to experiment with concessions and conflict.
-%de dreu bases experiments on shelling 60 and bacharach and lawler 81/ lawler 92 about deterrance, the shelling conflict spiral was not fully rejected, but the alternative of deterrance was supported
-%In addition to concessions, De Dreu also reports laboratory results on mediation; he concludes that a weaker mediator should work with promises while a more powerful one can be effective with threats.
-Larson (1988) and others have applied this framework to political science questions.
-On the theoretical side, Filson and Werner (2007) use a bargaining setup to explore the sensitivities of costs compared to the sensitivity of giving concessions.
-%LAKE: The psychological literature as applied in political science spent a lot of time in the 1970s and 1980s focusing on Graduated Reductions in Tensions (GRIT) as a form of confidence building.
-See Debbie LarsonÕs work (sheÕs at Poli Sci, UCLA, I donÕt have the cites handy).
-This is clearly relevant to your discussion of the laboratory experiments on p.3.
-BH WATSON'S STARTING SMALL COULD BE RELEVANT HERE
 
@@
 And the gift giving literature, more so than the concessions literature, focuses specifically on the issue of efficiency.
-Inefficiency is defined for the purposes of this paper as giving a gift or concession that is more costly to the giver than it is valuable to the recipient, that is, using a concession as a signal and not taking advantage of its full inherent value.
-
-%Gift giving as a whole is inefficient (Waldfogel 2009); it has been estimated that Christmas gift-giving is only 75 percent efficient, meaning that the average gift is valued at 75 cents of the dollar that is spent on it (Waldfogel 1993).
-But merely looking at aggregate numbers blurs together many possible reasons for gift giving.
-It has even been theorized that buying something that the receiver would not buy himself is an inherent component of gift giving (Thaler 1985).
+Inefficiency is defined for the purposes of this paper as giving a gift (i.e.
+a concession) that is more costly to the giver than it is valuable to the recipient.
 
@@
 Since inefficient gift giving is more likely involved in nascent relationships and partnerships, it is natural to suppose that inefficient gifts play a signaling role in addition to the material value of transferring the gift's inherent worth.
-%Several situations have been proposed where inefficient gifts can help keep types separated in partnership models.
-However the current literature on inefficiency in gift giving relies on unrealistic special cases that do not apply in more general partnership formation environments.
 
@@
 But the most relevant explanation for the field of international relations is that gift giving is strategic.
-Camerer also uses mechanism design to model gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
+Camerer uses mechanism design to model gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
 This strategic giving of gifts in societies looks very much like the strategic giving of concessions to remedy conflict situations.
-When modeled game-theoretically, these different environments look even more similar.
+When modeled game-theoretically, these environments look even more similar.
 
 Camerer's model includes players that have one period to signal before they decide whether to partner.
-There are two types, high types and low types, and a separating equilibrium is characterized by a threshold gift that is necessary for high types to reveal themselves while low types do not send a gift (or send a gift of  zero cost).
+There are two types, high types and low types, and a separating equilibrium is characterized by a threshold gift that is necessary for high types to reveal themselves while low types do not send a gift.
 Two high types who have just received each other's gifts will then choose to create a partnership with a positive payoff; other combinations will not find it economical to form a partnership.
@@
 Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts.\footnote{In an environment with repeated opportunities for concessions Watson (1999) is able to show that a strong relationship can be reached by starting with small ``gifts'' and increasing their size as the relationship becomes more committed.
-See Van de Ven (2000) for an overview of this literature.} In order to explain inefficiency, Camerer adds in an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts.
+See Van de Ven (2000) for an overview of this literature.} In order to explain inefficiency, Camerer adds an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts.
 If types separate in the pre-play period with low types not being willing to pay, high types are saved the cost of sending a signal to low types in the main game.
@@
 Such an action can keep out the low types and this can raise the expected payoff for a high type by saving on the gifts given.
-%While pre-play communication can lead to inefficient gift-giving, it is not realistic to think that partnership formation generally has this structure, therefore while Camerer's explanation is theoretically sound, it lacks the ability to be a general explanation for inefficient gifts.
-
-%Iannaccone (1992), Rabin (1993),  Kranton (1996) and Carmichael and MacLeod (1997) all use a similar explanation for inefficient gifts with various modifications to the model.
-In an environment with repeated opportunities for concessions Watson (1996, 1999) is able to show that a strong relationship can be reached by starting with small gifts and increasing their size as the relationship becomes more committed.\footnote{See Van de Ven (2000) for an overview of this literature.}
-
-The second major explanation for inefficient gifts is expressed in Prendergast and Stole (2001).
+
+Prendergast and Stole (2001) provide a second explanation for inefficient gifts.
 The authors explain inefficient gift giving by modeling the utility of matching.
@@
 
-% However, there are some inadequacies in the model.
-In their model, agents derive utility from giving and receiving the ``correct" gift because it signals that a friendship is true.
-There are two types of receivers, A and B.
-Givers have a prior belief along the A-B continuum that must remain unknown to receivers for the model to work.
-Givers can choose to give gift A, gift B, or cash.
-The technological constraint of only two types/ gifts is crucial to the inefficiency result as well in the sense that the gift is in fact an imprecise signal of the giver's belief.
-Givers' utility includes altruism and a match payoff.
-This match payoff means players might be willing to risk giving the wrong gift- hence inefficiency.
-Altruism (wanting recipients to be happy) keeps a giver from giving a gift if his prior is ambiguous enough.
-Receivers' utility derives from a match payoff as well as the inherent utility of the gift.
-One limitation of the model is that if (realistic) cheap talk were allowed in addition to the gift, cash could be sent with a note telling which gift the sender believes is correct to ensure efficiency.
-Receivers do not tell their type because that would sacrifice the match payoff.
-The authors ``solve" this issue for givers by claiming bought gifts yield a higher payoff than cash with a note.
-This last explanation works mathematically but is not a general theory- essentially they just argue ``people like gifts."
-
-We propose a different conceptual framework to explain this real-life phenomenon that is more rooted in a realistic international relations puzzle.
+We propose a different conceptual framework to explain this real-life phenomenon that is rooted in a realistic international relations puzzle.
 The basic formulation of our mechanism-design approach is an expansion of Camerer's (1988) analysis.
 The model can achieve the basic `inefficient gifts' results of Camerer (1988) and Prendergast and Stole (2001) but does so using a very different explanation for inefficiency.
-%An extension at the end of our paper compares simultaneous versus sequential concessions in a bilateral negotiation environment.
-The theory yields results about the effectiveness of different types of enforcement in various circumstances.
-%Since neither the models exemplified by Camerer nor Prendergast and Stole uses a truly general formulation to yield inefficient gift giving % in a one-shot setting,
-%This paper expands upon the existing literature by generalizing the analysis using mechanism design theory more extensively than has been done thus far.
-%The analysis for this paper is more extensive than any of the published papers mentioned and shows where mechanisms can and cannot improve upon the benchmark bilateral results.
-The basic model is a costly signaling model, at its root similar to ideas in Spence (1973) and subsequent papers.\footnote{See Connelly et al.
-(2011) for a review of the costly signaling literature.} In essence, the model shows that if concessions can be later used against the party that gives, then it can be in a negotiating party's best interest to give inefficient concessions.
+The basic model is a costly signaling model, at its root similar to Spence (1973) and subsequent papers.\footnote{See Connelly et al.
+(2011) for a review of the costly signaling literature.} In essence, the model shows that if concessions can be later used against the party that gives them, then it can be in a negotiating party's best interest to give inefficient concessions.
 While our model is tailored to an international relations setting, the explanation for inefficient giving of concessions may be more broadly applicable.
-
-%In these and many other situations, a lack of trust is an impediment to peace, preventing parties from making necessary concessions.
-Mediation has long been understood as a mechanism for reducing mistrust, but in much of the published literature on international conflict mediation lacks a rigorous theoretical framework.
 
@@
 Third party involvement is ubiquitous in conflict and mediation has been extensively studied in the literature, but still the question of third party effectiveness is intensely debated.
-Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others insist that a correct analysis finds mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al.
+Some authors have concluded that mediation has little impact, (Bercovitch 1996;  Bercovitch and Langley 1993; Fortna 2003) while others find mediation playing a positive role in resolving conflict (Dixon 1996; Beardsley et al.
 2006).
@@
 This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has manipulative abilities.
-Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006).
-In this paper, parties are in conflict and can benefit from seeking mediation in order to overcome mistrust.
-Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
-Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).
+Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006), and parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
+We thus model parties to a conflict who can benefit from seeking mediation in order to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).}
 
 These empirical results have until recently lacked strong theoretical foundations.
-Mediation is used, but we are only beginning to understand why actors use it.
-Recently, mediation has begun to be modeled using mechanism design for settings where militarization or the resolve to fight are private information (Bester and Warneryd 2006; Fey and Ramsay 2008, 2010 and 2011; Horner et.
+Mediation is not uncommon, but we are only beginning to understand why actors use it.
+Recently, mediation has begun to be modeled using mechanism design for settings where militarization or the resolve to fight are private information (Bester and Warneryd 2006; Fey and Ramsay 2009, 2010 and 2011; Horner et.
 al.
@@
 \section{Model}
-\label{sec:model} %A DIFFERENT MODEL BUT SAME RESULT AS FR 10; THIS SHOULD BUILD OUR CONFIDENCE IN MODELLING.
-EMPHASIZE SCENARION (EGYPT USRAEL ETC) THAT ARE BETTER TO MODEL WITH Our MODEL.
-IT CAN ALSO BE THOUGHT OF AS REDUCED FORM OF A BARGAINING MOEL, BUT IT DOES NOT NEED TO BE!
-NEED TO GIVE EXAMPLES WHERE Our MODEL IS BETTER THAN BARGAINING- EXAMPLES.
-WHEN TRUST IS AN ISSUE (PUT THIS IN THE TRUST SECTION)
-%Need to add risk aversion in MAIN TEXT
+\label{sec:model}
 
@@
 A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
-The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict; that is, throughout the analysis we will define a low type as a player whose only sequentially rational strategy is to remain in conflict in all periods.
+The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict; that is, throughout the analysis we will define a low type to be a player whose only sequentially rational strategy is to remain in conflict in all periods.
 It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
@@
 Our model can be thought of as a reduced form bargaining model, but it can also be considered somewhat differently.
-That is, when trust is the issue to be solved, there are several solutions to conflict.
-Concessions are one way in which countries can signal their commitment.
-By modeling the conflict in such a way we can also gain insight as to how a third party can ameliorate trust issues inherent to the conflict.
-%might want to cite fearon and bargaining lit here
-%might want to eventually add the stochastic type switch- or at least talk about how that changes analysis
+That is, when trust is the issue to be solved, concessions are one way in which countries can signal their commitment.
+By modeling conflict in such a way, we can also gain insight as to how a third party can ameliorate trust issues inherent to the conflict.
 
@@
 Thus, a stag hunt or other game structures are also possible.
-The Prisoner's Dilemma is used because of its wide exposure in the literature.\footnote{This payoff matrix does not distinguish between civil and interstate conflict, though in practice the effects on the payoffs might indeed have a different structure in the different cases.} %cite difference from fearon here?
-%LAKE More generally, the problem of war, on which you implicitly focus, is now understood as a pure bargaining game (i.e., zero sum).
-This is not well represented by the PD.
-You need to make the link Ð or differentiate Ð what youÕre doing here from the Fearon-Powell models to which you appeal.
+The Prisoner's Dilemma is used because of its wide exposure in the literature.\footnote{This payoff matrix does not distinguish between civil and interstate conflict, though in practice the effects on the payoffs might indeed have a different structure in the different cases.}
 
@@
 We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
-This also ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
+Note that this ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
 
@@
 Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
-If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}=\frac {T}{1- \delta_i}$.
-Likewise $X_{TF}=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}=\frac{W-D}{1- \delta_i}$, and  $X_{FT}=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
-Note that because types have different discount factors, the payoffs differ by type, and when ambiguous will be super-scripted to indicate the type, e.g.
-$X_{FT}^h$ represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period.
+If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}^i=\frac {T}{1- \delta_i}$.
+Likewise $X_{TF}^i=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}^i=\frac{W-D}{1- \delta_i}$, and  $X_{FT}^i=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
+$X_{FT}^h$, for example, represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period.
+Note that because types have different discount factors, the payoffs differ by type.
 
 Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
-%Countries' utility is calculated as ex interim utility (Holmstrom and Myerson 1983),  i.e.
-when countries know their own type but not that of the other country.
-Depending on parameters, multiple equilibria are often possible.
 We will take the measure of social welfare, and thus the determinant of the optimal equilibrium, to be the sum of participating high types' expected utilities.
@@
 \label{sec:bench}
-When countries are faced with uncertainty about each other's motives, they can proceed in several different ways, including giving concessions in order to signal their willingness and ability to make peace.
+When countries are faced with uncertainty about each other's motives, they can proceed in several ways, including giving concessions in order to signal their ability to make peace.
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
@@
 In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Fight in every period beginning with period 1.
-Countries continue to doubt, doing nothing to bridge the credibility gap, and thus not cooperating.
+Countries do nothing to bridge the credibility gap, and thus do not cooperate.
 This \emph{pooling equilibrium} is likely to happen when countries are in long-set patterns of distrust.
@@
 Sri Lanka is another example.
-While the government has finally won the war of secession, it still refuses to address grievances of the minorities and leaves the conflict still unresolved.
+While the government has finally won the war of secession, it still refuses to address grievances of the minorities and leaves the conflict unresolved.
 Other prominent examples of this pooling equilibrium include Israel and its neighbors, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
-The mistrust of the other party is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
+The mistrust is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
 
@@
 Otherwise, both countries play Fight in all following periods.
-
-%In this equilibrium, no concessions are given by either type in period 0.
-In all periods starting at period 1, both countries play ``Trust'' as long as the other plays ``Trust'' and play ``Fight'' if there is ever a deviation from ``Trust.''
-
-%For a Peace equilibrium to exist, $\delta_i$ must be high enough for each country so that sustaining Peace is more attractive than deviating. 
-%The threshold needed is \be
- %\delta^{gt} = \frac{W}{T+D}
- %\ee
-%where the superscript $gt$ stand for `grim trigger.'
 
@@
 Any country with $\delta_l < \delta^{nc}$ is a low type.
-This means that two high types---and only two high types---can sustain the ``Peace'' outcome in a simple repeated game.
+This means that two high types---and only two high types---can sustain the ``Peace'' outcome.
 
@@
 Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
-Certain relationships between the USA and countries that its WikiLeaks alienated -- such as Italy -- would be an example.
+Certain relationships between the USA and countries alienated by WikiLeaks -- such as Italy -- would be an example.
 Italy essentially laughed off the criticisms and reassured the USA of its commitment to their relationship.
@@
 
-Of course, it is possible that one country can take advantage of the other in a \emph{no-concessions separating equilibrium}.
-It can be argued that indeed that did happen in the Warsaw Pact cases; the Eastern Bloc countries were first exploited before the fall of the iron curtain; eventually this led to a steely relationship between many of those countries and Russia that exists to this day in Poland, Lithuania and other countries.
-
-%Though it will not be modeled here, a stochastic component -- when countries occasionally unilaterally defect -- can explain why powerful countries like the USSR more often ``get away'' with cheating: the payoffs to the relationship are not symmetric.
-Losing the USA or USSR as an ally is much more devastating for a satellite country than vise versa, therefore big countries can have their alliances and take advantage of them too.
 \subsection{Concessions Separating Equilibrium}
@@
 In this equilibrium, concessions are given before more substantive actions and thus remove the possibility of playing one of the cheating corners of the Prisoner's Dilemma.
-Concessions are a costly signal that the other country is serious about cooperating and can be sued to avoid continual distrust.
+Concessions are a costly signal that the other country is serious about cooperating and can be used to avoid continual distrust.
 That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing peace.
@@
 Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Fight in subsequent periods.
-Because of the signaling value of the concessions given in period 0, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Fight.
+The signaling value of concessions in period 0 means that, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Fight.
 
@@
 \emph{Proof:} See Appendix.
+
+Low types don't give gifts in this separating equilibrium because the gift wouldn't serve any purpose: the low type will be identified through the separating behavior of the high types and there is thus nothing to gain.
 
@@
 
-Concessions separating equilibria are a way for countries to solve their disputes when the \emph{no concessions separating equilibrium} is unavailable or unattractive.
+Concessions separating equilibria are a way for countries to solve their disputes when the \emph{no concessions separating equilibrium} is unattractive or unavailable.
 By giving costly concessions, they signal their intentions in a way that a partner unwilling to make peace would not be willing to signal.
 
-One example of such an equilibrium is Israel and Egypt at the Camp David Accords.
+One example of an equilibrium involving concessions is Israel and Egypt at the Camp David Accords.
 Both parties gave concessions (Israel a material land concession and Egypt diplomatic recognition of Israel) that signaled their willingness to end the stalemate that had characterized the previous five years.
 Of course this result depended on Carter's use of mediation techniques, including use of manipulative mediation -- a concept we will explore in Section~\ref{sec:med} below.
-
-%another example
 
@@
 To be clear, in Sections~\ref{sec:model} and \ref{sec:bench}, the gift only benefits the party who receives it in the period in which it is received, that is, Period 0.
-In this section, we assume that there is an additional value from the gift in each period that the repeated game is played, that is, Period 1 and onward.
+In this section, we assume that there is an additional value from the gift in each period of the repeated game, that is, Period 1 and onward.
 
 The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society.
-Using concessions to build military strength hurts the giver of the concessions in war; using the concessions to strengthen civil society helps the giver in peace.
+The recipient using concessions to build military strength hurts the giver of the concessions in war; the recipient using the concessions to strengthen civil society helps the giver in peace.
 The Golan heights is such an example: if Syria maintains peaceful relations with Israel, the Golan Heights is a reasonable concession to make, but if Syria renews military conflict with Israel, surrender of the strategic land would be disastrous for Israel.
-%Another example is ADD more examples
 
@@
 The first is an additional decision for the negotiating parties.
-In Period 0, after receiving a concession, each country makes a decision about how to allocate the value of the concession between military and civil society.
+In Period 0, each country makes a decision about how to allocate the value of any concession it receives between military and civil society.
 $\alpha_i$ is the portion of the received concession that country $i$ chooses to dedicate to civil society; $(1- \alpha_i$) is the portion country $i$ dedicates to military buildup.
@@
 
-Concessions are immediately converted into civil society or military gifts.
-They are incorporated into payoff functions starting in Period 1.
+Concessions are immediately converted into civil society or military gifts and are incorporated into payoff functions starting in Period 1.
 Periods 1 to $\infty$ are as before but with the modified stage game payoffs shown in Table 2.
@@
 
-If both countries play Fight, Country 1 (symmetric for Country 2) receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, it also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
-The (Fight,Trust) and (Trust,Fight) payoffs are modified analogously.
+For example, if both countries play Fight, Country 1 receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
+However, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
+The other payoffs are modified analogously.
 
@@
 Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
+
+We turn next to characterizing a concessions separating equilibrium in this environment with future material value.
 
@@
 
-The problem with concessions with material value is that when the potential for the low type to invest the concessions in the military can make the high type unwilling to take a chance that it will be matched with a high type because the costs of being matched with a low type are too high.
+The problem with concessions with material value is that the potential for the low type to invest the concessions in the military makes the high type unwilling to take a chance that it will be matched with a high type when the costs of being matched with a low type are too high.
 
@@
 	Assume that high types are not patient enough to separate without concessions but that they can separate using concessions when gifts have no material value.
-If negotiating parties use concessions with future material value that the low-type country can use to reduce the future payoffs of its negotiating partner instead of concessions with no future material value, there are parameters under which the future material value of gifts destroys negotiating partners' ability to separate through concessions, i.e.
+If countries use concessions with future material value instead of concessions with no future material value, there are parameters under which the future material value of gifts destroys countries' ability to separate through concessions, i.e.
 peace cannot be achieved when there are two high types.
@@
 Let $T = 1$, $W=1$ and $D = 1$.
-The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de = \frac{1}{1+1} = .5$.
-Let $\de_h = 0.7$ and $\de_l = .3$ and $p = .9$.
+The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de = \frac{1}{1+1} = 0.5$.
+Let $\de_h = 0.7$ and $\de_l = 0.3$ and $p = 0.9$.
 
@@
 
-The patience threshold to separate through concessions with efficient gifts is much higher under these parameters when the concessions carry future material value: by Theorem~\ref{theorem:csemv}(a), this threshold is $0.979$.
+The patience threshold to separate through concessions with future material value is much higher under these parameters when the concessions carry future material value: by Theorem~\ref{theorem:csemv}(a), this threshold is $0.979$.
 Thus the \emph{concessions separating equilibrium with efficient gifts} is \emph{not} possible.
@@
 
-Comparative statics provide intuition for why using concessions with future material value makes it harder to make peace.
-The patience threshold is decreasing in $T$, that is, the benefit from the additional future value when a high type achieves `Peace' with another high type who used the material value for civil society.
+Comparative statics provide intuition for why using concessions with future material value makes it harder to achieve peace.
+The patience threshold is decreasing in $T$ because the benefit from cooperating with another high type increases.
 Similarly, the threshold is increasing in $D$ because the magnitude of future damages from pairing with a low type increases.
@@
 Finally, and perhaps surprisingly, the patience threshold is increasing in $p$.
-This happens because the size of gift must be increased in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}
+This happens because the gift must be larger in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}
 
@@
 We now relax the assumption about the benefit of a concession being equal to its cost and instead allow countries to ``burn'' a portion of the concession they give.
-For example, an expensive display of pageantry to a dignitary might benefit the receiving country very little, if at all, but it still signals good intentions on behalf of the giving country.
-The option to give efficient concessions is still available along with new options to give a variety of less efficient concessions.
+For instance, when decommissioning weapons, rebels leave no material value of the weapons intact to benefit the recipient, but it still signals good intentions on behalf of the giver.
+Here, we allow the giving of efficient concessions along with new options to give a variety of less efficient concessions.
 
 We implement this assumption by allowing countries to choose a scalar $e \in[0,1]$ by which to multiply their given concession $g$.
-$C(g)= g$ as before, but while the receiving country incurs the full cost of the concession $g$, the future benefit to the recipient is now only $eg$.\footnote{More generally, we could think of $e$ as a function $E(g)$ instead of a simple scalar transformation.
-Without further restriction, $E(\cdot)$ could increase the value of the concession.} Table 3 provides the modified payoffs in the repeated game.
+$C(g)= g$ as before, but while the receiving country incurs the full cost of the concession $g$, the future benefit to the recipient is now only $eg$.
 
@@
 
-%need to also write constraints for high type IC to be satisfied, or appeal to forward induction
-%?
-And, a mechanism improves upon inefficiency because it allows a high types to only give a gift to other high types, thus decreasing their costs and still giving the same equilibrium matches.
-.
-Does this rely on varied costs of giving- i.e with same costs can a mechanism still improve?
-%note damages due to alpha can be understood as political losses/ embarrassment of failure to make peace as much as they can be seen as military damages.
-%{\bf Theorem 12:}\\  
-%When concessions are inefficient, $M$ can still improve over bilateral negotiation. \\
-% \emph{Proof}: A mechanism works as in proof (6) with the additional liability that high-high concession exchanges are no longer efficient so a mechanism's advantage is not as strong. 
 The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens $p$ of the time.
-On other other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
+On the other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
 Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
@@
 Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$.
-As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.} %This is not at all obvious because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}
+As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium with $0<e<1$} exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.} %This is not at all obvious because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}
 
@@
 Inefficient concessions are optimal when there's a good chance of facing a low type who will use the concession against you (i.e.
-$p$ is small) as well as when the benefits from ``Peace'' are low relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication can also be found in our model.
+$p$ is small) as well as when the benefits from ``Peace'' are small relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
@@
 \label{sec:med}
-All the results in this paper thus far have relied on bilateral engagement.
+The results in this paper thus far have relied on bilateral engagement.
 We will now consider the involvement of a mediator when concessions have future material value that can benefit or harm the giver.
 
-Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz 2002), much of the literature has focused on self-enforcing mechanisms.
+Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz 2001), much of the literature has focused on self-enforcing mechanisms.
 If however a credible third party exists, then results beyond self enforcing agreements can be relevant.
@@
 In Sections~\ref{sec:bench} and \ref{sec:IC}, the same concession must be sent to both types since types are private information.
-Importantly, here the mechanism $M$ can differentiate based on recipient's type.
+Importantly, here the mechanism $M$ can differentiate by recipient type.
 Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value that can optionally be destroyed.
+
 As usual, truthful self-revelation requires that the incentive compatibility constraint for each type must be satisfied.
-
-%The individual rationality constraints are satisfied for both types.
-The individual rationality constraint of the low types is satisfied because they have the same outcome as they do outside of the mechanism---that is, they remain in the `War' equilibrium and neither give nor receive concessions.
-For the high type, the constraint is looser.
-Outside of the mechanism, they would also remain in the `War' equilibrium and neither give nor receive concessions.
-If they participate, they receive the `War' payoffs with probability $(1-p)$ but they receive `Peace' payoffs with probability $p$.
-Because the `Peace' payoffs are higher than the `War' payoffs, this average is above their reservation payoffs.
-High types give and receive gifts of the same size
 
@@
 In order to make the mechanism incentive compatible for the low types, some value of the concessions must be destroyed, i.e.
-$e<1$.
-The low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism; this puts an upper bound on how efficient concessions can be.
-In some cases, the high type incentive constraint also provides an upper bound on the size of the concession, which puts a lower bound on efficiency.
+$e<1$, so that the low type is not tempted to misrepresent its type in order to receive the gift.
+The range of efficiency that allows for a mechanism $M$ to be incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
 
@@
 		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)},$ with the denominator of this expression strictly positive.
-		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type when the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
+		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type either when $Te < (1-\de_h)(1-e)$ or the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
 \end{enumerate}
@@
 
+The low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism; this puts an upper bound on how efficient concessions can be.
+In some cases, the high type incentive constraint also provides an upper bound on the size of the concession.
+
 Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that the mediation mechanism $M$ can do both.
@@
 	\begin{enumerate}
-		\item[(a)] improve welfare by increasing the efficiency of concessions when only a \emph{concessions separating equilibrium with inefficient gifts} is possible; or
+		\item[(a)] improve welfare by increasing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is not possible; or
 		\item[(b)] improve welfare despite reducing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
@@
 
-To understand part (a), remember that concessions are not exchanged if there is even one report of ``Low.'' Since a concession is only given to the high types and high types invest in civil society, the efficiency of the concession can be increased subject to satisfying the low type's constraints without creating extra damages when matched with a low type.
-High-type welfare is improved because no transfer is made to the low types and there is no threat of future damage from the concession that is made since it goes only to a high type.
+To understand part (a), remember that concessions are not exchanged in the mechanism if there is even one report of ``Low.'' Since a concession is only given to the high types and high types invest in civil society, the efficiency of the concession can be increased without creating extra damages when matched with a low type; this is of course subject to satisfying the low type's constraints.
+High-type welfare is improved because no transfer is made to the low types and there is no threat of future damage from the concessions since they only go to a high type.
 
 Here, inefficiency can be mitigated because the mediator is able to mandate concessions only between declared high types.
-The inefficiency is no longer need to prevent low types from using concessions against high types.
-However, some inefficiency is needed in order to incentivize low types to truthfully reveal their type.
+The inefficiency is no longer needed to prevent low types from using concessions against high types.
+However, some inefficiency is required in order to incentivize low types to truthfully reveal their type.
 
@@
 This happens when the possibility of the low type using concessions against their negotiating partner and the magnitude of the damages that can be imposed are small enough that efficient gifts are possible but large enough that the full efficiency of the gifts has a large, negative impact on welfare.
-The mediator removes the possibility of the future damages, but has to require some inefficiency in order to, gain, incentivize low types to truthfully reveal.
-
-(c) When the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the benefits and damages from investing in military power are too large, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
+The mediator removes the possibility of the future damages, but has to require some inefficiency in order to incentivize low types to truthfully reveal.
+
+(c) When the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
 By ensuring that only high types exchange gifts, the mediator removes this threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
@@
 \section{Conclusion}
-In states of perpetual conflict, concessions have been shown in the literature to ease distrust.
-Our paper shows a mechanism by which this might work.
+In situations of perpetual conflict, concessions have been shown in the empirical literature to ease distrust.
+This paper introduces a mechanism by which this might work.
 In our model's setup, there are three classes of interesting equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which is essentially a state of war for all types.
 Second, if prior trust is sufficiently high, a no-concessions pooling equilibrium exists where high types trust in the first period and can maintain that trust if both are high types.
-Third, the most intuitive or realistic type of equilibrium, a concessions giving separating equilibrium exists where high types offer concessions to eliminate the distrust.
+Third, a concessions giving separating equilibrium exists where high types offer concessions to eliminate the distrust.
+This is the most interesting class of equilibria for our purposes.
 
@@
 This explanation captures the hesitancy of nations to fully engage in moving forward with a peace process when there is mutual distrust.
-%As previously shown in the literature, if parties are trying to enter a club or alliance, it may be necessary to give inefficient concessions.
-%Our model can achieve that result, first shown in Camerer (1988), that inefficiency plays a role in pre-play communication and can be used to separate out unwanted partners.
-Our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred.
-To achieve this countries must have preferences over the types of the recipients of their concessions.
-If there is a regret of giving a concession to a country who does not pan out to be an ally, then inefficiency can be preferred.
-While this is a relatively behavioral or emotional explanation for interpersonal gift giving, it might hold some weight in an international political arena.
-This flavor, of matching types, is similar in nature to Prendergast and Stole, who use two different, though equal types, while our explanation uses a high and a low type.
-%I have further shown that
 
@@
 
-In practice, in ``sons of the soil'' conflicts, concessions are indivisible (Walter 2002); if inefficient concessions need to be given to achieve peace, in the absence of a mediator no concessions will be given as an inefficient concession is an impossibility.
-The full value is the only concession worth making because it is the only one that will be accepted: although countries may prefer to give inefficient concessions, they obviously do not prefer to receive them.
-Inefficient concessions can have the same signaling value as efficient concessions, but unless signaling is the only facet of a concession that is valued, this is not necessarily enough to achieve peace.
-
 This points out that when we think about concessions, we should think about their nature as being fixed.
@@
 These observations do not undermine the model.
-The nature of the desired concessions helps determine whether inefficient concessions can help achieve peace when efficient concessions cannot and thus also when a mediator can restore the efficiency of concessions.
+The nature of the desired concessions helps determine whether inefficient concessions can help achieve peace when efficient concessions cannot and thus also when a mediator can improve the efficiency of concessions.
 
 The effectiveness of mediation is debated in the literature; this paper shows that a third party mediator can remedy a particular kind of inefficiency if she is trusted.
-One contribution of this paper is to show the mechanisms through which a mediator can help.
-Since the mediator eliminates inefficient concessions, the observation that inefficient concessions may not do the trick only underscores the potential value of a mediator.
-%our model can also be used to achieve a similar matching result as Prendergast and Stole (2001) who show how if player values his own type, inefficiency can be preferred.
-
-This model uses manipulative mediation, which is indeed used in resolving conflicts.
-However, the usefulness of mediation relies on perfect trust of the mediator.
+One contribution of this paper is to show a new mechanism through which a mediator can help.
+
+This model focuses on manipulative mediation, which is indeed used in resolving conflicts.
+However, the usefulness of mediation in this case relies on the mediator being both perfectly trustworthy and perfectly able to enforce concessions.
 Such an all-powerful mediator is a strong assumption, and while useful as a benchmark, it is unlikely to exist in all scenarios.
@@
 
-While it is important theoretically to show how a mediator can help in conflict situations, it should also be noted that mediation is not free, at least to the providing (third) party.
+While it is important theoretically to show how a mediator can help in conflict situations, it should be noted that mediation is not free, at least to the providing (third) party.
 Therefore, the inefficiencies borne by the inefficient concessions and/or by the ongoing conflict must not be outweighed by the cost of providing the mediation.
@@
 
-This paper shows that inefficient concessions may be used to achieve peace when efficient concessions are not sufficient to do so; it also demonstrates how a mediator can achieve peace in these situations without resorting to inefficient concessions.
+This paper shows that inefficient concessions may be used to achieve peace when efficient concessions are not sufficient to do so; it also demonstrates how a mediator can achieve peace in these situations when the parties to the conflict cannot do so on their own.
 Opportunities for further research clearly include looking at the roles of different types of mediation.
 Because of the many humanitarian, security and diplomatic implications of this work, both deeper and broader analysis is required.
-%This said, if the paper is really about mediation, then the mediator needs more scrutiny.
-What are the mediatorÕs incentives?
-Why should he reveal truthfully what the parties tell him?
-It would seem simple enough to make the mediator part of the game, with an payment function that is a fraction of the surplus from eliminating the inefficiency.
-This leads to interesting implications.
-Given some cost to the mediator, they will be more likely to volunteer when e* is large, etc.
-But treating the mediator as a deus ex machina leaves the current model incomplete.
 
@@
 \begin{lemma}
-	From period 1 on, playing fight in all periods regardless of beliefs constitutes an equilibrium strategy of the continuation game for both types.
+	From period 1 on, playing (Fight,Fight) in all periods is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
 	\label{lemma:1}
 \end{lemma}
-\emph{Proof}: As $D\geq0$ and $W\geq0$ the dominant stage game action for all types is to play Fight.
+\emph{Proof}: As $D>0$ and $W>0$ the dominant stage game action for all types is to play Fight.
 Thus the stage game equilibrium is (Fight, Fight) and in any repeated game, playing the stage game equilibrium in each period is an equilibrium of the entire game.
@@
 
-%\begin{lemma}
-%	From period 1 on, playing fight in all periods is the only sequentially rational strategy for low types regardless of their beliefs of the other country's type and strategy.
-%	\label{lemma:2}
-%\end{lemma}
-%\emph{Proof}: Because $W\geq0$, the dominant stage game action for all types is to play Fight.
-Playing Trust is only possible in equilibrium where there is punishment for playing Fight.
-The minimax payoff is $W-D$, and punishing a country by playing it every period is the worst possible punishment, hence it gives the greatest potential for a country to be given incentives to play Trust.
-Low types, with $\delta_l < \delta^{gt}$ achieve a higher payoff from being punished than they do from cooperation, so they cannot be given incentives to play anything except Fight.
-\hfill $\blacksquare$\\
-
-That is, one high type equilibrium strategy is to pool with the low types---who always play ``Fight'' by definition---and always play Fight.
+That is, one high type equilibrium strategy is to pool with the low types---by always playing ``Fight'' by definition---and always play Fight.
 If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, then either type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior.
@@
 Types pool by never giving concessions and always playing Fight.
- %add intro about the 3 types of equilibria. 
- \\
- \\
+
 \subsection{No-Concessions Separating Equilibrium}
@@
 \hfill $\blacksquare$
-%\noindent{\emph{Proof of Corollary \ref{corollary:1}}:\\
-%High-type welfare under the no-concessions separating equilibrium is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D) \right\} = \frac{1}{1-\de_h}\left\{pT + (1-p)\left[W-D + \de_h(W-D)\right]\right\}$$
-%High-type welfare under the grim trigger repeated game equilibrium is $\frac{1}{1-\de_h}\left\{pT + (1-p)\left[-D + \de_h(W-D) \right]\right\}$
-%When $e=0$, welfare is $$\frac{1}{1-\de_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$$
-%This type of separating equilibrium can exist for some sets of parameters.
-Since the high types have sufficient incentive to separate under appropriate parameter values even without concessions being given in period 0, we refer to such an equilibrium as a \emph{no-concessions separating equilibrium}.
-This is why the threshold patience level for this type of equilibrium is labeled $\de_h^{nc}$.
 
@@
 
-If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessions-in period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
+If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessions in period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
 A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of the ``War'' outcome that would occur under pooling.
@@
 We refer to the equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type.
-These equilibrium gifts will mean that when period 1 is reached, countries know which type the other country is and choose to play accordingly.
+These equilibrium gifts will mean that when period 1 is reached, countries know which type the other country is and play accordingly.
 The concessions phase acts as a coordination device to match countries' actions.
@@
 \emph{Proof of Lemma~\ref{lemma:3}:}\\
-In accord with the revelation principle, we focus on concessions separating equilibrium in which countries reveal their types truthfully.
+In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on concessions separating equilibrium in which countries reveal their types truthfully.
 This allows high types to only play ``Trust'' in period 1 with other high types and to play Fight with low types.
@@
 
-Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it distinguishes them from the high types \emph{and} this gives them some advantage.
+Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it gives them some advantage.
 Here, high types only cooperate with other high types, so giving a concession cannot help low types to achieve a higher payoff in the repeated game.
@@
 \end{equation*}
-This expression represents the low types' incentives by truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift.
-Simplifying this inequality, we see that the high types need give a gift
+This expression represents the low types' incentives for truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift.
+Simplifying this inequality, we see that the high types need to give a gift
 \be
-	g_h \geq p(X_{FT}^l-X_{FF}^l). 
+	g_h \geq p(X_{FT}^l-X_{FF}^l)
 	\label{eq:cse}
@@
 High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
-Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation.
+Since utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible while still achieving separation.
 This occurs when Expression~\ref{eq:cse} holds with equality.
@@
 \be
-%p_1(\frac{T+D-W}{1-\delta_h}-p_2(T+D)\geq 0. point is the p's arent the same; i might have gotten them backwards. simplified this is:
 \delta_h \geq \frac{W}{T+D} = \de^c
@@
 $$(T+D) > (1-p)W +p(T+D).$$
-Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positive and so we can divide through by both and multiply both sides by $W$:
+Since $0<p<1$ and W,T, and D are all positive, both sides of the inequality are positive. Thus we have:
 $$\de^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de^{c} $$
 
-In the case that both types of equilibria exist, i.e. $\de_h \geq \de^{nc}$, the high types will prefer the \emph{concessions separating equilibrium} if and only if
-\begin{equation*}
-p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h \geq p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right)
+In the case that both types of equilibria exist, i.e. $\de_h \geq \de^{nc}$, the high types will prefer the \emph{no concessions separating equilibrium} if and only if
+\begin{equation*}
+p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right) \geq p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h 
 \end{equation*}
 This simplifies to preferring the concessions separating equilibrium if and only if
-$$(1-p)W-p(1-p)(T+D)\geq 0$$
+$$0 \geq (1-p)W-p(1-p)(T+D)$$
 Rearranging,
 \be
- \frac{W}{T+D}\geq p
+ p \geq \frac{W}{T+D}
 \ee
@@
 \end{equation}
-The $\al_i$'s vary depending on the situation.
 On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$).
@@
 
-On the left side, the low type is giving a gift and also receiving a gift from the high type with probability $p$.
+On the right side, the low type is giving a gift and also receiving a gift from the high type with probability $p$.
 With probability $p$, this low type faces a high type who invests the gift in civil society.
-With probability $(1-p)$, the low type's gift goes to another low type who invests in the military and low type does not receive a gift.
+With probability $(1-p)$, the low type's gift goes to another low type who invests in the military and the low type does not receive a gift.
 So the right hand side of Expression~\ref{eq:matval1} becomes $-g_h + pg_h + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)$.
 
-Substituting into Expression~\ref{eq:matval1} and simplifying a bit, we have
+Substituting into Expression~\ref{eq:matval1} and simplifying, we have
 %\begin{multline*}
@@
 This occurs when Expression~\ref{eq:matval2} holds with equality.
-That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.\footnote {While not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
-Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils.
-Thus, a more powerful country would be more able to plunder, and hence has to make a greater concession to convincingly convey its type as being high.
-}
+That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.
 
@@
 %$$\de_h \geq \frac{p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1 }{g^1}$$
-$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
+%$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
 $$\de_h \geq \frac{p(W-D-T)}{g^1} + p (W-T) + (1-p)D + 1$$
@@
 \be
-	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1
+	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1
 \ee
@@
 \emph{Proof of Lemma~\ref{lemma:efficiency}:}\\
-%The benefit of a gift appears on both sides of the incentive compatibility constraint for both types and thus cancels out in the low type incentive compatibility constraint $(peg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+peg_h )$ and in the high type incentive compatibility constraint: $(pX_{TT}^h+(1-p)X_{FF}^h - g_h +peg_h \geq X_{FF}^h +peg_h)$.
-Therefore, receiving a gift where $e<1$  does not affect incentives to truth tell about the countries' types.
 The expected separation utility for the high type under the game with material value that can be destroyed is
@@
 \emph{Proof of Lemma \ref{lemma:e-patient}:}\\
-The proof will be by contradiction.
-Suppose that the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}.
+The proof proceeds by contradiction.
+Suppose the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}.
 Since low types have patience levels below the threshold, we have that
@@
 \end{equation*}
-Combining with the inequality in Expression~\ref{eq:cont2}, we arrive at
+Combining this with the inequality in Expression~\ref{eq:cont2}, we arrive at
 \begin{equation*}
@@
  \hfill $\blacksquare$
-%\\
-%\emph{Proof of Theorem \ref{theorem:4}:}\\
-%High types choose $\alpha=1$ (because a concession would only come from another high type in equilibrium) and low types choose $\alpha=0$. The high type's utility when $e=1$ is
-%$$\frac{1}{1-\de_h}\left\{pT(1+g^1) + (1-p)(W-D(1+g^1))\right\} - (1-p)g^1 $$
-%where $g^1= \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$.
-
-%When $e=0$---that is, the future material value of the concessions is destroyed---we are essentially back in the case of Section~\ref{sec:cse}.
-High type utility when $e=0$ is $$\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - (1-p)g^0$$ where the minimum separating concession is $g^0=p(T+D)$.
-The threshold for high types to cooperate is again $\frac{W}{T+D}$.
-
-%Whether it is beneficial for high types to settle on the efficient concession or the inefficient concession is determined by comparing the utility under each, and either can be larger.
-Inefficient concessions are made optimal when $p$ is low (there's a good chance of facing a low type who will use the concession against you) as well as when $\de_l$ is low ($g^1$ is decreasing in the patience of the low type, as a larger concession is required to deter an impatient low-type from being untruthful).
-\hfill $\blacksquare$
 
@@
 
-Here was have assumed that the mediator specifies $e=1$, which means that gift giving and receiving cancels out.
-The left hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type.
-The mediator only specifies strictly positive gifts if there are two reports of `High.' Likewise, there are no gifts in the $(1-p)X_{FF}^l$ term on the right because the negotiating partner has made a report of `Low.' This leaves
+Here we specify that the mediator chooses $e=1$, which means that gift giving and receiving cancels out.
+The left hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type and the mediator only specifies strictly positive gifts if there are two reports of `High.' Likewise, there are no gifts in the $(1-p)X_{FF}^l$ term on the right because the negotiating partner has made a report of `Low.' This leaves
 		$$X_{FF}^l \geq X_{FT}^l.$$
@@
 The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium.
-The low-type player under consideration knows it will defect and end up in a ``War'' equilibrium and so invests entirely in the military.
+The low-type player knows it will defect and be in a ``War'' equilibrium and so invests entirely in the military.
 %		\begin{multline}
@@
 
-For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Theorem~\ref{theorem:med}.
+For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Lemma \ref{lemma:med}.
 So we start from
@@
 Simplifying, we have
-\[
-	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
-\]
-Gathering the terms involving $g_h$ on the left hand side:
+%\[
+%	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
+%\]
+%Gathering the terms involving $g_h$ on the left hand side:
 \[
@@
 If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
-(b) We now turn to the high type, whose incentive compatibility constraint is
+(b) The high type incentive compatibility constraint is
 \begin{equation}
@@
 \end{equation*}
-\begin{equation*}
-  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
-\end{equation*}
+%\begin{equation*}
+%  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
+%\end{equation*}
 \begin{equation*}
@@
 Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
-By Theorem~\ref{theorem:2}, separation through concessions is possible.
+By Theorem~\ref{theorem:2}, the \emph{concessions separating equilibrum with efficient gifts} is possible.
 
@@
 Using the mediation mechanism $M$ with $e=0.18$ and $g_h=7.7669$, we satisfy both the low type constraint the $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$.
-Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with efficient gifts}.
+Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with inefficient gifts}.
 		\item[(c)] Let $T = 1$, $W=1$ and $D = 1$.
@@
 
-Because the calculations are the same for the \emph{concessions separating equilibrium} and the \emph{concessions separating equilibrium with inefficient gifts}, we use Theorem~\ref{theorem:2}(a) to find the patience threshold to separate through concessions with inefficient concessions is $0.5$.
+We use Theorem~\ref{theorem:2}(a) to find that the patience threshold to separate through concessions with inefficient concessions is $0.5$.
 This combined with Lemma~\ref{lemma:e-patient} shows that neither the \emph{concessions separating equilibrium with efficient gifts} nor the \emph{concessions separating equilibrium with inefficient gifts} is possible.
@@
 \newpage
-\section{Bibliography} %can add search(kaplan), expoeriments (2) and workplace gift exchange papers (the "gift giving as a medium" explanation
+\section{Bibliography}
 
@@
 
-\item Allee, Todd L. and Paul K. Huth. (2006). ``Legitimizing Dispute Settlement: International Legal Rulings as Domestic Political Cover." \emph{American Political Science Review} 100:2, 219-34.
-
-\item Arena, Philip. (2013). ``Costly Signaling, Resolve, and Martial Effectiveness." Unpublished manuscript.
-
-\item Beardsley, Kyle. (2010). ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. 47:2, 395-406.
-
-\item Beardsley, Kyle, David M. Quinn, Bidisha Biswas, and Jonathan Wilkenfeld. (2006). ``Mediation Style and Crisis Outcomes." \emph{The Journal of Conflict Resolution} 50:1,  58-86.
-
-\item Beardsley, Kyle and Nigel Lo. (2014). ``Third-Party Conflict Management and the Willingness to Make Concessions." \emph{The Journal of Conflict Resolution} 58:2, 363-392.
-
-\item Bercovitch, Jacob, ed. (1996). \emph{Resolving International Conflicts: The Theory and Practice of Mediation.} Boulder, CO: Lynne Rienner.
-
-\item Bercovitch, Jacob. (1997). ``Mediation in International Conflict," in I.W. Zartman and J.L. Rasmussen (eds.), \emph{Peacemaking in International Conflict}, Washington DC: US Institute of Peace.
-
-\item Bercovitch, Jacob. (2000). ``Why do they do it like this? An analysis of factors influencing mediation in international conflicts." \emph{Journal of Conflict Resolution} 44:2, 170-202.
+\item Allee, Todd L. and Paul K. Huth. ``Legitimizing Dispute Settlement: International Legal Rulings as Domestic Political Cover." \emph{American Political Science Review} 100, no. 2 (2006), 219-34.
+
+\item Arena, Philip. ``Costly Signaling, Resolve, and Martial Effectiveness." Unpublished manuscript, 2013.
+
+\item Beardsley, Kyle. ``Pain, Pressure, and Political Cover: Explaining Mediation Incidence." \emph{Journal of Peace Research}. 47, no. 2(2010), 395-406.
+
+\item Beardsley, Kyle, David M. Quinn, Bidisha Biswas, and Jonathan Wilkenfeld. ``Mediation Style and Crisis Outcomes." \emph{The Journal of Conflict Resolution} 50, no. 1 (2006),  58-86.
+
+\item Beardsley, Kyle and Nigel Lo. ``Third-Party Conflict Management and the Willingness to Make Concessions." \emph{The Journal of Conflict Resolution} 58, no. 2 (2014), 363-392.
+
+\item Bercovitch, Jacob, ed. \emph{Resolving International Conflicts: The Theory and Practice of Mediation.} Boulder, CO: Lynne Rienner,  1996.
+
+\item Bercovitch, Jacob. ``Mediation in International Conflict," in I.W. Zartman and J.L. Rasmussen (eds.), \emph{Peacemaking in International Conflict}, Washington DC: US Institute of Peace, 1997.
+
+\item Bercovitch, Jacob. ``Why do they do it like this? An analysis of factors influencing mediation in international conflicts." \emph{Journal of Conflict Resolution} 44, no. 2 (2000), 170-202.
 
 \item Bercovitch, Jacob and Richard Jackson.
-(2001).
 ``Negotiation or Mediation?
-An Exploration of Factors Affecting the Choice of Conflict Management in International Conflict.'' \emph{Negotiation Journal} 17:1, 59-77.
-
-\item Bercovitch, Jacob, and Jeff Langley. (1993). ``The Nature of Dispute and the Effectiveness of International Mediation.'' \emph{Journal of Conflict Resolution} 37, 670-691.
-
-\item Bester, Helmut and Karl Warneryd. (2006). ``Conflict and the Social Contract." \emph{ Scandinavian Journal of Economics} 108(2), 231-49.
+An Exploration of Factors Affecting the Choice of Conflict Management in International Conflict.'' \emph{Negotiation Journal} 17, no.
+1 (2001), 59-77.
+
+\item Bercovitch, Jacob, and Jeff Langley. ``The Nature of Dispute and the Effectiveness of International Mediation.'' \emph{Journal of Conflict Resolution} 37 (1993), 670-691.
+
+\item Bester, Helmut and Karl Warneryd. ``Conflict and the Social Contract." \emph{ Scandinavian Journal of Economics} 108, no.2 (2006), 231-49.
 
 \item Camerer, Colin.
-(1988).
 ``Gifts as Economic Signals and Social Symbols.'' \emph {The American Journal of Sociology,} Vol.
-94, Supplement: Organizations and Institutions: Sociological and Economic Approaches to the Analysis of Social Structure: S180-S214.
-
-\item Carmichael, H. Lorne and W. Bentley MacLeod. (1997). ``Gift Giving and the Evolution of Cooperation.'' \emph {International Economic Review} 38:3, 485-509.
-
-\item Connelly, Brian L., S. Trevis Certo, R. Duane Ireland and Christopher R. Reutzel. (2011). ``Signaling Theory: A Review and Assessment.'' \emph {Journal of Management}. 37:1, 39-67.
+94 (1988), Supplement: Organizations and Institutions: Sociological and Economic Approaches to the Analysis of Social Structure: S180-S214.
+
+% \item Carmichael, H. Lorne and W. Bentley MacLeod. (1997). ``Gift Giving and the Evolution of Cooperation.'' \emph {International Economic Review} 38:3, 485-509.
+
+\item Connelly, Brian L., S. Trevis Certo, R. Duane Ireland and Christopher R. Reutzel. ``Signaling Theory: A Review and Assessment.'' \emph {Journal of Management}. 37, no. 1 (2011), 39-67.
 
@@
 
-\item Dixon, William. (1996). ``Third-Party Techniques for Preventing Conflict Escalation and Promoting Peaceful Settlement.'' \emph{International Organization} 50, 653-681.
-
-\item Duursma, Allard. (2020). ``African Solutions to African Challenges: The Role of Legitimacy in Mediating Civil Wars in Africa." \emph{International Organization} 74:2, 295-330.
-
-\item Fearon, James. (1996). ``Bargaining Over Objects that Influence Future Bargaining Power.'' \emph{Chicago Center on Democracy Working Paper}, University of Chicago.
-
-\item Fey, Mark and Kristopher W. Ramsay. (2009). ``Mechanism Design Goes to War: Peaceful Outcomes with Interdependent and Correlated Types." \emph{Review of Economic Design} 13:3, 233-250.
-
-\item Fey, Mark and Kristopher W. Ramsay. (2010). ``When Is Shuttle Diplomacy Worth the Commute?" \emph{World Politics} 62:4, 529-60.
+\item Dixon, William. ``Third-Party Techniques for Preventing Conflict Escalation and Promoting Peaceful Settlement.'' \emph{International Organization} 50 (1996), 653-681.
+
+\item Duursma, Allard. ``African Solutions to African Challenges: The Role of Legitimacy in Mediating Civil Wars in Africa." \emph{International Organization} 74, no. 2 (2020), 295-330.
+
+\item Fearon, James. ``Bargaining Over Objects that Influence Future Bargaining Power.'' \emph{Chicago Center on Democracy Working Paper}, University of Chicago, 1996.
+
+\item Fey, Mark and Kristopher W. Ramsay. ``Mechanism Design Goes to War: Peaceful Outcomes with Interdependent and Correlated Types." \emph{Review of Economic Design} 13, no. 3 (2009), 233-250.
+
+\item Fey, Mark and Kristopher W. Ramsay. ``When Is Shuttle Diplomacy Worth the Commute?" \emph{World Politics} 62, no. 4 (2010), 529-60.
 
@@
 Ramsay.
-(2011).
-``Uncertainty and Incentives in Crisis Bargaining: Game-Free Analysis of International Conflict." \emph{American Journal of Political Science} 55, 149-169.
+``Uncertainty and Incentives in Crisis Bargaining: Game-Free Analysis of International Conflict." \emph{American Journal of Political Science} 55 (2011), 149-169.
 
@@
 
-\item Fortna, Virginia Page. (2003). \emph{ Peace Time: Cease-Fire Agreements and the Durability of Peace.} Princeton: Princeton University Press.
-
-\item Greig, J. Michael. (2005a). ``Moments of Opportunity: Recognizing Conditions of Ripeness for International Mediation Between Enduring Rivals,'' \emph{Journal of Conflict Resolution} 45, 691-718.
-
-\item Greig, J. Michael, (2005b). ``Stepping into the Fray: When Do Mediators Mediate?'' \emph{American Journal of Political Science} 49:2, 249-66.
-
-\item Greig, J. Michael and Paul F. Diehl. (2006). ``Softening Up: Making Conflicts More Amenable to Diplomacy,'' \emph{International Interactions} 32, 355-84.
-
-\item Hensel, Paul. (1996). ``Charting A Course To Conflict: Territorial Issues and Interstate Conflict, 1816-1992," \emph{Journal of Conflict Resolution} 15:1, 43-73.
-
-\item Horner, Johannes, Massimo Morelli and Francesco Squintani. (2010). ``Mediation and Peace.'' \emph{The Review of Economic Studies} 84, 1483-1501.
-
-\item Iannaccone, Laurence. (1992). ``Sacrifice and Stigma: reducing free-riding in cults, communes, and other collectives.'' \emph{Journal of Political Economy} 100:2, 271-291.
+\item Fortna, Virginia Page. \emph{ Peace Time: Cease-Fire Agreements and the Durability of Peace.} Princeton: Princeton University Press, 2003.
+
+\item Greig, J. Michael. ``Moments of Opportunity: Recognizing Conditions of Ripeness for International Mediation Between Enduring Rivals,'' \emph{Journal of Conflict Resolution} 45 (2005a), 691-718.
+
+\item Greig, J. Michael. ``Stepping into the Fray: When Do Mediators Mediate?'' \emph{American Journal of Political Science} 49, no. 2 (2005b), 249-66.
+
+\item Greig, J. Michael and Paul F. Diehl. ``Softening Up: Making Conflicts More Amenable to Diplomacy,'' \emph{International Interactions} 32 (2006), 355-84.
+
+\item Hensel, Paul. ``Charting A Course To Conflict: Territorial Issues and Interstate Conflict, 1816-1992," \emph{Journal of Conflict Resolution} 15, no. 1 (1996), 43-73.
+
+\item Horner, Johannes, Massimo Morelli and Francesco Squintani. ``Mediation and Peace.'' \emph{The Review of Economic Studies} 84 (2010), 1483-1501.
+
+%\item Iannaccone, Laurence. (1992). ``Sacrifice and Stigma: reducing free-riding in cults, communes, and other collectives.'' \emph{Journal of Political Economy} 100:2, 271-291.
 
@@
 
-\item Kranton, Rachel (1996). ``The formation of cooperative relationships.'' \emph{Journal of Law, Economics, and Organization}, 12:1, 214-233.
-
-\item Kydd, Andrew. (2003). ``Which Side Are You On? Bias, Credibility, and Mediation." \emph{American Journal of Political Science} 47:4, 597-611.
-
-\item Larson, Deborah Welch. (1987). ``The psychology of reciprocity in international relations.'' \emph{Negotiation Journal.} 4:3, 281-301.
-
-\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2012). ``Mediation and Strategic Militarization.'' Unpublished manuscript.
-
-\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. (2015). ``Dispute Resolution Institutions
-and Strategic Militarization.'' Unpublished manuscript.
-
-\item Myerson, Roger B. (1979). ``Incentive Compatibility and the Bargaining Problem." \emph {Econometrica} 47, 61-73.
+% \item Kranton, Rachel (1996). ``The formation of cooperative relationships.'' \emph{Journal of Law, Economics, and Organization}, 12:1, 214-233.
+
+\item Kydd, Andrew. ``Which Side Are You On? Bias, Credibility, and Mediation." \emph{American Journal of Political Science} 47, no. 4 (2003), 597-611.
+
+%\item Larson, Deborah Welch. (1987). ``The psychology of reciprocity in international relations.'' \emph{Negotiation Journal.} 4, no. 3, 281-301.
+
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. ``Mediation and Strategic Militarization.'' Unpublished manuscript, 2012.
+
+\item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. ``Dispute Resolution Institutions
+and Strategic Militarization.'' Unpublished manuscript, 2015.
+
+\item Myerson, Roger B. ``Incentive Compatibility and the Bargaining Problem." \emph {Econometrica} 47 (1979), 61-73.
 
@@
 
-\item Prendergast, Canice and Lars Stole. (2001). ``The Non-Monetary Nature of Gifts.'' \emph {European Economic Review} 45:10, 1793-810.
-
-\item Rabin, Matthew. (1993). ``Incorporating fairness into game theory and economics.'' \emph{American Economic Review} 83:5, 1281-1301.
-
-\item Rauchhaus, Robert. (2006). ``Asymmetric Information, Mediation, and Conflict Management.'' \emph{World Politics} 58:2, 207-401.
-
-\item Slantchev, Branislav. (2011). ``Military Threats: The Costs of Coercion and the Price of Peace.'' Cambridge: Cambridge University Press.
-
-\item Smith, Alastair, and Alan Stam. (2003). ``Mediation and Peacekeeping in a Random Walk Model of Civil and Interstate War." \emph{International Studies Review} 5:4, 115-35.
-
-\item Spence, Michael. (1973). ``Job Market Signaling." \emph {The Quarterly Journal of Economics}, 87:3, 355-74.
-
-\item Svensson, Isak. (2008). ``Do Mediators Go Where they Are Needed Most? Mediation Selection in Civil Wars,'' Unpublished manuscript.
-
-\item Terris, Lesley G. and Zeev Maoz. (2005). ``Rational Mediation: A Theory and a Test.'' \emph{Journal of Peace Research} 44:5, 563-583.
-
-%\item Thaler, Richard. (1985). ``Mental Accounting and Consumer Choice.'' \emph{Marketing Science} 4:3, 199-214.
-
-\item Van Damme, E. (1989). ``Stable equilibria and forward induction. \emph{Journal of Economic Theory} 48:2, 476-496.
-
-\item Van de Ven, Jeroen. (2000).``The economics of the gift.'' Unpublished manuscript.
-
-%\item Waldfogel, Joel (2009). \emph{Scroogenomics: Why You Shouldn't Buy Presents for the Holidays}. Princeton: Princeton University Press.
-
-%\item Waldfogel, Joel (1993). ``The deadweight loss of Christmas,'' \emph{The American Economic Review} 83:5, 1328-1336.
-
-\item Walter, Barbara F. (2002). \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton: Princeton University Press.
-
-\item Waltz, Kenneth (2001).  \emph {Man, the State and War: A Theoretical Analysis.} New York : Columbia University Press. %ref cites page 159
-
-%\item Watson, Joel (1996). ``Building a Relationship,'' Unpublished manuscript.
-
-\item Watson, Joel. (1999). ``Starting Small and Renegotiation,'' {Journal of Economic Theory} 85:1, 52-90.
+\item Powell, Robert. ``Bargaining in the Shadow of Power.'' \emph{Games and Economic Behavior} 15, no. 2 (1996a), 255-289.
+
+\item Powell, Robert. ``Uncertainty, Shifting Power, and Appeasement.'' \emph{American Political Science Review} 90, no. 4 (1996b), 749-764.
+
+\item Powell, Robert. ``The Modeling Enterprise and Security Studies.'' \emph{International Security} 24, no. 2 (1999), 97-106.
+
+\item Powell, Robert. ``War as a commitment problem.'' \emph{International Organization} 60, no. 1 (2006), 169-203.
+
+\item Prendergast, Canice and Lars Stole. ``The Non-Monetary Nature of Gifts.'' \emph {European Economic Review} 45, no. 10 (2001), 1793-810.
+
+%\item Rabin, Matthew. (1993). ``Incorporating fairness into game theory and economics.'' \emph{American Economic Review} 83:5, 1281-1301.
+
+\item Rauchhaus, Robert. ``Asymmetric Information, Mediation, and Conflict Management.'' \emph{World Politics} 58, no. 2 (2006), 207-401.
+
+\item Schelling, Thomas. C. ``Arms and influence.'' New Haven: Yale University Press, 1996.
+
+\item Slantchev, Branislav. ``Military Threats: The Costs of Coercion and the Price of Peace.'' Cambridge: Cambridge University Press, 2011.
+
+\item Smith, Alastair, and Alan Stam. ``Mediation and Peacekeeping in a Random Walk Model of Civil and Interstate War." \emph{International Studies Review} 5, no. 4 (2003), 115-35.
+
+\item Spence, Michael. ``Job Market Signaling." \emph {The Quarterly Journal of Economics}, 87, no. 3 (1973), 355-74.
+
+\item Svensson, Isak. ``Do Mediators Go Where they Are Needed Most? Mediation Selection in Civil Wars,'' Unpublished manuscript, 2008.
+
+\item Terris, Lesley G. and Zeev Maoz. ``Rational Mediation: A Theory and a Test.'' \emph{Journal of Peace Research} 44, no. 5 (2005), 563-583.
+
+%\item Thaler, Richard. (1985). ``Mental Accounting and Consumer Choice.'' \emph{Marketing Science} 4, no. 3, 199-214.
+
+%\item Van Damme, E. (1989). ``Stable equilibria and forward induction. \emph{Journal of Economic Theory} 48, no. 2, 476-496.
+
+\item Van de Ven, Jeroen. `The economics of the gift.'' Unpublished manuscript, 2000.
+
+\item Walter, Barbara F. ``The Critical Barrier to Civil War Settlement.'' \emph{International Organization} 51, no. 3 (1997), 335-364.
+
+\item Walter, Barbara F. \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton: Princeton University Press, 2002.
+
+\item Waltz, Kenneth. \emph {Man, the State and War: A Theoretical Analysis.} New York: Columbia University Press, 2001. %ref cites page 159
+
+\item Watson, Joel. ``Starting Small and Renegotiation,'' {Journal of Economic Theory} 85, no. 1 (1999), 52-90.
 

### 2021-02-23 draft.tex
add back in author information and acknowledgements

@@
 \title{Inefficient Concessions and Mediation}
-%\author{Kristy Buzard\\ \footnote{We thank Eli Berman, Renee Bowen, Ben Graham, Joel Watson as well as seminar
-%participants at ... for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance.}
-%Syracuse University \\
-%kbuzard@syr.edu\\
-%\\
-%Ben Horne\\ 
-%University of California, San Diego\\
-%\\}
+\author{Kristy Buzard\footnote{We thank Eli Berman, Renee Bowen, Ben Graham, and Joel Watson as well as generous seminar
+participants for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance. All remaining errors are our own.}\\
+Syracuse University \\
+kbuzard@syr.edu\\
+\\
+Ben Horne\\ 
+University of California, San Diego\\
+\\}
 \date{\today}

### 2021-12-13 draft.tex
add references to Maor & Solan

@@
 
-Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.
-While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
+Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors but no signaling game, see Maor and Solan (2015).
+They focus on the players' belief structures, while our initial signaling stage simplifies the analysis of beliefs.} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 
+\item Maor, Cy, and Eilon Solan. ``Cooperation under incomplete information on the discount factors.'' \emph{International Journal of Game Theory} 44, no. 2 (2015), 321-346.
+
 \item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. ``Mediation and Strategic Militarization.'' Unpublished manuscript, 2012.

### 2021-12-23 draft.tex
revise draft to submit to QJPS

@@
   \usepackage{setspace}
-  \onehalfspacing
+  \doublespacing
 
@@
 
-Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.
-Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
+Equilibrium payoffs beginning from round 1 are now easily described by noting only the collective first round behavior.\footnote{If a parameter of the model changes after period 0, the equilibrium may be disrupted.
+Although it is beyond the scope of this paper, one could model this by adding a probability of equilibrium disruption followed by a new round of concessions that would essentially re-start the game--albeit with altered parameters.} Let $X_{ij}$ represent the sum of discounted payoffs for country $i$ where subscripts represent first round strategies of that country.
 If both countries play T in round 1, the corresponding payoff to country $i$ is represented as $ X_{TT}^i=\frac {T}{1- \delta_i}$.
@@
 So long as the costs are small enough to be worth her participation the mediator can effectively enter and assist in solving the conflict.
+
+One might worry about the requirement that the mediator be willing and able to ensure that the specified concessions are delivered.
+While it is by no means guaranteed that a mediator who will play this role exists for every conflict, it is not difficult to believe that such a mediator exists for many conflicts.
+We do not require a formal international enforcement mechanism, but rather that the mediator has, and is willing to use, sufficient leverage to punish a deviating party.
+Common examples of such punishments are financial or trade sanctions, or the withdrawal of aid or military support.
+Further, the mechanism can work if the mediator is either (1) only able to incentivize some portion of the concessions or (2) enforces the concessions with some probability less than 1.
+This would tighten the low type's incentive constraint and loosen the high type's incentive constraint, creating a different level of optimal efficiency of the concessions.\footnote{To see this, in the incentive constraints in the proof of Theorem~\ref{theorem:med}, replace $g_h$ with $q \cdot g_h$, where $q$ represents the proportion of the concession that can be enforced or the probability with which the full concession is enforced.}
 

### 2023-03-06 draft_narrow.tex
Update draft_narrow.tex
Working to broaden the language in the introduction to incorporate application to non-military domains.

--- 2021-12-23 draft.tex
@@
 In the course of a military conflict, settlement negotiations often occur simultaneously with continued fighting.
-If settlement can be achieved, lives are saved and destruction averted.
+This is true in non-violent disputes as well -- parties engage in costly conflict while they negotiate.
+If settlement can be achieved, additional costs of conflict -- including additional death and destruction -- are averted.
 Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective (e.g., Bercovitch 2000; Greig 2005a; Beardsley et al.
 2006; Duursma 2020).
-This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that combatants can offer.
+This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that conflict participants can offer.
 In our context, the efficiency of a concession is determined by how much of the material value of the concession is intact when the recipient receives it.
@@
 We introduce a two-sided signaling model in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
-Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to peace.
-Perhaps more importantly, the mediator can also sometimes facilitate peace when the negotiating parties cannot achieve it through bilateral interaction.
-
-Two archetypal situations illustrate the significance and difficulty of efficient concession-making in war settlement.
+Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to a settlement.
+Perhaps more importantly, the mediator can also sometimes facilitate settlement when the negotiating parties cannot achieve it through bilateral interaction.
+
+Two archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
 The first is the case of disarmament and the second is the concession of control over strategically valuable territory.
+In latter sections of the paper we discuss the applicability of the model to cases of nonviolent conflict as well, but peacemaking provides a particularly challenging and impactful context to illustrate the utility of inefficient concessions.
 
@@
 This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can both help increase the efficiency of concessions and make peace.
-Weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
-One way to address this concern is to destroy the future value of the concession---e.g.
-decommission weapons or attempt to reduce the strategic value of the territory.
+In the war context, weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
+More broadly, countries are reluctant to make concessions that can be used against them in latter rounds of conflict or negotiation.
+One way to address this concern of dangerous concessions is to destroy the future value of the concession---e.g.
+decommission weapons or attempt to reduce the strategic value of the territory being conceded.
 Another option, and the one on which we focus in this paper, is third-party mediation.
-We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling combatants to make more efficient concessions, even when there is a risk those concessions might increase the bargaining power of their opponent in the future.
+We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling disputants to make more efficient concessions, even when there is a risk those concessions might increase the bargaining power of their opponent in the future.
 
@@
 When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation (Fearon 1996).
+%[OUTSIDE THE WAR CONTEXT..., ???]
 
@@
 This is not always the case, however.
-Mahmous Abbas may be a low type, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.
+Mahmoud Abbas, President of the Palestinian National Authority, may be a low type with respect to his negotiations with Israel, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.
 

### 2023-03-13 draft_narrow.tex
Update draft_narrow.tex
More minor tweaks to the intro.
China-US case added to intro
The China-US case is now worked into the intro with export controls on dual-use technology as a 3rd archetypal case -- along with disarmament and strategic territory.

@@
 In the course of a military conflict, settlement negotiations often occur simultaneously with continued fighting.
-This is true in non-violent disputes as well -- parties engage in costly conflict while they negotiate.
+This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition -- parties engage in costly conflict while they negotiate.
 If settlement can be achieved, additional costs of conflict -- including additional death and destruction -- are averted.
@@
 Perhaps more importantly, the mediator can also sometimes facilitate settlement when the negotiating parties cannot achieve it through bilateral interaction.
-
-Two archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
-The first is the case of disarmament and the second is the concession of control over strategically valuable territory.
-In latter sections of the paper we discuss the applicability of the model to cases of nonviolent conflict as well, but peacemaking provides a particularly challenging and impactful context to illustrate the utility of inefficient concessions.
+In other words, commitment is essentially a far-sighted preferences that allows cooperation to emerge, uncertainty can result in missed opportunities for cooperation, and concessions and mediation can facilitate conflict settlement.
+%The sentence above literally parrots the editor's words back to them. Too on the nose?
+
+%Attempting to add in the China-US case in a prominent way. The prose is more awkward than I would like still. - March 13, 2023 BG
+Three archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
+The first is the case of disarmament, the second is the concession of control over strategically valuable territory, and the third is the export of advanced technology.
+%In each case, efficient concessions are difficult to make because the item conceded may be used by the recipient to bolster their military capabilities, altering the balance of power in the ongoing conflict.
+Also true in each case, if dispute settlement is achieved, a public good is produced -- peace in the first two cases and innovation and growth in the civilian economy in the third case.
 
@@
 
+In our third archetypal example, the US has recently moved to restrict the export of cutting-edge technology to China.
+China and the US are engaged in geo-strategic competition.
+Both countries could benefit from the more rapid innovation and growth that free trade in chips and other technology would enable, but there is risk that the technology exported will be used in the military sector to pursue advanced weapons, altering the military balance of power.
+As of 2023, trade in advanced technologies is restricted, reducing the global pace of innovation and economic growth.
+
 Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
-Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996).
-Can mediation offer a path to settlement in these challenging contexts?
+Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
+Can mediation offer a path to settlement -- and a path to peace and prosperity -- in these challenging contexts?
 
@@
 One way to address this concern of dangerous concessions is to destroy the future value of the concession---e.g.
-decommission weapons or attempt to reduce the strategic value of the territory being conceded.
+decommission weapons, attempt to reduce the strategic value of the territory being conceded, or only allowing trade in technologies without military applications.
 Another option, and the one on which we focus in this paper, is third-party mediation.
@@
 
+%I need to add a bit about historical international relations, and a couple of cites, to the two paragraphs below. BG 3-13-2023
 Often, inefficient gifts occur in the formative stages of relationships or in immature relationships (Camerer 1988).

### 2023-03-20 draft_narrow.tex
Added back in the Golan heights opener
I am now quite happy with the first 6 pages.

@@
 \begin{abstract}
-When two parties are engaged in conflict and each distrusts the other's ability to pursue peace, concessions can be used to indicate an interest in making peace.
+When two parties are engaged in conflict and each distrusts the other's ability to cooperate or make peace, concessions can be used to indicate an interest in cooperation or peacemaking.
 However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made.
-It can also reduce the possibility of peace.
-We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
+It can also reduce the possibility of peace or cooperation.
+We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation.
 In this process, we open up a new rationale for mediation: to increase the inefficiency of signaling in a preliminary round of negotiations.
@@
 
-In the course of a military conflict, settlement negotiations often occur simultaneously with continued fighting.
-This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition -- parties engage in costly conflict while they negotiate.
+In negotiations with its neighbors, Israel is hesitant to give certain concessions.
+The Golan Heights, captured from Syria during the 1967 War, is a particular point of contention in Israeli-Syrian relations.
+While the Golan Heights does not have the West Bank’s historic or religious importance, Israel values it for its highly strategic location.
+The Golan Heights could be a useful concession, but Israel senses that were she to give over the land, Syria may ultimately use the concession against them.
+This same hesitancy exists with the West Bank settlements.
+Many are located on hilltops that could offer strategic military outposts for forces hostile to Israel.
+When it occasionally abandons settlements, Israel generally dismantles all infrastructure, including water and electricity, and bulldozes the buildings.
+Although inefficient, this reduces the possibility of those settlements being used against Israeli interests.
+Without trust, the most efficient concessions often are not made.
+
+In both active wars and long-simmering conflicts, settlement negotiations often occur simultaneously with continued fighting.
+This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition: parties engage in costly conflict while they negotiate.
 If settlement can be achieved, additional costs of conflict -- including additional death and destruction -- are averted.
@@
 Three archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
-The first is the case of disarmament, the second is the concession of control over strategically valuable territory, and the third is the export of advanced technology.
+The first is the case of disarmament, the second is the concession of strategically valuable territory, and the third is the export of advanced technology to a strategic rival.
 %In each case, efficient concessions are difficult to make because the item conceded may be used by the recipient to bolster their military capabilities, altering the balance of power in the ongoing conflict.
@@
 Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide military advantage in a future conflict.
-
 Following the 1992 war between Armenia and Azerbaijan over the disputed region of Ngorno-Karabakh, Armenia retained control of a significant amount of Azeribaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland.
@@
 
-In our third archetypal example, the US has recently moved to restrict the export of cutting-edge technology to China.
+In our third archetypal example, under both the Trump and Biden administrations, the US has restricted the export of cutting-edge technology to China.
 China and the US are engaged in geo-strategic competition.
-Both countries could benefit from the more rapid innovation and growth that free trade in chips and other technology would enable, but there is risk that the technology exported will be used in the military sector to pursue advanced weapons, altering the military balance of power.
-As of 2023, trade in advanced technologies is restricted, reducing the global pace of innovation and economic growth.
+Both countries could benefit from the more rapid innovation and growth that free trade in chips and other technology would enable, but there is risk that any technology exported will be used in the military sector to pursue advanced weapons, altering the military balance of power.
+As of 2023, trade in numerous advanced technologies is restricted, reducing the global pace of innovation and economic growth.
 
@@
 Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
-Can mediation offer a path to settlement -- and a path to peace and prosperity -- in these challenging contexts?
+Can mediation offer a path to more settlement, peace and prosperity in these challenging contexts?
 
 This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can both help increase the efficiency of concessions and make peace.
-In the war context, weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
-More broadly, countries are reluctant to make concessions that can be used against them in latter rounds of conflict or negotiation.
-One way to address this concern of dangerous concessions is to destroy the future value of the concession---e.g.
-decommission weapons, attempt to reduce the strategic value of the territory being conceded, or only allowing trade in technologies without military applications.
+Weapons, strategically valuable territory, and the sharing of advanced technology will not be conceded if the conceding side fears that these items may be used in future attacks against them.
+Countries are reluctant to make concessions that can be used against them in latter rounds of conflict or negotiation.
+One way to mitigate the risk of dangerous concessions is to destroy the future value of the concession---e.g.
+decommission weapons, attempt to reduce the strategic value of the territory being conceded, or only allow trade in less advanced technologies or technologies without military applications.
 Another option, and the one on which we focus in this paper, is third-party mediation.
@@
 
-In these models war can be averted by splitting the pie (i.e.
-the disputed territory) in a way acceptable to both parties.
+In these models war can be averted by splitting the pie (e.g., the disputed territory) in a way acceptable to both parties.
 Concessions are modeled as offering part of the pie to the other party, and asymmetric information is about each party's \textit{resolve} to fight and/or military capabilities (Arena 2013).
@@
 
-We will approach the commitment problem through this same general understanding, but we model a party's ability to cooperate as private information.
+We approach the commitment problem through this same general understanding, but we model a party's ability to cooperate as private information.
 A high type is able to cooperate; a low type has incentives not to cooperate.
@@
 
-In conflict resolution, concessions may act as signals or as an end in themselves -- or as both simultaneously.
+In our model, concessions may act as signals or as an end in themselves -- or as both simultaneously.
 One contribution of this paper is that it allows concessions to have future material value, signaling value, and both.

### 2023-03-20 draft_narrow.tex
misc nits

@@
 
-In efforts to explain the existence of gift giving,  Camerer (1988) and Van de Ven (2000) give several anthropological explanations for inefficiency.
-Amongst these explanations are altruism, social mores, and egoism.
+In efforts to explain the existence of gift giving,  Camerer (1988) and Van de Ven (2000) give several anthropological explanations for inefficiency.\footnote{Prendergast and Stole (2001) also provide an explanation for inefficient gift giving focused on the utility of matching.} Amongst these explanations are altruism, social mores, and egoism.
 But the most relevant explanation for the field of international relations is that gift giving is strategic.
@@
 
-Prendergast and Stole (2001) provide a second explanation for inefficient gifts.
+%Prendergast and Stole (2001) provide a second explanation for inefficient gifts.
 The authors explain inefficient gift giving by modeling the utility of matching.
@@
 The basic formulation of our mechanism-design approach is an expansion of Camerer's (1988) analysis.
-The model can achieve the basic `inefficient gifts' results of Camerer (1988) and Prendergast and Stole (2001) but does so using a very different explanation for inefficiency.
+The model can achieve the basic `inefficient gifts' results of Camerer (1988) %and Prendergast and Stole (2001)
+but does so using a very different explanation for inefficiency.
 The basic model is a costly signaling model, at its root similar to Spence (1973) and subsequent papers.\footnote{See Connelly et al.
@@
 This \emph{pooling equilibrium} is likely to happen when countries are in long-set patterns of distrust.
-Active fighting is not necessary; remaining outside of a state of peace is all that is required.
+Active fighting is not necessary; remaining outside of a state of peace/cooperation is all that is required.
 See the Appendix for a formal characterization of this type of equilibrium.
 
-Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward.
+%Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward.
 While both sides posture that they want peace, and while there has been some lessening of tensions, very few concrete actions have been taken that move the sides toward settlement.
@@
 
-Sri Lanka is another example.
+Sri Lanka offers one example.
 While the government has finally won the war of secession, it still refuses to address grievances of the minorities and leaves the conflict unresolved.
-Other prominent examples of this pooling equilibrium include Israel and its neighbors, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
+Other prominent examples of this pooling equilibrium include Israel and its neighbors, Cyprus's civil war, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
 The mistrust is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
+
+Outside the war context, [EXAMPLE NEEDED].
 

### 2023-08-05 draft_narrow.tex
address semi-separating equilibria

@@
 
-In the \emph{concessions separating equilibrium}, low types do not give concessions while high types give a concession in period 0.
+In the \emph{concessions separating equilibrium}, low types do not give concessions because the concession level is set as the smallest amount that will deter the impatient type from mimicking the patient type.
+In contrast, high types always give a concession in period 0.
+Thus, the patience level of both countries is fully revealed in equilibrium.
 If both countries receive concessions, they know the other is a high type and both play Trust in subsequent periods.
@@
 
-Low types don't give gifts in this separating equilibrium because the gift wouldn't serve any purpose: the low type will be identified through the separating behavior of the high types and there is thus nothing to gain.
+Low types don't give gifts in this separating equilibrium because the gift wouldn't serve any purpose: the low type will be identified through the separating behavior of the high types and there is thus nothing to gain.\footnote{The transmission of information about each country's type is, by definition, essential for the existence of a \emph{concessions separating equilibrium}.
+Thus, there cannot exist a \emph{concessions semi-separating equilibrium} where the low type gives a concession with strictly positive probability; the concessions would not transmit the information required to build trust.
+If no information is transmitted, then the high type has no incentive itself to give a concession, so neither is there a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions where the players separate in the repeated game as in the no concessions separating equilibrium.}
 
@@
 
-Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.
-Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.\footnote{When $\de = \frac{W}{T+D}$, there is also a semi-separating equilibrium where only some high types give a concession.
+Here, high types give a smaller expected concession and trade off a lower probability of achieving peace.
+We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for peace.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
 

### 2023-08-06 draft_narrow.tex
Update draft_narrow.tex
Add an extra sentence to set up our discussion of how hard settlement/public goods provision is.
Update draft_narrow.tex
Chop out the two paragraphs on the bargaining model of war and compress them into a footnote that is introduced when we first talk about Walter and civil war settlement.

@@
 If the rebels can instead decommission those weapons, an important stumbling block to peace is removed.\footnote{Other stumbling blocks remain, including the fact that government retains its weapons.
-Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.
+Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.\footnote{Walter's approach is part of a much broader literature on the bargaining model of war that looks at concessions and asymmetric information, including  Fearon (1996), Powell (1996a and 1996b, 2006), Slantchev (2011) and Arena (2013).}
 
@@
 
+In all three of these archetypal examples, cooperative/peaceful outcomes are extremely challenging to reach.
 Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
 Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
-Can mediation offer a path to more settlement, peace and prosperity in these challenging contexts?
+Can mediation offer a path to more settlement, peace, and prosperity in these challenging contexts?
 
@@
 
-While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research.
+%While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research.
 The broader literature that attempts to model war has included concessions as part of bargaining, but has not explicitly considered the role of concessions in achieving peace.
@@
 
-In these models war can be averted by splitting the pie (e.g., the disputed territory) in a way acceptable to both parties.
+%In these models war can be averted by splitting the pie (e.g., the disputed territory) in a way acceptable to both parties.
 Concessions are modeled as offering part of the pie to the other party, and asymmetric information is about each party's \textit{resolve} to fight and/or military capabilities (Arena 2013).
@@
 
-We approach the commitment problem through this same general understanding, but we model a party's ability to cooperate as private information.
+%We approach the commitment problem through this same general understanding, but
+
+We model a party's ability to cooperate as private information.
 A high type is able to cooperate; a low type has incentives not to cooperate.

### 2023-08-06 draft_narrow.tex
Update draft_narrow.tex
Update the description of why we define welfare the way we do.

@@
 Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
-We will take the measure of social welfare, and thus the determinant of the optimal equilibrium, to be the sum of participating high types' expected utilities.
+We take achieving peace, or more broadly, achieving the provision of public goods, as the normative goal with respect to advancing social welfare.
+Only high types are capable of making peace/providing public goods, and thus we will take as the measure of social welfare to be the sum of the participating high types’ utilities.
 

### 2023-08-06 draft_narrow.tex
Broaden conclusion language slightly
Add "public goods" in a few places where we only talk about peace

@@
 
-Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
+%Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way.
 Certain relationships between the USA and countries alienated by WikiLeaks -- such as Italy -- would be an example.
@@
 In particular, if concessions may be used to harm the giver materially, it may be better to give inefficient concessions.
-This explanation captures the hesitancy of nations to fully engage in moving forward with a peace process when there is mutual distrust.
+This explanation captures the hesitancy of nations to fully engage in moving forward with a peace process or other cooperation when there is mutual distrust.
 
@@
 
-This model focuses on manipulative mediation, which is indeed used in resolving conflicts.
+This model focuses on manipulative mediation, which is indeed used in resolving conflicts and achieving cooperation.
 However, the usefulness of mediation in this case relies on the mediator being both perfectly trustworthy and perfectly able to enforce concessions.
@@
 
-This paper shows that inefficient concessions may be used to achieve peace when efficient concessions are not sufficient to do so; it also demonstrates how a mediator can achieve peace in these situations when the parties to the conflict cannot do so on their own.
+This paper shows that inefficient concessions may be used to achieve peace or cooperation to provide of other public goods when efficient concessions are not sufficient to do so; it also demonstrates how a mediator can achieve cooperation in these situations when the parties to the conflict cannot do so on their own.
 Opportunities for further research clearly include looking at the roles of different types of mediation.

### 2023-08-07 draft_narrow.tex
re-work mediation section to put emphasis on mediator

@@
 The results in this paper thus far have relied on bilateral engagement.
-We will now consider the involvement of a mediator when concessions have future material value that can benefit or harm the giver.
+We will now consider the involvement of a mediator when concessions have future material value.
+We model the mediator as solving a mechanism design problem to create a plan for concessions that elicits truthful revelation of the parties' abilities to commit to cooperation.
 
 Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz 2001), much of the literature has focused on self-enforcing mechanisms.
-If however a credible third party exists, then results beyond self enforcing agreements can be relevant.
+If, however, a credible third party exists, then results beyond self enforcing agreements can be relevant.
 A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997).
 We will now introduce a mediator who does the latter.\footnote{Here the parties' actions in the stage game as well as their choices of whether to spend concessions on the civil versus the military sector are assumed to derive from their type, so there is no need for the mediator to enforce these decisions once the type is revealed.
-Thus, we do not assume that the mediator can do either because it is not necessary.}
+Thus, it is not necessary to assume that the mediator can do both.}
 
 The model setup is as before, but instead of parties being free to choose their concession levels, the mediator solicits type reports and then enforces incentive compatible concessions.
-The Revelation Principle tells us that it is without loss of generality to restrict attention to direct mechanisms, that is, mechanisms in which countries simply declare their types (Myerson 1979).
 This mediator will be modeled as a mechanism $M$.
 
-After learning their type, each country chooses to participate in the mechanism or not; that is, whether to send a message that declares its type to be High or Low.
-By the revelation principle, it is again without loss of generality to consider equilibria in which both countries participate and send truthful reports.
-Therefore we have a mechanism $M$ that inputs the reports $t_i \in \left\{High,Low\right\}$ for $i \in \left\{1,2\right\}$ and outputs the required concessions $g_i$ and efficiency levels $e_i$ so that $ M:(t_1,t_2)\rightarrow( e_1, g_1; e_2,g_2)$.
-The countries are bound to send the mandated concessions.
+After learning its type, each country chooses to participate in the mechanism or not.
+By the Revelation Principle (Myerson 1979), it is without loss of generality to restrict attention to direct mechanisms\footnote{Direct mechanisms are those in which countries simply declare their types.} and to focus on equilibria in which both countries participate and send truthful reports.
+Participation in the mechanism therefore involves sending a message that declares one's type to be High or Low and then being bound to send the mandated concessions.
+Formally, the mechanism $M$ inputs the reports $t_i \in \left\{High,Low\right\}$ for $i \in \left\{1,2\right\}$ and outputs the required concessions $g_i$ and efficiency levels $e_i$ so that $ M:(t_1,t_2)\rightarrow( e_1, g_1; e_2,g_2)$.
 
@@
 Otherwise, the setup is the same as in Section~\ref{sec:matval} where concessions have future material value that can optionally be destroyed.
-
-As usual, truthful self-revelation requires that the incentive compatibility constraint for each type must be satisfied.
+In the mechanism design context, we focus on the incentive compatibility constraints that must be satisfied for each type to truthfully reveal its type.
+
+We find that, to prevent the low type from being tempted to misrepresent its type in order to receive the gift, some value of the concessions must be destroyed.
+That is, $e<1$, implying that the gifts mandated by the mediator must be inefficient.
 
@@
 
-In order to make the mechanism incentive compatible for the low types, some value of the concessions must be destroyed, i.e.
-$e<1$, so that the low type is not tempted to misrepresent its type in order to receive the gift.
 The range of efficiency that allows for a mechanism $M$ to be incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
@@
 \begin{enumerate}
-		\item[(a)] The mediation mechanism $M$ is incentive compatible and individually rational for the low type when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)},$ with the denominator of this expression strictly positive.
-		\item[(b)] The mediation mechanism $M$ is incentive compatible and individually rational for the high type either when $Te < (1-\de_h)(1-e)$ or the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
+		\item[(a)] A mediator using mechanism $M$ must ensure that $M$ is incentive compatible and individually rational for the low type.
+This happens when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)},$ with the denominator of this expression strictly positive.
+		\item[(b)] A mediator using mechanism $M$ must ensure that $M$ is incentive compatible and individually rational for the high type.
+This happens when either $Te < (1-\de_h)(1-e)$ or the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
 \end{enumerate}
@@
 
-The low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism; this puts an upper bound on how efficient concessions can be.
-In some cases, the high type incentive constraint also provides an upper bound on the size of the concession.
-
-Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that the mediation mechanism $M$ can do both.
+In part (a), we see that the low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism.
+This puts an upper bound on how efficient concessions can be.
+In part (b), we see that the high type incentive constraint also provides an upper bound on the size of the concession in some cases.
+
+Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that a mediator who implements mechanism $M$ can do both.
 
 \begin{theorem}
-	When concessions have future material value, the mediation mechanism $M$ can be used to
+	When concessions have future material value, a mediator can use mechanism $M$ to
 	\begin{enumerate}
@@
 
-(c) When the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
-By ensuring that only high types exchange gifts, the mediator removes this threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
-This allows types with lower patience levels to separate through the mechanism when those same types cannot separate in the bilateral game with concessions with future material value.
+Part (c) is relevant when the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large.
+In this case, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
+By ensuring that only high types exchange gifts, the mediator removes the threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
+Here, the help of the mediator allows types with lower patience levels to separate when those same types cannot separate in the bilateral game with concessions with future material value.
 
@@
 (2010) take cheap talk communication as their benchmark of unmediated communication, whereas we take the unmediated signaling game as our benchmark.} In our model, a successful mediator relies on the parties trusting her.
-However, here the mediator had no incentive to lie: lying can only potentially hurt the high types, the only type who the mediator can possibly help.
+However, here the mediator has no incentive to lie: lying can only potentially hurt the high types, the only type who the mediator can possibly help.
 

### 2023-08-07 draft_narrow.tex
add footnote about bargaining theory of war contrasts

@@
 A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in [0,1].$ Before the start of the game, nature independently determines the types of country 1 and country 2.
-The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict; that is, throughout the analysis we will define a low type to be a player whose only sequentially rational strategy is to remain in conflict in all periods.
-It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
+The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict; that is, throughout the analysis we will define a low type to be a player whose only sequentially rational strategy is to remain in conflict in all periods.\footnote{This is in contrast to the bargaining theory of war, where a high(low) type has strong(weak) military capability that then interacts with a symmetric, known level of $\delta$.
+This accounts for the different impact of $\delta$ in the two models.} It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}
 

### 2023-08-07 draft_narrow.tex
add comparative statics on p

@@
 When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type.
-Finally, and perhaps surprisingly, the patience threshold is increasing in $p$.
-This happens because the gift must be larger in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}
+Finally, the patience threshold is decreasing in $p$, the proportion of cooperative types in the population.
+This happens because a higher $p$ increases the chances of cooperation, a reciprocated gift, and the benefits from the associated public goods.
+This gain outweighs the cost of giving a larger gift, which is necessary to deter the low type from mimicking the high type when the probability of receiving a gift increases with $p$.
+In contrast, in the model with no material value---where the incentives are the same as in the model of the next section where material value can be destroyed---the need to give a larger gift is exactly offset by the increased value of cooperation when there is no material value.
+Thus, an increase in $p$ increases the range of patience levels under which cooperation can be achieved when there is material value but makes no change if there is no material value.\footnote{Comparative statics calculations available from the authors upon request.}
 

### 2023-08-07 draft_narrow.tex
fix a typo

@@
 We take achieving peace, or more broadly, achieving the provision of public goods, as the normative goal with respect to advancing social welfare.
-Only high types are capable of making peace/providing public goods, and thus we will take as the measure of social welfare to be the sum of the participating high types’ utilities.
+Only high types are capable of making peace/providing public goods, and thus we will take the measure of social welfare to be the sum of the participating high types’ utilities.
 

### 2023-08-07 draft_narrow.tex
make Ben's editorial changes to my new text from memo, fix footnote 11

@@
 
-Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors but no signaling game, see Maor and Solan (2015).
-They focus on the players' belief structures, while our initial signaling stage simplifies the analysis of beliefs.} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
+Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors, focused on studying players' belief structures, see Maor and Solan (2015).
+Our model differs in that it adds an initial period, before the repeated Prisoner's Dilemma begins, in which players make costly concessions to each other.
+We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler.} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 Thus, there cannot exist a \emph{concessions semi-separating equilibrium} where the low type gives a concession with strictly positive probability; the concessions would not transmit the information required to build trust.
-If no information is transmitted, then the high type has no incentive itself to give a concession, so neither is there a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions where the players separate in the repeated game as in the no concessions separating equilibrium.}
+If no information is transmitted, then the high type has no incentive itself to give a concession.
+Therefore, there cannot be a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions and the players separating in the repeated game as in the no concessions separating equilibrium.}
 
@@
 This happens because a higher $p$ increases the chances of cooperation, a reciprocated gift, and the benefits from the associated public goods.
-This gain outweighs the cost of giving a larger gift, which is necessary to deter the low type from mimicking the high type when the probability of receiving a gift increases with $p$.
+The larger expected gain from a gift makes states willing to bear the cost of giving a larger gift; thus, when p is higher, a larger gift is necessary to deter the low type from mimicking the high type.
 In contrast, in the model with no material value---where the incentives are the same as in the model of the next section where material value can be destroyed---the need to give a larger gift is exactly offset by the increased value of cooperation when there is no material value.

### 2023-08-09 draft_narrow.tex
address Meirowitz model and make stronger argument about our contributions

@@
 It can also reduce the possibility of peace or cooperation.
-We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation.
-In this process, we open up a new rationale for mediation: to increase the inefficiency of signaling in a preliminary round of negotiations.
+We show this formally using a repeated game that is preceded by an opportunity to signal one's commitment to cooperation through the provision of concessions.
+We then use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation.
+In this process, we open up a new rationale for mediation: to increase the efficiency of signaling in a preliminary round of negotiations and to overcome the concern that concessions will be used against the giver in the future.
 \end{abstract}
@@
 
-We introduce a two-sided signaling model in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
+We introduce a two-sided signaling model followed by a repeated Prisoner's Dilemma in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
+We use this model to show that cooperation can be undermined by concerns that concessions could be used against the giver in the future.
 Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to a settlement.
@@
 2010; Meirowitz et al.
-2012, 2015).
-This paper expands the theoretical literature by modeling the role of mediation when information is asymmetric about parties' abilities to commit to peace.
-Here, a mediator can remove the incentive to make concessions that are inefficient.
+2012, 2019).
+In particular, Meirowitz et al.
+2019 shows that---when asymmetric information is about the level of militarization---a `Myerson' mediator can circumvent the incentives for militarization that arises in unmediated peace talks and improve the changes for peace.
+This paper expands the theoretical literature by modeling the role of a manipulative mediator when the information asymmetry is about parties' abilities to commit to cooperation and concessions have future material value that could be used to harm the giver.
+Here, a mediator can achieve peace (1) in situations where bilateral concessions cannot, and (2) with concessions that are more efficient when bilateral concessions must be inefficient to achieve peace.
 
@@
 \item Meirowitz, Adam; Massimo Morelli; Kristopher W. Ramsey and Francesco Squintani. ``Dispute Resolution Institutions
-and Strategic Militarization.'' Unpublished manuscript, 2015.
+and Strategic Militarization.'' \emph{Journal of Political Economy} 127, no. 1 (2019), 378-418.
 

### 2023-08-09 draft_narrow.tex
add footnote about material value functional form, pump up abstract

@@
 It can also reduce the possibility of peace or cooperation.
-We show this formally using a repeated game that is preceded by an opportunity to signal one's commitment to cooperation through the provision of concessions.
+Using a repeated game that is preceded by an opportunity to signal one's commitment to cooperation through the provision of concessions, we formally demonstrate that concerns over the future use of concessions can explain the existence of inefficient concessions.
 We then use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation.
@@
 However, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
-The other payoffs are modified analogously.
+The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, or if they are scaled by these variables but with a proportion other than 1.
+The results are a bit simpler if there is no scaling, but we believe it is more realistic to assume that the future benefits and costs of the gifts are proportional to the direct benefits and costs of cooperation/non-cooperation.
+For instance, a county who could impose more damage without the future value of the concessions is likely to be able to better leverage a concession than a country who can impose less damage.}
 

### 2023-08-09 draft_narrow.tex
highlight contribution of concessions that don't need credible commitment

@@
 We will show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.
+Another contribution is that the way we model concessions does not require countries to make an agreement that requires credible commitment, as is common in bargaining models.
+Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve peace in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}
 

### 2023-08-09 draft_narrow.tex
small mods to address Reviewer 2's 'minor points'

@@
 \\
-Here, as in each further iteration of the model, we define a high type as a country who prefers to play the ``Peace'' equilibrium, i.e.
+Here, as in each further iteration of the model, we define a high type as a country who has a discount factor at or above the threshold for cooperation.
+That is, high types prefer to play the ``Peace'' equilibrium, i.e.
 $\delta_h \geq \delta^{nc}$.
-Any country with $\delta_l < \delta^{nc}$ is a low type.
-This means that two high types---and only two high types---can sustain the ``Peace'' outcome.
+Any country with $\delta_l < \delta^{nc}$ is a low type for the purposes of the \emph{no concessions separating equilibrium}.
+This means that two high types---and only two high types---can sustain the ``Peace'' outcome.\footnote{Note that, because we define high and low types relative to each type of equilibrium, a country with a given discount factor can be a high type in some equilibria and a low type in others.}
 
@@
 
-For example, if both countries play Fight, Country 1 receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
+For example, if both countries play Fight, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
+Its welfare now has two additional terms.
+First, an additional benefit term in each period of the repeated game $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
+Second, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ in each period of the repeated game that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
 The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, or if they are scaled by these variables but with a proportion other than 1.

### 2023-08-10 draft_narrow.tex
tweak last sentence of intro

@@
 This paper expands the theoretical literature by modeling the role of a manipulative mediator when the information asymmetry is about parties' abilities to commit to cooperation and concessions have future material value that could be used to harm the giver.
-Here, a mediator can achieve peace (1) in situations where bilateral concessions cannot, and (2) with concessions that are more efficient when bilateral concessions must be inefficient to achieve peace.
+Here, a mediator can achieve peace or the provision of other public goods (1) in situations where bilateral concessions cannot, and (2) with concessions that are more efficient when bilateral concessions must be inefficient to achieve peace.
 

### 2023-08-10 draft_narrow.tex
add detail about non-linearity in footnote on material value functional form

@@
 Second, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ in each period of the repeated game that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
-The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, or if they are scaled by these variables but with a proportion other than 1.
+The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, or if they are scaled by these variables but with a proportion other than 1 or many plausible non-linear functions of $T$, $W$ and $D$.
 The results are a bit simpler if there is no scaling, but we believe it is more realistic to assume that the future benefits and costs of the gifts are proportional to the direct benefits and costs of cooperation/non-cooperation.

### 2023-08-16 draft_narrow.tex
revise comparative statics and add calcs to appendix

@@
 Here, high types give a smaller expected concession and trade off a lower probability of achieving peace.
-We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for peace.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for peace and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
 
@@
 
-Comparative statics provide intuition for why using concessions with future material value makes it harder to achieve peace.
-The patience threshold is decreasing in $T$ because the benefit from cooperating with another high type increases.
-Similarly, the threshold is increasing in $D$ because the magnitude of future damages from pairing with a low type increases.
-Perhaps less obvious is the impact of $W$: here the threshold is again increasing.
-This is because the high type's own temptation to not give a gift and to use a received concession for military purposes increases in $W$.
-
-When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type.
-Finally, the patience threshold is decreasing in $p$, the proportion of cooperative types in the population.
-This happens because a higher $p$ increases the chances of cooperation, a reciprocated gift, and the benefits from the associated public goods.
-The larger expected gain from a gift makes states willing to bear the cost of giving a larger gift; thus, when p is higher, a larger gift is necessary to deter the low type from mimicking the high type.
-In contrast, in the model with no material value---where the incentives are the same as in the model of the next section where material value can be destroyed---the need to give a larger gift is exactly offset by the increased value of cooperation when there is no material value.
-Thus, an increase in $p$ increases the range of patience levels under which cooperation can be achieved when there is material value but makes no change if there is no material value.\footnote{Comparative statics calculations available from the authors upon request.}
-
-Thus only an increase in the benefit from `Peace' and an increase in the low type's patience level make it easier to achieve `Peace' when gifts have future material value.
-Increases in all other parameters make it harder to achieve `Peace.'
+The comparative statics for the patience threshold $\de^c = \frac{W}{T+D}$ are straightforward for the \emph{concession separating equilibrium} when there's no material value.
+The threshold increases and cooperation becomes less likely when $W$ increases; the threshold decreases when either $T$ or $D$ increase.
+These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value when the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Fight larger.
+The patience threshold decreases in $T$ and $D$, but for different reasons.
+$T$ is straightforward: a larger $T$ is a larger benefit from playing Trust.
+In contrast, a larger $D$ is a bigger cost of the negotiating partner playing Fight.
+These relationships are not fundamentally changed by the presence of future material value because the future material value is proportional to the fundamental values of $W$, $T$, and $D$.
+
+There are, however, two variables that do not affect the patience threshold in the no material value case that \textit{do} affect the threshold when there is future material value: $\de_l$ and $p$.
+When the low type's patience level $\de_l$ increases, the high type's patience threshold increases; this is because a more patient low type requires a larger gift in order not to mimic the high type.
+In the case of no material value, the low type's discount factor doesn't enter into the gift, and therefore it doesn't influence how much patience is required for cooperation.
+
+The other variable that influences the patience threshold in the case of future value is $p$, the proportion of cooperative types in the population.
+Although the gift in the no-future-material-value case \emph{is} a function of $p$, it is a linear function of $p$ just like the variables $T$, $W$, and $D$.
+Thus the cost of paying the gift and the direct benefits in the repeated game increase at the same rate.
+In the future-material-value case, the size of the gift required to separate the high types from the low types increases more than linearly in $p$ and thus faster than the other terms.
+Therefore the patience threshold increases as $p$ increases.\footnote{For the comparative statics calculations, see Appendix~\ref{ap:mat_val}.}
 
@@
 \subsection{Concessions with Material Value}
+\label{ap:mat_val}
 \emph{Proof of Theorem \ref{theorem:csemv}:}\\
@@
 That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$
+
+\vskip.3in
+\noindent\emph{Comparative statics}
+
+First, we examine the gifts in a \emph{concessions separating equilibrium} first with no material value (or destroyed material value) and then when there is future material value.
+
+That the gift in the {concessions separating equilibrium} with no material value (or destroyed material value) is increasing in $p$ is direct since the gift is equal to $p(T+D)$.
+It is also clearly increasing in both $T$ and $D$.
+
+That the gift in the model with material value, $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, is increasing in $p$ is straightforward.
+Recall that all the variables are assumed to be strictly positive, with $0 < \delta_l < 1$.
+It follows that the numerator is increasing in $p$ and the denominator is decreasing in $p$ and assumed positive.
+Therefore, $g^1$ is increasing in $p$.
+In formal terms, $\frac{\partial g^1}{\partial p} = \frac{(1 - \de_l +D)(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2} > 0$.
+
+$g^1$ is unchanged in $W$ since $W$ does not enter the expressing anywhere. The other three parameters require working out the formal result.
+
+Patience level of the low type: $$\frac{\partial g^1}{\partial \delta_l} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(-p)(T+D) - \left(1-\de_l\right)p\left(D + T\right)(-1)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$  $$= \frac{-\left(\left(1-\de_l\right)\left(1 - pT \right)p(T+D) + (1-p) D\right)p(T+D) + \left(1-\de_l\right)p\left(D +	 T\right)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$ $$= \frac{(1-p) pD(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term so it is positive.
+Therefore we have $\frac{\partial g^1}{\partial \delta_l} > 0$.
+
+Benefit from negotiating partner playing Trust: 
+$$\frac{\partial g^1}{\partial T} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(\de_l p -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 - pT + pD + pT\right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 + pD \right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term so it is positive.
+Therefore we have $\frac{\partial g^1}{\partial T} > 0$.
+
+Damages from negotiating partner playing Fight: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) - T(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{1-\de_l -pT + \de_l p T - T +pT\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{1-\de_l + \de_l p T - T\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Because both the denominator and $(1-\de_l)p$ are strictly positive, the sign of this derivative matches the sign of $1-\de_l + \de_l p T - T$.
+It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise.
+So, when the benefit from the partner playing trust is sufficiently mall, the gift size will increase in $D$, but otherwise the gift size will decrease in the damages from the negotiating partner playing Fight.
+
+We now turn to the patience threshold that defines the high type.
+In the {concessions separating equilibrium} with no material value, we have $\frac{W}{T+D} = \de^{c}$, which increases in $W$ and decreases in $T$ and $D$.
+Notice it is not a function of $\delta_l$ or $p$.
+
+The results for the patience threshold when there is material value are more complex.
+First, recall that $\de^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$ where the denominator of the first term is simply $\delta^1$.
+
+As in the case of no material value, the patience threshold is increasing in $W$: $\frac{\partial \delta^1}{\partial W} = \frac{p}{g^1} + p > 0$ since both $p$ and $g^1$ are strictly positive.
+
+The patience threshold is increasing in $p$. That is, 
+$$\frac{\partial \delta^1}{\partial p} = \frac{g^1 (W-D-T) - p(W-D-T)\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ W-T-D$$$$= (W-D-T)\left\{\frac{g^1  - p\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ 1\right\}=\frac{W-D-T	}{(g^1)^2}\left\{g^1  - p\frac{\partial g^1}{\partial p} + (g^1)^2\right\}$$
+$$=\frac{W-D-T}{(g^1)^2}\left\{p(T+D)\left[-\de_l (1-\de_l) - \de_l D - \de_l p D(1-\de_l)\right]\right\} > 0.$$
+We assume that $T > W - D$, so the numerator of the fraction is positive, while the denominator is positive since it's a squared term.
+$p(T+D)$ is positive because all three variables are positive.
+Each term in the square brackets is negative.
+Therefore the full expression is positive.
+
+The patience threshold is also increasing in the low type's patience level $\de_l$. That is,
+$$\frac{\partial \delta^1}{\partial \de_l} = \frac{g^1 \cdot 0 + p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} = \frac{p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} > 0.$$
+The result holds because each term in the expression is positive.
+
+In contrast, the patience threshold is decreasing in the benefit from the negotiating partner playing Trust, $T$. That is,
+$$\frac{\partial \delta^1}{\partial T} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial T}}{(g^1)^2}-p = \frac{p}{(g^1)^2}\left\{ p(T+D-W) \frac{\partial g^1}{\partial T} - g^1 -(g^1)^2 \right\}$$
+$$= \frac{p}{(g^1)^2}\left\{-(1-\de_l)W - (1- \de_l P)WD -2TD(1-\de_l)p \right\} < 0.$$
+The result holds because $p$ and $g^1$ are positive, while each additive term in the curly braces is negative.
+
+The result is more nuanced for $D$, the cost of the negotiating partner playing Fight. 
+$$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$
+If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression will always be negative.
+As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_lD(1-p)}{1-\de_l}$.
+When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.
 

### 2023-08-16 draft_narrow.tex
two small clarifications in responses to referees

@@
 Our model differs in that it adds an initial period, before the repeated Prisoner's Dilemma begins, in which players make costly concessions to each other.
-We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler.} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
+We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler than in Maor and Solan (2015).} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 The other variable that influences the patience threshold in the case of future value is $p$, the proportion of cooperative types in the population.
-Although the gift in the no-future-material-value case \emph{is} a function of $p$, it is a linear function of $p$ just like the variables $T$, $W$, and $D$.
-Thus the cost of paying the gift and the direct benefits in the repeated game increase at the same rate.
+Although the gift in the no-future-material-value case \emph{is} an increasing function of $p$, it is a linear function of $p$ just like the variables $T$, $W$, and $D$.
+Thus the cost of paying the gift and the direct benefits in the repeated game increase at the same rate so that the likelihood of cooperative types does not vary in $p$ when gifts have no future material value.
 In the future-material-value case, the size of the gift required to separate the high types from the low types increases more than linearly in $p$ and thus faster than the other terms.
-Therefore the patience threshold increases as $p$ increases.\footnote{For the comparative statics calculations, see Appendix~\ref{ap:mat_val}.}
+Therefore the patience threshold in the future-material-value case increases as $p$ increases.
+That is, the cost of giving the gift weighs more heavily in the decision to cooperate relative to the material costs and benefits, requiring states to be more patient to separate and thus reducing the likelihood of cooperative types.\footnote{For the comparative statics calculations, see Appendix~\ref{ap:mat_val}.}
 

### 2023-08-17 draft_narrow.tex
change 'Fight' to 'Distrust' throughout for stage-game action

@@
 
-The countries' stage game actions will be referred to as ``Trust'' and ``Fight'' as represented in Table 1, where Country 1 is the row player and Country 2 is the column player.
+The countries' stage game actions will be referred to as ``Trust'' and ``Distrust'' as represented in Table 1, where Country 1 is the row player and Country 2 is the column player.
 
@@
 \begin{tabular}{|l|c|c|}
-  \hline      & Trust & Fight \\ \hline
+  \hline      & Trust & Distrust \\ \hline
 	 Trust& $T$, $T$& $-D$, $T+W$ \\ \hline
-	Fight & $T+W$, $-D$& $W-D$, $W-D$ \\ \hline
+	Distrust & $T+W$, $-D$& $W-D$, $W-D$ \\ \hline
 \end{tabular}
@@
 Here $T>0$ represents the benefit from a country's negotiating partner playing Trust.
-$D>0$ represents the damages incurred when a country's negotiating partner plays Fight, while $W>0$ is the additional benefit a country receives when it plays Fight itself.
-We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
+$D>0$ represents the damages incurred when a country's negotiating partner plays Distrust, while $W>0$ is the additional benefit a country receives when it plays Distrust itself.
+We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
 Note that this ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
@@
 
-We will use grim trigger punishments throughout: that is, (Fight, Fight) will be played forever if Fight is played by any party in any round.
+We will use grim trigger punishments throughout: that is, (Distrust, Distrust) will be played forever if Distrust is played by any party in any round.
 Because we use grim trigger punishments, there are only 4 interesting paths of play after concessions are given:
 1) Both countries play Trust always; 
-2) Both play Fight always; 
-3) Country 1 plays Fight in round 1 while country 2 plays Trust, which is followed by both countries playing Fight from round 2 onwards; and 
-4) Country 2 plays Fight in round 1 while country 1 plays Trust, which is followed by both countries playing Fight from round 2 onwards.
+2) Both play Distrust always; 
+3) Country 1 plays Distrust in round 1 while country 2 plays Trust, which is followed by both countries playing Distrust from round 2 onwards; and 
+4) Country 2 plays Distrust in round 1 while country 1 plays Trust, which is followed by both countries playing Distrust from round 2 onwards.
 
@@
 Likewise $X_{TF}^i=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}^i=\frac{W-D}{1- \delta_i}$, and  $X_{FT}^i=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$.
-$X_{FT}^h$, for example, represents payoffs for the high type of country 1 when country 1 fights and country 2 trusts in the first period.
+$X_{FT}^h$, for example, represents payoffs for the high type of country 1 when country 1 plays Distrust and country 2 plays Trust in the first period.
 Note that because types have different discount factors, the payoffs differ by type.
@@
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
-Consider for instance oscillating every other period between (Trust,Trust) and (Fight,Fight) with a grim trigger ``War'' threat.
+Consider for instance oscillating every other period between (Trust,Trust) and (Distrust,Distrust) with a grim trigger ``War'' threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
@@
 \subsection{Pooling equilibrium}
-In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Fight in every period beginning with period 1.
+In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Distrust in every period beginning with period 1.
 Countries do nothing to bridge the credibility gap, and thus do not cooperate.
@@
 In this equilibrium, no concessions are given by either type in period 0.
-In period 1, high types play Trust while low types play Fight.
+In period 1, high types play Trust while low types play Distrust.
 So long as there are two high types as revealed by their period 1 play, both countries play Trust in all following periods.
-Otherwise, both countries play Fight in all following periods.
+Otherwise, both countries play Distrust in all following periods.
 
@@
 	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}=\de^{nc}$.
-A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give no concessions in period 0 and play Trust unless the other country defects to Fight.
+A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give no concessions in period 0 and play Trust unless the other country defects to Distrust.
 	\label{theorem:1}
@@
 If both countries receive concessions, they know the other is a high type and both play Trust in subsequent periods.
-Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Fight in subsequent periods.
-The signaling value of concessions in period 0 means that, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Fight.
+Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Distrust in subsequent periods.
+The signaling value of concessions in period 0 means that, starting from period 1 in the Trust/Distrust game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Distrust.
 
@@
 		\item[(a)] Assume $\delta_h \geq \frac{W}{T+D} = \de^{c}$.
-Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
 		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
@@
 \begin{tabular}{|l|c|c|}
-  \hline      & Trust & Fight \\ \hline
+  \hline      & Trust & Distrust \\ \hline
 	 Trust& \small$T+T\alpha_2 g_1$, & \small$-[D+D(1-\alpha_2) g_1],$ \\
   & \small$T+T\alpha_1 g_2$ & \small$[T+T\alpha_1 g_2] + [W+W(1-\alpha_2) g_1] $\\ \hline
-	Fight & \small$[T+T\alpha_2 g_1]+[W+W(1-\alpha_1) g_2],$& \small$[W+W(1-\alpha_1) g_2]-[D+D(1-\alpha_2) g_1],$ \\
+	Distrust & \small$[T+T\alpha_2 g_1]+[W+W(1-\alpha_1) g_2],$& \small$[W+W(1-\alpha_1) g_2]-[D+D(1-\alpha_2) g_1],$ \\
 	 & \small$-[D+D(1-\alpha_1) g_2] $ & \small$[W+W(1-\alpha_2) g_1]-[D+D(1-\alpha_1) g_2]$ \\ \hline
@@
 
-For example, if both countries play Fight, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
+For example, if both countries play Distrust, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
 Its welfare now has two additional terms.
@@
 		\item[(a)] Assume $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D$ is positive and $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$.
-Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
 		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
@@
 The threshold increases and cooperation becomes less likely when $W$ increases; the threshold decreases when either $T$ or $D$ increase.
-These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value when the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Fight larger.
+These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value when the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Distrust larger.
 The patience threshold decreases in $T$ and $D$, but for different reasons.
 $T$ is straightforward: a larger $T$ is a larger benefit from playing Trust.
-In contrast, a larger $D$ is a bigger cost of the negotiating partner playing Fight.
+In contrast, a larger $D$ is a bigger cost of the negotiating partner playing Distrust.
 These relationships are not fundamentally changed by the presence of future material value because the future material value is proportional to the fundamental values of $W$, $T$, and $D$.
@@
 \begin{tabular}{|l|c|c|}
-  \hline      & Trust & Fight \\ \hline
+  \hline      & Trust & Distrust \\ \hline
 	 Trust& \small$T+T\alpha_2 e g_1$, & \small$-[D+D(1-\alpha_2) eg_1],$ \\
   & \small$T+T\alpha_1 eg_2$ & \small$[T+T\alpha_1 eg_2] + [W+W(1-\alpha_2) eg_1] $\\ \hline
-	Fight & \small$[T+T\alpha_2 eg_1]+[W+W(1-\alpha_1) eg_2],$& \small$[W+W(1-\alpha_1) eg_2]-[D+D(1-\alpha_2) eg_1],$ \\
+	Distrust & \small$[T+T\alpha_2 eg_1]+[W+W(1-\alpha_1) eg_2],$& \small$[W+W(1-\alpha_1) eg_2]-[D+D(1-\alpha_2) eg_1],$ \\
 	 & \small$-[D+D(1-\alpha_1) eg_2] $ & \small$[W+W(1-\alpha_2) eg_1]-[D+D(1-\alpha_1) eg_2]$ \\ \hline
@@
 On the other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
-Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
+Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Distrust, the larger is the welfare loss when the negotiating partner turns out to be a low type.
 
@@
 \begin{lemma}
-	From period 1 on, playing (Fight,Fight) in all periods is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
+	From period 1 on, playing (Distrust,Distrust) in all periods is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
 	\label{lemma:1}
 \end{lemma}
-\emph{Proof}: As $D>0$ and $W>0$ the dominant stage game action for all types is to play Fight.
-Thus the stage game equilibrium is (Fight, Fight) and in any repeated game, playing the stage game equilibrium in each period is an equilibrium of the entire game.
+\emph{Proof}: As $D>0$ and $W>0$ the dominant stage game action for all types is to play Distrust.
+Thus the stage game equilibrium is (Distrust, Distrust) and in any repeated game, playing the stage game equilibrium in each period is an equilibrium of the entire game.
 \hfill $\blacksquare$\\
 
-That is, one high type equilibrium strategy is to pool with the low types---by always playing ``Fight'' by definition---and always play Fight.
-If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays fight, then either type of player $i$ is made strictly better off by playing Fight in each period given player $j$'s behavior.
-Given that the stage-game equilibrium will be (Fight,Fight), there is no incentive to give a concession in period 0 because concessions are costly and signaling one's type can give no benefit in this equilibrium.
-Types pool by never giving concessions and always playing Fight.
+That is, one high type equilibrium strategy is to pool with the low types---by always playing ``Distrust'' by definition---and always play Distrust.
+If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays Distrust, then either type of player $i$ is made strictly better off by playing Distrust in each period given player $j$'s behavior.
+Given that the stage-game equilibrium will be (Distrust,Distrust), there is no incentive to give a concession in period 0 because concessions are costly and signaling one's type can give no benefit in this equilibrium.
+Types pool by never giving concessions and always playing Distrust.
 
@@
  \noindent{\emph{Proof of Theorem \ref{theorem:1}}:\\
-Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Fight in the first period and then every period thereafter by the one-shot deviation principle.
+Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first period and then every period thereafter by the one-shot deviation principle.
 If both countries play Trust in a period, a ``Peace'' equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
-Low types play Fight in the first period, so a high type that observed Fight being played would respond by playing Fight in period 2 and in all future periods.
+Low types play Distrust in the first period, so a high type that observed Distrust being played would respond by playing Distrust in period 2 and in all future periods.
 A country plays Trust if and only if the following condition is satisfied:
@@
 
-If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
-Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
+If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust.
+Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each period even if the other country plays Trust.
 Thus we call these countries low types for purposes of this equilibrium.
@@
 In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on concessions separating equilibrium in which countries reveal their types truthfully.
-This allows high types to only play ``Trust'' in period 1 with other high types and to play Fight with low types.
-Low types play Fight (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
+This allows high types to only play ``Trust'' in period 1 with other high types and to play Distrust with low types.
+Low types play Distrust (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
 
@@
 On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$).
-Then (Fight, Fight) is played, and the payoffs depend on whether this low type is facing a high type or a low type because the implications for future material value are different.
+Then (Distrust, Distrust) is played, and the payoffs depend on whether this low type is facing a high type or a low type because the implications for future material value are different.
 With probability $p$, the low type received a gift and invested in the military.
@@
 That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types.
-Note that if the high type pools with the low type, it knows it will be playing Fight and so invests any concession received in military buildup.
+Note that if the high type pools with the low type, it knows it will be playing Distrust and so invests any concession received in military buildup.
 \begin{equation*}
@@
 
-Damages from negotiating partner playing Fight: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+Damages from negotiating partner playing Distrust: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
 $$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
@@
 It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise.
-So, when the benefit from the partner playing trust is sufficiently mall, the gift size will increase in $D$, but otherwise the gift size will decrease in the damages from the negotiating partner playing Fight.
+So, when the benefit from the partner playing trust is sufficiently mall, the gift size will increase in $D$, but otherwise the gift size will decrease in the damages from the negotiating partner playing Distrust.
 
@@
 
-The result is more nuanced for $D$, the cost of the negotiating partner playing Fight. 
+The result is more nuanced for $D$, the cost of the negotiating partner playing Distrust. 
 $$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$

### 2023-08-17 draft_narrow.tex
change from Peace to Cooperation for stage-game outcome

@@
 Another contribution is that the way we model concessions does not require countries to make an agreement that requires credible commitment, as is common in bargaining models.
-Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve peace in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}
+Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve cooperation in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}
 
@@
 $D>0$ represents the damages incurred when a country's negotiating partner plays Distrust, while $W>0$ is the additional benefit a country receives when it plays Distrust itself.
-We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
-Note that this ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
+We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as ``War.'' We will refer to (Trust,Trust) as Cooperation.
+In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
+Note that this ensures that the joint payoffs from Cooperation are the highest among all the stage-game action profiles.
 
@@
 Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
-We take achieving peace, or more broadly, achieving the provision of public goods, as the normative goal with respect to advancing social welfare.
+We take achieving peace, or more broadly, achieving cooperation with the provision of public goods, as the normative goal with respect to advancing social welfare.
 Only high types are capable of making peace/providing public goods, and thus we will take the measure of social welfare to be the sum of the participating high types’ utilities.
@@
 \label{sec:bench}
-When countries are faced with uncertainty about each other's motives, they can proceed in several ways, including giving concessions in order to signal their ability to make peace.
+When countries are faced with uncertainty about each other's motives, they can proceed in several ways, including giving concessions in order to signal their ability to Cooperate.
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
@@
 These long lasting stalemates are the types of conflict which are most appropriate for mediator involvement.
-In Section~\ref{sec:med}, we will present a mediation mechanism that illustrates how mediation can help achieve peace in this context.
+In Section~\ref{sec:med}, we will present a mediation mechanism that illustrates how mediation can help achieve cooperation in this context.
 In some sense, these are the cases that are most interesting because the international community might play a positive role.
@@
 The other two equilibria on which we focus are separating equilibria in which low types and high types have different strategies.
-If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat.
+If $\delta_i$ is high enough for both countries, the Cooperation outcome can be sustained with no concessions and a grim trigger punishment threat.
 We call this a \emph{no-concessions separating equilibrium}.
@@
 Here, as in each further iteration of the model, we define a high type as a country who has a discount factor at or above the threshold for cooperation.
-That is, high types prefer to play the ``Peace'' equilibrium, i.e.
+That is, high types prefer to play the Cooperation equilibrium, i.e.
 $\delta_h \geq \delta^{nc}$.
 Any country with $\delta_l < \delta^{nc}$ is a low type for the purposes of the \emph{no concessions separating equilibrium}.
-This means that two high types---and only two high types---can sustain the ``Peace'' outcome.\footnote{Note that, because we define high and low types relative to each type of equilibrium, a country with a given discount factor can be a high type in some equilibria and a low type in others.}
+This means that two high types---and only two high types---can sustain the Cooperation outcome.\footnote{Note that, because we define high and low types relative to each type of equilibrium, a country with a given discount factor can be a high type in some equilibria and a low type in others.}
 
@@
 Concessions are a costly signal that the other country is serious about cooperating and can be used to avoid continual distrust.
-That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing peace.
+That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing cooperation.
 
@@
 Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.\footnote{When $\de = \frac{W}{T+D}$, there is also a semi-separating equilibrium where only some high types give a concession.
-Here, high types give a smaller expected concession and trade off a lower probability of achieving peace.
-We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for peace and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+Here, high types give a smaller expected concession and trade off a lower probability of achieving cooperation.
+We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
 
@@
 Concessions separating equilibria are a way for countries to solve their disputes when the \emph{no concessions separating equilibrium} is unattractive or unavailable.
-By giving costly concessions, they signal their intentions in a way that a partner unwilling to make peace would not be willing to signal.
+By giving costly concessions, they signal their intentions in a way that a partner unwilling to cooperate would not be willing to signal.
 
@@
 
-Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the ``Peace'' outcome will be played.
+Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the Cooperation outcome will be played.
 Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
@@
 If countries use concessions with future material value instead of concessions with no future material value, there are parameters under which the future material value of gifts destroys countries' ability to separate through concessions, i.e.
-peace cannot be achieved when there are two high types.
+Cooperation cannot be achieved when there are two high types.
 	\label{corollary:matval}
@@
 $\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5,.979)$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
-That is, future material value can destroy the opportunity for peace.
+That is, future material value can destroy the opportunity for cooperation.
 \hfill $\blacksquare$
@@
 
-Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to achieve peace, we first formally establish the welfare implications.
+Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to cooperate, we first formally establish the welfare implications.
 
 \begin{lemma}
-	If the \emph{concessions separating equilibrium with efficient concessions} exists, it is preferred to the \emph{concessions separating equilibrium with inefficient gifts} when both the probability of encountering a high type and the benefit from making peace are sufficiently large.
+	If the \emph{concessions separating equilibrium with efficient concessions} exists, it is preferred to the \emph{concessions separating equilibrium with inefficient gifts} when both the probability of encountering a high type and the benefit from Cooperation are sufficiently large.
 	\label{lemma:efficiency}
@@
 
-This means that there are parameters under which ``Peace'' cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but ``Peace'' can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
+This means that there are parameters under which Cooperation cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but Cooperation can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
 This is part of the substance of Theorem~\ref{theorem:4}.
@@
 
-However, even if the negotiating parties are patient enough to separate when gifts are efficient, Lemma~\ref{lemma:efficiency} tells us that welfare will be higher with efficient gifts only when the probability of encountering a high type and the benefit from making peace are sufficiently large.
+However, even if the negotiating parties are patient enough to separate when gifts are efficient, Lemma~\ref{lemma:efficiency} tells us that welfare will be higher with efficient gifts only when the probability of encountering a high type and the benefit from Cooperation are sufficiently large.
 Otherwise, welfare is higher under the \emph{concessions separating equilibrium with inefficient gifts} and this equilibrium is thus optimal.
@@
 Inefficient concessions are optimal when there's a good chance of facing a low type who will use the concession against you (i.e.
-$p$ is small) as well as when the benefits from ``Peace'' are small relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
+$p$ is small) as well as when the benefits from Cooperation are small relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
@@
 
-Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that a mediator who implements mechanism $M$ can do both.
+Ultimately, mediation is desirable if it can improve welfare or improve the chances for cooperation. Theorem~\ref{theorem:medwel} shows that a mediator who implements mechanism $M$ can do both.
 
@@
 		\item[(b)] improve welfare despite reducing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
-		\item[(c)] achieve peace when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
+		\item[(c)] achieve cooperation when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
 	\end{enumerate}
@@
 Part (b) may be somewhat surprising.
-Here, a mediator would insert inefficiency when it is not necessary to make peace.
+Here, a mediator would insert inefficiency when it is not necessary to achieve a cooperative outcome.
 This happens when the possibility of the low type using concessions against their negotiating partner and the magnitude of the damages that can be imposed are small enough that efficient gifts are possible but large enough that the full efficiency of the gifts has a large, negative impact on welfare.
@@
 Part (c) is relevant when the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large.
-In this case, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
+In this case, the parties cannot cooperate on their own even with the possibility of signaling their type through concessions.
 By ensuring that only high types exchange gifts, the mediator removes the threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
@@
 Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first period and then every period thereafter by the one-shot deviation principle.
-If both countries play Trust in a period, a ``Peace'' equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
+If both countries play Trust in a period, a Cooperation equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
 Low types play Distrust in the first period, so a high type that observed Distrust being played would respond by playing Distrust in period 2 and in all future periods.
@@
 
-If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust.
+If the potential advantages of Cooperation are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust.
 Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each period even if the other country plays Trust.
@@
 
-High types have the incentive to play Trust only in the ``Peace'' equilibrium, which can only be sustained by a pair of high types.
+High types have the incentive to play Trust only in the Cooperation equilibrium, which can only be sustained by a pair of high types.
 Both types benefit from the other country playing Trust so all countries have incentive to signal that they are high types if concessions are costless (cheap talk).
@@
 Both parties are instructed to give efficient gifts.
-The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium.
+The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the Cooperation equilibrium.
 The low-type player knows it will defect and be in a ``War'' equilibrium and so invests entirely in the military.

### 2023-08-17 draft_narrow.tex
change War to No Cooperation

@@
 Our model differs in that it adds an initial period, before the repeated Prisoner's Dilemma begins, in which players make costly concessions to each other.
-We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler than in Maor and Solan (2015).} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
+We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler than in Maor and Solan (2015).} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continuing conflict--military or otherwise.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 $D>0$ represents the damages incurred when a country's negotiating partner plays Distrust, while $W>0$ is the additional benefit a country receives when it plays Distrust itself.
-We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as ``War.'' We will refer to (Trust,Trust) as Cooperation.
+We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as No Cooperation.
+We will refer to (Trust,Trust) as Cooperation.
 In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
@@
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
-Consider for instance oscillating every other period between (Trust,Trust) and (Distrust,Distrust) with a grim trigger ``War'' threat.
+Consider for instance oscillating every other period between (Trust,Trust) and (Distrust,Distrust) with a grim trigger Distrust threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
@@
 Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the Cooperation outcome will be played.
-Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
+Conversely, in equilibrium, low types only participate in the No Cooperation equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
 
@@
 Inefficient concessions are optimal when there's a good chance of facing a low type who will use the concession against you (i.e.
-$p$ is small) as well as when the benefits from Cooperation are small relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
+$p$ is small) as well as when the benefits from Cooperation are small relative to the damages from No Cooperation.
+This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
@@
 Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first period and then every period thereafter by the one-shot deviation principle.
-If both countries play Trust in a period, a Cooperation equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
+If both countries play Trust in a period, a Cooperation equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of Distrust.
 Low types play Distrust in the first period, so a high type that observed Distrust being played would respond by playing Distrust in period 2 and in all future periods.
@@
 If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved with no concessions in period 0.\footnote{Countries need to deliver concessions in period 0, not just promise them.
-A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of the ``War'' outcome that would occur under pooling.
+A concession that is promised but not delivered will count as cheap talk.} If instead high-type negotiating parties have sufficient incentive to give a concession that reveals their type in period 0, the high types could safely play Trust in period 1, allowing two high types to avoid the trap of the No Cooperation outcome that would occur under pooling.
 
@@
 The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the Cooperation equilibrium.
-The low-type player knows it will defect and be in a ``War'' equilibrium and so invests entirely in the military.
+The low-type player knows it will defect and be in a No Cooperation equilibrium and so invests entirely in the military.
 %		\begin{multline}
@@
 \emph{Proof of Theorem~\ref{theorem:med}:}\\
-(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the `War' payoff forever outside the mechanism; it also gets the `War' payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
+(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the No Cooperation payoff forever outside the mechanism; it also gets the No Cooperation payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
 
@@
 This means that there will be no concessions when a high type lies.
-This implies that Expression~\ref{eq:med4} is also the individual rationality constraint since outside the mechanism they get the `War' payoff and exchange no concessions.
+This implies that Expression~\ref{eq:med4} is also the individual rationality constraint since outside the mechanism they get the No Cooperation payoff and exchange no concessions.
 

### 2023-08-17 draft_narrow.tex
Line/type edits, especially for shift to cooperation

@@
 In both active wars and long-simmering conflicts, settlement negotiations often occur simultaneously with continued fighting.
-This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition: parties engage in costly conflict while they negotiate.
+This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition: parties engage in costly conflict while they negotiate, foregoing the value of the public goods they could create through cooperation.
 If settlement can be achieved, additional costs of conflict -- including additional death and destruction -- are averted.
@@
 We introduce a two-sided signaling model followed by a repeated Prisoner's Dilemma in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
-We use this model to show that cooperation can be undermined by concerns that concessions could be used against the giver in the future.
+We use this model to show that concerns that concessions could be used against the giver in the future can undermine cooperation.
 Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to a settlement.
 Perhaps more importantly, the mediator can also sometimes facilitate settlement when the negotiating parties cannot achieve it through bilateral interaction.
-In other words, commitment is essentially a far-sighted preferences that allows cooperation to emerge, uncertainty can result in missed opportunities for cooperation, and concessions and mediation can facilitate conflict settlement.
+In other words, commitment is essentially a far-sighted preference that allows cooperation to emerge, uncertainty can result in missed opportunities for cooperation, and concessions and mediation can facilitate conflict settlement and the provision of public goods.
 %The sentence above literally parrots the editor's words back to them. Too on the nose?
@@
 
-This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can both help increase the efficiency of concessions and make peace.
+This paper provides an explanation for why efficient concessions are sometimes impossible to make.
+It also revises our understanding of why inefficient concessions can sometimes be beneficial and how mediators can both help increase the efficiency of concessions and make cooperation possible.
 Weapons, strategically valuable territory, and the sharing of advanced technology will not be conceded if the conceding side fears that these items may be used in future attacks against them.
@@
 Another option, and the one on which we focus in this paper, is third-party mediation.
-We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling disputants to make more efficient concessions, even when there is a risk those concessions might increase the bargaining power of their opponent in the future.
+We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling disputants to make more efficient concessions.
+The mediator does this by removing therisk that concessions might be used against the giver in the future.
 
@@
 A high type is able to cooperate; a low type has incentives not to cooperate.
-These types map onto the commitment problem, with a high type one who is able to commit in certain scenarios.
+These types map onto the commitment problem, with a high type one who is able to commit.
 A low type, though perhaps willing, is unable to do so.
@@
 But the most relevant explanation for the field of international relations is that gift giving is strategic.
-Camerer uses mechanism design to model gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
+Camerer uses mechanism design to model gifts as costly signals, where inefficiency is useful in pre-play communication in order to form relationships between like types.
 This strategic giving of gifts in societies looks very much like the strategic giving of concessions to remedy conflict situations.
@@
 This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has manipulative abilities.
-Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006), and parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
-We thus model parties to a conflict who can benefit from seeking mediation in order to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).}
+Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008); we thus model parties to a conflict who can benefit from seeking mediation in order to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).}
 
@@
 In particular, Meirowitz et al.
-2019 shows that---when asymmetric information is about the level of militarization---a `Myerson' mediator can circumvent the incentives for militarization that arises in unmediated peace talks and improve the changes for peace.
+2019 shows that---when asymmetric information is about the level of militarization---a `Myerson' mediator can circumvent the incentives for militarization that arise in unmediated peace talks and improve the changes for peace.
 This paper expands the theoretical literature by modeling the role of a manipulative mediator when the information asymmetry is about parties' abilities to commit to cooperation and concessions have future material value that could be used to harm the giver.
@@
 The mistrust is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
-
-Outside the war context, [EXAMPLE NEEDED].
+This is also possible outside the war context, for instance, when U.S.
+officials block Chinese firms' access to cutting-edge technology in order to prevent that technology from being used against U.S.
+interests.
 
@@
 Here, high types give a smaller expected concession and trade off a lower probability of achieving cooperation.
-We will thus focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+We will focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
 
@@
 
-The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society.
+The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society, including through the provision of public goods.
 The recipient using concessions to build military strength hurts the giver of the concessions in war; the recipient using the concessions to strengthen civil society helps the giver in peace.
@@
 
-For example, if both countries play Distrust, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
+If both countries play Distrust, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
 Its welfare now has two additional terms.
@@
 Second, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ in each period of the repeated game that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
-The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, or if they are scaled by these variables but with a proportion other than 1 or many plausible non-linear functions of $T$, $W$ and $D$.
+The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, if they are scaled linearly by these variables but with a proportion other than 1, or if they are scaled by many plausible non-linear functions of $T$, $W$ and $D$.
 The results are a bit simpler if there is no scaling, but we believe it is more realistic to assume that the future benefits and costs of the gifts are proportional to the direct benefits and costs of cooperation/non-cooperation.
@@
 
-The problem with concessions with material value is that the potential for the low type to invest the concessions in the military makes the high type unwilling to take a chance that it will be matched with a high type when the costs of being matched with a low type are too high.
+The problem with concessions with material value is that the potential for the low type to invest the concessions in the military makes more patient types less willing to take a chance that it will be matched with a high type when the costs of being matched with a low type are too high.
 
@@
 The threshold increases and cooperation becomes less likely when $W$ increases; the threshold decreases when either $T$ or $D$ increase.
-These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value when the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Distrust larger.
+These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value, where the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Distrust larger.
 The patience threshold decreases in $T$ and $D$, but for different reasons.
@@
 
-The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens $p$ of the time.
+The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens with probability $p$.
 On the other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
@@
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
-In Prendergast and Stole the two types are equal except in labeling; in our model, high types and low types are used so there is an incentive for low types to try to pose as high types.
-However, putting this difference aside, the inefficiency result can be viewed as similar to that in Prendergast and Stole (2001).
+In Prendergast and Stole the two types are equal except in labeling; in our model, there is an incentive for low types to try to pose as high types.
+However, putting this difference aside, the inefficiency result can be viewed as having the same flavor as that in Prendergast and Stole (2001).
 That is, if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types from entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against the giver of the concessions in the future.
@@
 
-The range of efficiency that allows for a mechanism $M$ to be incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
+The range of efficiency that allows a mediator to make mechanism $M$ incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
 
@@
 
-To understand part (a), remember that concessions are not exchanged in the mechanism if there is even one report of ``Low.'' Since a concession is only given to the high types and high types invest in civil society, the efficiency of the concession can be increased without creating extra damages when matched with a low type; this is of course subject to satisfying the low type's constraints.
+To understand part (a), remember that concessions are not exchanged in the mechanism if there is even one report of ``Low.'' Since a concession is only given to the high types and high types invest in civil society and public goods, the efficiency of the concession can be increased without creating extra damages when matched with a low type; this is of course subject to satisfying the low type's constraints.
 High-type welfare is improved because no transfer is made to the low types and there is no threat of future damage from the concessions since they only go to a high type.
@@
 
-Thus a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve peace.
+Thus a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve the cooperative outcome.
 The improvements by the mediator here do not rely on the mediator's private information as in the models of Kydd (2003), Rauchhaus (2006) and Smith and Stam (2003).
@@
 This paper introduces a mechanism by which this might work.
-In our model's setup, there are three classes of interesting equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which is essentially a state of war for all types.
+In our model's setup, there are three classes of interesting equilibria: first, if prior trust is low a no-concessions pooling equilibrium exists, which leaves all types in a state of non-cooperation.
 Second, if prior trust is sufficiently high, a no-concessions pooling equilibrium exists where high types trust in the first period and can maintain that trust if both are high types.
@@
 These observations do not undermine the model.
-The nature of the desired concessions helps determine whether inefficient concessions can help achieve peace when efficient concessions cannot and thus also when a mediator can improve the efficiency of concessions.
+The nature of the desired concessions helps determine whether inefficient concessions can help achieve cooperation when efficient concessions cannot and thus also when a mediator can improve the efficiency of concessions.
 
@@
 While it is important theoretically to show how a mediator can help in conflict situations, it should be noted that mediation is not free, at least to the providing (third) party.
-Therefore, the inefficiencies borne by the inefficient concessions and/or by the ongoing conflict must not be outweighed by the cost of providing the mediation.
+Therefore, mediation should not be undertaken if the cost of providing the mediation is larger than the benefits of increased cooperation and/or efficiency of concessions.
 If the model accurately captures the costs, the expected savings of mediation can be calculated and therefore the value of mediation in a specific scenario can be determined.
@@
 If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression will always be negative.
-As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_lD(1-p)}{1-\de_l}$.
+As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_l D(1-p)}{1-\de_l}$.
 When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.
@@
 Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
-By Theorem~\ref{theorem:2}, the \emph{concessions separating equilibrum with efficient gifts} is possible.
+By Theorem~\ref{theorem:2}, the \emph{concessions separating equilibrium with efficient gifts} is possible.
 

### 2023-08-20 draft_narrow.tex
add missing CSE italics throughout

@@
 \begin{lemma}
-	In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a concessions separating equilibrium.
+	In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a \emph{concessions separating equilibrium}.
 	\label{lemma:3}
@@
 If no information is transmitted, then the high type has no incentive itself to give a concession.
-Therefore, there cannot be a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions and the players separating in the repeated game as in the no concessions separating equilibrium.}
+Therefore, there cannot be a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions and the players separating in the repeated game as in the \emph{no-concessions separating equilibrium}.}
 
@@
 Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
-		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
+		\item[(b)] In the best \emph{concessions separating equilibrium}, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
 Equilibria with higher concessions yield strictly lower payoffs.
@@
 
-This `best' concessions separating equilibrium, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
+This `best' \emph{concessions separating equilibrium}, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
 
@@
 Here, high types give a smaller expected concession and trade off a lower probability of achieving cooperation.
-We will focus on the pure concessions separating equilibrium in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
-
-We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no concessions separating equilibrium} in Section~\ref{sec:ncse}.
+We will focus on the pure \emph{concessions separating equilibrium} in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+
+We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no-concessions separating equilibrium} in Section~\ref{sec:ncse}.
 
@@
 
-We turn next to characterizing a concessions separating equilibrium in this environment with future material value.
+We turn next to characterizing a \emph{concessions separating equilibrium} in this environment with future material value.
 
@@
 Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
-		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
+		\item[(b)] In the best \emph{concessions separating equilibrium} when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
 Equilibria with higher concessions yield strictly lower payoffs.
@@
 
-By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.
+By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no-concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.
 
@@
 
-We have established the results for the concessions separating equilibrium when no material value is destroyed, i.e.
+We have established the results for the \emph{concessions separating equilibrium} when no material value is destroyed, i.e.
 $e=1$, in Section~\ref{sec:IC}.
-It turns out that we have also established the results for the concessions separating equilibrium when all material value is destroyed, i.e.
+It turns out that we have also established the results for the \emph{concessions separating equilibrium} when all material value is destroyed, i.e.
 $e=0$.
@@
 \emph{Proof of Lemma~\ref{lemma:3}:}\\
-In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on concessions separating equilibrium in which countries reveal their types truthfully.
+In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on \emph{concessions separating equilibria} in which countries reveal their types truthfully.
 This allows high types to only play ``Trust'' in period 1 with other high types and to play Distrust with low types.
@@
 \ee
-Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a concessions separating equilibrium to exist:
+Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a \emph{concessions separating equilibrium} to exist:
 \be
@@
 \emph{Proof of Corollary~\ref{corollary:1}:}\\
-To show that the patience threshold for the \emph{no concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$
+To show that the patience threshold for the \emph{no-concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$
 
@@
 
-In the case that both types of equilibria exist, i.e. $\de_h \geq \de^{nc}$, the high types will prefer the \emph{no concessions separating equilibrium} if and only if
+In the case that both types of equilibria exist, i.e. $\de_h \geq \de^{nc}$, the high types will prefer the \emph{no-concessions separating equilibrium} if and only if
 \begin{equation*}
@@
 \end{equation*}
-This simplifies to preferring the concessions separating equilibrium if and only if
+This simplifies to preferring the \emph{concessions separating equilibrium} if and only if
 $$0 \geq (1-p)W-p(1-p)(T+D)$$
@@
 
-Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a concessions separating equilibrium to exist in terms of fundamentals:
+Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a \emph{concessions separating equilibrium} to exist in terms of fundamentals:
 \be

### 2023-08-20 draft.tex
rename working document draft_narrow back to draft

@@
 \begin{abstract}
-When two parties are engaged in conflict and each distrusts the other's ability to pursue peace, concessions can be used to indicate an interest in making peace.
+When two parties are engaged in conflict and each distrusts the other's ability to cooperate or make peace, concessions can be used to indicate an interest in cooperation or peacemaking.
 However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made.
-It can also reduce the possibility of peace.
-We use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace.
-In this process, we open up a new rationale for mediation: to increase the inefficiency of signaling in a preliminary round of negotiations.
+It can also reduce the possibility of peace or cooperation.
+Using a repeated game that is preceded by an opportunity to signal one's commitment to cooperation through the provision of concessions, we formally demonstrate that concerns over the future use of concessions can explain the existence of inefficient concessions.
+We then use mechanism design to explore ways in which a third party mediator can act as a guarantor that promised concessions will be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation.
+In this process, we open up a new rationale for mediation: to increase the efficiency of signaling in a preliminary round of negotiations and to overcome the concern that concessions will be used against the giver in the future.
 \end{abstract}
@@
 
-In the course of a military conflict, settlement negotiations often occur simultaneously with continued fighting.
-If settlement can be achieved, lives are saved and destruction averted.
+In negotiations with its neighbors, Israel is hesitant to give certain concessions.
+The Golan Heights, captured from Syria during the 1967 War, is a particular point of contention in Israeli-Syrian relations.
+While the Golan Heights does not have the West Bank’s historic or religious importance, Israel values it for its highly strategic location.
+The Golan Heights could be a useful concession, but Israel senses that were she to give over the land, Syria may ultimately use the concession against her.
+This same hesitancy exists with the West Bank settlements.
+Many are located on hilltops that could offer strategic military outposts for forces hostile to Israel.
+When she occasionally abandons settlements, Israel generally dismantles all infrastructure, including water and electricity, and bulldozes the buildings.
+Although inefficient, this reduces the possibility of those settlements being used against Israeli interests.
+Without trust between negotiating parties, the most efficient concessions often are often difficult to arrange.
+
+In both active wars and long-simmering conflicts, settlement negotiations often occur simultaneously with continued fighting.
+This is true in non-violent disputes as well, such as long-running episodes of geo-strategic competition: parties engage in costly conflict while they negotiate, foregoing the value of the public goods they could create through cooperation.
+If settlement can be achieved, additional costs of conflict -- including additional death and destruction -- are averted.
 Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective (e.g., Bercovitch 2000; Greig 2005a; Beardsley et al.
 2006; Duursma 2020).
-This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that combatants can offer.
-In our context, the efficiency of a concession is determined by how much of the material value of the concession is intact when the recipient receives it.
+This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that conflict participants can offer.
+In our context, the efficiency of a concession is determined by how much of the concessions's material value is intact when the recipient receives it.
 If the party who gives the concession destroys any of its material value, the concession is deemed to be less than fully efficient.
 
-We introduce a two-sided signaling model in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
-Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to peace.
-Perhaps more importantly, the mediator can also sometimes facilitate peace when the negotiating parties cannot achieve it through bilateral interaction.
-
-Two archetypal situations illustrate the significance and difficulty of efficient concession-making in war settlement.
-The first is the case of disarmament and the second is the concession of control over strategically valuable territory.
+We introduce a two-sided signaling model followed by a repeated Prisoner's Dilemma in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player the conceding state is.
+We use this model to show that concerns surrounding the possibility that concessions could be used against the giver in the future can undermine cooperation.
+Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to a settlement.
+Perhaps more importantly, the mediator can also sometimes facilitate settlement when the negotiating parties cannot achieve it through bilateral interaction.
+In other words, commitment is essentially a far-sighted preference that allows cooperation to emerge, uncertainty can result in missed opportunities for cooperation, and concessions and mediation can facilitate conflict settlement and the provision of public goods.
+%The sentence above literally parrots the editor's words back to them. Too on the nose?
+
+%Attempting to add in the China-US case in a prominent way. The prose is more awkward than I would like still. - March 13, 2023 BG
+Three archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
+The first is the case of disarmament, the second is the concession of strategically valuable territory, and the third is the export of advanced technology to a strategic rival.
+%In each case, efficient concessions are difficult to make because the item conceded may be used by the recipient to bolster their military capabilities, altering the balance of power in the ongoing conflict.
+Also true in each case, if dispute settlement is achieved, a public good is produced -- peace in the first two cases and innovation and growth in the civilian economy in the third case.
 
@@
 Disarmament by rebels is an efficient concession if fully-operational weapons are turned over to the central government for its own use, while disarmament accompanied by decommissioning is inefficient because the value of the arms is destroyed.
-Disarming and turning over fully functional weapons is an incredibly difficult concession for rebels to make: once they turn over their arms, they lose future bargaining leverage and have no guarantee that their own weapons won't later be used against them.
-If the rebels can instead decommission those weapons, an important stumbling block to peace is removed.\footnote{Other stumbling blocks remain, including the fact that government retains its weapons.
-Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.
+Disarming and turning over fully functional weapons is an incredibly difficult concession for rebels to make: once they turn over their arms, they lose future bargaining leverage and have no guarantee that their own weapons will not be used against them later.
+If the rebels can instead decommission those weapons, an important stumbling block to peace is removed.\footnote{Other stumbling blocks remain, including the fact that the government retains its weapons.
+Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.\footnote{Walter's approach is part of a much broader literature on the bargaining model of war that looks at concessions and asymmetric information, including  Fearon (1996), Powell (1996a and 1996b, 2006), Slantchev (2011) and Arena (2013).}
 
@@
 
+In our third archetypal example, under both the Trump and Biden administrations, the US has restricted the export of cutting-edge technology to China.
+China and the US are engaged in geo-strategic competition.
+Both countries could benefit from the more rapid innovation and growth that free trade in chips and other technology would enable, but there is risk that any technology exported will be used in the military sector to pursue advanced weapons, altering the military balance of power.
+As of 2023, trade in numerous advanced technologies is restricted, reducing the global pace of innovation and economic growth.
+
+In all three of these archetypal examples, cooperative/peaceful outcomes are extremely challenging to reach.
 Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
-Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996).
-Can mediation offer a path to settlement in these challenging contexts?
-
-This paper revises our understanding of the reasons why efficient concessions are sometimes impossible to make, why inefficient concessions can sometimes be beneficial, and how mediators can both help increase the efficiency of concessions and make peace.
-Weapons or strategically valuable territory will not be conceded if the conceding side fears that territory or weapons may be used in future attacks against them.
-One way to address this concern is to destroy the future value of the concession---e.g.
-decommission weapons or attempt to reduce the strategic value of the territory.
+Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
+Can mediation offer a path to more settlement, peace, and prosperity in these challenging contexts?
+
+This paper provides an explanation for why efficient concessions are sometimes impossible to make.
+It also revises our understanding of why inefficient concessions can sometimes be beneficial and how mediators can both help increase the efficiency of concessions and make cooperation possible.
+Weapons, strategically valuable territory, and the sharing of advanced technology will not be conceded if the conceding side fears that these items may be used in future attacks against them.
+Countries are reluctant to make concessions that can be used against them in latter rounds of conflict or negotiation.
+One way to mitigate the risk of dangerous concessions is to destroy the future value of the concession---e.g.
+decommission weapons, attempt to reduce the strategic value of the territory being conceded, or only allow trade in less advanced technologies or technologies without military applications.
 Another option, and the one on which we focus in this paper, is third-party mediation.
-We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling combatants to make more efficient concessions, even when there is a risk those concessions might increase the bargaining power of their opponent in the future.
-
-While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research.
+We use this model to demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling disputants to make more efficient concessions.
+The mediator does this by only requiring concessions of negotiating parties who are able to cooperate, thereby removing the risk that concessions might be used against the giver in the future.
+
+%While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research.
 The broader literature that attempts to model war has included concessions as part of bargaining, but has not explicitly considered the role of concessions in achieving peace.
@@
 When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation (Fearon 1996).
-
-In these models war can be averted by splitting the pie (i.e.
-the disputed territory) in a way acceptable to both parties.
+%[OUTSIDE THE WAR CONTEXT..., ???]
+
+%In these models war can be averted by splitting the pie (e.g., the disputed territory) in a way acceptable to both parties.
 Concessions are modeled as offering part of the pie to the other party, and asymmetric information is about each party's \textit{resolve} to fight and/or military capabilities (Arena 2013).
@@
 
-We will approach the commitment problem through this same general understanding, but we model a party's ability to cooperate as private information.
+%We approach the commitment problem through this same general understanding, but
+
+We model a party's ability to cooperate as private information.
 A high type is able to cooperate; a low type has incentives not to cooperate.
-These types map onto the commitment problem, with a high type one who is able to commit in certain scenarios.
+These types map onto the commitment problem, with a high type one who is able to commit.
 A low type, though perhaps willing, is unable to do so.
@@
 This is not always the case, however.
-Mahmous Abbas may be a low type, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.
-
-In conflict resolution, concessions may act as signals or as an end in themselves -- or as both simultaneously.
+Mahmoud Abbas, President of the Palestinian National Authority, may be a low type with respect to his negotiations with Israel, not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.
+
+In our model, concessions may act as signals or as an end in themselves -- or as both simultaneously.
 One contribution of this paper is that it allows concessions to have future material value, signaling value, and both.
 We will show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed and thus inefficiencies can emerge.
+Another contribution is that the way we model concessions does not require countries to make an agreement that requires credible commitment, as is common in bargaining models.
+Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve cooperation in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}
 
@@
 Like concessions, costly gifts have been shown to have a valuable role in relationship building.
-And the gift giving literature, more so than the concessions literature, focuses specifically on the issue of efficiency.
+Furthermore, the gift giving literature---more so than the concessions literature---focuses specifically on the issue of efficiency.
 Inefficiency is defined for the purposes of this paper as giving a gift (i.e.
@@
 
-In efforts to explain the existence of gift giving,  Camerer (1988) and Van de Ven (2000) give several anthropological explanations for inefficiency.
-Amongst these explanations are altruism, social mores, and egoism.
+In efforts to explain the existence of gift giving,  Camerer (1988) and Van de Ven (2000) give several anthropological explanations for inefficiency.\footnote{Prendergast and Stole (2001) also provide an explanation for inefficient gift giving focused on the utility of matching.} Amongst these explanations are altruism, social mores, and egoism.
 But the most relevant explanation for the field of international relations is that gift giving is strategic.
-Camerer uses mechanism design to model gifts as costly signals; inefficiency is useful in pre-play communication in order to form relationships between like types.
+Camerer uses mechanism design to model gifts as costly signals, where inefficiency is useful in pre-play communication in order to form relationships between like types.
 This strategic giving of gifts in societies looks very much like the strategic giving of concessions to remedy conflict situations.
@@
 
-Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts.\footnote{In an environment with repeated opportunities for concessions Watson (1999) is able to show that a strong relationship can be reached by starting with small ``gifts'' and increasing their size as the relationship becomes more committed.
+Camerer shows that in this general formulation, a costly signaling model will always yield efficient gifts.\footnote{In an environment with repeated opportunities for concessions, Watson (1999) is able to show that a strong relationship can be reached by starting with small ``gifts'' and increasing their size as the relationship becomes more committed.
 See Van de Ven (2000) for an overview of this literature.} In order to explain inefficiency, Camerer adds an additional pre-play period where players must pay a cost in order to enter the game and send and receive gifts.
@@
 
-It is essential to focus more precisely on the specific actions and environments that make use of particular types of mediation, which is how we approach the question.
-This paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has manipulative abilities.
-Mediation rarely occurs in the absence of violent conflict (Bercovitch 1996; Beardsley 2006), and parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008).
-We thus model parties to a conflict who can benefit from seeking mediation in order to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).}
+It is essential to focus more precisely on the specific actions and environments that make use of particular types of mediation.
+To this end, this paper models an environment where the primary issue is trust, not uncertainty about an opponent's capabilities, and where a mediator is employed who has manipulative abilities.
+Parties are more likely to seek mediation when they are entrenched in costly conflict (Bercovitch and Jackson 2001; Greig 2005b; Greig and Diehl 2006; Terris and Maoz 2005; Svensson 2008); we thus model parties to a conflict who can benefit from seeking mediation in order to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies (Allee and Huth 2006, Beardsley 2010; Beardsley and Lo 2014).}
 
@@
 2010; Meirowitz et al.
-2012, 2015).
-This paper expands the theoretical literature by modeling the role of mediation when information is asymmetric about parties' abilities to commit to peace.
-Here, a mediator can remove the incentive to make concessions that are inefficient.
+2012, 2019).
+In particular, Meirowitz et al.
+2019 shows that---when asymmetric information is about the level of militarization---a `Myerson' mediator can circumvent the incentives for militarization that arise in unmediated peace talks and improve the changes for peace.
+This paper expands the theoretical literature by modeling the role of a manipulative mediator when the information asymmetry is about parties' abilities to commit to cooperation and concessions have future material value that could be used to harm the giver.
+Here, a mediator can achieve peace or the provision of other public goods (1) in situations where bilateral concessions cannot, and (2) with concessions that are more efficient when bilateral concessions must be inefficient to achieve peace.
 
@@
 
-Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors but no signaling game, see Maor and Solan (2015).
-They focus on the players' belief structures, while our initial signaling stage simplifies the analysis of beliefs.} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continued conflict.
+Beginning in period 1, countries engage in an infinitely repeated Prisoner's Dilemma once per period with stage game payoffs in Table 1 below.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors, focused on studying players' belief structures, see Maor and Solan (2015).
+Our model differs in that it adds an initial period, before the repeated Prisoner's Dilemma begins, in which players make costly concessions to each other.
+We will see that these concessions enable signaling between the players that render the analysis of their beliefs much simpler than in Maor and Solan (2015).} While not a good representation of all-out war or even a zero-sum short term war, the Prisoner's Dilemma is appropriate to represent a limited, continuing conflict--military or otherwise.
 In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so.
@@
 Here $T>0$ represents the benefit from a country's negotiating partner playing Trust.
-$D>0$ represents the damages incurred when a country's negotiating partner plays Fight, while $W>0$ is the additional benefit a country receives when it plays Fight itself.
-We will refer to the stage-game Nash Equilibrium of (Fight, Fight) as ``War.'' We will refer to (Trust,Trust) as ``Peace.'' In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
-Note that this ensures that the joint payoffs from ``Peace'' are the highest among all the stage-game action profiles.
+$D>0$ represents the damages incurred when a country's negotiating partner plays Distrust, while $W>0$ is the additional benefit a country receives when it plays Distrust itself.
+We will refer to the stage-game Nash Equilibrium of (Distrust, Distrust) as No Cooperation.
+We will refer to (Trust,Trust) as Cooperation.
+In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$.
+Note that this ensures that the joint payoffs from Cooperation are the highest among all the stage-game action profiles.
 
@@
 Parameters are common knowledge with the exception of $\delta_i$, which is country $i$'s private information.
-We will take the measure of social welfare, and thus the determinant of the optimal equilibrium, to be the sum of participating high types' expected utilities.
+We take achieving peace, or more broadly, achieving cooperation with the provision of public goods, as the normative goal with respect to advancing social welfare.
+Only high types are capable of making peace/providing public goods, and thus we will take the measure of social welfare to be the sum of the participating high types’ utilities.
 
@@
 \label{sec:bench}
-When countries are faced with uncertainty about each other's motives, they can proceed in several ways, including giving concessions in order to signal their ability to make peace.
+When countries are faced with uncertainty about each other's motives, they can proceed in several ways, including giving concessions in order to signal their ability to Cooperate.
 We will examine three types of equilibria.\footnote{If the discount factor is high enough, there are many types of equilibria.
-Consider for instance oscillating every other period between (Trust,Trust) and (Fight,Fight) with a grim trigger ``War'' threat.
+Consider for instance oscillating every other period between (Trust,Trust) and (Distrust,Distrust) with a grim trigger Distrust threat.
 In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios.
@@
 \subsection{Pooling equilibrium}
-In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Fight in every period beginning with period 1.
+In the \emph{pooling equilibrium}, neither negotiating party gives concessions in period 0, then both parties play Distrust in every period beginning with period 1.
 Countries do nothing to bridge the credibility gap, and thus do not cooperate.
 This \emph{pooling equilibrium} is likely to happen when countries are in long-set patterns of distrust.
-Active fighting is not necessary; remaining outside of a state of peace is all that is required.
+Active fighting is not necessary; remaining outside of a state of peace/cooperation is all that is required.
 See the Appendix for a formal characterization of this type of equilibrium.
 
-Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward.
+%Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward.
 While both sides posture that they want peace, and while there has been some lessening of tensions, very few concrete actions have been taken that move the sides toward settlement.
@@
 
-Sri Lanka is another example.
+Sri Lanka offers one example.
 While the government has finally won the war of secession, it still refuses to address grievances of the minorities and leaves the conflict unresolved.
-Other prominent examples of this pooling equilibrium include Israel and its neighbors, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
+Other prominent examples of this pooling equilibrium include Israel and its neighbors, Cyprus's civil war, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts.
 The mistrust is perhaps justified; indeed if one party did take the first step and give a concession first, they may be taken advantage of.
+This is also possible outside the war context, for instance, when U.S.
+officials block Chinese firms' access to cutting-edge technology in order to prevent that technology from being used against U.S.
+interests.
 
@@
 The other two equilibria on which we focus are separating equilibria in which low types and high types have different strategies.
-If $\delta_i$ is high enough for both countries, the ``Peace'' outcome can be sustained with no concessions and a grim trigger punishment threat.
+If $\delta_i$ is high enough for both countries, the Cooperation outcome can be sustained with no concessions and a grim trigger punishment threat.
 We call this a \emph{no-concessions separating equilibrium}.
 In this equilibrium, no concessions are given by either type in period 0.
-In period 1, high types play Trust while low types play Fight.
+In period 1, high types play Trust while low types play Distrust.
 So long as there are two high types as revealed by their period 1 play, both countries play Trust in all following periods.
-Otherwise, both countries play Fight in all following periods.
+Otherwise, both countries play Distrust in all following periods.
 
@@
 \\
-Here, as in each further iteration of the model, we define a high type as a country who prefers to play the ``Peace'' equilibrium, i.e.
+Here, as in each further iteration of the model, we define a high type as a country who has a discount factor at or above the threshold for cooperation.
+That is, high types prefer to play the Cooperation equilibrium, i.e.
 $\delta_h \geq \delta^{nc}$.
-Any country with $\delta_l < \delta^{nc}$ is a low type.
-This means that two high types---and only two high types---can sustain the ``Peace'' outcome.
+Any country with $\delta_l < \delta^{nc}$ is a low type for the purposes of the \emph{no concessions separating equilibrium}.
+This means that two high types---and only two high types---can sustain the Cooperation outcome.\footnote{Note that, because we define high and low types relative to each type of equilibrium, a country with a given discount factor can be a high type in some equilibria and a low type in others.}
 
@@
 Concessions are a costly signal that the other country is serious about cooperating and can be used to avoid continual distrust.
-That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing peace.
-
-In the \emph{concessions separating equilibrium}, low types do not give concessions while high types give a concession in period 0.
+That is, high types make use of concessions to identify themselves as trustworthy partners in hopes of establishing cooperation.
+
+In the \emph{concessions separating equilibrium}, low types do not give concessions because the concession level is set as the smallest amount that will deter the impatient type from mimicking the patient type.
+In contrast, high types always give a concession in period 0.
+Thus, the patience level of both countries is fully revealed in equilibrium.
 If both countries receive concessions, they know the other is a high type and both play Trust in subsequent periods.
-Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Fight in subsequent periods.
-The signaling value of concessions in period 0 means that, starting from period 1 in the Trust/Fight game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Fight.
+Otherwise, if even one player does not receive a concession, there is at least one low type so both countries play Distrust in subsequent periods.
+The signaling value of concessions in period 0 means that, starting from period 1 in the Trust/Distrust game, both countries play the same strategy in a separating equilibrium, that is both play Trust if there were two high signals and otherwise both play Distrust.
 
@@
 
-Low types don't give gifts in this separating equilibrium because the gift wouldn't serve any purpose: the low type will be identified through the separating behavior of the high types and there is thus nothing to gain.
+Low types don't give gifts in this separating equilibrium because the gift would fail to serve any purpose: the low type will be identified through the separating behavior of the high types and there is thus nothing to gain.\footnote{The transmission of information about each country's type is, by definition, essential for the existence of a \emph{concessions separating equilibrium}.
+Thus, there cannot exist a \emph{concessions semi-separating equilibrium} where the low type gives a concession with strictly positive probability; the concessions would not transmit the information required to build trust.
+If no information is transmitted, then the high type has no incentive itself to give a concession.
+Therefore, there cannot be a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions and the players separating in the repeated game as in the \emph{no-concessions separating equilibrium}.}
 
@@
 		\item[(a)] Assume $\delta_h \geq \frac{W}{T+D} = \de^{c}$.
-Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
-		\item[(b)] In the best concessions separating equilibrium, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
+		\item[(b)] In the best \emph{concessions separating equilibrium}, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate.
 Equilibria with higher concessions yield strictly lower payoffs.
@@
 
-This `best' concessions separating equilibrium, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
-
-Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.
-Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
-
-We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no concessions separating equilibrium} in Section~\ref{sec:ncse}.
+This `best' \emph{concessions separating equilibrium}, where `best' is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement, in which out of equilibrium beliefs put zero weight on types that can never gain from deviating.
+
+Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from ``Trust'' is discouraged through grim trigger punishments.\footnote{When $\de = \frac{W}{T+D}$, there is also a semi-separating equilibrium where only some high types give a concession.
+Here, high types give a smaller expected concession and trade off a lower probability of achieving cooperation.
+We will focus on the ff \emph{concessions separating equilibrium} in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types therefore can be seen as making up for the imperfect information in this setting.
+
+We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no-concessions separating equilibrium} in Section~\ref{sec:ncse}.
 
@@
 
-The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society.
+The intuition for this addition to the model is that the country that receives the concessions can use them to build up their military or to build up their civil society, including through the provision of public goods.
 The recipient using concessions to build military strength hurts the giver of the concessions in war; the recipient using the concessions to strengthen civil society helps the giver in peace.
-The Golan heights is such an example: if Syria maintains peaceful relations with Israel, the Golan Heights is a reasonable concession to make, but if Syria renews military conflict with Israel, surrender of the strategic land would be disastrous for Israel.
+The Golan Heights is such an example: if Syria maintains peaceful relations with Israel, the Golan Heights is a reasonable concession to make, but if Syria renews military conflict with Israel, surrender of the strategic land would be disastrous for Israel.
 
@@
 
-For example, if both countries play Fight, Country 1 receives an additional benefit term $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
-However, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
-The other payoffs are modified analogously.
-
-Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the ``Peace'' outcome will be played.
-Conversely, in equilibrium, low types only participate in the ``War'' equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
-
-We turn next to characterizing a concessions separating equilibrium in this environment with future material value.
+If both countries play Distrust, Country 1 receives not only the immediate value of the concession and then $W-D$ in each period.
+Its welfare now has two additional terms.
+First, an additional benefit term in each period of the repeated game $W(1-\alpha_1) g_2$, which accounts for the value of the received concession as well as how much Country 1 invested in the military.
+Second, Country 1 also incurs extra damages $D(1-\alpha_2) g_1$ in each period of the repeated game that are proportional to the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2.
+The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, if they are scaled linearly by these variables but with a proportion other than 1, or if they are scaled by many plausible non-linear functions of $T$, $W$ and $D$.
+The results are a bit simpler if there is no scaling, but we believe it is more realistic to assume that the future benefits and costs of the gifts are proportional to the direct benefits and costs of cooperation/non-cooperation.
+For instance, a county who could impose more damage without the future value of the concessions is likely to be able to better leverage a concession than a country who can impose less damage.}
+
+Because $\al_i$ enters into the payoffs in a linear fashion, the choice that maximizes welfare in equilibrium is $\alpha=1$ for high types since a concession would only come from another high type in equilibrium, and thus only the Cooperation outcome will be played.
+Conversely, in equilibrium, low types only participate in the No Cooperation equilibrium and thus maximize their payoffs by choosing $\alpha=0$.
+
+We turn next to characterizing a \emph{concessions separating equilibrium} in this environment with future material value.
 
@@
 		\item[(a)] Assume $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D$ is positive and $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$.
-Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Fight and the high types give a concession in period 0 and play Trust unless the other country defects to Fight.
-		\item[(b)] In the best concessions separating equilibrium when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
+Then a subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give a concession in period 0 and play Trust unless the other country defects to Distrust.
+		\item[(b)] In the best \emph{concessions separating equilibrium} when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate.
 Equilibria with higher concessions yield strictly lower payoffs.
@@
 $\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5,.979)$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value.
-That is, future material value can destroy the opportunity for peace.
+That is, future material value can destroy the opportunity for cooperation.
 \hfill $\blacksquare$
 
-Comparative statics provide intuition for why using concessions with future material value makes it harder to achieve peace.
-The patience threshold is decreasing in $T$ because the benefit from cooperating with another high type increases.
-Similarly, the threshold is increasing in $D$ because the magnitude of future damages from pairing with a low type increases.
-Perhaps less obvious is the impact of $W$: here the threshold is again increasing.
-This is because the high type's own temptation to not give a gift and to use a received concession for military purposes increases in $W$.
-
-When the low type's patience level $\de_l$ increases, the high type's patience threshold decreases because a smaller gift is required to disincentivize the low type from pretending to be a high type.
-Finally, and perhaps surprisingly, the patience threshold is increasing in $p$.
-This happens because the gift must be larger in order to discourage low types from giving a gift, and this effect outweighs the increased attractiveness to the high type that comes directly from the increased probability of positive impacts from the future material value.\footnote{Comparative statics calculations available from the authors upon request.}
-
-Thus only an increase in the benefit from `Peace' and an increase in the low type's patience level make it easier to achieve `Peace' when gifts have future material value.
-Increases in all other parameters make it harder to achieve `Peace.'
+The comparative statics for the patience threshold $\de^c = \frac{W}{T+D}$ are straightforward for the \emph{concession separating equilibrium} when there's no material value.
+The threshold increases and cooperation becomes less likely when $W$ increases; the threshold decreases when either $T$ or $D$ increase.
+These relationships hold with a small caveat for the \emph{concession separating equilibrium} when there \emph{is} material value, where the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat is that, if both $T$ and $W$ become sufficiently large, the patience threshold will increase in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Distrust larger.
+The patience threshold decreases in $T$ and $D$, but for different reasons.
+$T$ is straightforward: a larger $T$ is a larger benefit from playing Trust.
+In contrast, a larger $D$ is a bigger cost of the negotiating partner playing Distrust.
+These relationships are not fundamentally changed by the presence of future material value because the future material value is proportional to the fundamental values of $W$, $T$, and $D$.
+
+There are, however, two variables that do not affect the patience threshold in the no material value case that \textit{do} affect the threshold when there is future material value: $\de_l$ and $p$.
+When the low type's patience level $\de_l$ increases, the high type's patience threshold increases; this is because a more patient low type requires a larger gift in order not to mimic the high type.
+In the case of no material value, the low type's discount factor doesn't enter into the gift, and therefore it doesn't influence how much patience is required for cooperation.
+
+The other variable that influences the patience threshold in the case of future value is $p$, the proportion of cooperative types in the population.
+Although the gift in the no-future-material-value case \emph{is} an increasing function of $p$, it is a linear function of $p$ just like the variables $T$, $W$, and $D$.
+Thus the cost of paying the gift and the direct benefits in the repeated game increase at the same rate so that the likelihood of cooperation does not vary in $p$ when gifts have no future material value.
+In the future-material-value case, the size of the gift required to separate the high types from the low types increases more than linearly in $p$ and thus faster than the other terms.
+Therefore the patience threshold in the future-material-value case increases as $p$ increases.
+That is, the cost of giving the gift weighs more heavily in the decision to cooperate relative to the material costs and benefits, requiring states to be more patient to separate and thus reducing the likelihood of cooperative types.\footnote{For the comparative statics calculations, see Appendix~\ref{ap:mat_val}.}
 
@@
 
-The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens $p$ of the time.
+The intuition for Lemma~\ref{lemma:efficiency} is that future material value of concession helps you when your negotiating partner turns out to be a high type, and this happens with probability $p$.
 On the other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type.
-Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Fight, the larger is the welfare loss when the negotiating partner turns out to be a low type.
+Similarly, the larger are the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type and the larger are the damages from Distrust, the larger is the welfare loss when the negotiating partner turns out to be a low type.
 
@@
 Inefficient concessions are optimal when there's a good chance of facing a low type who will use the concession against you (i.e.
-$p$ is small) as well as when the benefits from ``Peace'' are small relative to the damages from ``War.'' This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
+$p$ is small) as well as when the benefits from Cooperation are small relative to the damages from No Cooperation.
+This finding of inefficiency is for profoundly different reasons than the literature related to Camerer (1988) or Prendergast and Stole (2001).\footnote{Since our initial setup is essentially identical to Camerer's, inefficiency of  pre-play communication would also manifest in our model if a stage of pre-play communication were added.
 With a slight behavioral modification, the reasoning of Prendergast and Stole (2001) can also be had: if a country suffers regret after efficiently giving to a type different than their own, there is a premium for guessing correctly.
-In Prendergast and Stole the two types are equal except in labeling; in our model, high types and low types are used so there is an incentive for low types to try to pose as high types.
-However, putting this difference aside, the inefficiency result can be viewed as similar to that in Prendergast and Stole (2001).
+In Prendergast and Stole the two types are equal except in labeling; in our model, there is an incentive for low types to try to pose as high types.
+However, putting this difference aside, the inefficiency result can be viewed as having the same flavor as that in Prendergast and Stole (2001).
 That is, if countries suffer a ``mismatching'' cost due to giving to the wrong type, they will be hesitant to do so and may offer inefficient concessions.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types from entering the game altogether, here making concessions inefficient is a device to prevent low types from using those concessions against the giver of the concessions in the future.
@@
 
-In order to make the mechanism incentive compatible for the low types, some value of the concessions must be destroyed, i.e.
-$e<1$, so that the low type is not tempted to misrepresent its type in order to receive the gift.
-The range of efficiency that allows for a mechanism $M$ to be incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
+The range of efficiency that allows a mediator to make mechanism $M$ incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
 
@@
 
-The low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism; this puts an upper bound on how efficient concessions can be.
-In some cases, the high type incentive constraint also provides an upper bound on the size of the concession.
-
-Ultimately, mediation is desirable if it can improve welfare or improve the chances for peace. Theorem~\ref{theorem:medwel} shows that the mediation mechanism $M$ can do both.
+In part (a), we see that the low type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism.
+This puts an upper bound on how efficient concessions can be.
+In part (b), we see that the high type incentive constraint also provides an upper bound on the size of the concession in some cases.
+
+Ultimately, mediation is desirable if it can improve welfare or improve the chances for cooperation. Theorem~\ref{theorem:medwel} shows that a mediator who implements mechanism $M$ can do both.
 
 \begin{theorem}
-	When concessions have future material value, the mediation mechanism $M$ can be used to
+	When concessions have future material value, a mediator can use mechanism $M$ to
 	\begin{enumerate}
@@
 
-(c) When the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large, the parties cannot make peace on their own even with the possibility of signaling their type through concessions.
-By ensuring that only high types exchange gifts, the mediator removes this threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
-This allows types with lower patience levels to separate through the mechanism when those same types cannot separate in the bilateral game with concessions with future material value.
-
-Thus a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve peace.
+Part (c) is relevant when the impacts of future material value are too strong, i.e when the probability of a low type is too high and/or the damages from investing in military power are too large.
+In this case, the parties cannot cooperate on their own even with the possibility of signaling their type through concessions.
+By ensuring that only high types exchange gifts, the mediator removes the threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type.
+Here, the help of the mediator allows types with lower patience levels to separate when those same types cannot separate in the bilateral game with concessions with future material value.
+
+Thus a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve the cooperative outcome.
 The improvements by the mediator here do not rely on the mediator's private information as in the models of Kydd (2003), Rauchhaus (2006) and Smith and Stam (2003).
@@
  \noindent{\emph{Proof of Theorem \ref{theorem:1}}:\\
-Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Fight in the first period and then every period thereafter by the one-shot deviation principle.
-If both countries play Trust in a period, a ``Peace'' equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of the ``War'' equilibrium.
-Low types play Fight in the first period, so a high type that observed Fight being played would respond by playing Fight in period 2 and in all future periods.
+Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first period and then every period thereafter by the one-shot deviation principle.
+If both countries play Trust in a period, a Cooperation equilibrium takes place and both countries continue to play Trust in every period with the grim trigger threat of Distrust.
+Low types play Distrust in the first period, so a high type that observed Distrust being played would respond by playing Distrust in period 2 and in all future periods.
 A country plays Trust if and only if the following condition is satisfied:
@@
 
-If the potential advantages of ``Peace'' are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Fight.
-Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Fight in each period even if the other country plays Trust.
+If the potential advantages of Cooperation are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust.
+Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each period even if the other country plays Trust.
 Thus we call these countries low types for purposes of this equilibrium.
@@
 \emph{Proof of Lemma~\ref{lemma:3}:}\\
-In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on concessions separating equilibrium in which countries reveal their types truthfully.
-This allows high types to only play ``Trust'' in period 1 with other high types and to play Fight with low types.
-Low types play Fight (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
+In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on \emph{concessions separating equilibria} in which countries reveal their types truthfully.
+This allows high types to only play ``Trust'' in period 1 with other high types and to play Distrust with low types.
+Low types play Distrust (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
 
@@
 That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$
+
+\vskip.3in
+\noindent\emph{Comparative statics}
+
+First, we examine the gifts in a \emph{concessions separating equilibrium} first with no material value (or destroyed material value) and then when there is future material value.
+
+That the gift in the {concessions separating equilibrium} with no material value (or destroyed material value) is increasing in $p$ is direct since the gift is equal to $p(T+D)$.
+It is also clearly increasing in both $T$ and $D$.
+
+That the gift in the model with material value, $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, is increasing in $p$ is straightforward.
+Recall that all the variables are assumed to be strictly positive, with $0 < \delta_l < 1$.
+It follows that the numerator is increasing in $p$ and the denominator is decreasing in $p$ and assumed positive.
+Therefore, $g^1$ is increasing in $p$.
+In formal terms, $\frac{\partial g^1}{\partial p} = \frac{(1 - \de_l +D)(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2} > 0$.
+
+$g^1$ is unchanged in $W$ since $W$ does not enter the expressing anywhere. The other three parameters require working out the formal result.
+
+Patience level of the low type: $$\frac{\partial g^1}{\partial \delta_l} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(-p)(T+D) - \left(1-\de_l\right)p\left(D + T\right)(-1)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$  $$= \frac{-\left(\left(1-\de_l\right)\left(1 - pT \right)p(T+D) + (1-p) D\right)p(T+D) + \left(1-\de_l\right)p\left(D +	 T\right)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$ $$= \frac{(1-p) pD(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term so it is positive.
+Therefore we have $\frac{\partial g^1}{\partial \delta_l} > 0$.
+
+Benefit from negotiating partner playing Trust: 
+$$\frac{\partial g^1}{\partial T} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(\de_l p -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 - pT + pD + pT\right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 + pD \right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term so it is positive.
+Therefore we have $\frac{\partial g^1}{\partial T} > 0$.
+
+Damages from negotiating partner playing Distrust: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) - T(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{1-\de_l -pT + \de_l p T - T +pT\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
+$$= \frac{(1-\de_l)p\left\{1-\de_l + \de_l p T - T\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Because both the denominator and $(1-\de_l)p$ are strictly positive, the sign of this derivative matches the sign of $1-\de_l + \de_l p T - T$.
+It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise.
+So, when the benefit from the partner playing trust is sufficiently mall, the gift size will increase in $D$, but otherwise the gift size will decrease in the damages from the negotiating partner playing Distrust.
+
+We now turn to the patience threshold that defines the high type.
+In the {concessions separating equilibrium} with no material value, we have $\frac{W}{T+D} = \de^{c}$, which increases in $W$ and decreases in $T$ and $D$.
+Notice it is not a function of $\delta_l$ or $p$.
+
+The results for the patience threshold when there is material value are more complex.
+First, recall that $\de^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$ where the denominator of the first term is simply $\delta^1$.
+
+As in the case of no material value, the patience threshold is increasing in $W$: $\frac{\partial \delta^1}{\partial W} = \frac{p}{g^1} + p > 0$ since both $p$ and $g^1$ are strictly positive.
+
+The patience threshold is increasing in $p$. That is, 
+$$\frac{\partial \delta^1}{\partial p} = \frac{g^1 (W-D-T) - p(W-D-T)\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ W-T-D$$$$= (W-D-T)\left\{\frac{g^1  - p\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ 1\right\}=\frac{W-D-T	}{(g^1)^2}\left\{g^1  - p\frac{\partial g^1}{\partial p} + (g^1)^2\right\}$$
+$$=\frac{W-D-T}{(g^1)^2}\left\{p(T+D)\left[-\de_l (1-\de_l) - \de_l D - \de_l p D(1-\de_l)\right]\right\} > 0.$$
+We assume that $T > W - D$, so the numerator of the fraction is positive, while the denominator is positive since it's a squared term.
+$p(T+D)$ is positive because all three variables are positive.
+Each term in the square brackets is negative.
+Therefore the full expression is positive.
+
+The patience threshold is also increasing in the low type's patience level $\de_l$. That is,
+$$\frac{\partial \delta^1}{\partial \de_l} = \frac{g^1 \cdot 0 + p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} = \frac{p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} > 0.$$
+The result holds because each term in the expression is positive.
+
+In contrast, the patience threshold is decreasing in the benefit from the negotiating partner playing Trust, $T$. That is,
+$$\frac{\partial \delta^1}{\partial T} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial T}}{(g^1)^2}-p = \frac{p}{(g^1)^2}\left\{ p(T+D-W) \frac{\partial g^1}{\partial T} - g^1 -(g^1)^2 \right\}$$
+$$= \frac{p}{(g^1)^2}\left\{-(1-\de_l)W - (1- \de_l P)WD -2TD(1-\de_l)p \right\} < 0.$$
+The result holds because $p$ and $g^1$ are positive, while each additive term in the curly braces is negative.
+
+The result is more nuanced for $D$, the cost of the negotiating partner playing Distrust. 
+$$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$
+If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression will always be negative.
+As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_l D(1-p)}{1-\de_l}$.
+When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.
 
@@
 Both parties are instructed to give efficient gifts.
-The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the ``Peace'' equilibrium.
-The low-type player knows it will defect and be in a ``War'' equilibrium and so invests entirely in the military.
+The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the Cooperation equilibrium.
+The low-type player knows it will defect and be in a No Cooperation equilibrium and so invests entirely in the military.
 %		\begin{multline}

### 2023-11-29 draft.tex
Remove Walter
I decided the simplest way to alleviate the reviewer's concern was to simply remove the discussion of Walter, as it is a motivating example only. So I rewrote with 2 archetypes instead of 3.

It would also be possible to keep Walter in, but position disarmament as the second example, rather than the first. However, I think the reviewer is right that the destruction of weapons is not a major point of contention usually. The key issue is the rebels giving up their weapons -- the government (usually) doesn't really care if they are confiscated vs. destroyed.  So it isn't a great arc

@@
 %Attempting to add in the China-US case in a prominent way. The prose is more awkward than I would like still. - March 13, 2023 BG
-Three archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
-The first is the case of disarmament, the second is the concession of strategically valuable territory, and the third is the export of advanced technology to a strategic rival.
+Two archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement.
+The first is the concession of strategically valuable territory in a military dispute, and the second is the export of advanced technology to a strategic rival.
 %In each case, efficient concessions are difficult to make because the item conceded may be used by the recipient to bolster their military capabilities, altering the balance of power in the ongoing conflict.
@@
 
-Barbara Walter identified disarmament as the ``critical barrier to civil war settlement'' (1997).
+%Barbara Walter identified disarmament as the ``critical barrier to civil war settlement'' (1997).
 Particularly in conflicts between a rebel group and a central government, the best-achievable negotiated settlement often involves policy concessions by the government in exchange for disarmament and recognition of government authority by the rebels.
@@
 
-Control of strategically valuable territory can pose similar challenges in both civil and interstate wars.
+Control of strategically valuable territory is often contested in both civil and interstate wars.
 Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide military advantage in a future conflict.
@@
 Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory.
-Thus, it might have been efficient in the mid-1990s for the Armenian/Karabahk side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence.
+Thus, it might have been efficient in the mid-1990s for the Armenian/Karabakh side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence.
 However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor, which connects Ngorno-Karabakh and Armenia.
@@
 
-In our third archetypal example, under both the Trump and Biden administrations, the US has restricted the export of cutting-edge technology to China.
+In our second archetypal example, under both the Trump and Biden administrations, the US has restricted the export of cutting-edge technology to China.
 China and the US are engaged in geo-strategic competition.
@@
 
-In all three of these archetypal examples, cooperative/peaceful outcomes are extremely challenging to reach.
-Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
-Interstate wars over territory are similarly prone to violent, rather than negotiated, resolution (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
+In both of these archetypal examples, cooperative/peaceful outcomes are extremely challenging to reach.
+%Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement.
+Interstate wars over territory tend to end on the battlefield, rather than through negotiated settlement (Hensel 1996), and the trajectory of competition and cooperation between the US and China remains highly uncertain.
 Can mediation offer a path to more settlement, peace, and prosperity in these challenging contexts?
@@
 
-\item Walter, Barbara F. ``The Critical Barrier to Civil War Settlement.'' \emph{International Organization} 51, no. 3 (1997), 335-364.
-
-\item Walter, Barbara F. \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton: Princeton University Press, 2002.
+%\item Walter, Barbara F. ``The Critical Barrier to Civil War Settlement.'' \emph{International Organization} 51, no. 3 (1997), 335-364.
+
+%\item Walter, Barbara F. \emph{Committing to Peace: The Successful Settlement of Civil Wars.} Princeton: Princeton University Press, 2002.
 

### 2023-12-03 draft.tex
change theorem to proposition throughout the paper

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
 \newtheorem{lemma}{Lemma}
@@
 
-\begin{theorem}
+\begin{proposition}
 \emph{No Concessions Separating Equilibrium}\\
@@
 A subgame perfect Nash equilibrium exists in which low types give no concessions in period 0 and always play Distrust and the high types give no concessions in period 0 and play Trust unless the other country defects to Distrust.
-	\label{theorem:1}
-\end{theorem}
+	\label{proposition:1}
+\end{proposition}
 \emph{Proof}: See Appendix.
@@
 
-\begin{theorem}
+\begin{proposition}
 \emph{Concessions Separating Equilibrium (CSE)}
@@
 \end{enumerate}
-	\label{theorem:2}
-\end{theorem}
+	\label{proposition:2}
+\end{proposition}
 \emph{Proof:} See Appendix.
@@
 
-\begin{theorem}
+\begin{proposition}
 \emph{Concessions Separating Equilibrium (CSE) with Material Value}
@@
 \end{enumerate}
-	\label{theorem:csemv}
-\end{theorem}
+	\label{proposition:csemv}
+\end{proposition}
 \emph{Proof:} See Appendix.
@@
 
-By Theorems~\ref{theorem:1} and ~\ref{theorem:2}, both the \emph{no-concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.
-
-The patience threshold to separate through concessions with future material value is much higher under these parameters when the concessions carry future material value: by Theorem~\ref{theorem:csemv}(a), this threshold is $0.979$.
+By Propositions~\ref{proposition:1} and ~\ref{proposition:2}, both the \emph{no-concessions separating equilibrium} and the \emph{concessions separating equilibrium} are possible when gifts have no material value.
+
+The patience threshold to separate through concessions with future material value is much higher under these parameters when the concessions carry future material value: by Proposition~\ref{proposition:csemv}(a), this threshold is $0.979$.
 Thus the \emph{concessions separating equilibrium with efficient gifts} is \emph{not} possible.
@@
 This means that there are parameters under which Cooperation cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but Cooperation can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}.
-This is part of the substance of Theorem~\ref{theorem:4}.
-
-\begin{theorem}
+This is part of the substance of Proposition~\ref{proposition:4}.
+
+\begin{proposition}
 		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed.
 There are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
-	\label{theorem:4}
-\end{theorem}
+	\label{proposition:4}
+\end{proposition}
 \emph{Proof}: We invoke Lemmas~\ref{lemma:efficiency} and \ref{lemma:e-patient} as two different reasons for which the parties would choose the \emph{concessions separating equilibrium with inefficient gifts}.
@@
 
-The range of efficiency that allows a mediator to make mechanism $M$ incentive compatible and individually rational for both types is given in Theorem~\ref{theorem:med}.
-
-\begin{theorem}
+The range of efficiency that allows a mediator to make mechanism $M$ incentive compatible and individually rational for both types is given in Proposition~\ref{proposition:med}.
+
+\begin{proposition}
 \emph{Mediation}
@@
 \end{enumerate}
-	\label{theorem:med}
-\end{theorem}
+	\label{proposition:med}
+\end{proposition}
 \emph{Proof:} See Appendix.
@@
 
-Ultimately, mediation is desirable if it can improve welfare or improve the chances for cooperation. Theorem~\ref{theorem:medwel} shows that a mediator who implements mechanism $M$ can do both.
-
-\begin{theorem}
+Ultimately, mediation is desirable if it can improve welfare or improve the chances for cooperation.
+Proposition~\ref{proposition:medwel} shows that a mediator who implements mechanism $M$ can do both.
+
+\begin{proposition}
 	When concessions have future material value, a mediator can use mechanism $M$ to
@@
 	\end{enumerate}
-	\label{theorem:medwel}
-\end{theorem}
+	\label{proposition:medwel}
+\end{proposition}
 \emph{Proof:} See Appendix.
@@
 Further, the mechanism can work if the mediator is either (1) only able to incentivize some portion of the concessions or (2) enforces the concessions with some probability less than 1.
-This would tighten the low type's incentive constraint and loosen the high type's incentive constraint, creating a different level of optimal efficiency of the concessions.\footnote{To see this, in the incentive constraints in the proof of Theorem~\ref{theorem:med}, replace $g_h$ with $q \cdot g_h$, where $q$ represents the proportion of the concession that can be enforced or the probability with which the full concession is enforced.}
+This would tighten the low type's incentive constraint and loosen the high type's incentive constraint, creating a different level of optimal efficiency of the concessions.\footnote{To see this, in the incentive constraints in the proof of Proposition~\ref{proposition:med}, replace $g_h$ with $q \cdot g_h$, where $q$ represents the proportion of the concession that can be enforced or the probability with which the full concession is enforced.}
 
@@
 
- \noindent{\emph{Proof of Theorem \ref{theorem:1}}:\\
+ \noindent{\emph{Proof of Proposition \ref{proposition:1}}:\\
 Playing Trust in the first period and thereafter as long as Trust has always been played will be incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first period and then every period thereafter by the one-shot deviation principle.
@@
 \\
-\emph{Proof of Theorem \ref{theorem:2}:}\\
+\emph{Proof of Proposition \ref{proposition:2}:}\\
 In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low type gift.
@@
 \label{ap:mat_val}
-\emph{Proof of Theorem \ref{theorem:csemv}:}\\
+\emph{Proof of Proposition \ref{proposition:csemv}:}\\
 In the separating equilibrium constructed here, players will believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low type gift.
@@
 			\\
-\emph{Proof of Theorem~\ref{theorem:med}:}\\
+\emph{Proof of Proposition~\ref{proposition:med}:}\\
 (a) The low type's individual rationality constraint is satisfied trivially: the low type gets the No Cooperation payoff forever outside the mechanism; it also gets the No Cooperation payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
@@
 \\
-\emph{Proof of Theorem~\ref{theorem:medwel}:}\\
+\emph{Proof of Proposition~\ref{proposition:medwel}:}\\
 An example suffices to prove each part.
@@
 Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
-By Theorem~\ref{theorem:2}, the \emph{concessions separating equilibrium with efficient gifts} is possible.
-
-By Theorem~\ref{theorem:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.75$.
+By Proposition~\ref{proposition:2}, the \emph{concessions separating equilibrium with efficient gifts} is possible.
+
+By Proposition~\ref{proposition:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.75$.
 Using Lemma~\ref{lemma:e-patient}, we see that both the \emph{concessions separating equilibrium with efficient gifts} and the \emph{concessions separating equilibrium with inefficient gifts} are possible.
@@
 
-We use Theorem~\ref{theorem:2}(a) to find that the patience threshold to separate through concessions with inefficient concessions is $0.5$.
+We use Proposition~\ref{proposition:2}(a) to find that the patience threshold to separate through concessions with inefficient concessions is $0.5$.
 This combined with Lemma~\ref{lemma:e-patient} shows that neither the \emph{concessions separating equilibrium with efficient gifts} nor the \emph{concessions separating equilibrium with inefficient gifts} is possible.

### 2024-01-20 QJPS/Inefficient_Concessions.tex
Add QJPS submission files (conditional accept stage)
The .tex is compiled on OverLeaf b/c I hired an editor to help implement the style guidelines. Inefficient_Concessions.pdf replaces draft.pdf as the most recent version of the manuscript, but I can't get it to compile on my local machine.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Please note that whilst this template provides a 
% preview of the typeset manuscript for submission, it 
% will not necessarily be the final publication layout.
%
%% Document class options: (**...** are defaults)
%  - bibtex: Uses bibtex+natbib, chicago.bst 
%  - biblatex: Uses biblatex-chicago
%      You MUST select one of the above two options, depending
%      on whether you prefer bibtex or biblatex. This template
%      contains code that uses bibtex.
%  - twocolumn: Switch to two column for main text
%  - singlespace/onehalfspace/**doublespace**: 
%         changes line spacing for main text
%  - **blind**/nonblind: Anonymises authors 
%         and affiliations, or not
%  - autowc: Automatically inserts a word count
%         after the abstract, using texcount. 
%         The abstract is ignored. 
%         NOTE THAT THIS WILL ONLY WORK IF YOU HAVE  
%         INSTALLED TEXCOUNT, AND HAVE ENABLED --shell-escape
%         OR --enable-write18. (These will work on Overleaf.)
%         If you get an error about "texcount not found", delete
%         the autowc option, and manually specify the wordcount 
%         with \totalwordcount{xxx}.
%%% autowc may cause longer compilation time. You can 
%%% disable it first while actively editing, and only
%%% enable it when you're ready to take stock and check
%%% on your work.
\documentclass[bibtex,autowc]{apsr_submission}
% \totalwordcount{500}

%% Example alternative options with everything the opposite of the above: (DO NOT USE AUTOWC WITH BIBLATEX; the word count will be greatly over-reported)
% \documentclass[biblatex,nonblind,singlespace,twocolumn]{apsr_submission}

\title{Inefficient Concessions and Mediation}

% The custom \author command takes THREE arguments:
% #1 = Author name
% #2 = Affiliation name
% #3 = Brief author profile, or anything that you'd usually put in a \thanks. Leave blank {} if there's nothing to be said.
\author{Kristy Buzard}
       {Syracuse University}
       {We are indebted to Ben Graham for his many contributions. We thank Eli Berman, Renee Bowen, and Joel Watson as well as generous seminar participants for helpful discussions and comments. Affan Rahman and Apurvi Bhartia provided excellent research assistance. All remaining errors are our own.}

% \author{Author Two}
%        {Affiliation C}
%        {Author Two is Assistant Professor, Faculty of Z, Affiliation B, 42813. Corresponding Author (a.2@acme.edu) Additional notes about Author Two.}

% \author{Author Three}
%        {Affiliation B}
%        {Author Three is ...}

%% Any other acknowledgements or author notes

%% These are used for the headers
% \runningtitle{APSR Submission Template}
\runningauthor{Kristy Buzard} % 4 + Authors, Author One et al.

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{rotating}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bi}{\begin{itemize*}}
\newcommand{\ei}{\end{itemize*}}
\newcommand{\mb}{\mathbf}
\newcommand{\ve}{\varepsilon}
\newcommand{\real}{\mathbb{R}}
\newcommand{\de}{\delta}
\newcommand{\al}{\alpha}
  \usepackage{setspace}
  \doublespacing

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{fact}{Fact}
\newtheorem{corollary}{Corollary}

%% If you are using a custom figure or table environment from a package and it's not getting framed, add \makeframedenv{MyFigure} in the preamble, where the custom figure environment is \begin{MyFigure}...\end{MyFigure}.
%% Currently table, table*, figure, figure*, longtable, supertabular, sidewaystable and sidewaysfigure will be automatically framed.

%% Handy for setting wide tables/figures in landscape
\usepackage{pdflscape}

%% Recent LaTeX distributions should be able to automatically convert .eps to .pdf; but if this isn't happening, try loading the epstopdf package manually
% \usepackage{epstopdf}

%% Just to add some dummy text
\usepackage{lipsum}
% \usepackage[font=sf]{caption}
% \usepackage[font=sf]{floatrow}

%%% Use \addbibresource{...} if using BibLaTeX
% \addbibresource{sample.bib}

\begin{document}
% %% DO NOT REMOVE THESE LINES. For automatic word count.
% TC:ignore
\begin{frontmatter}
\begin{abstract}
When two parties are engaged in conflict and each distrusts the other's ability to cooperate or make peace, concessions can be used to indicate an interest in cooperation or peacemaking. However, when negotiating parties are concerned that concessions could be used against them in the future, a lack of trust can prevent optimal concessions from being made and therefore reduce the possibility of peace or cooperation. Using a repeated game that is preceded by an opportunity to signal one's commitment to cooperation through the provision of concessions, we formally demonstrate that concerns over the future use of concessions can explain the existence of inefficient concessions. We then use mechanism design to explore ways a third-party mediator can act as a guarantor that promised concessions would be delivered, thereby reducing inefficiencies and increasing the potential for peace and cooperation. In this process, we open up a new rationale for mediation: to increase the efficiency of signaling in a preliminary round of negotiations and to overcome the concern that concessions could be used against the giver in the future. 
\end{abstract}
\end{frontmatter}
% %% DO NOT REMOVE THIS LINE. For automatic word count.
% TC:endignore

% \section{Introduction}

In negotiations with its neighbors, Israel is hesitant to give certain concessions. The Golan Heights, captured from Syria during the 1967 War, is a particular point of contention in Israeli-Syrian relations. Although the Golan Heights does not have the West Bank’s historical or religious importance, Israel values it for its highly strategic location. The Golan Heights could be a useful concession, but Syria might use the concession against Israel if Israel gave over the land. The West Bank settlements are similar; many are located on hilltops that could offer strategic military outposts for forces hostile to Israel. When Israel occasionally abandons settlements, it generally dismantles all infrastructure, including water and electricity, and bulldozes the buildings. Although inefficient, this reduces the possibility that the settlements will be used against Israeli interests. Without trust between negotiating parties, the most efficient concessions are often difficult to arrange.

In both active wars and long-simmering conflicts, settlement negotiations often occur simultaneously with continued fighting. This is also true in non-violent disputes, such as long-running episodes of geo-strategic competition: parties engage in costly conflict while negotiating, foregoing the value of the public goods they could create through cooperation. If settlement is achieved, additional costs of conflict -- including additional death and destruction -- are averted. Third-party mediators often participate in such negotiations, but the literature remains divided regarding how and under what conditions mediation can be effective \citep{bercovitch2000why, greig2005a, beardsley2006mediation, duursma2020}. This paper sheds new light on the productive role mediators can play by examining their effect on the efficiency of the concessions that conflict participants can offer. In our context, the efficiency of a concession is determined by how much of the concession's material value is intact when the recipient receives it. If the party who gives the concession destroys any of its material value, the concession is deemed to be less than fully efficient.

We introduce a two-sided signaling model followed by a repeated Prisoner's Dilemma in which concessions can provide future value to the recipient and/or serve as a signal that provides the recipient with information about the type of player making concessions. We use this model to show that concerns that concessions could be used against the giver in the future can undermine cooperation. Using a mechanism design framework, we demonstrate that a mediator can facilitate more efficient concessions by removing uncertainty about the ability of the parties to commit to a settlement. Perhaps more importantly, the mediator can also facilitate settlement sometimes when the negotiating parties cannot achieve it through bilateral interaction. In other words, commitment is essentially a far-sighted preference that allows cooperation to emerge, uncertainty can result in missed opportunities for cooperation, and concessions and mediation can facilitate conflict settlement and the provision of public goods.

Two archetypal situations illustrate the significance and difficulty of efficient concession-making in dispute settlement. The first is the concession of strategically valuable territory in a military dispute, and the second is the export of advanced technology to a strategic rival. %In each case, efficient concessions are difficult to make because the item conceded may be used by the recipient to bolster their military capabilities, altering the balance of power in the ongoing conflict. Also true in each case, if dispute settlement is achieved, a public good is produced --- peace in the first two cases and innovation and growth in the civilian economy in the third case.

%Barbara Walter identified disarmament as the ``critical barrier to civil war settlement'' (1997). Particularly in conflicts between a rebel group and a central government, the best-achievable negotiated settlement often involves policy concessions by the government in exchange for disarmament and recognition of government authority by the rebels. Disarmament by rebels is an efficient concession if fully-operational weapons are turned over to the central government for its own use, while disarmament accompanied by decommissioning is inefficient because the value of the arms is destroyed. Disarming and turning over fully functional weapons is an incredibly difficult concession for rebels to make: once they turn over their arms, they lose future bargaining leverage and have no guarantee that their own weapons will not be used against them later. If the rebels can instead decommission those weapons, an important stumbling block to peace is removed.\footnote{Other stumbling blocks remain, including the fact that the government retains its weapons. Thus, credible commitment on the part of the government remains difficult, even if decommissioning occurs.} Peace may therefore be possible with inefficient concessions where it is impossible with efficient concessions.\footnote{Walter's approach is part of a much broader literature on the bargaining model of war that looks at concessions and asymmetric information, including  Fearon (1996), Powell (1996a and 1996b, 2006), Slantchev (2011) and Arena (2013).}

Control of strategically valuable territory is often contested in both civil and interstate wars. Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide a military advantage in a future conflict. Following the 1992 war between Armenia and Azerbaijan over the disputed region of Ngorno-Karabakh, Armenia retained control of a significant amount of Azerbaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland. Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory. Thus, it might have been efficient in the mid-1990s for the Armenian/Karabakh side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence. However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor that connects Ngorno-Karabakh and Armenia. Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Ngorno-Karabakh and Armenia. The territory was not conceded, and the conflict persisted in a costly stalemate for almost twenty years until war broke out anew in 2020.

In our second archetypal example, the US has restricted the export of cutting-edge technology to China under both the Trump and Biden administrations. China and the US are engaged in geo-strategic competition. The more rapid innovation and growth that free trade in chips and other technology would enable could benefit both countries. However, any technology the U.S. exports could be used in the military sector to pursue advanced weapons, altering the military balance of power. As of 2024, trade in numerous advanced technologies is restricted, reducing the global pace of innovation and economic growth.

In both archetypal examples, cooperative/peaceful outcomes are extremely challenging to reach. %Walter (1997) observes empirically that, due to the difficulty of making efficient disarmament concessions, civil wars tend to end on the battlefield, rather than through negotiated settlement. 
Interstate wars over territory tend to end on the battlefield rather than through negotiated settlement \citep{hensel1996}, and the trajectory of competition and cooperation between the US and China remains highly uncertain. Can mediation offer a path to more settlement, peace, and prosperity in these challenging contexts?

This paper explains why efficient concessions are sometimes impossible to make. It also revises our understanding of why inefficient concessions can sometimes be beneficial and how mediators can help increase the efficiency of concessions and make cooperation possible. Weapons, strategically valuable territory, and the sharing of advanced technology will not be conceded if the conceding side fears these items may be used in future attacks against them. Countries are reluctant to make concessions that can be used against them in later rounds of conflict or negotiation. One way to mitigate the risk of dangerous concessions is to destroy the future value of the concession---e.g., decommission weapons, reduce the strategic value of the territory being conceded, or only allow trade in less advanced technologies or technologies without military applications. Another option, and the one on which we focus in this paper, is third-party mediation. We demonstrate that a third-party mediator can facilitate negotiated settlement by increasing trust and enabling disputants to make more efficient concessions. The mediator does this by only requiring concessions from negotiating parties who are able to cooperate, thereby removing the risk that concessions might be used against the giver in the future.

%While an integral part of the literature on conflict, concessions have been only partially addressed by theoretical research. The broader literature that attempts to model war has included concessions as part of bargaining, but has not explicitly considered the role of concessions in achieving peace. Schelling's \emph{Arms and Influence} (1966) modeled war with a game theoretic framework, and Powell (1999) has also defended the use of modeling in understanding war. Fearon (1996), Powell (1996a and 1996b, 2006) and others consider war to be a bargaining failure, caused by commitment problems and asymmetric information. When the assets that are the object of the bargaining confer future power, a lack of credible commitment, or trust, can create a holdup problem that prevents the optimal level of cooperation (Fearon 1996). %[OUTSIDE THE WAR CONTEXT..., ???]

%In these models war can be averted by splitting the pie (e.g., the disputed territory) in a way acceptable to both parties. Concessions are modeled as offering part of the pie to the other party, and asymmetric information is about each party's \textit{resolve} to fight and/or military capabilities (Arena 2013). In this context, an example of costly signaling would be military preparations for war (Slantchev 2011).

%We approach the commitment problem through this same general understanding, but

We model a party's ability to cooperate as private information. A high type can cooperate; a low type has incentives not to cooperate. These types map onto the commitment problem, where a high type is a player who is able to commit. A low type, though perhaps willing, is unable to do so. A low type may posture like the high type but lacks the political muscle or will to follow through on a peace agreement. Democratic leaders may more often be high types because they are less likely to face coups or other hostilities in reaction to short-term decisions. This is not always the case, however. Mahmoud Abbas, President of the Palestinian National Authority, may be a low type with respect to his negotiations with Israel not because he does not want to make peace, but because he cannot credibly act on behalf of the entire Palestinian population.

In our model, concessions may act as signals, as an end in themselves, or as both simultaneously. One contribution of this paper is that it allows concessions to have future material value, signaling value, and both. We show that when concessions have both signaling and future material value, some of the material value of the concessions may be purposefully destroyed, and thus inefficiencies can emerge. Another contribution is that our model of concessions does not require countries to make an agreement that requires credible commitment, as is common in bargaining models. Instead, countries willingly provide a concession if they expect the signal it sends to provide a benefit in terms of future cooperation and public good provision.\footnote{When mediation is required to achieve cooperation in the model, it relies upon a manipulative mediator to enforce the required level of concessions.}

In analyzing both the signaling and material value of concessions, an extensive literature on gift giving is particularly helpful. Like concessions, costly gifts are shown to have a valuable role in relationship building. Furthermore, the gift-giving literature---more so than the concessions literature---focuses specifically on the issue of efficiency. For the purposes of this paper, we define inefficiency as giving a gift (i.e., a concession) whose cost to the giver is larger than its value to the recipient.

Often, inefficient gifts occur in the formative stages of relationships or in immature relationships \citep{camerer1988}. Gifts given in established relationships, such as wedding presents or spousal gifts, are more likely to be cash gifts or gifts that are specifically requested and, therefore, efficient. Because inefficient gift-giving is more likely in relationships and partnerships in the early stages of development, it is natural to suppose that inefficient gifts play a signaling role in addition to the material value of transferring the gift's inherent worth.

In efforts to explain the existence of gift-giving, \cite{camerer1988} and \cite{van2000economics} give several anthropological explanations for inefficiency.\footnote{\cite{prendergast2001} also provide an explanation for inefficient gift-giving that focuses on the utility of matching.} Amongst these explanations are altruism, social mores, and egoism. However, the most relevant explanation for international relations is that gift-giving is strategic. Camerer uses mechanism design to model gifts as costly signals, where inefficiency is useful in pre-play communication to form relationships between like types. This strategic giving of gifts in societies looks much like the strategic giving of concessions to remedy conflict situations. When modeled game-theoretically, these environments look even more similar.

Camerer's model has one period in which players---who are either low or high types---can signal before deciding whether to partner. A separating equilibrium is characterized by a threshold gift that is necessary for high types to reveal themselves, while low types do not send a gift. Two high types who receive each other's gifts choose to create a partnership with a positive payoff; other combinations do not find it worthwhile to form a partnership.

Camerer shows that in this general formulation, a costly signaling model always yields efficient gifts.\footnote{In an environment with repeated opportunities for concessions, \cite{watson1999starting}  shows that a strong relationship can be reached by starting with small gifts and increasing their size as the relationship becomes more committed. See \cite{van2000economics} for an overview of this literature.} In order to explain inefficiency, Camerer adds an additional pre-play period where players must pay a cost to enter the game and send and receive gifts. If types separate in the pre-play period with low types not being willing to pay, high types save the cost of sending a signal to low types in the main game. Under some parameterizations, high types have incentives to give inefficient equilibrium gifts in the main game to reduce the low types' expected payoff of playing below the pay-to-play fee. Such an action can keep out the low types, raising the expected payoff for a high type.

%Prendergast and Stole (2001) provide a second explanation for inefficient gifts. The authors explain inefficient gift-giving by modeling the utility of matching. That is, if players are of a like mindset they get an extra benefit so they are willing to take the risk of giving the wrong gift.

We propose a different conceptual framework that is rooted in a realistic international relations puzzle to explain this real-life phenomenon. The basic formulation of our mechanism-design approach expands on \cite{camerer1988}'s analysis. The model can achieve the basic \emph{inefficient gifts} results of \cite{camerer1988} %and Prendergast and Stole (2001) 
but does so using a different explanation for inefficiency. The basic model is a costly signaling model, at its root, similar to that in \cite{spence1973} and subsequent papers.\footnote{See \cite{connelly2011} for a review of the costly signaling literature.} In essence, the model shows that if concessions can be later used against the party that gives them, then it can be in a negotiating party's best interest to give inefficient concessions. Although our model is tailored to an international relations setting, the explanation for the inefficient giving of concessions may be more broadly applicable.

This demonstration of the incentives for inefficient concessions leads to a new explanation for the role of mediators in conflict resolution. Third-party involvement is ubiquitous in conflict, and mediation has been extensively studied in the literature. Still, the question of third-party effectiveness is intensely debated. Some authors have concluded that mediation has little impact \citep{bercovitch1996resolving, bercovitch1993nature, fortna2003}, while others find mediation plays a positive role in resolving conflict \citep{dixon1996, beardsley2006mediation}. However, the term mediation connotes a broad range of actions and interactions, making any one-size-fits-all conclusion on the efficacy of mediation difficult. The type of mediation affects the negotiation outcome \citep{bercovitch2000why, beardsley2006mediation}, as does the legitimacy of the mediator (e.g., \cite{duursma2020}) and the timing of the mediator's intervention \citep{greig2005a}.

It is essential to focus more precisely on the specific actions and environments that use particular types of mediation. To this end, this paper models an environment where parties employ a mediator who has manipulative abilities and where the primary issue is trust, not uncertainty about an opponent's capabilities. Parties are more likely to seek mediation when they are entrenched in costly conflict \citep{bercovitch2001negotiation, greig2005, greig2006, terris2005rational, svensson2006mediators}; we thus model parties to a conflict who can benefit from mediation in their efforts to overcome mistrust.\footnote{Alternatively, parties may seek a mediator to justify difficult concessions and avoid angering domestic constituencies \citep{allee2006legitimizing, beardsley2010pain, beardsley2014thirdparty}.}

The empirical results on mediation have, until recently, lacked strong theoretical foundations. Mediation is not uncommon, but we are only beginning to understand why actors use it. Recent literature models mediation using mechanism design for settings where militarization or the resolve to fight are private information \citep{bester2006, fey2009, fey2010, fey2011, horner2010, meirowitz2012, meirowitz2019}. In particular, \cite{meirowitz2019} show that---when asymmetric information is about the level of militarization---a \textit{Myerson mediator} can circumvent the incentives for militarization that arise in unmediated peace talks and improve the chances for peace. This paper expands the theoretical literature by modeling the role of a manipulative mediator when the information asymmetry is about parties' abilities to commit to cooperation and concessions have a future material value that could be used to harm the giver. Here, a mediator can achieve peace or the provision of other public goods in situations where bilateral concessions cannot and with concessions that are more efficient when bilateral concessions must be inefficient to achieve peace.

\section{Model}
\label{sec:model}

Countries\footnote{We refer to players as countries, though it may also be appropriate to think of players as intra-state actors, as in a civil war.} are of two possible types, high and low. A high type discounts future period payoffs at rate $\delta_h$ and a low type discounts at $\delta_l$ where $\delta_h >\delta_l$ and $\delta_h ,\delta_l$ $\in (0,1].$ Before the start of the game, nature independently determines the types of Country 1 and Country 2. The type distinction, as explained in detail later, encompasses the country's willingness to cooperate in solving the conflict. That is, throughout the analysis we define a low type as a player whose only sequentially rational strategy is to remain in conflict in all periods.\footnote{This is in contrast to the bargaining theory of war, where a high(low) type has strong(weak) military capability that then interacts with a symmetric, known level of $\delta$. This accounts for the different impact of $\delta$ in the two models.} It is not necessary to think of a type as fixed; it can change as regimes and relations between countries change.\footnote{We can enrich the model to assign a probability (and even different probabilities) of a country's type shifting from high to low or low to high in a given period.}

The probability of nature selecting the high type for a given country is $p$. The probability of nature selecting the low type is $1-p$.\footnote{Note that, consistent with the literature, parameters are symmetric across countries. Qualitative results do not depend on this assumption, and equilibria and equilibrium concessions can easily be calculated for parameterizations that are asymmetric parameters.} Countries are aware of their own type but not the type of the other country. Similar scenarios have been modeled as credible commitment problems in the bargaining literature. Our model can be thought of as a reduced form bargaining model, but it can also be considered somewhat differently. That is, when trust is the issue to be solved, concessions are one way in which countries can signal their commitment. By modeling conflict in this way, we gain insight into how a third party can ameliorate trust issues inherent to the conflict.

In Period 0, Countries 1 and 2 simultaneously give costly concessions $g_i$ $\in \mathbb{R} \geq 0$, where $i\in\left\{1,2\right\}$. Concessions are given at cost $C(g_i)$ and are valued by the recipient in the amount $g_i$. For simplicity, we assume throughout that the cost of giving the gift is equal to the value to the recipient, that is, $C(g_i)= g_i$.

Beginning in period 1---which we refer to as \textit{Round 1} to emphasize that this is the first period of the repeated game---countries engage in an infinitely repeated Prisoner's Dilemma once per round with stage game payoffs in Table \ref{tab-1}.\footnote{For a game-theoretic analysis of the repeated Prisoner's Dilemma with uncertainty over discount factors that focuses on studying players' belief structures, see \cite{maor2015}. Our model differs in that it adds an initial period before the repeated Prisoner's Dilemma begins, in which players make costly concessions to each other. These concessions that enable signaling between the players make the analysis of their beliefs much simpler than in \cite{maor2015}.} Although not a good representation of all-out war or even a zero-sum short-term war, the Prisoner's Dilemma is appropriate to represent a limited, continuing conflict, military or otherwise. In cases appropriately modeled by a Prisoner's Dilemma, it would be better for both parties to exit the protracted conflict, but no party has the unilateral incentive to do so. The critical results of this paper do not depend on a Prisoner's dilemma structure; they require only that a better result can be achieved through trust or credible commitment. Thus, a stag hunt or other game structures are also possible. The Prisoner's Dilemma is used because of its wide exposure in the literature.\footnote{This payoff matrix does not distinguish between civil and interstate conflict, though in practice, the effects on the payoffs might have a different structure in the different cases.}

The countries' stage game actions are referred to as Trust and Distrust as represented in Table \ref{tab-1}, where Country 1 is the row player and Country 2 is the column player.

\begin{table}[hbt!]
\sffamily
    \centering
\caption{Stage game payoffs.}\label{tab-1}
\begin{tabular}{l|c|c}
        & Trust & Distrust \\ \hline
	 Trust& $T$, $T$& $-D$, $T+W$ \\ \hline
	Distrust & $T+W$, $-D$& $W-D$, $W-D$
\end{tabular}
\end{table}

Here, $T>0$ represents the benefit from a country's negotiating partner playing Trust. $D>0$ represents the damages incurred when a country's negotiating partner plays Distrust, while $W>0$ is the additional benefit a country receives when it plays Distrust. We refer to the stage-game Nash Equilibrium of (Distrust,Distrust) as No Cooperation. We refer to (Trust,Trust) as Cooperation. In line with the assumption that the countries play a Prisoner's Dilemma in the stage game, we assume $T>W-D$. Note that this ensures that the joint payoffs from Cooperation are the highest among all the stage-game action profiles.

Payoffs for a country are the sum of the stage game payoffs, discounted by $\delta_i$. For example, if both parties play Trust in every round, the payoff for player $i$ is $\sum_{t=1}^\infty \de_i^{t-1} T = \frac{T}{1-\de_i}.$

We use grim trigger punishments throughout. That is, (Distrust,Distrust) is played forever if any party plays Distrust in any round. Because we use grim trigger punishments, only four paths of play after the concessions stage are interesting:
\raggedbottom
\begin{enumerate}
    \item Both countries always play Trust; 
    \item Both always play Distrust; 
    \item Country 1 plays Distrust in Round 1 while Country 2 plays Trust, which is followed by both countries playing Distrust from Round 2 onward; and 
    \item Country 2 plays Distrust in Round 1 while Country 1 plays Trust, followed by both countries playing Distrust from Round 2 onward.
\end{enumerate}
\raggedbottom
Equilibrium payoffs beginning from Round 1 are now easily described by noting only the collective first-round behavior.\footnote{If a parameter of the model changes after Period 0, the equilibrium may be disrupted. Although it is beyond the scope of this paper, one could model this by adding a probability of equilibrium disruption followed by a new round of concessions that would essentially restart the game---albeit with altered parameters.} Let $X_{ij}$ represent the sum of discounted payoffs for Country $i$ where subscripts represent first-round strategies of that country. If both countries play T in Round 1, the corresponding payoff to Country $i$ is $ X_{TT}^i=\frac {T}{1- \delta_i}$. Likewise $X_{TF}^i=({-D}+\frac{\delta_i(W-D)}{1- \delta_i} )$, $ X_{FF}^i=\frac{W-D}{1- \delta_i}$, and  $X_{FT}^i=T+W +\frac{\delta_i(W-D)}{1- \delta_i}$. $X_{FT}^h$, for example, represents payoffs for the high type of Country 1 when Country 1 plays Distrust and Country 2 plays Trust in the first round. Note that the payoffs differ by type because types have different discount factors.

All parameters are common knowledge except $\delta_i$, which is Country $i$'s private information. We take achieving peace, or more broadly, achieving cooperation with the provision of public goods, as the normative goal with respect to advancing social welfare. Only high types are capable of making peace/providing public goods, and thus, we take the measure of social welfare to be the sum of the participating high types’ utilities.

\section{Analysis of Benchmark Cases}
\label{sec:bench}
When countries are uncertain about each other's motives, they can proceed in several ways, including giving concessions to signal their ability to Cooperate. We examine three types of equilibria.\footnote{If the discount factor is high enough, many types of equilibria exist. Consider, for instance, oscillating every other round between (Trust,Trust) and (Distrust,Distrust) with a grim trigger Distrust threat. In this paper, we are not interested in these equilibria because they are not as realistic for applications to conflict scenarios. These are also always payoff-dominated by at least one of the other equilibria discussed and, thus, are not attractive.} The Appendix provides a thorough analysis of each equilibrium as well as most proofs.

\subsection{Pooling equilibrium}
In the \emph{pooling equilibrium}, neither negotiating party gives concessions in Period 0; then both parties play Distrust in every round of the repeated game. Countries do nothing to bridge the credibility gap and thus do not cooperate. This \emph{pooling equilibrium} is likely to happen when countries are in long-set patterns of distrust. Active fighting is unnecessary; remaining outside of a state of peace/cooperation is all that is required. See the Appendix for a formal characterization of this type of equilibrium.

%Cyprus' civil war is a good example of the pooling equilibrium where neither side is taking actions to move things forward. While both sides posture that they want peace, and while there has been some lessening of tensions, very few concrete actions have been taken that move the sides toward settlement. This conflict is a stalemate.

Sri Lanka offers one example. Although the government has finally won the war of secession, it still refuses to address the grievances of minorities and leaves the conflict unresolved. Other prominent examples of this pooling equilibrium include Israel and its neighbors, Cyprus's civil war, North and South Korea, Greece and Turkey, and a multitude of other long-lasting conflicts. The mistrust is perhaps justified; indeed, if one party took the first step and gave a concession, the other party may take advantage. This is also possible outside the war context, for instance, when U.S. officials block Chinese firms' access to cutting-edge technology to prevent that technology from being used against U.S. interests.

Without a third party, little hope exists for overcoming mistrust. These long-lasting stalemates are the types of conflict which are most appropriate for mediator involvement. In the section on mediation, we present a mediation mechanism that illustrates how mediation can help achieve cooperation in this context. In some sense, these cases are the most interesting because the international community might play a positive role.

\subsection{No-Concessions Separating Equilibrium}
\label{sec:ncse}
The other two equilibria on which we focus are separating equilibria in which low and high types choose different strategies. If $\delta_i$ is high enough for both countries, the Cooperation outcome can be sustained with no concessions and a grim trigger punishment threat. We call this a \emph{no-concessions separating equilibrium}. In this equilibrium, no concessions are given by either type in Period 0. In Round 1, high types play Trust while low types play Distrust. So long as the countries are both high types as revealed by their Round 1 play, both countries play Trust in all following rounds. Otherwise, both countries play Distrust in all following rounds. 
\raggedbottom
\begin{proposition}
\emph{No Concessions Separating Equilibrium}\\
	Assume $\delta_h \geq \frac{W}{(1-p)W + p(T+D)}=\de^{nc}$. A subgame perfect Nash equilibrium exists in which low types give no concessions in Period 0 and always play Distrust and the high types give no concessions in Period 0 and play Trust unless the other country defects to Distrust.
	\label{proposition:1}
\end{proposition}
\vspace{-5pt}
\emph{Proof}: See Appendix.
\\
Here, as in each further iteration of the model, we define a high type as a country with a discount factor at or above the threshold for cooperation. That is, high types prefer to play the Cooperation equilibrium, i.e., $\delta_h \geq \delta^{nc}$. Any country with $\delta_l < \delta^{nc}$ is a low type for the purposes of the \emph{no concessions separating equilibrium}. This means that two high types---and only two high types---can sustain the Cooperation outcome.\footnote{Note that because we define high and low types relative to each type of equilibrium, a country with a given discount factor can be a high type in some equilibria and a low type in others.}

In this equilibrium, two mutually distrustful countries \emph{behave} as if they trust each other, taking a risk. This generally happens when the result of trusting and then being betrayed is not catastrophic or the odds of such a scenario are small. Here, countries have suspicions about each other but proceed anyway.

%Examples of a \emph{no-concessions separating equilibrium} are most likely to be those where countries have traditionally had good relations but something has recently come in the way. Certain relationships between the USA and countries alienated by WikiLeaks --- such as Italy --- would be an example. Italy essentially laughed off the criticisms and reassured the USA of its commitment to their relationship. Warsaw Pact countries generally allowed the USSR similar leeway; it was better to have occasionally imperfect cooperation than conflict. Some events can disrupt trust without completely derailing cooperation.

\subsection{Concessions Separating Equilibrium}
\label{sec:cse}
The other separating equilibrium of interest involves distrustful countries using concessions as a way of building trust. We call this the \emph{concessions separating equilibrium}. In this equilibrium, the cost of giving a concession can be worth the investment if the other country also cooperates. It is also not as risky as the \emph{no-concession separating equilibrium}. In this equilibrium, concessions are given before more substantive actions, thus removing the possibility of playing one of the cheating corners of the Prisoner's Dilemma. Concessions are a costly signal that the other country is serious about cooperating and can be used to avoid continual distrust. High types use concessions to identify themselves as trustworthy partners in hopes of establishing cooperation.

In the \emph{concessions separating equilibrium}, low types do not give concessions because the concession level is set as the smallest amount that deters the impatient type from mimicking the patient type. In contrast, high types always give a concession in Period 0. Thus, the patience level of both countries is fully revealed in equilibrium. If both countries receive concessions, they know the other is a high type, and both play Trust in subsequent rounds. Otherwise, if even one player does not receive a concession, there is at least one low type, so both countries play Distrust in subsequent rounds. The signaling value of concessions in Period 0 means that starting from Round 1 in the Trust/Distrust game, both countries play the same strategy in a separating equilibrium. That is, both play Trust if there are two high signals, and otherwise, both play Distrust.

Details of the analysis are in the Appendix. We begin by characterizing the concession (or \emph{gift}) giving behavior of the low type. We then present the patience threshold and gift-giving behavior of the high type.

\begin{lemma}
	In a separating equilibrium, low types do not give a concession. Cheap talk does not allow for a \emph{concessions separating equilibrium}.
	\label{lemma:3}
\end{lemma}
\emph{Proof:} See Appendix.

Low types don't give gifts in this separating equilibrium because giving the gift would serve no purpose for the low type: the low type will be identified through the separating behavior of the high types, thus have nothing to gain.\footnote{The transmission of information about each country's type is, by definition, essential for the existence of a \emph{concessions separating equilibrium}. Thus, a \emph{concessions semi-separating equilibrium} cannot exists where the low type gives a concession with strictly positive probability; the concessions would not transmit the information required to build trust. If no information is transmitted, the high type has no incentive to give a concession. Therefore, a semi-separating equilibrium with the low type mixing between strictly positive and zero concessions and the players separating in the repeated game as in the \emph{no-concessions separating equilibrium} cannot exist.}

\begin{proposition}
\emph{Concessions Separating Equilibrium (CSE)}
	\begin{enumerate}
		\item[(a)] Assume $\delta_h \geq \frac{W}{T+D} = \de^{c}$. Then a subgame perfect Nash equilibrium exists in which low types give no concessions in Period 0 and always play Distrust and the high types give a concession in Period 0 and play Trust unless the other country defects to Distrust.
		\item[(b)] In the best \emph{concessions separating equilibrium}, high types give a concession of $p(T + D)$, which is the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower expected payoffs.
\end{enumerate}
	\label{proposition:2}
\end{proposition}
\emph{Proof:} See Appendix.

This  \emph{concessions separating equilibrium}, where \emph{best} is from the standpoint of high-type welfare, is justified by appeal to the Intuitive Criterion equilibrium refinement in which out-of-equilibrium beliefs put zero weight on types that can never gain from deviating.

Interestingly, the patience threshold for this equilibrium to exist, $\de^c = \frac{W}{T+D}$, is the same as the threshold for the complete information repeated game in which deviating from Trust is discouraged through grim trigger punishments.\footnote{When $\de = \frac{W}{T+D}$, there is also a semi-separating equilibrium where only some high types give a concession. Here, high types give a smaller expected concession and trade off a lower probability of achieving cooperation. We focus on the \emph{concessions separating equilibrium} in the analysis below because it provides the best chance for Cooperation and is possible over a much larger portion of the parameter space.} Using concessions to separate the types, therefore, can be seen as making up for the imperfect information in this setting.

We complete our analysis of the \emph{concessions separating equilibrium} by comparing it to the \emph{no-concessions separating equilibrium}.

\begin{corollary}
	The \emph{no-concessions separating equilibrium} requires countries to be more patient than the \emph{concessions separating equilibrium}. If both equilibria exist, the \emph{no-concessions separating equilibrium} is preferred.
	\label{corollary:1}
\end{corollary}
\emph{Proof}: See Appendix.

A large probability of a high type makes the \emph{no-concessions separating equilibrium} very attractive because the risk of ending up in the cheating corner of the Prisoner's Dilemma is low, and no concessions have to be made. If countries are patient enough to separate with no concessions, $p$ is also high enough so that the countries prefer the \emph{no-concessions separating equilibrium}.

Concessions separating equilibria are a way for countries to solve their disputes when the \emph{no concessions separating equilibrium} is unavailable. By giving costly concessions, they signal their intentions in a way that a partner unwilling to cooperate would not be willing to signal.

One example of an equilibrium involving concessions is Israel and Egypt at the Camp David Accords. Both parties gave concessions (Israel a material land concession and Egypt diplomatic recognition of Israel) that signaled their willingness to end the stalemate that had characterized the previous five years. Of course, this result depended on Carter's use of mediation techniques, including use of manipulative mediation---a concept we explore in the section on mediation below.

\section{Material Value of Concession and Inefficiency} 
\label{sec:IC}

In the previous two sections, we assume that the gift only benefits the party who receives it in the period in which it is received, that is, Period 0. In this section, we assume that the gift has an additional value in each round of the repeated game, that is, Round 1 and onward. That is, the country that receives the concessions can use them to build up its military or to build up its civil society, including through the provision of public goods. The recipient using concessions to build military strength hurts the giver of the concessions in war; the recipient using the concessions to strengthen civil society helps the giver in peace. The Golan Heights is an example: if Syria maintains peaceful relations with Israel, it is reasonable to concede, but if Syria renews military conflict with Israel, surrender of the strategic land would be disastrous for Israel.

To incorporate future material value, we add two elements to the benchmark model. The first is an additional decision for the negotiating parties. In Period 0, each country decides how to allocate the value of any concession it receives between military and civil society. $\alpha_i$ is the portion of the received concession that Country $i$ chooses to dedicate to civil society; $(1- \alpha_i$) is the portion Country $i$ dedicates to military buildup. This decision is a simple optimization problem for each country. Parameters are common knowledge, so the result of this decision is well known for each type.

The value of the concessions for the military or civil society is incorporated into payoff functions starting in Round 1. All rounds of the repeated game are as before but with the modified stage game payoffs shown in Table \ref{tab-2}.

\begin{table}[hbt!]
    \centering
    \caption{Stage game payoffs when concessions have material value.}
    \begin{tabular}{l|c|c}\label{tab-2}
      & Trust & Distrust \\ \hline
	 Trust& \small$T+T\alpha_2 g_1$, & \small$-[D+D(1-\alpha_2) g_1],$ \\
  & \small$T+T\alpha_1 g_2$ & \small$[T+T\alpha_1 g_2] + [W+W(1-\alpha_2) g_1] $\\ \hline
	Distrust & \small$[T+T\alpha_2 g_1]+[W+W(1-\alpha_1) g_2],$& \small$[W+W(1-\alpha_1) g_2]-[D+D(1-\alpha_2) g_1],$\\ 
	 & \small$-[D+D(1-\alpha_1) g_2] $ & \small$[W+W(1-\alpha_2) g_1]-[D+D(1-\alpha_1) g_2]$
    \end{tabular}
\end{table}

This modification to the payoffs is the second change relative to the baseline model. We add a term to each of $T$, $W$, and $D$ that represents the additional benefit or harm flowing from the future material value of the concession. When both countries play Trust, they each receive the base benefit $T$ as well as an additional benefit of the concession they \textit{gave} that is scaled by the proportion the recipient invested in civil society.

If both countries play Distrust, Country 1 receives not only the immediate value of the concession but also $W-D$ in each round. Its welfare now has two additional terms. First, an additional benefit term in each round of the repeated game $W(1-\alpha_1) g_2$ accounts for the value of the received concession as well as how much Country 1 invested in the military. Second, Country 1 incurs extra damages $D(1-\alpha_2) g_1$ in each round of the repeated game that account for the size of the concession it \textit{gave} and how much of that concession was invested in the military by Country 2. The other payoffs are modified analogously.\footnote{The results are qualitatively unchanged if the gifts are not scaled by the variables that represent the impacts of cooperation and non-cooperation, if they are scaled linearly by these variables but with a proportion other than 1, or if they are scaled by many plausible non-linear functions of $T$, $W$ and $D$. The results are simpler without scaling. However, we believe it is more realistic to assume that the future benefits and costs of the gifts are proportional to the direct benefits and costs of cooperation/non-cooperation. For instance, a county that could impose more damage without the future value of the concessions is likely able to leverage a concession better than a country that can impose less damage.}

High types maximize welfare by choosing $\alpha=1$ because $\al_i$ enters into the payoffs in a linear fashion and a concession would only come from another high type in equilibrium. Thus, only the Cooperation outcome is played. Conversely, in equilibrium, low types only participate in the No Cooperation equilibrium and thus maximize their payoffs by choosing $\alpha=0$.

We turn next to characterizing a \emph{concessions separating equilibrium} in this environment with future material value.

\begin{proposition}
\emph{Concessions Separating Equilibrium (CSE) with Material Value}
	\begin{enumerate}
		\item[(a)] Assume $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D$ is positive and $\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^{1}$. Then a subgame perfect Nash equilibrium exists in which low types give no concessions in Period 0 and always play Distrust and the high types give a concession in Period 0 and play Trust unless the other country defects to Distrust.
		\item[(b)] In the best \emph{concessions separating equilibrium} when gifts have full material value, high types give a concession of $\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, which is the smallest concession necessary to separate. Equilibria with higher concessions yield strictly lower payoffs to high types.
\end{enumerate}
	\label{proposition:csemv}
\end{proposition}
\vspace{-5pt}
\emph{Proof:} See Appendix.

The problem with concessions with material value is the potential for the low type to invest the concessions in the military. This makes a high type less willing to take a chance of being matched with another high type because the costs of being matched with a low type are higher. Corollary~\ref{corollary:matval} shows that future material value can destroy the ability of concessions to achieve cooperation.

\begin{corollary}
	Assume that high types are patient enough to separate using concessions when gifts have no material value. If countries use concessions with future material value instead of concessions with no future material value, there are parameters under which the future material value of gifts destroys countries' ability to separate through concessions, i.e., Cooperation cannot be achieved when both countries are high types.
	\label{corollary:matval}
\end{corollary}

\emph{Proof}: An example suffices as proof. Let $T = 1$, $W=1$ and $D = 1$. The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate when concessions do not have future material value is $\de^c = \frac{1}{1+1} = 0.5$. Let $\de_h = 0.7$ and $\de_l = 0.3$ and $p = 0.9$.

By Proposition~\ref{proposition:2}, the \emph{concessions separating equilibrium} is possible when gifts have no material value.

The patience threshold to separate through concessions with future material value is much higher under these parameters when the concessions carry future material value: by Proposition~\ref{proposition:csemv}(a), this threshold is $0.979$. Thus, the \emph{concessions separating equilibrium with efficient gifts} is \emph{not} possible.

$\de_h$ is not involved in any of these calculations, so we can see that for any $\de_h \in [.5,.979)$, separating through concessions is possible when concessions have no material value but is not possible when they do have future material value. That is, future material value can destroy the opportunity for cooperation. \hfill $\blacksquare$

The comparative statics for the patience threshold $\de^c = \frac{W}{T+D}$ are straightforward for the \emph{concessions separating equilibrium} when concessions have no material value. The threshold increases and cooperation becomes less likely when $W$ increases; the threshold decreases when either $T$ or $D$ increase.

These relationships hold with a small caveat for the \emph{concession separating equilibrium with efficient gifts}, where the patience threshold becomes $\de^{1} = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D + T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$.\footnote{The caveat: if both $T$ and $W$ become sufficiently large, the patience threshold increases in $D$.} The patience threshold increases in $W$ because it makes the benefit from playing Distrust larger. The patience threshold decreases in $T$ and $D$ but for different reasons. $T$ is straightforward: a larger $T$ is a larger benefit from playing Trust. In contrast, a larger $D$ is a higher cost of the negotiating partner playing Distrust. The presence of future material value does not fundamentally change these relationships because the future material value is proportional to the fundamental values of $W$, $T$, and $D$.

However, two variables do not affect the patience threshold in the no material value case that \textit{do} affect the threshold when gifts have future material value: $\de_l$ and $p$. When the low type's patience level $\de_l$ increases, the patience threshold for cooperation increases because the gift size has to increase to deter a low type from mimicking the high type. In the case of no material value, the low type's discount factor doesn't enter into the gift, and therefore, it doesn't influence how much patience is required for cooperation.

The other variable that influences the patience threshold in the case of future value is $p$, the proportion of cooperative types in the population. Although the gift in the no-future-material-value case \emph{is} an increasing function of $p$, it is a linear function of $p$ just like the variables $T$, $W$, and $D$. Thus, the cost of paying the gift and the direct benefits in the repeated game increase at the same rate so that the likelihood of cooperation does not vary in $p$ when gifts have no future material value. In the future-material-value case, the size of the gift required to separate the low types from the high types increases more than linearly in $p$ and thus faster than the other terms. Therefore, the patience threshold in the future-material-value case increases as $p$ increases. That is, the cost of giving the gift weighs more heavily in the decision to cooperate relative to the material costs and benefits, requiring states to be more patient to separate and thus reducing the likelihood of cooperative types.\footnote{See the appendix for the comparative statics calculations.}

We now relax the assumption that the benefit of a concession is equal to its cost. Instead, allow countries to destroy some of the value of the concession they give. For instance, when decommissioning weapons, rebels leave no material value of the weapons intact to benefit the recipient, while still signaling good intentions. Here, we allow the giving of efficient concessions along with new options to give a variety of less efficient concessions.

We implement this assumption by allowing countries to choose a scalar $e \in[0,1]$ by which to multiply their given concession $g$. $C(g)= g$ as before, but although the receiving country incurs the full cost of the concession $g$, the future benefit to the recipient is now only $eg$.

\begin{table}[hbt!]
    \centering
    \caption{Stage game payoffs when concessions have material value that can be destroyed.}
\begin{tabular}{l|c|c}\label{tab-3}
       & Trust & Distrust \\ 
	 Trust& \small$T+T\alpha_2 e g_1$, & \small$-[D+D(1-\alpha_2) eg_1],$ \\
  & \small$T+T\alpha_1 eg_2$ & \small$[T+T\alpha_1 eg_2] + [W+W(1-\alpha_2) eg_1] $\\  \hline
	Distrust & \small$[T+T\alpha_2 eg_1]+[W+W(1-\alpha_1) eg_2],$& \small$[W+W(1-\alpha_1) eg_2]-[D+D(1-\alpha_2) eg_1],$ \\
	 & \small$-[D+D(1-\alpha_1) eg_2] $ & \small$[W+W(1-\alpha_2) eg_1]-[D+D(1-\alpha_1) eg_2]$
  \end{tabular}
\end{table}

We have already established the results for the \emph{concessions separating equilibrium} when all material value is destroyed, i.e., $e=0$. Notice that if $e=0$, the payoffs in Table \ref{tab-3} are the same as those in Table \ref{tab-1}, and thus, the results that use the payoffs in Table \ref{tab-1} apply. We have also established the results for the \emph{concessions separating equilibrium} when no material value is destroyed, i.e., $e=1$, earlier in this section.

Before turning to the question of how the possibility of destroying the value of concessions impacts the ability of the parties to cooperate, we formally establish the welfare implications.

\begin{lemma}
	If the \emph{concessions separating equilibrium with efficient concessions} exists, it is preferred to the \emph{concessions separating equilibrium with inefficient gifts} when both the probability of encountering a high type and the benefit from Cooperation are sufficiently large.
	\label{lemma:efficiency}
\end{lemma}
\emph{Proof:} See Appendix.

The intuition for Lemma~\ref{lemma:efficiency} is that the future material value of concessions helps you when your negotiating partner turns out to be a high type, and this happens with probability $p$. On the other hand, the material value of your concession \emph{hurts} you when your negotiating partner turns out to be a low type. Similarly, the larger the benefits from Trust, the larger the welfare gain when the negotiating partner is a high type, and the larger the damages from Distrust, the more significant the welfare loss when the negotiating partner turns out to be a low type.

Lemma~\ref{lemma:efficiency} implies that the high types prefer either $e=1$ or $e=0$. As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium with $0<e<1$} exists and improves upon high type welfare when high types are patient enough to separate if $e=0$ but not if $e=1$.} %This is not at all obvious because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}

\begin{lemma}
	The \emph{concessions separating equilibrium with efficient concessions} requires countries to be more patient than the \emph{concessions separating equilibrium with inefficient concessions}. 
	\label{lemma:e-patient}
\end{lemma}
\emph{Proof}: See Appendix.

Lemma~\ref{lemma:e-patient} implies there are parameters under which Cooperation cannot be achieved in a \emph{concessions separating equilibrium with efficient gifts} but Cooperation can be achieved in a \emph{concessions separating equilibrium with inefficient gifts}. This is part of the substance of Proposition~\ref{proposition:4}.

\begin{proposition}
		Assume the high types are not patient enough to separate without concessions and that concessions have material value that can be destroyed. There are parameters under which the optimal equilibrium is a separating equilibrium in which concessions are inefficient.
	\label{proposition:4}
\end{proposition}
\emph{Proof}: We invoke Lemmas~\ref{lemma:efficiency} and \ref{lemma:e-patient} as two different reasons for which the parties would choose the \emph{concessions separating equilibrium with inefficient gifts}. First, they may be patient enough to separate when gifts are inefficient but not when gifts are efficient (Lemma~\ref{lemma:e-patient}). In this case, the \emph{concessions separating equilibrium with efficient gifts} is not available to them.

However, even if the negotiating parties are patient enough to separate when gifts are efficient, Lemma~\ref{lemma:efficiency} tells us that welfare is higher with efficient gifts only when the probability of encountering a high type and the benefit from Cooperation are sufficiently large. Otherwise, welfare is higher under the \emph{concessions separating equilibrium with inefficient gifts}, and this equilibrium is thus optimal. \hfill $\blacksquare$\\
\vspace{-5pt}

Inefficient concessions are optimal in two situations: when the chance of facing a low type who will use the concession against you (i.e., $p$ is small) is high, and when the benefits from Cooperation are small relative to the damages from No Cooperation. This finding of inefficiency is for profoundly different reasons than the literature related to \cite{camerer1988} or \cite{prendergast2001}.\footnote{Because our initial setup is essentially identical to Camerer's, the inefficiency of pre-play communication would also manifest in our model if a stage of pre-play communication were added. With a slight behavioral modification, we also get something akin to \cite{prendergast2001}: if a high-type country suffers regret after efficiently giving to a low type, there is a premium for guessing correctly.} Instead of being in reaction to a behavioral regret for mismatching or serving as a way to discourage low types from entering the game altogether, here, the conceding party makes concessions inefficient to prevent low types from using those concessions against itself in the future.

\section{Mediation}
\label{sec:med}
The results in this paper up to this point have relied on bilateral engagement. We now consider the involvement of a mediator when concessions have future material value. We model the mediator as someone who solves a mechanism design problem to create a plan for concessions that elicits truthful revelation of the parties' abilities to commit to cooperation.

Because many conflicts occur in an international arena with no clear enforceable rule of law \citep{waltz2018man}, much of the literature focuses on self-enforcing mechanisms. If, however, a credible third party exists, results beyond self-enforcing agreements can be relevant. A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions'' \citep{bercovitch1996resolving}. We now introduce a mediator who does the latter.\footnote{Here, the parties' actions in the stage game, as well as their choices of whether to spend concessions on the civil versus the military sector, are assumed to derive from their type, so the mediator does not need to enforce these decisions once the type is revealed. Thus, it is not necessary to assume that the mediator can do both.}

The model setup is as before, but instead of parties being free to choose their concession levels, the mediator solicits type reports and then enforces incentive-compatible concessions. This mediator is modeled by a mechanism $M$.

After learning its type, each country chooses to participate in the mechanism or not. By the Revelation Principle (Myerson 1979), it is without loss of generality to restrict attention to direct mechanisms\footnote{Direct mechanisms are those in which countries simply declare their types.} and to focus on equilibria in which both countries participate and send truthful reports. Participation in the mechanism, therefore, involves sending a message that declares one's type to be High or Low and then being bound to send the mandated concessions. Formally, the mechanism $M$ inputs the reports $t_i \in \left\{High,Low\right\}$ for $i \in \left\{1,2\right\}$ and outputs the required concessions $g_i$ and efficiency levels $e_i$ so that $ M:(t_1,t_2)\rightarrow( e_1, g_1; e_2,g_2)$.

Under the assumptions of the previous sections, the same concession must be sent to both types because types are private information. Importantly, here, the mechanism $M$ can be differentiated by recipient type. Otherwise, the setup is the same as in the bilateral case where concessions have future material value that can optionally be destroyed. In the mechanism design context, we focus on the incentive compatibility constraints that must be satisfied for each type to reveal its type truthfully.

We find that some value of the concessions must be destroyed to prevent the low type from being tempted to misrepresent its type in order to receive the gift. That is, $e<1$, implying that the gifts mandated by the mediator must be inefficient.

\begin{lemma}
	A manipulative mediator cannot facilitate the most efficient concessions, i.e., $e=1$ is not incentive compatible under mechanism $M$. 
	\label{lemma:med}
\end{lemma}
\emph{Proof}: See Appendix.

Proposition~\ref{proposition:med} gives the range of efficiency that allows a mediator to make mechanism $M$ incentive compatible and individually rational for both types.

\begin{proposition}
\emph{Mediation}
\begin{enumerate}
		\item[(a)] A mediator using mechanism $M$ must ensure that $M$ is incentive-compatible and individually rational for the low type. This happens when the specified concession is greater than or equal to $\frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)},$ with the denominator of this expression strictly positive.
		\item[(b)] A mediator using mechanism $M$ must ensure that $M$ is incentive-compatible and individually rational for the high type. This happens when either $Te < (1-\de_h)(1-e)$ or the specified concession is less than or equal to $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}$.
\end{enumerate}
	\label{proposition:med}
\end{proposition}
\emph{Proof:} See Appendix.

In part (a), we see that the low-type incentive compatibility constraint determines a lower bound on the size of the concession specified by the mechanism. This puts an upper bound on how efficient concessions can be. In part (b), we see that, in some cases, the high-type incentive constraint also provides an upper bound on the concession size.

Ultimately, mediation is desirable if it can improve welfare or improve the chances for cooperation. Proposition~\ref{proposition:medwel} shows that a mediator who implements mechanism $M$ can do both.

\begin{proposition}
	When concessions have future material value, a mediator can use mechanism $M$ to
	\begin{enumerate}
		\item[(a)] improve welfare by increasing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is not possible; or
		\item[(b)] improve welfare despite reducing the efficiency of concessions when a \emph{concessions separating equilibrium with efficient gifts} is possible; or
		\item[(c)] achieve cooperation when it cannot be achieved either in a \emph{concessions separating equilibrium with efficient gifts} or a \emph{concessions separating equilibrium with inefficient gifts}.
	\end{enumerate}
	\label{proposition:medwel}
\end{proposition}
\emph{Proof:} See Appendix.

To understand part (a), remember that concessions are not exchanged in the mechanism if even one of the reports is Low. Because a concession is only given to the high types and high types invest in civil society and public goods, the efficiency of the concession can be increased without creating extra damages when matched with a low type; this is of course subject to satisfying the low type's constraints. High-type welfare is improved because no transfer is made to the low types, and no threat of future damage from the concessions exists because they only go to a high type.

Here, inefficiency can be mitigated because the mediator is able to mandate concessions only between declared high types. The inefficiency is no longer needed to prevent low types from using concessions against high types. However, some inefficiency is required to incentivize low types to reveal their type truthfully.

Part (b) may be somewhat surprising. Here, a mediator would insert inefficiency when it is not necessary to achieve a cooperative outcome. This happens when the possibility of the low type using concessions against their negotiating partner and the magnitude of the damages that can be imposed are small enough that efficient gifts are possible but large enough that the full efficiency of the gifts has a large, negative impact on welfare. The mediator removes the possibility of future damages but requires some inefficiency to incentivize low types to reveal truthfully.

Part (c) is relevant when the impacts of future material value are too strong, i.e., when the probability of a low type is too high and/or the damages from investing in military power are too large. In this case, the parties cannot cooperate on their own, even with the possibility of signaling their type through concessions. By ensuring that only high types exchange gifts, the mediator removes the threat of damaging behavior by one's negotiating partner as well as the cost of giving the concession to a low type. Here, the mediator's help allows types with lower patience levels to separate when those same types cannot separate in the bilateral game with concessions with future material value.

Thus, a mediator is able to both improve welfare and bring willing parties to the table to give the concessions necessary to achieve the cooperative outcome. The improvements by the mediator here do not rely on the mediator's private information as in the models of \cite{kydd2003}, Rauchhaus (2006), and Smith and Stam (2003). Therefore, the mediator's preferences are not an important factor in her participation. So long as the costs are small enough to be worth participating, the mediator can effectively enter and assist in solving the conflict.

One might worry about the requirement that the mediator be willing and able to ensure that the specified concessions are delivered. Although it is not guaranteed that a mediator who can play this role exists for every conflict, it is not difficult to believe that such a mediator exists for many conflicts. We do not require a formal international enforcement mechanism but rather that the mediator has, and is willing to use, sufficient leverage to punish a deviating party. Examples of such punishments are financial or trade sanctions or the withdrawal of aid or military support. Furthermore, the mechanism can work if the mediator is either (1) only able to incentivize some portion of the concessions or (2) enforces the concessions with some probability less than 1. This would tighten the low type's incentive constraint and loosen the high type's incentive constraint, creating a different level of optimal efficiency of the concessions.\footnote{To see this, in the incentive constraints in the proof of Proposition~\ref{proposition:med}, replace $g_h$ with $q \cdot g_h$, where $q$ represents the proportion of the concession that can be enforced or the probability with which the full concession is enforced.}

The value of truth telling by the mediator has been examined in the literature. \cite{kydd2003} studies bias in mediation and how a mediator can credibly communicate information to the parties. Conversely, \cite{horner2010} rely on the mediator to hoard information in order to improve on unmediated interaction.\footnote{\cite{horner2010} take cheap talk communication as their benchmark of unmediated communication, whereas we take the unmediated signaling game as our benchmark.} In our model, a successful mediator relies on the parties trusting her. However, here, the mediator has no incentive to lie: lying can only potentially hurt the high types, the only type the mediator can help.

\section{Conclusion}
In situations of perpetual conflict, the empirical literature has show that concessions can ease distrust. This paper introduces a mechanism by which this might work. In our model's setup, three classes of equilibria are interesting. First, if prior trust is low, a no-concessions pooling equilibrium exists, which leaves all types in a state of non-cooperation. Second, if prior trust is sufficiently high, a no-concessions pooling equilibrium exists where high types trust in the first round and can maintain that trust if both are high types. Third, a concessions-giving separating equilibrium exists where high types offer concessions to eliminate distrust. This is the most interesting class of equilibria for our purposes.

Although parties generally are better off when concessions are efficient, we have shown that inefficiency may be useful. In particular, if concessions may be used to harm the giver materially, it may be better to give inefficient concessions. This explanation captures the hesitancy of nations to fully engage with a peace process or other cooperation when they distrust each other.

At first glance, it may seem somewhat abstract to model a concession as a number. However, the magnitude of concessions can indeed vary: often, concessions do come in sizes, for example, the number of prisoners released, the amount of land ceded, or the amount of time given to carry out actions. But although magnitudes often do vary, this points to a very real caveat. The nature of the concessions is sometimes non-negotiable. For instance, if one country demands the release of hostages, it is not possible----or at least not realistic----for the other country to give the equivalent value in land, cash, or weapons.

This points out that when we think about concessions, we should think about their nature as being fixed. With this in mind, we can then accurately consider whether concessions are of sufficient size. These observations do not undermine the model. The nature of the desired concessions helps determine whether inefficient concessions can help achieve cooperation when efficient concessions cannot and thus also when a mediator can improve the efficiency of concessions.

The effectiveness of mediation is debated in the literature; this paper shows that a trusted third-party mediator can remedy a particular kind of inefficiency. One contribution of this paper is to show a new mechanism through which a mediator can help.

This model focuses on manipulative mediation, which is indeed used in resolving conflicts and achieving cooperation. However, the usefulness of mediation in this case relies on the mediator being both trustworthy and able to enforce concessions. Such an all-powerful mediator is a strong assumption, and although useful as a benchmark, it is unlikely to exist in all scenarios. It would be useful as a further exercise to examine the effectiveness of mediators with different strengths of enforcement capabilities.

Although it is important theoretically to show how a mediator can help in conflict situations, mediation is not free, at least to the providing (third) party. Therefore, mediation should not be undertaken if the cost of providing the mediation is higher than the benefits of increased cooperation and/or efficiency of concessions. If the model accurately captures the costs, the expected savings of mediation can be calculated, and therefore, the value of mediation in a specific scenario can be determined. This would allow the mediator to analyze whether her involvement is worthwhile.

This paper shows that inefficient concessions may be used to achieve peace or cooperation to provide other public goods when efficient concessions are insufficient; it also demonstrates how a mediator can achieve cooperation in these situations when the parties to the conflict cannot do so on their own. Opportunities for further research include looking at the roles of different types of mediation. Because of the many humanitarian, security, and diplomatic implications of this work, both deeper and broader analysis is required.

\section{Appendix}

\subsection{Pooling equilibrium}
\begin{lemma}
	From Round 1 on, playing (Distrust,Distrust) in all rounds is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
	\label{lemma:1}
\end{lemma}
\emph{Proof}: As $D>0$ and $W>0$, the dominant stage game action for all types is to play Distrust. Thus, the stage game equilibrium is (Distrust,Distrust), and in any repeated game, playing the stage game equilibrium in each round is an equilibrium of the entire game. \hfill $\blacksquare$\\

That is, one high-type equilibrium strategy is to pool with the low types by always playing Distrust. If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays Distrust, then either type of player $i$ is made strictly better off by playing Distrust in each round given player $j$'s behavior. Given that the stage-game equilibrium will be (Distrust,Distrust), players have no incentive to give a concession in Period 0 because concessions are costly, and signaling one's type can give no benefit in this equilibrium. Types pool by never giving concessions and always playing Distrust.

\subsection{No-Concessions Separating Equilibrium}

 We examine the conditions for a separating equilibrium held in place by a grim trigger.

 \noindent{\emph{Proof of Proposition \ref{proposition:1}}:\\
Playing Trust in the first round and thereafter, as long as Trust has always been played, is incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first round and then every round thereafter by the one-shot deviation principle. If both countries play Trust in a round, a Cooperation equilibrium takes place, and both countries continue to play Trust in every round with the grim trigger threat of Distrust. Low types play Distrust in the first round, so a high type that observed Distrust being played would respond by playing Distrust in Round 2 and all future rounds. A country plays Trust if and only if the following condition is satisfied:
\begin{equation*}
  p\left(\frac{T}{1- \delta}\right) +(1-p)\left({-D}+\frac{\delta(W-D)}{1- \delta} \right)\geq p \left(T + W + \frac{\de}{1-\de}(W-D)\right) +(1-p)\frac{W-D}{1- \delta}.
\end{equation*}
Simplifying, we have
%\be
%  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
%\ee
\begin{equation*}
  pT \geq p \left((1-\de)(T + W) + \de (W-D)\right) + (1-\de)(1-p)W
\end{equation*}
\begin{equation*}
  pT \geq pT -p\de T +pW -p\de W + p \de W -p \de D  + W -\de W -pW + p\de W
\end{equation*}
\begin{equation*}
  p\de T +p \de D + \de W - p\de W  \geq W 
\end{equation*}
\be
	\delta \geq \frac{W}{(1-p)W + p(T+D)} = \de^{nc}.
	\label{eq:ncse}
\ee

If the potential advantages of Cooperation are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust. Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each round even if the other country plays Trust. Thus, we call these countries low types for purposes of this equilibrium. \hfill $\blacksquare$

\subsection{Concessions Separating Equilibrium}

If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved in the absence of concessions in Period 0.\footnote{Countries need to deliver concessions in Period 0, not just promise them.} If, instead, two negotiating parties have sufficient incentive to give a concession in Period 0 that indicates they are capable of cooperation, these high types could safely play Trust in Round 1, allowing two high types to avoid the trap of the No Cooperation outcome that would occur under pooling.

Below are the details of the \emph{concessions separating equilibrium} analysis. We denote the equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type. These equilibrium gifts mean that when Round 1 is reached, countries know which type the other country is and play accordingly. The concessions phase acts as a coordination device to match countries' actions. For two countries of the same type to play different actions is an off-equilibrium contingency. These off-equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession. 
\\
\\
\emph{Proof of Lemma~\ref{lemma:3}:}\\
In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on \emph{concessions separating equilibria} in which countries reveal their types truthfully. This allows high types to only play Trust in Round 1 with other high types and to play Distrust with low types. Low types play Distrust (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.

Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it gives them some advantage. Here, high types only cooperate with other high types, so giving a concession cannot help low types to achieve a higher payoff in the repeated game. Because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is, therefore, 0.

High types have the incentive to play Trust only in the Cooperation equilibrium, which can only be sustained by a pair of high types. Both types benefit from the other country playing Trust, so all countries have an incentive to signal that they are high types if concessions are costless (cheap talk). Thus, costless announcements cannot lead to truthful revelation. If concessions are to lead to a separating equilibrium, they must be costly. \hfill $\blacksquare$
\\
\\
\emph{Proof of Proposition \ref{proposition:2}:}\\
In the separating equilibrium constructed here, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift. In this case, the binding incentive compatibility constraint is the low type IC constraint. When we set $g_l=0$ following Lemma~\ref{lemma:3}, the low-type IC constraint is\\  
\begin{equation*}
	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
\end{equation*}
This expression represents the low types' incentives for truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift. Simplifying this inequality, we see that the high types need to give a gift 
\be
	g_h \geq p(X_{FT}^l-X_{FF}^l)
	\label{eq:cse}
\ee 
in order to separate from the low type.

High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$. Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible while still achieving separation. This occurs when Expression~\ref{eq:cse} holds with equality. Substituting in from the definitions of $X_{FT}^l$ and $X_{FF}^l$ yields the minimum separating gift\footnote {Although not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made. Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils. Thus, a more powerful country would be more able to plunder and hence has to make a greater concession to convincingly convey that it is a high type.}
\be
	g_h^*=p(T+D).
	\label{eq:cse2}
\ee 
 To get the high types to send nonzero concessions, the high type incentive compatibility constraint must be satisfied. That is, the payoff from separating must be higher than the payoff from pooling with the low types: 
$$pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h.$$
In terms of fundamentals, we have
\be
	p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}.
	\label{eq:cse3}
\ee
Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a \emph{concessions separating equilibrium} to exist:
\be
\delta_h \geq \frac{W}{T+D} = \de^c.
\ee
That is, we need the high types to have a sufficiently large discount factor. \hfill $\blacksquare$\\
\\
\emph{Proof of Corollary~\ref{corollary:1}:}\\
To show that the patience threshold for the \emph{no-concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$

We multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
$$(T+D) > (1-p)W +p(T+D).$$
Because $0<p<1$ and $W$, $T$, and $D$ are all positive, both sides of the inequality are positive. Thus, we have
$$\de^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de^{c}.$$

In the case that both types of equilibria exist, i.e., $\de_h \geq \de^{nc}$, the high types prefer the \emph{no-concessions separating equilibrium} if and only if
\begin{equation*}
p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right) \geq p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h.
\end{equation*}
This simplifies to preferring the \emph{concessions separating equilibrium} if and only if
$$0 \geq (1-\de_h)W-p(1-\de_h)(T+D).$$
Rearranging, we have
\be
 p \geq \frac{W}{T+D}.
\ee
That is, the high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$

\subsection{Concessions with Material Value}
\label{ap:mat_val}
\emph{Proof of Proposition \ref{proposition:csemv}:}\\
In the separating equilibrium constructed in Proposition~\ref{proposition:csemv}, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift. In this case, the binding incentive compatibility constraint is the low type IC constraint. Taking account of the result of  Lemma~\ref{lemma:3} that $g_l=0$, we have
\begin{equation}
	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
	\label{eq:matval1}
\end{equation}
On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$). Then (Distrust,Distrust) is played, and the payoffs depend on whether this low type faces a high or a low type because the implications for future material value are different. With probability $p$, the low type receives a gift and invests in the military. With probability $(1-p)$, neither side gives concessions. The left side of Expression~\ref{eq:matval1} is then $pg_h + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right]$.

On the right side, the low type gives and receives a gift from the high type with probability $p$. With probability $p$, this low type faces a high type who invests the gift in civil society. With probability $(1-p)$, the low type's gift goes to another low type who invests in the military, and the low type does not receive a gift. So the right hand side of Expression~\ref{eq:matval1} becomes $-g_h + pg_h + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)$.

Substituting into Expression~\ref{eq:matval1} and simplifying, we have
%\begin{multline*}
%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right] \geq \\
%-g_1 + pg_1 + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)
%\end{multline*}
\begin{equation*}
	g_h + p(W+Wg_h-D) \geq p\left(T + Tg_h +W + Wg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
\end{equation*}
%\begin{equation*}
%	g_h - pD \geq p\left(T + Tg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
%\end{equation*}
\begin{equation*}
	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h\geq \left(1-\de_l\right)p\left(D +	 T\right).
\end{equation*}
We have assumed that $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D > 0$ so we can divide to get
%\begin{equation*}
%	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h \geq \left(1-\de_l\right)p\left(D +	 T\right)
%\end{equation*}
\begin{equation}
	g_h \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g^1
	\label{eq:matval2}
\end{equation}

This implies that the high types need to give a gift at least as large as $g^1$ to separate from the low type; that is, if the high types give a gift smaller than $g^1$, a low type has the incentive to mimic the high type and the separating equilibrium is destroyed.

High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$. Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation. This occurs when Expression~\ref{eq:matval2} holds with equality. That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.

The high-type incentive compatibility constraint must not be violated for high types to send nonzero concessions. That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types. Note that if the high type pools with the low type, it knows it will play Distrust and so invests any concession received in military buildup. Therefore, the high-type IC constraint is
\begin{equation*}
	p\frac{T+Tg^1}{1-\de_h} + (1-p)\frac{W-D-Dg^1}{1-\de_h} - (1-p)g^1 \geq 
	p\frac{W+Wg^1-D}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} +pg^1.
\label{eq:matval3}
\end{equation*}

\noindent Simplifying, we have
$$p(T+Tg^1) + (1-p)(W-D-Dg^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
%$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
$$\de_h g^1 \geq p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1$$
%$$\de_h \geq \frac{p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1 }{g^1}$$
%$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
$$\de_h \geq \frac{p(W-D-T)}{g^1} + p (W-T) + (1-p)D + 1.$$

Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a \emph{concessions separating equilibrium} to exist in terms of fundamentals:
\be
	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1.
\ee
That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$

\vskip.3in
\noindent\emph{Comparative statics}

We start by examining the gifts in a \emph{concessions separating equilibrium}, first with no material value (or destroyed material value) and then when concessions have future material value.

It is direct that the gift in the {concessions separating equilibrium} with no material value (or destroyed material value) increases in $p$ because the gift is equal to $p(T+D)$. The gift also clearly increases in both $T$ and $D$.

It is straightforward that the gift in the model with material value, $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, increases in $p$. Recall that all the variables are assumed to be strictly positive, with $0 < \delta_l < 1$. It follows that the numerator increases in $p$ and the denominator decreases in $p$. Recall that we assume the denominator is positive. Therefore, $g^1$ increases in $p$. In formal terms, $\frac{\partial g^1}{\partial p} = \frac{(1 - \de_l +D)(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2} > 0$.

$g^1$ does not changed with $W$ because $W$ does not enter the expressing anywhere. The other three parameters require working out the formal result.

For the patience level of the low type: $$\frac{\partial g^1}{\partial \delta_l} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(-p)(T+D) - \left(1-\de_l\right)p\left(D + T\right)(-1)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$  $$= \frac{-\left(\left(1-\de_l\right)\left(1 - pT \right)p(T+D) + (1-p) D\right)p(T+D) + \left(1-\de_l\right)p\left(D +	 T\right)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$ $$= \frac{(1-p) pD(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive. Therefore we have $\frac{\partial g^1}{\partial \delta_l} > 0$.

For the benefit from negotiating partner playing Trust: 
$$\frac{\partial g^1}{\partial T} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(\de_l p -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 - pT + pD + pT\right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 + pD \right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive. Therefore we have $\frac{\partial g^1}{\partial T} > 0$.

For the damages from negotiating partner playing Distrust: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) - T(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{1-\de_l -pT + \de_l p T - T +pT\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
$$= \frac{(1-\de_l)p\left\{1-\de_l + \de_l p T - T\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Because both the denominator and $(1-\de_l)p$ are strictly positive, the sign of this derivative matches the sign of $1-\de_l + \de_l p T - T$. It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise. So, when the benefit from the partner playing Trust is sufficiently small, the gift size increases in $D$. However, otherwise, the gift size decreases in the damages from the negotiating partner playing Distrust.

We now turn to the patience threshold that defines the high type. In the {concessions separating equilibrium} with no material value, we have $\frac{W}{T+D} = \de^{c}$, which increases in $W$ and decreases in $T$ and $D$. Notice it is not a function of $\delta_l$ or $p$.

The results for the patience threshold are more complex when concessions have future material value. First, recall that $\de^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$ where the denominator of the first term is simply $g^1$.

As in the case of no material value, the patience threshold increases in $W$: $\frac{\partial \delta^1}{\partial W} = \frac{p}{g^1} + p > 0$ because both $p$ and $g^1$ are strictly positive.

The patience threshold increases in $p$. That is, 
$$\frac{\partial \delta^1}{\partial p} = \frac{g^1 (W-D-T) - p(W-D-T)\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ W-T-D$$$$= (W-D-T)\left\{\frac{g^1  - p\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ 1\right\}=\frac{W-D-T	}{(g^1)^2}\left\{g^1  - p\frac{\partial g^1}{\partial p} + (g^1)^2\right\}$$
$$=\frac{W-D-T}{(g^1)^2}\left\{p(T+D)\left[-\de_l (1-\de_l) - \de_l D - \de_l p D(1-\de_l)\right]\right\} > 0.$$
We assume that $T > W - D$, so the fraction's numerator is positive, while the denominator is positive because it's a squared term. $p(T+D)$ is positive because all three variables are positive. Each term in the square brackets is negative. Therefore, the full expression is positive.

The patience threshold also increases in the low type's patience level $\de_l$. That is,
$$\frac{\partial \delta^1}{\partial \de_l} = \frac{g^1 \cdot 0 + p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} = \frac{p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} > 0.$$
The result holds because each term in the expression is positive.

In contrast, the patience threshold decreases in the benefit from the negotiating partner playing Trust, $T$. That is,
$$\frac{\partial \delta^1}{\partial T} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial T}}{(g^1)^2}-p = \frac{p}{(g^1)^2}\left\{ p(T+D-W) \frac{\partial g^1}{\partial T} - g^1 -(g^1)^2 \right\}$$
$$= \frac{p}{(g^1)^2}\left\{-(1-\de_l)W - (1- \de_l P)WD -2TD(1-\de_l)p \right\} < 0.$$
The result holds because $p$ and $g^1$ are positive, while each additive term in the curly braces is negative.

The result is more nuanced for $D$, the cost of the negotiating partner playing Distrust. The change in the patience threshold when $D$ changes is 
$$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$
If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression is always negative. As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_l D(1-p)}{1-\de_l}$. When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.

\subsection{Material Value of Concessions can be Destroyed}
\emph{Proof of Lemma~\ref{lemma:efficiency}:}\\
The expected separation utility for the high type in the game with material value that can be destroyed is
$$p\frac{T+Teg_h}{1-\de_h} + (1-p)\frac{W-D-Deg_h}{1-\de_h} - (1-p)g_h.$$
The derivative with respect to $e$ is
$$\frac{1}{1-\de_h}\left\{pTg_h - (1-p)Dg_h)\right\}.$$
This is non-negative when $pT \geq (1-p)D$. High-type welfare is thus non-decreasing in $e$ when this condition is met. Thus, the largest admissible value of $e$, i.e., $e=1$, thus maximizes welfare when $pT \geq (1-p)D$.\footnote{If $pT = (1-p)D$, $e=1$ is not the unique maximizer but is still a maximizer.} \hfill $\blacksquare$\\
%\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function. It also holds for any monotone cost function.} 
\\
\emph{Proof of Lemma \ref{lemma:e-patient}:}\\
The proof is by contradiction. Suppose the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}. Because low types have patience levels below the threshold, we have that 
\begin{equation}
	\de^c = \frac{W}{T+D} \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1> \de_l.
	\label{eq:cont}
\end{equation}
It follows directly that $W > \de_l(T+D)$. Because $\de_l < 1$, it is also true that $\frac{1-p}{1-\de_l p} < 1$. Combining this with the previous fact, we have
\begin{equation}
	W > \de_l(T+D) > \frac{\de_l(T+D)(1-p)}{1-\de_l p}.
	\label{eq:cont2}
\end{equation}
We invoke Expression~\ref{eq:cont2} below. First we go back to Expression~\ref{eq:cont}, simplifying and creating a common denominator for $\de^1$, we have
\begin{multline*}
	\frac{W}{T+D} \geq %\frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
	%+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = \\
	\frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{multline*}
Subtract $\frac{W}{T+D}$ from both sides to get
\begin{multline*}
	0 \geq \frac{-W(1-\de_l) + W\left(1-\de_l\right)-(D+T)\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT}{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
	+ \frac{(W-(D+T))(1-p) D + p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{multline*}
Canceling the first two terms as well as the third and last terms and then 
%\begin{multline*}
%	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
%	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 %T\right)}
%\end{multline*}
expanding and canceling the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
%\begin{multline*}
%	0 \geq \frac{-W\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
%	+ \frac{pW\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
%\end{multline*}
%Expand even more and then cancel out $(1-p)D\left(D +	 T\right)$ terms
\begin{equation*}
	0 \geq \frac{-W\left(1-\de_l\right)pT +W(1-p) D + pW\left(1-\de_l\right)\left(D +	 T\right) }{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
Expanding once more and then canceling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
%\begin{equation*}
%	0 \geq \frac{W(1-p) D + pW(1-\de_l)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
%	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
%\end{equation*}
%Expand everything from the first fraction and cancel out $-pWD$ terms
\begin{equation*}
	0 \geq \frac{WD - \de_lpWD}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
Combining this with the inequality in Expression~\ref{eq:cont2}, we arrive at
\begin{equation*}
	0 \geq \frac{WD(1- \de_lp)}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} > \frac{\frac{\de_l(T+D)(1-p)}{1-\de_l p}\left[D(1 - \de_lp)\right]}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
\end{equation*}
To simplify, we have
\begin{equation*}
	0 > \frac{\de_l(T+D)(1-p)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = 0
\end{equation*}
We have arrived at a contradiction from Expression~\ref{eq:cont}, and therefore, it must be that 
\begin{equation}
	\frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 > \frac{W}{D+T}
\end{equation}
 \hfill $\blacksquare$

\subsection{Mediation}
\emph{Proof of Lemma \ref{lemma:med}:}\\
We show that the low type's incentive compatibility constraint cannot hold when the mediator specifies fully efficient gifts. The low type's incentive compatibility constraint in the mechanism $M$ is
$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h.$$

\vspace{-5pt}
Here we specify that the mediator chooses $e=1$, which means that gift-giving and receiving cancel out. The left-hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type, and the mediator only specifies strictly positive gifts if two countries report that they are High types. Likewise, the $(1-p)X_{FF}^l$ term on the right does not contain a gift because the negotiating partner has made a report of Low. This leaves
		$$X_{FF}^l \geq X_{FT}^l.$$
		Expanding, we have
		\[
			\frac{W-D}{1-\de_l} \geq T + \left(\cdot \right) + W + \left(\cdot \right) + \frac{\de_l}{1-\de_l}\left(W+ \left(\cdot \right) -D - \left(\cdot \right) \right)
		\]
The left-hand side has no gifts, so the payoffs from Table \ref{tab-1} apply. The right-hand side has placeholders $\left(\cdot\right)$ for the impact of the material value of gifts. On the right-hand side, we only have cases where both parties declare themselves to be high types. Both parties are instructed to give efficient gifts. The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the Cooperation equilibrium. The low-type player knows it will defect and be in a No Cooperation equilibrium and so invests entirely in the military. 
%		\begin{multline}
%			W-D \geq 
%			\left(1-\de_l\right) \left[T + \al_2Tg^M + W + \left(1-\al_1\right)Wg_2 \right] \\
%			+ \de_l \left(W + \left(1-\al_1\right)Wg_2-D - \left(1-\al_2\right)Dg^M\right)
%			\label{eq:lowICex}
%		\end{multline}
		\begin{equation}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Tg_h + W + Wg_h \right] + \de_l \left(W + Wg_h -D \right)
			\label{eq:med}
		\end{equation}
Canceling like terms and rearranging, we have
    \[
	0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg_h + Wg_h + \left(1 - \de_l \right) D
    \]
Because we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are strictly positive and $0 < \de_l < 1$, this inequality can never hold.	\hfill $\blacksquare$\\
			\\
\emph{Proof of Proposition~\ref{proposition:med}:}\\
(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the No Cooperation payoff forever outside the mechanism; it also gets the No Cooperation payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
\vspace{-5pt}

For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Lemma \ref{lemma:med}. So, we start from
\begin{equation*}
			W-D \geq 
			\left(1-\de_l\right) \left[T + Teg_h + W + Weg_h \right] + \de_l \left(W + Weg_h -D \right) + peg_h - pg_h.
		\end{equation*}
Simplifying, we have
%\[
%	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
%\]
%Gathering the terms involving $g_h$ on the left hand side:
\[
	g_h\left[p\left(1 - e\right) -(1-\de_l)eT -eW \right] \geq \left(T - \de_l T \right) + \left(1 - \de_l \right) D.
\]
The right-hand side is positive. If the left-hand side were negative, we would have a negative upper bound on the size of the gift. Given the requirement that the gift be non-negative, the low type's incentive compatibility constraint cannot be satisfied when the left-hand side is negative, and we must have that $p > e\left(p+\left(1-\de_l\right)T + W\right)$. Using this to isolate $g_h$ on the left-hand side and gathering terms, we have 
\begin{equation}
	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}.
	\label{eq:med3}
\end{equation}
If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
(b) The high-type incentive compatibility constraint is
\begin{equation}
	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h .
	\label{eq:med4}
\end{equation}
It is always optimal for the high type to invest in civil society when they truthfully reveal. When a high type misrepresents itself as a low type, the mechanism specifies that gifts are exchanged only when both countries are high types. This means that there are no concessions when a high type lies. This implies that Expression~\ref{eq:med4} is also the individual rationality constraint because outside the mechanism they get the No Cooperation payoff and exchange no concessions.

Thus the constraint for both incentive compatibility and individual rationality is
\begin{equation*}
  \frac{p}{1-\de_h}\left(T + Teg_h \right) - pg_h +peg_h+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right).
\end{equation*}
This simplifies to
\begin{equation*}
  \frac{1}{1-\de_h}\left(T + Teg_h \right) - g_h +eg_h \geq \frac{1	}{1-\de_h}\left(W-D\right)
\end{equation*}
%\begin{equation*}
%  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
%\end{equation*}
\begin{equation*}
  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
\end{equation*}
\begin{equation*}
  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g_h. 
\end{equation*}
If $Te < (1-\de_h)(1-e)$, this is a negative lower bound on the size of the concession and thus implies no additional restriction. If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption. If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g_h$. \hfill $\blacksquare$\\
\\
\emph{Proof of Proposition~\ref{proposition:medwel}:}\\
An example suffices to prove each part.
	\begin{enumerate}
		\item[(a)] Examine the parameterization in Corollary~\ref{corollary:matval}. $\de_h = 0.7$ and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is the same as when concessions have no future material value, i.e., 0.5. By Corollary~\ref{corollary:matval}, the \emph{concessions separating equilibrium with inefficient gifts} is possible. Corollary~\ref{corollary:matval} also showed that the \emph{concessions separating equilibrium with efficient gifts} is not possible because the relevant patience threshold of $0.979$ is too high.

Using the mediation mechanism $M$ with $e=0.29$ and $g_h=12.98$, we satisfy both the low type constraint that $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$. Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$. The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$. Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$. By Proposition~\ref{proposition:2}, the \emph{concessions separating equilibrium with efficient gifts} is possible.

By Proposition~\ref{proposition:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.75$. Using Lemma~\ref{lemma:e-patient}, we see that both the \emph{concessions separating equilibrium with efficient gifts} and the \emph{concessions separating equilibrium with inefficient gifts} are possible.

Using the mediation mechanism $M$ with $e=0.18$ and $g_h=7.7669$, we satisfy both the low type constraint the $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$. Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with inefficient gifts}.
		\item[(c)] Let $T = 1$, $W=1$ and $D = 1$. The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when concessions have no future material value is $\de = \frac{1}{1+1} = 0.5$. Let $\de_h = 0.49$ and $\de_l = 0.25$ and $p = \frac{15}{16} = 0.9375$.

We use Proposition~\ref{proposition:2}(a) to find that the patience threshold to separate through concessions with inefficient concessions is $0.5$. This, combined with Lemma~\ref{lemma:e-patient}, shows that neither the \emph{concessions separating equilibrium with efficient gifts} nor the \emph{concessions separating equilibrium with inefficient gifts} is possible.

Using the mediation mechanism $M$ with $e=0$ and $g_h=1.6$, we satisfy both the low type constraint $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=1.6$ and there is no high type constraint because $0=Te<(1-\de_h)(1-e)=0.0625$. Welfare is approximately 0.24, compared to 0 outside the mechanism.
	\end{enumerate}
	\hfill $\blacksquare$\\
\newpage

%% Use \bibliography{...} if using BibTeX
\bibliography{Inefficient_Concessions}

%TC:subst \printbibliography \bibliography
%TC:macro \field [0,1]
%TC:macro \name [0,0,0,1]
%TC:macro \list [0,0,1]
%% Use \printbibliography if using BibLaTeX
% \printbibliography

\end{document}

### 2024-02-03 QJPS/Inefficient_Concessions.tex
Format and zip files for final submission to QJPS

@@
 Even if transferring control of strategically valuable territory creates the best chance for peace, its transfer often involves a substantial risk that the territory will provide a military advantage in a future conflict.
-Following the 1992 war between Armenia and Azerbaijan over the disputed region of Ngorno-Karabakh, Armenia retained control of a significant amount of Azerbaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland.
+Following the 1992 war between Armenia and Azerbaijan over the disputed region of Nagorno-Karabakh, Armenia retained control of a significant amount of Azerbaijani territory that neither the Armenian government nor the Karabakh government viewed to be part of its homeland.
 Azerbaijan, however, valued control of the territory greatly as the home of Azeri residents and wished to govern the territory.
 Thus, it might have been efficient in the mid-1990s for the Armenian/Karabakh side to cede control of that territory to Azerbaijan as part of a deal in which Azerbaijan recognized Karabakh's independence.
-However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor that connects Ngorno-Karabakh and Armenia.
-Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Ngorno-Karabakh and Armenia.
+However, that territory was strategically valuable, including territory on both sides of the Lachin Corridor that connects Nagorno-Karabakh and Armenia.
+Azerbaijani control of the territory surrounding the corridor would empower Azerbaijan to seize military advantage in the future and cut off land travel between Nagorno-Karabakh and Armenia.
 The territory was not conceded, and the conflict persisted in a costly stalemate for almost twenty years until war broke out anew in 2020.
@@
 
-\section{Appendix}
-
-\subsection{Pooling equilibrium}
-\begin{lemma}
-	From Round 1 on, playing (Distrust,Distrust) in all rounds is a subgame perfect Nash equilibrium of the continuation game for both types regardless of beliefs.
-	\label{lemma:1}
-\end{lemma}
-\emph{Proof}: As $D>0$ and $W>0$, the dominant stage game action for all types is to play Distrust.
-Thus, the stage game equilibrium is (Distrust,Distrust), and in any repeated game, playing the stage game equilibrium in each round is an equilibrium of the entire game.
-\hfill $\blacksquare$\\
-
-That is, one high-type equilibrium strategy is to pool with the low types by always playing Distrust.
-If both the low and high type of player $j$ choose the strategy that gives no concessions and always plays Distrust, then either type of player $i$ is made strictly better off by playing Distrust in each round given player $j$'s behavior.
-Given that the stage-game equilibrium will be (Distrust,Distrust), players have no incentive to give a concession in Period 0 because concessions are costly, and signaling one's type can give no benefit in this equilibrium.
-Types pool by never giving concessions and always playing Distrust.
-
-\subsection{No-Concessions Separating Equilibrium}
-
- We examine the conditions for a separating equilibrium held in place by a grim trigger.
-
- \noindent{\emph{Proof of Proposition \ref{proposition:1}}:\\
-Playing Trust in the first round and thereafter, as long as Trust has always been played, is incentive compatible for high types if the expected payoffs from this strategy are greater than the payoffs from playing Distrust in the first round and then every round thereafter by the one-shot deviation principle.
-If both countries play Trust in a round, a Cooperation equilibrium takes place, and both countries continue to play Trust in every round with the grim trigger threat of Distrust.
-Low types play Distrust in the first round, so a high type that observed Distrust being played would respond by playing Distrust in Round 2 and all future rounds.
-A country plays Trust if and only if the following condition is satisfied:
-\begin{equation*}
-  p\left(\frac{T}{1- \delta}\right) +(1-p)\left({-D}+\frac{\delta(W-D)}{1- \delta} \right)\geq p \left(T + W + \frac{\de}{1-\de}(W-D)\right) +(1-p)\frac{W-D}{1- \delta}.
-\end{equation*}
-Simplifying, we have
-%\be
-%  p\left(\frac{T}{1- \delta_h}\right) \geq p \left(T + W + \frac{\de_h}{1-\de_h}(W-D)\right) +(1-p)W
-%\ee
-\begin{equation*}
-  pT \geq p \left((1-\de)(T + W) + \de (W-D)\right) + (1-\de)(1-p)W
-\end{equation*}
-\begin{equation*}
-  pT \geq pT -p\de T +pW -p\de W + p \de W -p \de D  + W -\de W -pW + p\de W
-\end{equation*}
-\begin{equation*}
-  p\de T +p \de D + \de W - p\de W  \geq W 
-\end{equation*}
-\be
-	\delta \geq \frac{W}{(1-p)W + p(T+D)} = \de^{nc}.
-	\label{eq:ncse}
-\ee
-
-If the potential advantages of Cooperation are large enough to outweigh the risks of encountering a low type in expected utility terms, that is $\de_h \geq \de^{nc}$, a county has the incentive to play Trust in the first round rather than Distrust.
-Any player with $\de < \de^{nc}$ has the incentive---by this same inequality---to play Distrust in each round even if the other country plays Trust.
-Thus, we call these countries low types for purposes of this equilibrium.
-\hfill $\blacksquare$
-
-\subsection{Concessions Separating Equilibrium}
-
-If the condition in Expression~\ref{eq:ncse} is not met, a separating equilibrium cannot be achieved in the absence of concessions in Period 0.\footnote{Countries need to deliver concessions in Period 0, not just promise them.} If, instead, two negotiating parties have sufficient incentive to give a concession in Period 0 that indicates they are capable of cooperation, these high types could safely play Trust in Round 1, allowing two high types to avoid the trap of the No Cooperation outcome that would occur under pooling.
-
-Below are the details of the \emph{concessions separating equilibrium} analysis.
-We denote the equilibrium separating gifts as $g_h$ from the high type and $g_l$ from the low type.
-These equilibrium gifts mean that when Round 1 is reached, countries know which type the other country is and play accordingly.
-The concessions phase acts as a coordination device to match countries' actions.
-For two countries of the same type to play different actions is an off-equilibrium contingency.
-These off-equilibrium payoffs are nonetheless necessary for calculating the minimum separating concession.
-\\
-\\
-\emph{Proof of Lemma~\ref{lemma:3}:}\\
-In accord with the Revelation Principle (Myerson 1979), we focus without loss of generality on \emph{concessions separating equilibria} in which countries reveal their types truthfully.
-This allows high types to only play Trust in Round 1 with other high types and to play Distrust with low types.
-Low types play Distrust (Lemma~\ref{lemma:1}) and their equilibrium payoff is $U_l=X_{FF}+ pg_h-g_l$.
-
-Though low types might be willing to give a non-zero gift in a separating equilibrium, they will only do this if it gives them some advantage.
-Here, high types only cooperate with other high types, so giving a concession cannot help low types to achieve a higher payoff in the repeated game.
-Because their concession $g_l$ enters negatively in the payoff function, low types' optimal concession is, therefore, 0.
-
-High types have the incentive to play Trust only in the Cooperation equilibrium, which can only be sustained by a pair of high types.
-Both types benefit from the other country playing Trust, so all countries have an incentive to signal that they are high types if concessions are costless (cheap talk).
-Thus, costless announcements cannot lead to truthful revelation.
-If concessions are to lead to a separating equilibrium, they must be costly.
-\hfill $\blacksquare$
-\\
-\\
-\emph{Proof of Proposition \ref{proposition:2}:}\\
-In the separating equilibrium constructed here, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift.
-In this case, the binding incentive compatibility constraint is the low type IC constraint.
-When we set $g_l=0$ following Lemma~\ref{lemma:3}, the low-type IC constraint is\\
-\begin{equation*}
-	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
-\end{equation*}
-This expression represents the low types' incentives for truth telling as opposed to posing as a high type and giving the corresponding equilibrium gift.
-Simplifying this inequality, we see that the high types need to give a gift
-\be
-	g_h \geq p(X_{FT}^l-X_{FF}^l)
-	\label{eq:cse}
-\ee 
-in order to separate from the low type.
-
-High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
-Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible while still achieving separation.
-This occurs when Expression~\ref{eq:cse} holds with equality.
-Substituting in from the definitions of $X_{FT}^l$ and $X_{FF}^l$ yields the minimum separating gift\footnote {Although not formally addressed in this paper, inference about sizes of concessions when parties are of unequal force can be made.
-Note that the constraints determining the requisite size of the separating gift depend on the low types' ability to gather war spoils.
-Thus, a more powerful country would be more able to plunder and hence has to make a greater concession to convincingly convey that it is a high type.}
-\be
-	g_h^*=p(T+D).
-	\label{eq:cse2}
-\ee 
- To get the high types to send nonzero concessions, the high type incentive compatibility constraint must be satisfied.
-That is, the payoff from separating must be higher than the payoff from pooling with the low types:
-$$pX_{TT}^h+(1-p)X_{FF}^h - g_h +pg_h \geq X_{FF}^h +pg_h.$$
-In terms of fundamentals, we have
-\be
-	p\frac{T}{1-\de_h}+(1-p)\frac{W-D}{1-\de_h} - g_h \geq \frac{W-D}{1-\de_h}.
-	\label{eq:cse3}
-\ee
-Combining Expressions~\ref{eq:cse2} and \ref{eq:cse3}, we have the condition for a \emph{concessions separating equilibrium} to exist:
-\be
-\delta_h \geq \frac{W}{T+D} = \de^c.
-\ee
-That is, we need the high types to have a sufficiently large discount factor. \hfill $\blacksquare$\\
-\\
-\emph{Proof of Corollary~\ref{corollary:1}:}\\
-To show that the patience threshold for the \emph{no-concessions separating equilibrium} is greater than the patience threshold for the \emph{concessions separating equilibrium}, we start with the assumption $T+D>W.$
-
-We multiply both sides by $(1-p)>0$ and then subtract $p(T+D)$ from both sides to get
-$$(T+D) > (1-p)W +p(T+D).$$
-Because $0<p<1$ and $W$, $T$, and $D$ are all positive, both sides of the inequality are positive. Thus, we have
-$$\de^{nc} = \frac{W}{(1-p)W +p(T+D)} > \frac{W}{T+D} = \de^{c}.$$
-
-In the case that both types of equilibria exist, i.e., $\de_h \geq \de^{nc}$, the high types prefer the \emph{no-concessions separating equilibrium} if and only if
-\begin{equation*}
-p\left(\frac{T}{1- \delta_h}\right) +(1-p)\left({-D}+\frac{\delta_h(W-D)}{1- \delta_h} \right) \geq p\left(\frac{T}{1- \delta_h}\right)+(1-p)\left(\frac{W-D}{1- \delta_h}\right) - (1-p)g_h.
-\end{equation*}
-This simplifies to preferring the \emph{concessions separating equilibrium} if and only if
-$$0 \geq (1-\de_h)W-p(1-\de_h)(T+D).$$
-Rearranging, we have
-\be
- p \geq \frac{W}{T+D}.
-\ee
-That is, the high types prefer the \emph{concessions separating equilibrium} when $p$ is smaller than $\frac{W}{T+D}$. \hfill $\blacksquare$
-
-\subsection{Concessions with Material Value}
-\label{ap:mat_val}
-\emph{Proof of Proposition \ref{proposition:csemv}:}\\
-In the separating equilibrium constructed in Proposition~\ref{proposition:csemv}, players believe that any concession not equal to the equilibrium concession of the high type $g_h$ is a low-type gift.
-In this case, the binding incentive compatibility constraint is the low type IC constraint.
-Taking account of the result of  Lemma~\ref{lemma:3} that $g_l=0$, we have
-\begin{equation}
-	pg_h +X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-g_h+pg_h.
-	\label{eq:matval1}
-\end{equation}
-On the left side, the low type does not give a concession but receives a concession if facing a high type ($pg_h$).
-Then (Distrust,Distrust) is played, and the payoffs depend on whether this low type faces a high or a low type because the implications for future material value are different.
-With probability $p$, the low type receives a gift and invests in the military.
-With probability $(1-p)$, neither side gives concessions.
-The left side of Expression~\ref{eq:matval1} is then $pg_h + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right]$.
-
-On the right side, the low type gives and receives a gift from the high type with probability $p$.
-With probability $p$, this low type faces a high type who invests the gift in civil society.
-With probability $(1-p)$, the low type's gift goes to another low type who invests in the military, and the low type does not receive a gift.
-So the right hand side of Expression~\ref{eq:matval1} becomes $-g_h + pg_h + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)$.
-
-Substituting into Expression~\ref{eq:matval1} and simplifying, we have
-%\begin{multline*}
-%	pg_1 + \frac{1}{1-\de_l}\left[p(W+Wg_h-D) + (1-p)(W-D) \right] \geq \\
-%-g_1 + pg_1 + p\left(T + Tg_h +W + Wg_h + \frac{\de_l}{1-\de_l}\left(W + Wg_h-D \right) \right) + (1-p)\left( \frac{1}{1-\de_l}\left(W-D-Dg_h \right) \right)
-%\end{multline*}
-\begin{equation*}
-	g_h + p(W+Wg_h-D) \geq p\left(T + Tg_h +W + Wg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
-\end{equation*}
-%\begin{equation*}
-%	g_h - pD \geq p\left(T + Tg_h \right) + (1-p)\left( \frac{-Dg_h}{1-\de_l}  \right)
-%\end{equation*}
-\begin{equation*}
-	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h\geq \left(1-\de_l\right)p\left(D +	 T\right).
-\end{equation*}
-We have assumed that $\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D > 0$ so we can divide to get
-%\begin{equation*}
-%	\left(1-\de_l\right)g_h\left(1 - pT \right) + (1-p) Dg_h \geq \left(1-\de_l\right)p\left(D +	 T\right)
-%\end{equation*}
-\begin{equation}
-	g_h \geq \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D} = g^1
-	\label{eq:matval2}
-\end{equation}
-
-This implies that the high types need to give a gift at least as large as $g^1$ to separate from the low type; that is, if the high types give a gift smaller than $g^1$, a low type has the incentive to mimic the high type and the separating equilibrium is destroyed.
-
-High type separating equilibrium utility is $U_h= pX_{TT}+(1-p)X_{FF} - g_h+pg_h$.
-Because utility is decreasing in $g_h$, it is optimal for high types to make $g_h$ as small as possible and still have separation.
-This occurs when Expression~\ref{eq:matval2} holds with equality.
-That is, the optimal high type gift in this equilibrium is $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$.
-
-The high-type incentive compatibility constraint must not be violated for high types to send nonzero concessions.
-That is, the payoff from separating must be higher than the payoff from not giving a gift and pooling with the low types.
-Note that if the high type pools with the low type, it knows it will play Distrust and so invests any concession received in military buildup.
-Therefore, the high-type IC constraint is
-\begin{equation*}
-	p\frac{T+Tg^1}{1-\de_h} + (1-p)\frac{W-D-Dg^1}{1-\de_h} - (1-p)g^1 \geq 
-	p\frac{W+Wg^1-D}{1-\de_h} + (1-p)\frac{W-D}{1-\de_h} +pg^1.
-\label{eq:matval3}
-\end{equation*}
-
-\noindent Simplifying, we have
-$$p(T+Tg^1) + (1-p)(W-D-Dg^1)) - (1-\de_h)g^1 \geq p(W+Wg^1-D) + (1-p)(W-D)$$
-%$$pT(1+g^1) - (1-p)Dg^1 - (1-\de_h)g^1 \geq p(W+Wg^1-D)$$
-$$\de_h g^1 \geq p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1$$
-%$$\de_h \geq \frac{p(W+Wg^1-D) - pT(1+g^1) + (1-p)Dg^1 + g^1 }{g^1}$$
-%$$\de_h \geq \frac{p(W-D-T) + pg^1 (W-T) + (1-p)Dg^1 + g^1 }{g^1}$$
-$$\de_h \geq \frac{p(W-D-T)}{g^1} + p (W-T) + (1-p)D + 1.$$
-
-Substituting the minimum efficient concession from Expression~\ref{eq:matval2}, we have the condition for a \emph{concessions separating equilibrium} to exist in terms of fundamentals:
-\be
-	\de_h \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1.
-\ee
-That is, there is no parameter restriction beyond our definition of what it means for a player to be a high type. \hfill $\blacksquare$
-
-\vskip.3in
-\noindent\emph{Comparative statics}
-
-We start by examining the gifts in a \emph{concessions separating equilibrium}, first with no material value (or destroyed material value) and then when concessions have future material value.
-
-It is direct that the gift in the {concessions separating equilibrium} with no material value (or destroyed material value) increases in $p$ because the gift is equal to $p(T+D)$.
-The gift also clearly increases in both $T$ and $D$.
-
-It is straightforward that the gift in the model with material value, $g^1 = \frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}$, increases in $p$.
-Recall that all the variables are assumed to be strictly positive, with $0 < \delta_l < 1$.
-It follows that the numerator increases in $p$ and the denominator decreases in $p$.
-Recall that we assume the denominator is positive.
-Therefore, $g^1$ increases in $p$.
-In formal terms, $\frac{\partial g^1}{\partial p} = \frac{(1 - \de_l +D)(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2} > 0$.
-
-$g^1$ does not changed with $W$ because $W$ does not enter the expressing anywhere. The other three parameters require working out the formal result.
-
-For the patience level of the low type: $$\frac{\partial g^1}{\partial \delta_l} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(-p)(T+D) - \left(1-\de_l\right)p\left(D + T\right)(-1)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$  $$= \frac{-\left(\left(1-\de_l\right)\left(1 - pT \right)p(T+D) + (1-p) D\right)p(T+D) + \left(1-\de_l\right)p\left(D +	 T\right)(1-pT)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$ $$= \frac{(1-p) pD(T+D)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive.
-Therefore we have $\frac{\partial g^1}{\partial \delta_l} > 0$.
-
-For the benefit from negotiating partner playing Trust: 
-$$\frac{\partial g^1}{\partial T} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(\de_l p -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 - pT + pD + pT\right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{\left[(1-\de_l)p\right] \left\{\left(1-\de_l\right)\left(1 + pD \right) + (1-p) D\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Every term in the numerator is positive, and the denominator is a squared term, so it is positive.
-Therefore we have $\frac{\partial g^1}{\partial T} > 0$.
-
-For the damages from negotiating partner playing Distrust: $$\frac{\partial g^1}{\partial D} = \frac{\left(\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right)(1-\de_l)p - \left(1-\de_l\right)p\left(D + T\right)(1 -p)}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D - \left(D + T\right)(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{(1-\de_l)p\left\{\left(1-\de_l\right)\left(1 - pT \right) - T(1 -p)\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{(1-\de_l)p\left\{1-\de_l -pT + \de_l p T - T +pT\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}$$
-$$= \frac{(1-\de_l)p\left\{1-\de_l + \de_l p T - T\right\}}{\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]^2}.$$ Because both the denominator and $(1-\de_l)p$ are strictly positive, the sign of this derivative matches the sign of $1-\de_l + \de_l p T - T$.
-It is positive when $\frac{1-\de_l}{1-\de_l p} > T$ and negative otherwise.
-So, when the benefit from the partner playing Trust is sufficiently small, the gift size increases in $D$.
-However, otherwise, the gift size decreases in the damages from the negotiating partner playing Distrust.
-
-We now turn to the patience threshold that defines the high type.
-In the {concessions separating equilibrium} with no material value, we have $\frac{W}{T+D} = \de^{c}$, which increases in $W$ and decreases in $T$ and $D$.
-Notice it is not a function of $\delta_l$ or $p$.
-
-The results for the patience threshold are more complex when concessions have future material value.
-First, recall that $\de^1 = \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1$ where the denominator of the first term is simply $g^1$.
-
-As in the case of no material value, the patience threshold increases in $W$: $\frac{\partial \delta^1}{\partial W} = \frac{p}{g^1} + p > 0$ because both $p$ and $g^1$ are strictly positive.
-
-The patience threshold increases in $p$. That is, 
-$$\frac{\partial \delta^1}{\partial p} = \frac{g^1 (W-D-T) - p(W-D-T)\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ W-T-D$$$$= (W-D-T)\left\{\frac{g^1  - p\frac{\partial g^1}{\partial p}}{\left(g^1\right)^2}+ 1\right\}=\frac{W-D-T	}{(g^1)^2}\left\{g^1  - p\frac{\partial g^1}{\partial p} + (g^1)^2\right\}$$
-$$=\frac{W-D-T}{(g^1)^2}\left\{p(T+D)\left[-\de_l (1-\de_l) - \de_l D - \de_l p D(1-\de_l)\right]\right\} > 0.$$
-We assume that $T > W - D$, so the fraction's numerator is positive, while the denominator is positive because it's a squared term.
-$p(T+D)$ is positive because all three variables are positive.
-Each term in the square brackets is negative.
-Therefore, the full expression is positive.
-
-The patience threshold also increases in the low type's patience level $\de_l$. That is,
-$$\frac{\partial \delta^1}{\partial \de_l} = \frac{g^1 \cdot 0 + p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} = \frac{p(T+D-W)\frac{\partial g^1}{\partial \de_l}}{\left(g^1\right)^2} > 0.$$
-The result holds because each term in the expression is positive.
-
-In contrast, the patience threshold decreases in the benefit from the negotiating partner playing Trust, $T$. That is,
-$$\frac{\partial \delta^1}{\partial T} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial T}}{(g^1)^2}-p = \frac{p}{(g^1)^2}\left\{ p(T+D-W) \frac{\partial g^1}{\partial T} - g^1 -(g^1)^2 \right\}$$
-$$= \frac{p}{(g^1)^2}\left\{-(1-\de_l)W - (1- \de_l P)WD -2TD(1-\de_l)p \right\} < 0.$$
-The result holds because $p$ and $g^1$ are positive, while each additive term in the curly braces is negative.
-
-The result is more nuanced for $D$, the cost of the negotiating partner playing Distrust. The change in the patience threshold when $D$ changes is 
-$$\frac{\partial \delta^1}{\partial D} = \frac{-p \cdot g^1 + p(T+D-W) \frac{\partial g^1}{\partial D}}{(g^1)^2}+ (1-p).$$
-If $T < \frac{1-\de_l}{1-\de_l p}$ so that $\frac{\partial g^1}{\partial D} > 0$, this expression is always negative.
-As $T$ grows so that $\frac{\partial g^1}{\partial D} < 0$, the derivative remains negative as long as $T < \frac{1-\de_l+ \de_l D(1-p)}{1-\de_l}$.
-When T grows even larger, the derivative remains negative as long as $W < \frac{(1-p)\de_l(T+D)^2}{T -1 + \de_l - \de_l p T}$.
-
-\subsection{Material Value of Concessions can be Destroyed}
-\emph{Proof of Lemma~\ref{lemma:efficiency}:}\\
-The expected separation utility for the high type in the game with material value that can be destroyed is
-$$p\frac{T+Teg_h}{1-\de_h} + (1-p)\frac{W-D-Deg_h}{1-\de_h} - (1-p)g_h.$$
-The derivative with respect to $e$ is
-$$\frac{1}{1-\de_h}\left\{pTg_h - (1-p)Dg_h)\right\}.$$
-This is non-negative when $pT \geq (1-p)D$.
-High-type welfare is thus non-decreasing in $e$ when this condition is met.
-Thus, the largest admissible value of $e$, i.e., $e=1$, thus maximizes welfare when $pT \geq (1-p)D$.\footnote{If $pT = (1-p)D$, $e=1$ is not the unique maximizer but is still a maximizer.} \hfill $\blacksquare$\\
-%\footnote{This result does not depend on the benefit so it holds for any monotonic benefit function. It also holds for any monotone cost function.} 
-\\
-\emph{Proof of Lemma \ref{lemma:e-patient}:}\\
-The proof is by contradiction.
-Suppose the patience threshold for the \emph{concessions separating equilibrium with inefficient gifts} is weakly larger than the patience threshold for the \emph{concessions separating equilibrium with efficient gifts}.
-Because low types have patience levels below the threshold, we have that
-\begin{equation}
-	\de^c = \frac{W}{T+D} \geq \frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 = \de^1> \de_l.
-	\label{eq:cont}
-\end{equation}
-It follows directly that $W > \de_l(T+D)$. Because $\de_l < 1$, it is also true that $\frac{1-p}{1-\de_l p} < 1$. Combining this with the previous fact, we have
-\begin{equation}
-	W > \de_l(T+D) > \frac{\de_l(T+D)(1-p)}{1-\de_l p}.
-	\label{eq:cont2}
-\end{equation}
-We invoke Expression~\ref{eq:cont2} below. First we go back to Expression~\ref{eq:cont}, simplifying and creating a common denominator for $\de^1$, we have
-\begin{multline*}
-	\frac{W}{T+D} \geq %\frac{(W-D-T)\left[\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D\right]}{\left(1-\de_l\right)\left(D +	 T\right)}
-	%+ \frac{\left[p(W-T) + (1-p)D + 1\right]\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = \\
-	\frac{(W-(D+T))\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
-	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{multline*}
-Subtract $\frac{W}{T+D}$ from both sides to get
-\begin{multline*}
-	0 \geq \frac{-W(1-\de_l) + W\left(1-\de_l\right)-(D+T)\left(1-\de_l\right) - (W-(D+T))\left(1-\de_l\right)pT}{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
-	+ \frac{(W-(D+T))(1-p) D + p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right) + \left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{multline*}
-Canceling the first two terms as well as the third and last terms and then 
-%\begin{multline*}
-%	0 \geq \frac{- (W-(D+T))\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
-%	+ \frac{p(W-T)\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 %T\right)}
-%\end{multline*}
-expanding and canceling the terms with $pT$ as well as $(1-p)D\left(D +	 T\right)$, we have
-%\begin{multline*}
-%	0 \geq \frac{-W\left(1-\de_l\right)pT +(W-(D+T))(1-p) D }{\left(1-\de_l\right)\left(D +	 T\right)} \\ 
-%	+ \frac{pW\left(1-\de_l\right)\left(D +	 T\right) + (1-p)D\left(1-\de_l\right)\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-%\end{multline*}
-%Expand even more and then cancel out $(1-p)D\left(D +	 T\right)$ terms
-\begin{equation*}
-	0 \geq \frac{-W\left(1-\de_l\right)pT +W(1-p) D + pW\left(1-\de_l\right)\left(D +	 T\right) }{\left(1-\de_l\right)\left(D +	 T\right)} 
-	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{equation*}
-Expanding once more and then canceling out the $W\left(1-\de_l\right)pT$ and $pWD$ terms
-%\begin{equation*}
-%	0 \geq \frac{W(1-p) D + pW(1-\de_l)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
-%	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-%\end{equation*}
-%Expand everything from the first fraction and cancel out $-pWD$ terms
-\begin{equation*}
-	0 \geq \frac{WD - \de_lpWD}{\left(1-\de_l\right)\left(D +	 T\right)} 
-	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{equation*}
-Combining this with the inequality in Expression~\ref{eq:cont2}, we arrive at
-\begin{equation*}
-	0 \geq \frac{WD(1- \de_lp)}{\left(1-\de_l\right)\left(D +	 T\right)} 
-	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} > \frac{\frac{\de_l(T+D)(1-p)}{1-\de_l p}\left[D(1 - \de_lp)\right]}{\left(1-\de_l\right)\left(D +	 T\right)} 
-	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)}
-\end{equation*}
-To simplify, we have
-\begin{equation*}
-	0 > \frac{\de_l(T+D)(1-p)D}{\left(1-\de_l\right)\left(D +	 T\right)} 
-	- \frac{\de_l (1-p)D\left(D +	 T\right)}{\left(1-\de_l\right)\left(D +	 T\right)} = 0
-\end{equation*}
-We have arrived at a contradiction from Expression~\ref{eq:cont}, and therefore, it must be that 
-\begin{equation}
-	\frac{p(W-D-T)}{\frac{\left(1-\de_l\right)p\left(D +	 T\right)}{\left(1-\de_l\right)\left(1 - pT \right) + (1-p) D}} + p (W-T) + (1-p)D + 1 > \frac{W}{D+T}
-\end{equation}
- \hfill $\blacksquare$
-
-\subsection{Mediation}
-\emph{Proof of Lemma \ref{lemma:med}:}\\
-We show that the low type's incentive compatibility constraint cannot hold when the mediator specifies fully efficient gifts. The low type's incentive compatibility constraint in the mechanism $M$ is
-$$X_{FF}^l \geq pX_{FT}^l+(1-p)X_{FF}^l-pg_h+peg_h.$$
-
-\vspace{-5pt}
-Here we specify that the mediator chooses $e=1$, which means that gift-giving and receiving cancel out.
-The left-hand side has zero gifts because the low-type player under consideration has truthfully revealed itself to be a low type, and the mediator only specifies strictly positive gifts if two countries report that they are High types.
-Likewise, the $(1-p)X_{FF}^l$ term on the right does not contain a gift because the negotiating partner has made a report of Low.
-This leaves
-		$$X_{FF}^l \geq X_{FT}^l.$$
-		Expanding, we have
-		\[
-			\frac{W-D}{1-\de_l} \geq T + \left(\cdot \right) + W + \left(\cdot \right) + \frac{\de_l}{1-\de_l}\left(W+ \left(\cdot \right) -D - \left(\cdot \right) \right)
-		\]
-The left-hand side has no gifts, so the payoffs from Table \ref{tab-1} apply.
-The right-hand side has placeholders $\left(\cdot\right)$ for the impact of the material value of gifts.
-On the right-hand side, we only have cases where both parties declare themselves to be high types.
-Both parties are instructed to give efficient gifts.
-The negotiating partner really \emph{is} a high type and thus invests entirely in civil society because they expect to play the Cooperation equilibrium.
-The low-type player knows it will defect and be in a No Cooperation equilibrium and so invests entirely in the military.
-%		\begin{multline}
-%			W-D \geq 
-%			\left(1-\de_l\right) \left[T + \al_2Tg^M + W + \left(1-\al_1\right)Wg_2 \right] \\
-%			+ \de_l \left(W + \left(1-\al_1\right)Wg_2-D - \left(1-\al_2\right)Dg^M\right)
-%			\label{eq:lowICex}
-%		\end{multline}
-		\begin{equation}
-			W-D \geq 
-			\left(1-\de_l\right) \left[T + Tg_h + W + Wg_h \right] + \de_l \left(W + Wg_h -D \right)
-			\label{eq:med}
-		\end{equation}
-Canceling like terms and rearranging, we have
-    \[
-	0 \geq \left(1 - \de_l \right) T + \left(1 - \de_l \right) Tg_h + Wg_h + \left(1 - \de_l \right) D
-    \]
-Because we assume throughout that gifts must be non-negative, each of $T, W$ and $D$ are strictly positive and $0 < \de_l < 1$, this inequality can never hold.	\hfill $\blacksquare$\\
-			\\
-\emph{Proof of Proposition~\ref{proposition:med}:}\\
-(a) The low type's individual rationality constraint is satisfied trivially: the low type gets the No Cooperation payoff forever outside the mechanism; it also gets the No Cooperation payoff forever \emph{inside} the mechanism while not giving or receiving any concession.
-\vspace{-5pt}
-
-For the general form of the low type incentive compatibility constraint, we start from Expression~\ref{eq:med} and add back in the $e$'s that were removed when assuming $e=1$ in the proof of Lemma \ref{lemma:med}.
-So, we start from
-\begin{equation*}
-			W-D \geq 
-			\left(1-\de_l\right) \left[T + Teg_h + W + Weg_h \right] + \de_l \left(W + Weg_h -D \right) + peg_h - pg_h.
-		\end{equation*}
-Simplifying, we have
-%\[
-%	pg_h\left(1 - e\right) \geq \left(T - \de_l T \right) \left(1 + eg_h\right) + Weg_h + \left(1 - \de_l \right) D
-%\]
-%Gathering the terms involving $g_h$ on the left hand side:
-\[
-	g_h\left[p\left(1 - e\right) -(1-\de_l)eT -eW \right] \geq \left(T - \de_l T \right) + \left(1 - \de_l \right) D.
-\]
-The right-hand side is positive.
-If the left-hand side were negative, we would have a negative upper bound on the size of the gift.
-Given the requirement that the gift be non-negative, the low type's incentive compatibility constraint cannot be satisfied when the left-hand side is negative, and we must have that $p > e\left(p+\left(1-\de_l\right)T + W\right)$.
-Using this to isolate $g_h$ on the left-hand side and gathering terms, we have
-\begin{equation}
-	g_h \geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T -W \right)}.
-	\label{eq:med3}
-\end{equation}
-If Condition~\ref{eq:med3} is met, the mechanism is incentive compatible for the low type.\\
-(b) The high-type incentive compatibility constraint is
-\begin{equation}
-	pX_{TT}^h+(1-p)X_{FF}^h - pg_h +peg_h \geq X_{FF}^h .
-	\label{eq:med4}
-\end{equation}
-It is always optimal for the high type to invest in civil society when they truthfully reveal.
-When a high type misrepresents itself as a low type, the mechanism specifies that gifts are exchanged only when both countries are high types.
-This means that there are no concessions when a high type lies.
-This implies that Expression~\ref{eq:med4} is also the individual rationality constraint because outside the mechanism they get the No Cooperation payoff and exchange no concessions.
-
-Thus the constraint for both incentive compatibility and individual rationality is
-\begin{equation*}
-  \frac{p}{1-\de_h}\left(T + Teg_h \right) - pg_h +peg_h+ \frac{1-p}{1-\de_h}\left(W-D\right) \geq \frac{1}{1-\de_h}\left(W-D\right).
-\end{equation*}
-This simplifies to
-\begin{equation*}
-  \frac{1}{1-\de_h}\left(T + Teg_h \right) - g_h +eg_h \geq \frac{1	}{1-\de_h}\left(W-D\right)
-\end{equation*}
-%\begin{equation*}
-%  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
-%\end{equation*}
-\begin{equation*}
-  T + Teg_h - (1-\de_h)(1-e)g_h \geq W-D
-\end{equation*}
-\begin{equation*}
-  T + D - W \geq \left[Te - (1-\de_h)(1-e)\right]g_h. 
-\end{equation*}
-If $Te < (1-\de_h)(1-e)$, this is a negative lower bound on the size of the concession and thus implies no additional restriction.
-If $Te = (1-\de_h)(1-e)$, there is again no restriction because $T+D >W$ by assumption.
-If $Te > (1-\de_h)(1-e)$, the mechanism is both individually rational and incentive compatible for the high type when $\frac{ T + D - W}{Te - (1-\de_h)(1-e)}>g_h$.
-\hfill $\blacksquare$\\
-\\
-\emph{Proof of Proposition~\ref{proposition:medwel}:}\\
-An example suffices to prove each part.
-	\begin{enumerate}
-		\item[(a)] Examine the parameterization in Corollary~\ref{corollary:matval}.
-$\de_h = 0.7$ and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is the same as when concessions have no future material value, i.e., 0.5.
-By Corollary~\ref{corollary:matval}, the \emph{concessions separating equilibrium with inefficient gifts} is possible.
-Corollary~\ref{corollary:matval} also showed that the \emph{concessions separating equilibrium with efficient gifts} is not possible because the relevant patience threshold of $0.979$ is too high.
-
-Using the mediation mechanism $M$ with $e=0.29$ and $g_h=12.98$, we satisfy both the low type constraint that $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$.
-Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
-		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$.
-The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$.
-Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$.
-By Proposition~\ref{proposition:2}, the \emph{concessions separating equilibrium with efficient gifts} is possible.
-
-By Proposition~\ref{proposition:csemv}(a), the patience threshold to separate through concessions with efficient concessions is $0.75$.
-Using Lemma~\ref{lemma:e-patient}, we see that both the \emph{concessions separating equilibrium with efficient gifts} and the \emph{concessions separating equilibrium with inefficient gifts} are possible.
-
-Using the mediation mechanism $M$ with $e=0.18$ and $g_h=7.7669$, we satisfy both the low type constraint the $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=7.143$ and the high type constraint $g_h\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=7.7669$.
-Welfare is 12.82, compared to 7.5 in the \emph{concessions separating equilibrium with inefficient gifts} and 7.67 in the \emph{concessions separating equilibrium with inefficient gifts}.
-		\item[(c)] Let $T = 1$, $W=1$ and $D = 1$.
-The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when concessions have no future material value is $\de = \frac{1}{1+1} = 0.5$.
-Let $\de_h = 0.49$ and $\de_l = 0.25$ and $p = \frac{15}{16} = 0.9375$.
-
-We use Proposition~\ref{proposition:2}(a) to find that the patience threshold to separate through concessions with inefficient concessions is $0.5$.
-This, combined with Lemma~\ref{lemma:e-patient}, shows that neither the \emph{concessions separating equilibrium with efficient gifts} nor the \emph{concessions separating equilibrium with inefficient gifts} is possible.
-
-Using the mediation mechanism $M$ with $e=0$ and $g_h=1.6$, we satisfy both the low type constraint $g_h\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=1.6$ and there is no high type constraint because $0=Te<(1-\de_h)(1-e)=0.0625$.
-Welfare is approximately 0.24, compared to 0 outside the mechanism.
-	\end{enumerate}
-	\hfill $\blacksquare$\\
 \newpage
